### 2020-01-18 1901.01963/main.tex
added directory with paper tex files

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphics, subfigure}
\usepackage[resetlabels, labeled]{multibib}
\newcites{supp}{References}

\title{Machine learning topological phases in real space}

\author[1,2*]{N. L. Holanda}
\author[2,3+]{M. A. R. Griffith}
\affil[1]{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
\affil[2]{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud, 150, Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
\affil[3]{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}

\affil[*]{linneu@cbpf.br}

\affil[+]{griffithphys@gmail.com}

\begin{abstract}
We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems in real lattice space. The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector-ensembling procedure. We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from lattice data in real space and show how the Gini impurity of ensembles of lattice eigenvectors can be used to retrieve a topological signal detailing how topological information is distributed along the lattice. The discovery of local Gini topological signals from the analysis of data from several thousand SSH systems illustrates how machine learning can advance the research and discovery of new quantum materials with exotic properties that may power future technological applications such as quantum computing. 
\end{abstract}
\begin{document}
\nocite{*}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

%\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}. These materials feature previously unthought-of traits like bulk insulation coupled with metallic conductance at the surface and the splitting of currents according to spin orientation. Adding to that, these properties are protected by non-trivial topology that renders them robust to many sources of perturbation like thermal noise. Such characteristics make them promising candidates to being the cornerstone of 21st century technologies like spintronics and quantum computing.

These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}. Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.

The SSH model is the simplest tight-binding model that exhibits a topological phase transition. As such, it can be viewed as the \emph{Drosophila} of the field, providing a simple framework for testing new techniques. The model can be expressed in terms of creation and annihilation operators by the Hamiltonian
\begin{equation}
\label{SSH_ham}
\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
\end{equation}
and describes e.g. the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material). The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.

Many recent papers have explored the possibility of treating the general problem of determining phase transition boundaries of physical systems as machine learning tasks \cite{carrasquilla2017machine}$^-$\cite{rodriguez2018identifying}. In the particular case of topological phase transitions, the usual approach for supervised learning is to generate a data set $\big(H_1(k), W_1\big)$, ..., $\big(H_n(k), W_n\big)$ whose inputs are representations of Hamiltonians in wavevector space $H_i(k)$ and targets are their corresponding topological invariants $W_i$ (for the SSH model the topological invariant is the winding number). Our paper extends this task to the case of learning topological phase diagrams from input data in real space. Strikingly, we find that information localized on a few lattice sites in real space is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.

To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector-ensembling algorithm) tailored for the task of learning phase transition boundaries from local features. The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems. We demonstrate its effectiveness by combining it with decision trees to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.

The advantage of using tree-based methods to learn from local eigenvector data is that their use of entropy-based cost functions (such as mixture entropy or Gini impurity) makes it much easier to trace the localization of relevant information along the features of a data set. We use this advantage to recover a topological signal quantifying the amount of topological information available from each lattice site as measured by normalized reduction in Gini impurity. This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task. To our knowledge this is the first time that a signal describing the localization of topological information in condensed matter systems is presented in the literature.

The topological signals presented for the first time in this work provide a clear illustration of how machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.

\begin{figure}
\centering
\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{ssh1.png}}\quad
\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{ssh2.png}}
\caption{Phase diagrams in parameter space. a) SSH model with first-neighbor hoppings $t_1$ and $t_2$. The (red) regions with winding number $W$ = 0 are trivial, while the (blue) regions with winding number $W$ = 1 are topologically non-trivial. b) SSH model with first ($t_1$ and $t_2$) and second ($T_1$ and $T_2$) nearest-neighbor hoppings. In this article we set $t_1$ = $t_2$ = 1 and renamed the variables $T_1$ $\rightarrow$ $t_1$, $T_2$ $\rightarrow$ $t_2$ for convenience. The (orange) region with winding number $W$ = 0 is trivial while the others with winding numbers $W$ = -1, $W$ = 1 and $W$ = 2 (red, green and blue respectively) are topologically non-trivial.}
\label{fig:phasediagrams}
\end{figure}

\section*{Numerical experiments}

The eigenvector-ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping. A detailed description of the algorithm is found in the section \textbf{The eigenvector-ensembling algorithm} in the Supplementary Material. Here we present results for the numerical experiments we performed with it. We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (figure \ref{ssh2}).

In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space. The goal in each experiment is to recover the corresponding phase diagram in 2D (i.e. two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).

This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable. For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the allowed winding number values. Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set. The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.

When generating these Hamiltonians we applied periodic boundary conditions to eliminate border effects. This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.

Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiments 1 and 2 as seen from parameter space. The accuracy statistics presented in the following subsections and probability heatmaps shown in figure \ref{heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times. The probability heatmaps shown in figure \ref{heatmaps} faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.

\subsection*{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}

Our test set in this experiment contained 1005 Hamiltonians (approx. 15.3\% of all data). Of the remaining 5556 Hamiltonians, 556 were randomly assigned to the training set (approx. 8.5\%) and 5000 (approx. 76.2\%) were used to compute validation scores at each iteration. These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from out of the test set were used for training at each iteration. The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1. The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$. Our algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.

The bootstrap allows us to collect several statistics to evaluate performance. In particular, we report mean accuracies on training eigenvectors (98.1\%), validation eigenvectors (96.4\%) and test eigenvectors (79.4\%). Eigenvector ensembling substantially improved mean accuracies for Hamiltonians. These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.3\% for test Hamiltonians.

\begin{figure}
\centering
\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{fig1a-6561-100-train_val_test_0.png}}\quad
\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{fig1a-6561-100-train_winding_labels_0.png}}
\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{fig1a-6561-100-prediction_grid_0.png}}
\caption{Visualization of a single iteration of experiment 1 as seen from 2D parameter space. (a) Train/validation/test split. (b) Distribution of winding numbers in the training set. (c) Phase prediction grid learned from real space.}
\label{figexp1_exp}
\end{figure}

\subsection*{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
\label{exp2}

This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions. For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 50 decision trees. Our data set consisted of 1040 (15.8\%) test Hamiltonians. The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving 2761 (42.1\%) training Hamiltonians and 2760 (42.1\%) validation Hamiltonians. The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (17.9\%), $W$ = 0 (32.5\%), $W$ = 1 (32.3\%) and $W$ = 2 (17.3\%). The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (36.3\%), $W$ = 0 (11.1\%), $W$ = 1 (12.7\%) and $W$ = 2 (39.9\%).

Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.4\% for validation eigenvectors and 67.4\% for test eigenvectors. Mean accuracies resulting from eigenvector-ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 87.9\% for test Hamiltonians. The large accuracy gain achieved by eigenvector-ensembling in the test set (going from 67.4\% eigenvector accuracy to 87.9\% Hamiltonian accuracy) attests to its power.

\begin{figure}
\centering
\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{fig1b-6561-100-train_val_test_0.png}}\quad
\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{fig1b-6561-100-train_winding_labels_0.png}}
\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{fig1b-6561-100-prediction_grid_0.png}}
\caption{Visualization of a single iteration of experiment 2 as seen from 2D parameter space. (a) Train/validation/test split. (b) Distribution of winding numbers in the training set. (c) Phase prediction grid learned from real space.}
\label{figexp2_exp}
\end{figure}

\section*{Information entropy signatures}

We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from local features (real space eigenvector coordinates on each lattice site). Alongside the fact that decision trees are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.

The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g. information entropy or Gini impurity \cite{friedman2001elements}). By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 and experiment 2 we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment. These signals are the information entropy signatures of each topological phase transition.

The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for experiments 1 and 2. They represent the information entropy signatures along the lattices in each SSH system. For experiment 1, only 6 lattice sites $S_1$ = (1, 2, 4, 51, 52, 54) corresponding to the two sharp peaks seen in figure \ref{feature_importances1} contributed more than 70\% of total reduction in Shannon entropy. Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by 18 lattice sites $S_2$ = (1, 2, 3, 4, 5, 6, 47, 49, 50, 51, 52, 54, 95, 96, 97, 98, 99, 100) located at the three peaks in figure \ref{feature_importances2}.

Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them. They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector-ensembling algorithm. We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.

To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only the most relevant lattice sites. In our rerun of experiment 1 using only lattice sites $S_1$, mean accuracies were 97.1\% for training eigenvectors, 94.5\% for validation eigenvectors and 78.6\% for test eigenvectors. Mean accuracies obtained from eigenvector-ensembling were 98.9\% for training Hamiltonians, 98.5\% for validation Hamiltonians and 98.9\% for test Hamiltonians.

Mean accuracies for our rerun of experiment 2 using only lattice sites $S_2$ were 99.9\% for training eigenvectors, 96.0\% for validation eigenvectors and 63.7\% for test eigenvectors. Eigenvector-ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.6\% for validation Hamiltonians and 90.4\% for test Hamiltonians.

These results demonstrate that learning topological phases from local real space data is still possible even for small subsets of lattice sites. We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.

\begin{figure}
\centering
\subfigure[]{\label{heatmap:a}\includegraphics[width=.50\textwidth]{fig1a-6561-100-simulation_merged_winding_grid.png}}
\subfigure[]{\label{heatmap:b}\includegraphics[width=.49\textwidth]{fig1b-6561-100-simulation_merged_winding_grid.png}}
\caption{Probability heatmaps learned from real space eigenvector data. Heatmaps were averaged across all 100 iterations in both experiments. (a) The probability heatmap learned in experiment 1 shows the probability that a Hamiltonian in the grid has winding number equal to 1.  (b) The probability heatmap learned in experiment 2 is a superposition of individual probability heatmaps learned for each winding number $W$ = -1, 0, 1 and 2.}
\label{heatmaps}
\end{figure}

\section*{Discussion}

Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand. Our work represents a step in this direction, as we have implemented a data-driven approach to the search for new topological materials bypassing the use of wavevector space data.

The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter. Such systems usually break translational symmetry and therefore are not amenable to wavevector space methods.

An advantage of using data from real space is that it enables us to investigate how topological information is distributed in the system. This was demonstrated by the Gini topological signals recovered from the Gini impurity of ensembles of eigenvectors in each experiment. The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.

We should remark on the subtleties of the Gini topological signals. Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, these importances actually express a global property of the whole lattice. Therefore, a lattice site that appears unimportant in a Gini topological signal may not be unimportant or void of topological information by itself. To give a concrete example, reduction in Gini impurity tends to be distributed among highly correlated variables. This implies that if only a single variable in a highly correlated subset is used, it will likely inherit most of the reduction in Gini impurity from the other variables in the subset. In this regard the Gini topological signals presented here express a summary of relations between lattice sites and are therefore intrinsically global. Furthermore, it should be emphasized that these signals were recovered from the analysis of data from several thousand SSH systems in each experiment and therefore they are not a property of a single SSH lattice. They are rather a pattern that emerges from correlating topological phase with lattice eigenvector data for several SSH systems.

We performed several tests on the Gini topological signals. By rerunning each experiment with longer lattices (i.e. increasing the number of unit cells) we have verified that the Gini topological signals in figures \ref{feature_importances1} and \ref{feature_importances2} appear to converge to well defined continuous density functions in the macroscopic limit. The macroscopic limit of Gini topological signals may be an important signature of topological systems and thus merits further theoretical investigation. A detailed discussion of this point is presented in the section \textbf{Gini topological signals in the macroscopic limit} in the Supplementary Material.

Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.  Given that topological signals such as the ones shown in figures \ref{feature_importances1} and \ref{feature_importances2} are measured in terms of quantities that have actual physical meaning such as mixture entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation. Whether there is any relationship between local topological markers and the entropy of mixing or the Gini impurity of the ensemble of eigenvectors is left for speculation.

The eigenvector-ensembling algorithm employed in this work is likely to have further applications in data-driven physics. This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles. It is therefore expected that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.

One final comment should be made about the flourishing relationship between physics and machine learning. In this work we have demonstrated how a machine learning approach can provide new insights into complex physical phenomena of current interest. The other direction of this relationship (physics enhancing understanding in machine learning) is equally important. As the need for ever more powerful machine learning algorithms continues to grow, the development of mathematical frameworks for understanding general data spaces (i.e., a physics of data) will be of crucial relevance. This pursuit is seen in many theoretical works investigating the intriguing connections between geometry, topology and data \cite{carlsson2009topology}$^-$\cite{belkin2003problems}. The detailed study of data generated by physical models with non-trivial geometrical and topological properties such as the SSH model may provide invaluable insights into the structure and shape of real world high-dimensional data, since these models usually underscore well known mathematical frameworks behind the data generating process, a feature that is often absent from machine learning applications. Thus, far from being restricted to applications in physics, the study of the topological and geometrical properties of data sets generated by physical models will also be of great value to the machine learning and artificial intelligence communities.

\begin{figure}
\centering
\subfigure[]{\label{feature_importances1}\includegraphics[width=0.49\textwidth]{fig1a-6561-100-feature_importances.png}}\quad
\subfigure[]{\label{feature_importances2}\includegraphics[width=0.49\textwidth]{fig1b-6561-100-feature_importances.png}}\quad
\caption{Information entropy signatures of the topological phase transitions studied in the paper. (a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for more than 70\% of reduction in information entropy. These two peaks correspond to the lattice sites $S_1$. (b) In experiment 2, the three visible peaks account for more than 30\% of reduction in information entropy. These three peaks are located on lattice sites $S_2$.}
\label{feature_importances}
\end{figure}

\begin{thebibliography}{10}
\urlstyle{rm}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{RevModPhys.82.3045}
\bibinfo{author}{Hasan, M.~Z.} \& \bibinfo{author}{Kane, C.~L.}
\newblock \bibinfo{journal}{\bibinfo{title}{Colloquium: Topological
  insulators}}.
\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
  \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{3045--3067}
  (\bibinfo{year}{2010}).

\bibitem{CONTINENTINO2017A1}
\bibinfo{author}{Continentino, M.~A.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological phase transitions}}.
\newblock {\emph{\JournalTitle{Physica B: Condensed Matter}}}
  \textbf{\bibinfo{volume}{505}}, \bibinfo{pages}{A1 -- A2}
  (\bibinfo{year}{2017}).

\bibitem{PhysRevB.95.094509}
\bibinfo{author}{Puel, T.~O.}, \bibinfo{author}{Sacramento, P.~D.} \&
  \bibinfo{author}{Continentino, M.~A.}
\newblock \bibinfo{journal}{\bibinfo{title}{$4\ensuremath{\pi}$ josephson
  currents in junctions of hybridized multiband superconductors}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{95}},
  \bibinfo{pages}{094509} (\bibinfo{year}{2017}).

\bibitem{PhysRevE.97.012107}
\bibinfo{author}{Griffith, M.~A.} \& \bibinfo{author}{Continentino, M.~A.}
\newblock \bibinfo{journal}{\bibinfo{title}{Casimir amplitudes in topological
  quantum phase transitions}}.
\newblock {\emph{\JournalTitle{Phys. Rev. E}}} \textbf{\bibinfo{volume}{97}},
  \bibinfo{pages}{012107} (\bibinfo{year}{2018}).

\bibitem{ryu2010topological}
\bibinfo{author}{Ryu, S.}, \bibinfo{author}{Schnyder, A.~P.},
  \bibinfo{author}{Furusaki, A.} \& \bibinfo{author}{Ludwig, A.~W.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological insulators and
  superconductors: tenfold way and dimensional hierarchy}}.
\newblock {\emph{\JournalTitle{New Journal of Physics}}}
  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{065010}
  (\bibinfo{year}{2010}).

\bibitem{atala2013direct}
\bibinfo{author}{Atala, M.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Direct measurement of the zak phase
  in topological bloch bands}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{9}},
  \bibinfo{pages}{795} (\bibinfo{year}{2013}).

\bibitem{Stuhl1514}
\bibinfo{author}{Stuhl, B.~K.}, \bibinfo{author}{Lu, H.-I.},
  \bibinfo{author}{Aycock, L.~M.}, \bibinfo{author}{Genkina, D.} \&
  \bibinfo{author}{Spielman, I.~B.}
\newblock \bibinfo{journal}{\bibinfo{title}{Visualizing edge states with an
  atomic bose gas in the quantum hall regime}}.
\newblock {\emph{\JournalTitle{Science}}} \textbf{\bibinfo{volume}{349}},
  \bibinfo{pages}{1514--1518} (\bibinfo{year}{2015}).

\bibitem{leder2016real}
\bibinfo{author}{Leder, M.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Real-space imaging of a
  topologically protected edge state with ultracold atoms in an
  amplitude-chirped optical lattice}}.
\newblock {\emph{\JournalTitle{Nature communications}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13112} (\bibinfo{year}{2016}).

\bibitem{goldman2016topological}
\bibinfo{author}{Goldman, N.}, \bibinfo{author}{Budich, J.} \&
  \bibinfo{author}{Zoller, P.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological quantum matter with
  ultracold gases in optical lattices}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
  \bibinfo{pages}{639} (\bibinfo{year}{2016}).

\bibitem{meier2016observation}
\bibinfo{author}{Meier, E.~J.}, \bibinfo{author}{An, F.~A.} \&
  \bibinfo{author}{Gadway, B.}
\newblock \bibinfo{journal}{\bibinfo{title}{Observation of the topological
  soliton state in the su--schrieffer--heeger model}}.
\newblock {\emph{\JournalTitle{Nature communications}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13986} (\bibinfo{year}{2016}).

\bibitem{hafezi2013imaging}
\bibinfo{author}{Hafezi, M.}, \bibinfo{author}{Mittal, S.},
  \bibinfo{author}{Fan, J.}, \bibinfo{author}{Migdall, A.} \&
  \bibinfo{author}{Taylor, J.}
\newblock \bibinfo{journal}{\bibinfo{title}{Imaging topological edge states in
  silicon photonics}}.
\newblock {\emph{\JournalTitle{Nature Photonics}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1001} (\bibinfo{year}{2013}).

\bibitem{lu2016topological}
\bibinfo{author}{Lu, L.}, \bibinfo{author}{Joannopoulos, J.~D.} \&
  \bibinfo{author}{Solja{\v{c}}i{\'c}, M.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological states in photonic
  systems}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
  \bibinfo{pages}{626} (\bibinfo{year}{2016}).

\bibitem{PhysRevX.5.031011}
\bibinfo{author}{Peano, V.}, \bibinfo{author}{Brendel, C.},
  \bibinfo{author}{Schmidt, M.} \& \bibinfo{author}{Marquardt, F.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological phases of sound and
  light}}.
\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{031011} (\bibinfo{year}{2015}).

\bibitem{kitagawa2012observation}
\bibinfo{author}{Kitagawa, T.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Observation of topologically
  protected bound states in photonic quantum walks}}.
\newblock {\emph{\JournalTitle{Nature communications}}}
  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{882} (\bibinfo{year}{2012}).

\bibitem{cardano2016statistical}
\bibinfo{author}{Cardano, F.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Statistical moments of quantum-walk
  dynamics reveal topological quantum transitions}}.
\newblock {\emph{\JournalTitle{Nature communications}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{11439} (\bibinfo{year}{2016}).

\bibitem{PhysRevX.7.031023}
\bibinfo{author}{Flurin, E.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Observing topological invariants
  using quantum walks in superconducting circuits}}.
\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
  \bibinfo{pages}{031023} (\bibinfo{year}{2017}).

\bibitem{soluyanov2015type}
\bibinfo{author}{Soluyanov, A.~A.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Type-ii weyl semimetals}}.
\newblock {\emph{\JournalTitle{Nature}}} \textbf{\bibinfo{volume}{527}},
  \bibinfo{pages}{495} (\bibinfo{year}{2015}).

\bibitem{PhysRevX.5.031013}
\bibinfo{author}{Lv, B.~Q.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Experimental discovery of weyl
  semimetal taas}}.
\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{031013} (\bibinfo{year}{2015}).

\bibitem{PhysRevLett.42.1698}
\bibinfo{author}{Su, W.~P.}, \bibinfo{author}{Schrieffer, J.~R.} \&
  \bibinfo{author}{Heeger, A.~J.}
\newblock \bibinfo{journal}{\bibinfo{title}{Solitons in polyacetylene}}.
\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{1698--1701}
  (\bibinfo{year}{1979}).

\bibitem{maffei2018topological}
\bibinfo{author}{Maffei, M.}, \bibinfo{author}{Dauphin, A.},
  \bibinfo{author}{Cardano, F.}, \bibinfo{author}{Lewenstein, M.} \&
  \bibinfo{author}{Massignan, P.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological characterization of
  chiral models through their long time dynamics}}.
\newblock {\emph{\JournalTitle{New Journal of Physics}}}
  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{013023}
  (\bibinfo{year}{2018}).

\bibitem{RevModPhys.73.681}
\bibinfo{author}{Heeger, A.~J.}
\newblock \bibinfo{journal}{\bibinfo{title}{Nobel lecture: Semiconducting and
  metallic polymers: The fourth generation of polymeric materials}}.
\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
  \textbf{\bibinfo{volume}{73}}, \bibinfo{pages}{681--700}
  (\bibinfo{year}{2001}).

\bibitem{kane2014topological}
\bibinfo{author}{Kane, C.} \& \bibinfo{author}{Lubensky, T.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological boundary modes in
  isostatic lattices}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{10}},
  \bibinfo{pages}{39} (\bibinfo{year}{2014}).

\bibitem{Chen13004}
\bibinfo{author}{Chen, B. G.-g.}, \bibinfo{author}{Upadhyaya, N.} \&
  \bibinfo{author}{Vitelli, V.}
\newblock \bibinfo{journal}{\bibinfo{title}{Nonlinear conduction via solitons
  in a topological mechanical insulator}}.
\newblock {\emph{\JournalTitle{Proceedings of the National Academy of
  Sciences}}} \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{13004--13009}
  (\bibinfo{year}{2014}).

\bibitem{carrasquilla2017machine}
\bibinfo{author}{Carrasquilla, J.} \& \bibinfo{author}{Melko, R.~G.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of
  matter}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
  \bibinfo{pages}{431} (\bibinfo{year}{2017}).

\bibitem{PhysRevX.7.031038}
\bibinfo{author}{Ch'ng, K.}, \bibinfo{author}{Carrasquilla, J.},
  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Khatami, E.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of strongly
  correlated fermions}}.
\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
  \bibinfo{pages}{031038} (\bibinfo{year}{2017}).

\bibitem{PhysRevB.94.195105}
\bibinfo{author}{Wang, L.}
\newblock \bibinfo{journal}{\bibinfo{title}{Discovering phase transitions with
  unsupervised learning}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{94}},
  \bibinfo{pages}{195105} (\bibinfo{year}{2016}).

\bibitem{broecker2017machine}
\bibinfo{author}{Broecker, P.}, \bibinfo{author}{Carrasquilla, J.},
  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Trebst, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning quantum phases of
  matter beyond the fermion sign problem}}.
\newblock {\emph{\JournalTitle{Scientific reports}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{8823} (\bibinfo{year}{2017}).

\bibitem{van2017learning}
\bibinfo{author}{Van~Nieuwenburg, E.~P.}, \bibinfo{author}{Liu, Y.-H.} \&
  \bibinfo{author}{Huber, S.~D.}
\newblock \bibinfo{journal}{\bibinfo{title}{Learning phase transitions by
  confusion}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
  \bibinfo{pages}{435} (\bibinfo{year}{2017}).

\bibitem{PhysRevLett.120.066401}
\bibinfo{author}{Zhang, P.}, \bibinfo{author}{Shen, H.} \&
  \bibinfo{author}{Zhai, H.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
  invariants with neural networks}}.
\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{066401}
  (\bibinfo{year}{2018}).

\bibitem{PhysRevB.98.085402}
\bibinfo{author}{Sun, N.}, \bibinfo{author}{Yi, J.}, \bibinfo{author}{Zhang,
  P.}, \bibinfo{author}{Shen, H.} \& \bibinfo{author}{Zhai, H.}
\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning topological
  invariants of band insulators}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{98}},
  \bibinfo{pages}{085402} (\bibinfo{year}{2018}).

\bibitem{PhysRevB.97.174435}
\bibinfo{author}{Suchsland, P.} \& \bibinfo{author}{Wessel, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{Parameter diagnostics of phases and
  phase transition learning by neural networks}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
  \bibinfo{pages}{174435} (\bibinfo{year}{2018}).

\bibitem{PhysRevLett.118.216401}
\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Kim, E.-A.}
\newblock \bibinfo{journal}{\bibinfo{title}{Quantum loop topography for machine
  learning}}.
\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
  \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{216401}
  (\bibinfo{year}{2017}).

\bibitem{PhysRevLett.120.257204}
\bibinfo{author}{Venderley, J.}, \bibinfo{author}{Khemani, V.} \&
  \bibinfo{author}{Kim, E.-A.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning out-of-equilibrium
  phases of matter}}.
\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{257204}
  (\bibinfo{year}{2018}).

\bibitem{ohtsuki2017deep}
\bibinfo{author}{Ohtsuki, T.} \& \bibinfo{author}{Ohtsuki, T.}
\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning the quantum phase
  transitions in random electron systems: Applications to three dimensions}}.
\newblock {\emph{\JournalTitle{Journal of the Physical Society of Japan}}}
  \textbf{\bibinfo{volume}{86}}, \bibinfo{pages}{044708}
  (\bibinfo{year}{2017}).

\bibitem{PhysRevB.97.205110}
\bibinfo{author}{Yoshioka, N.}, \bibinfo{author}{Akagi, Y.} \&
  \bibinfo{author}{Katsura, H.}
\newblock \bibinfo{journal}{\bibinfo{title}{Learning disordered topological
  phases by statistical recovery of symmetry}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
  \bibinfo{pages}{205110} (\bibinfo{year}{2018}).

\bibitem{PhysRevB.96.195145}
\bibinfo{author}{Deng, D.-L.}, \bibinfo{author}{Li, X.} \&
  \bibinfo{author}{Das~Sarma, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
  states}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
  \bibinfo{pages}{195145} (\bibinfo{year}{2017}).

\bibitem{PhysRevB.97.134109}
\bibinfo{author}{Huembeli, P.}, \bibinfo{author}{Dauphin, A.} \&
  \bibinfo{author}{Wittek, P.}
\newblock \bibinfo{journal}{\bibinfo{title}{Identifying quantum phase
  transitions with adversarial neural networks}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
  \bibinfo{pages}{134109} (\bibinfo{year}{2018}).

\bibitem{PhysRevB.97.115453}
\bibinfo{author}{Carvalho, D.}, \bibinfo{author}{Garc\'{\i}a-Mart\'{\i}nez,
  N.~A.}, \bibinfo{author}{Lado, J.~L.} \&
  \bibinfo{author}{Fern\'andez-Rossier, J.}
\newblock \bibinfo{journal}{\bibinfo{title}{Real-space mapping of topological
  invariants using artificial neural networks}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
  \bibinfo{pages}{115453} (\bibinfo{year}{2018}).

\bibitem{PhysRevB.96.245119}
\bibinfo{author}{Zhang, Y.}, \bibinfo{author}{Melko, R.~G.} \&
  \bibinfo{author}{Kim, E.-A.}
\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning ${\mathbb{z}}_{2}$
  quantum spin liquids with quasiparticle statistics}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
  \bibinfo{pages}{245119} (\bibinfo{year}{2017}).

\bibitem{rodriguez2018identifying}
\bibinfo{author}{Rodriguez-Nieva, J.~F.} \& \bibinfo{author}{Scheurer, M.~S.}
\newblock \bibinfo{journal}{\bibinfo{title}{Identifying topological order via
  unsupervised machine learning}}.
\newblock {\emph{\JournalTitle{arXiv preprint arXiv:1805.05961}}}
  (\bibinfo{year}{2018}).

\bibitem{breiman2017classification}
\bibinfo{author}{Breiman, L.}, \bibinfo{author}{Friedman, J.},
  \bibinfo{author}{Stone, C.~J.} \& \bibinfo{author}{Olshen, R.~A.}
\newblock \emph{\bibinfo{title}{Classification and regression trees}}
  (\bibinfo{publisher}{Chapman and Hall/CRC, London, UK},
  \bibinfo{year}{1984}).

\bibitem{Breiman2001}
\bibinfo{author}{Breiman, L.}
\newblock \bibinfo{journal}{\bibinfo{title}{Random forests}}.
\newblock {\emph{\JournalTitle{Machine Learning}}}
  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{5--32} (\bibinfo{year}{2001}).

\bibitem{friedman2001elements}
\bibinfo{author}{Friedman, J.}, \bibinfo{author}{Hastie, T.} \&
  \bibinfo{author}{Tibshirani, R.}
\newblock \emph{\bibinfo{title}{The elements of statistical learning}}
  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2001}).

\bibitem{PhysRevB.84.241106}
\bibinfo{author}{Bianco, R.} \& \bibinfo{author}{Resta, R.}
\newblock \bibinfo{journal}{\bibinfo{title}{Mapping topological order in
  coordinate space}}.
\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{84}},
  \bibinfo{pages}{241106} (\bibinfo{year}{2011}).

\bibitem{caio2019topological}
\bibinfo{author}{Caio, M.~D.}, \bibinfo{author}{M{\"o}ller, G.},
  \bibinfo{author}{Cooper, N.~R.} \& \bibinfo{author}{Bhaseen, M.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological marker currents in
  chern insulators}}.
\newblock {\emph{\JournalTitle{Nature Physics}}} \bibinfo{pages}{1}
  (\bibinfo{year}{2019}).

\bibitem{carlsson2009topology}
\bibinfo{author}{Carlsson, G.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topology and data}}.
\newblock {\emph{\JournalTitle{Bulletin of the American Mathematical Society}}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{255--308}
  (\bibinfo{year}{2009}).

\bibitem{wasserman2018topological}
\bibinfo{author}{Wasserman, L.}
\newblock \bibinfo{journal}{\bibinfo{title}{Topological data analysis}}.
\newblock {\emph{\JournalTitle{Annual Review of Statistics and Its
  Application}}} \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{501--532}
  (\bibinfo{year}{2018}).

\bibitem{wang2005adaptive}
\bibinfo{author}{Wang, J.}, \bibinfo{author}{Zhang, Z.} \&
  \bibinfo{author}{Zha, H.}
\newblock \bibinfo{title}{Adaptive manifold learning}.
\newblock In \emph{\bibinfo{booktitle}{Advances in neural information
  processing systems}}, \bibinfo{pages}{1473--1480} (\bibinfo{year}{2005}).

\bibitem{lin2008riemannian}
\bibinfo{author}{Lin, T.} \& \bibinfo{author}{Zha, H.}
\newblock \bibinfo{journal}{\bibinfo{title}{Riemannian manifold learning}}.
\newblock {\emph{\JournalTitle{IEEE Transactions on Pattern Analysis and
  Machine Intelligence}}} \textbf{\bibinfo{volume}{30}},
  \bibinfo{pages}{796--809} (\bibinfo{year}{2008}).

\bibitem{belkin2003problems}
\bibinfo{author}{Belkin, M.}
\newblock \emph{\bibinfo{title}{Problems of learning on manifolds}}
  (\bibinfo{publisher}{The University of Chicago, Chicago, IL, USA},
  \bibinfo{year}{2003}).

\end{thebibliography}

\section*{Acknowledgements}

We thank S. E. Rowley, J. F. de Oliveira, T. Micklitz and M. A. Continentino for insightful discussions and S. E. Rowley for carefully reading the manuscript and suggesting improvements. N. L. Holanda acknowledges financial support from CENPES/Petrobr\'as/CBPF. M. A. R. Griffith acknowledges financial support from Capes. N. L. Holanda is grateful to the Theory of Condensed Matter and Quantum Materials groups at the Cavendish Laboratory and the Quantum Information Group at CBPF.

\section*{Author contributions}

Both authors of this work contributed equally to its realization at all stages.

\section*{Competing financial interests}

The authors declare no competing financial or non-financial interests.

\section*{Additional information}

Correspondence and requests for materials should be addressed to N. L. Holanda.

\newpage

\begin{figure}
  \centering
  \includegraphics[width=.37\textwidth]{model.pdf}
  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
\label{fig:model}
\end{figure}

\begin{figure}%[h!]
  \centering
  \includegraphics[width=.37\textwidth]{winding.png}
  \caption{Winding number. The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point. Picture credits: Jim Belk, public domain.}
\label{fig:winding}
\end{figure}

\section*{Supplementary Material}
\subsection*{The SSH model}
\label{sshapp}

The SSH model \citesupp{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms. This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian. This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
\begin{equation}
\label{SSH}
\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
\end{equation}
where the column vector
\begin{equation*}
\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
\end{equation*}
contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
\begin{equation*}
\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
\end{equation*}
contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$. Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.

The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$. We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics. As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
\begin{equation}\label{hmatrix}
H(t_1,t_2,T_1,T_2)=\left(
  \begin{array}{cccccc}
    0 & t_1 & 0 & T_1 & 0 & \cdots \\
    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
    0 & t_2 & 0 & t_1 & 0 & \cdots\\
    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
    0 & T_2 & 0 & t_2 &  0& \cdots\\
    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
  \end{array}
  \right)_{N \times N}.
\end{equation}
Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase. Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.

The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions. This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system. In the particular case of the SSH model, the topological invariant used to classify the topological phases is the winding number.

The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself. It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative). Figure \ref{fig:winding} shows several closed, oriented curves and their winding numbers computed with respect to a given point.

An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points. This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a very challenging task.

For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
\begin{equation}\label{winding_number}
W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
\end{equation}
where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\hat{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator. Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure \ref{fig:phasediagrams}.

\begin{figure}
\centering
\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{fig1a-6561-less-simulation_merged_winding_grid.png}}
\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{fig1b-6561-less-simulation_merged_winding_grid.png}}
\caption{Probability heatmaps learned from most relevant lattice sites. (a) Probability heatmap learned in experiment 1 using only lattice sites $S_1$.  (b) Probability heatmap learned in experiment 2 using only lattice sites $S_2$.}
\label{less_feat}
\end{figure}

\subsection*{Learning topological phases from real space data}

The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq. \eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g. disordered systems in condensed matter) do not have. Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them. We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.

Our reasoning goes as follows. First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it. Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space. Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.

In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \citesupp{goodfellow2016deep}. Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
\begin{equation}
\label{localconstancy}
W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
\end{equation}

That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure \ref{fig:phasediagrams}, where we draw phase diagrams of SSH models with first-neighbor (figure \ref{ssh1}) and first- and second-neighbor (figure \ref{ssh2}) hoppings. In figure \ref{ssh1} for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase. Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.

It does not immediately follow, however, that the same strategy will be successful in real space. Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,

\begin{equation}
\label{parameter_to_real}
\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
\end{equation}
where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$. The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.

This fact is well illustrated by the numerical experiments discussed in the article. Although it may seem from figures \ref{figexp1_exp:b} and \ref{figexp2_exp:b} in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space. In such high-dimensional spaces, the data should be much sparser.

The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \citesupp{bishop2006pattern}. It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.

These conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space. Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \citesupp{rifai2011manifold}). As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}). In this sense, key topological information can be said to be localized on few lattice sites.

\subsection*{The eigenvector-ensembling algorithm}

We describe here in detail each step of the eigenvector-ensembling algorithm.
\vspace{.3cm}
\begin{enumerate}[topsep=0pt, partopsep=0pt]
\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2). These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
\item[2)] \textbf{Creating training, validation and test sets:} here we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning. More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$). We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$. Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$. Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified. This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian. In this work we estimate the class probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each class.
\item[5)] \textbf{Bootstrapping:} We refine the class probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space. The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
\end{enumerate}
\vspace{.3cm}
In this work we implemented the eigenvector ensembling algorithm with Python's Scikit tools.

\subsection*{Gini topological signals in the macroscopic limit}

A natural question that comes to mind regarding the Gini topological signals presented here is whether these signals are artifacts of the numerical procedure used to generate them.

The eigenvector-ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3). Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.

Artifacts resulting from randomization in the eigenvector-ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3). As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect. The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector-ensembling algorithm.

There are still artifacts that might arise from the hyperparameters used to generate the data. These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space). Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive. Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the Gini topological signals is lattice size.

All results presented in the article were obtained for lattices with 50 unit cells. Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$. Here we present the Gini topological signals obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{newtopsig1} and \ref{newtopsig2}). These Gini topological signals were generated in exactly the same way as the Gini topological signals obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).

It is clear from figures \ref{newtopsig1} and \ref{newtopsig2} that the patterns seen with 50 unit cells (figures \ref{feature_importances1} and \ref{feature_importances2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.

Figures \ref{newtopsig1} and \ref{newtopsig2} suggest that the Gini topological signals presented here can be viewed as topological mass functions along the lattices. In the limit of an infinite chain, the cumulative Gini topological distribution function (or cumulative Gini topological distribution for short) $F_G(x)$ associated with a Gini topological signal will be given by the integral of a Gini topological density function (or Gini topological density for short) $\rho_G$($x$),

\begin{equation}
\label{entropy_dens}
F_G(x) = \int_{0}^x\rho_G(x')dx'
\end{equation}
where $x$ $\in$ [0,1] is a spatial coordinate along the lattice (being strict, our use of periodic boundary conditions implies that the coordinate $x$ should be defined in the quotient space $[0,1]/R$, where $R$ is the equivalence relation in [0,1] defining the unit circle $S^1$, i.e. $x$ $R$ $x'$ if and only if $x$ = $x'$ or ($x$,$x'$) $\in$ \{(0,1), (1,0)\}. For open boundary conditions, the spatial coordinate $x$ is defined in the closed interval [0,1]). In this continuum limit, a Gini topological signal will be given by the Gini topological density $\rho_G(x)$. Figures \ref{cdf1} and \ref{cdf2} show the cumulative Gini topological distributions corresponding to the Gini topological signals in figures \ref{newtopsig1} and \ref{newtopsig2}.

The results presented in this article suggest that the macroscopic limit $\rho_G(x)$ of Gini topological signals may have strong theoretical interest and pave new roads to the investigation of topological materials.

\begin{figure}
\centering
\subfigure[]{\label{newtopsig1-70}\includegraphics[width=.32\textwidth]{fig1a-6561-140-feature_importances}}
\subfigure[]{\label{newtopsig1-90}\includegraphics[width=.32\textwidth]{fig1a-6561-180-feature_importances}}
\subfigure[]{\label{newtopsig1-110}\includegraphics[width=.32\textwidth]{fig1a-6561-220-feature_importances}}
\caption{Gini topological signals obtained for experiment 1 with higher lattice sizes. (a) Gini topological signal for 70 unit cells. (b) Gini topological signal for 90 unit cells. (c) Gini topological signal for 110 unit cells.}
\label{newtopsig1}
\end{figure}
\begin{figure}
\centering
\subfigure[]{\label{newtopsig2-70}\includegraphics[width=.32\textwidth]{fig1b-6561-140-feature_importances}}
\subfigure[]{\label{newtopsig2-90}\includegraphics[width=.32\textwidth]{fig1b-6561-180-feature_importances}}
\subfigure[]{\label{newtopsig2-110}\includegraphics[width=.32\textwidth]{fig1b-6561-220-feature_importances}}
\caption{Gini topological signals obtained for experiment 2 with higher lattice sizes. (a) Gini topological signal for 70 unit cells. (b) Gini topological signal for 90 unit cells. (c) Gini topological signal for 110 unit cells.}
\label{newtopsig2}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cdf1-70}\includegraphics[width=.32\textwidth]{fig1a-6561-140-cumulative_feature_importances-newer}}
\subfigure[]{\label{cdf1-90}\includegraphics[width=.32\textwidth]{fig1a-6561-180-cumulative_feature_importances-newer}}
\subfigure[]{\label{cdf1-110}\includegraphics[width=.32\textwidth]{fig1a-6561-220-cumulative_feature_importances-newer}}
\caption{Cumulative Gini topological distributions (CGTDs) for higher lattice sizes in experiment 1. (a) CGTD for 70 unit cells. (b) CGTD for 90 unit cells. (c) CGTD for 110 unit cells. The two visible leaps in the cumulative Gini topological distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
\label{cdf1}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cdf2-70}\includegraphics[width=.32\textwidth]{fig1b-6561-140-cumulative_feature_importances-newer}}
\subfigure[]{\label{cdf2-90}\includegraphics[width=.32\textwidth]{fig1b-6561-180-cumulative_feature_importances-newer}}
\subfigure[]{\label{cdf2-110}\includegraphics[width=.32\textwidth]{fig1b-6561-220-cumulative_feature_importances-newer}}
\caption{Cumulative Gini topological distributions (CGTDs) for higher lattice sizes in experiment 2. (a) CGTD for 70 unit cells. (b) CGTD for 90 unit cells. (c) CGTD for 110 unit cells. Here the leaps in the cumulative Gini topological distributions are less pronounced than in experiment 1, but still noticeable. The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case with 50 unit cells.}
\label{cdf2}
\end{figure}

\newpage
\begin{thebibliography}{1}
\urlstyle{rm}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{asboth2016short}
\bibinfo{author}{Asb{\'o}th, J.~K.}, \bibinfo{author}{Oroszl{\'a}ny, L.} \&
  \bibinfo{author}{P{\'a}lyi, A.}
\newblock \bibinfo{journal}{\bibinfo{title}{A short course on topological
  insulators}}.
\newblock {\emph{\JournalTitle{Lecture notes in physics}}}
  \textbf{\bibinfo{volume}{919}} (\bibinfo{year}{2016}).

\bibitem{goodfellow2016deep}
\bibinfo{author}{Goodfellow, I.}, \bibinfo{author}{Bengio, Y.} \&
  \bibinfo{author}{Courville, A.}
\newblock \emph{\bibinfo{title}{Deep learning}} (\bibinfo{publisher}{MIT press,
  Cambridge, MA, USA}, \bibinfo{year}{2016}).

\bibitem{bishop2006pattern}
\bibinfo{author}{Bishop, C.~M.}
\newblock \emph{\bibinfo{title}{Pattern recognition and machine learning}}
  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2006}).

\bibitem{cayton2005algorithms}
\bibinfo{author}{Cayton, L.}
\newblock \bibinfo{journal}{\bibinfo{title}{Algorithms for manifold learning}}.
\newblock {\emph{\JournalTitle{Univ. of California at San Diego Tech. Rep}}}
  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{1} (\bibinfo{year}{2005}).

\bibitem{narayanan2010sample}
\bibinfo{author}{Narayanan, H.} \& \bibinfo{author}{Mitter, S.}
\newblock \bibinfo{title}{Sample complexity of testing the manifold
  hypothesis}.
\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
  Processing Systems}}, \bibinfo{pages}{1786--1794} (\bibinfo{year}{2010}).

\bibitem{rifai2011manifold}
\bibinfo{author}{Rifai, S.}, \bibinfo{author}{Dauphin, Y.~N.},
  \bibinfo{author}{Vincent, P.}, \bibinfo{author}{Bengio, Y.} \&
  \bibinfo{author}{Muller, X.}
\newblock \bibinfo{title}{The manifold tangent classifier}.
\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
  Processing Systems}}, \bibinfo{pages}{2294--2302} (\bibinfo{year}{2011}).

\end{thebibliography}
\end{document}

### 2020-03-04 0_preprocessing/run_template.py
Trying to find problem in papermill

@@ -1,0 +1,44 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Mar  3 17:23:25 2020
+
+@author: linneu
+"""
+
+
+import papermill as pm
+from tqdm import tqdm
+import os
+
+WDIR = "/home/linneu/ml_topological_phases_in_real_space/0_preprocessing"
+os.chdir(WDIR)
+
+template = "preprocessing_template.ipynb"
+parameters = {"allowed_windings":[0,1], "epsilon":0.01, "to_csv":True}
+kernel_name = "ml_top_phases"
+grid_folders_csv_names_outputs = [("/home/linneu/ssh_grids/ssh1/periodic_100_6561", "/home/linneu/ssh_csvs/ssh1/periodic_100_6561.csv","preprocessing_output_periodic_100_6561.ipynb"),\
+                             ("/home/linneu/ssh_grids/ssh1/periodic_140_6561", "/home/linneu/ssh_csvs/ssh1/periodic_140_6561.csv","preprocessing_output_periodic_140_6561.ipynb"),\
+                             ("/home/linneu/ssh_grids/ssh1/periodic_180_6561", "/home/linneu/ssh_csvs/ssh1/periodic_180_6561.csv","preprocessing_output_periodic_180_6561.ipynb"),\
+                             ("/home/linneu/ssh_grids/ssh1/periodic_220_6561", "/home/linneu/ssh_csvs/ssh1/periodic_220_6561.csv","preprocessing_output_periodic_220_6561.ipynb")\
+                             ]
+    
+def execute_notebook(template,output_file,parameters,kernel_name,grid_folder,csv_name):
+    
+    parameters["grid_folder"]=grid_folder
+    parameters["csv_name"]=csv_name
+    nb = pm.execute_notebook(template,
+                        output_file,
+                        parameters=parameters,
+                        kernel_name=kernel_name)
+    #nbs = []
+    #nbs.append(nb)
+    return nb
+
+nbs = {}
+for grid_folder, csv_name, output_file in tqdm(grid_folders_csv_names_outputs):
+    filename = csv_name.split(".")[0].split("/")[-1]
+    nbs[filename] = execute_notebook(template,output_file,parameters,kernel_name,grid_folder,csv_name)
+    
+
+    

### 2020-03-06 1_simulation/simulation.py
Running run_simulation_template.ipynb

@@ -20,8 +20,8 @@ class Simulation(object):
     """
     Implements a machine learning simulation 
     """    
-       
-    def __init__(self, csv_path, model, allowed_windings, simulation_dir = "./simulation", val_split = 0, features_to_use = None, shuffle_features = False, random_state = None):            
+    _models_dict = {"DecisionTreeClassifier": DecisionTreeClassifier, "RandomForestClassifier": RandomForestClassifier}
+    def __init__(self, csv_path, model_name, model_kw, allowed_windings, simulation_dir = "./simulation", val_split = 0, features_to_use = None, shuffle_features = False, random_state = None):            
         """
         Simulation class constructor.
 
@@ -41,7 +41,9 @@ class Simulation(object):
         if random_state is not None:
             np.random.seed(random_state)
         self.csv_path = csv_path
-        self.model = model
+        self.model = None
+        self.model_name = model_name
+        self.model_kw = model_kw
         self.allowed_windings = allowed_windings
         self.val_split = val_split
         self.features_to_use = features_to_use
@@ -143,6 +145,8 @@ class Simulation(object):
         dataframe: a pandas dataframe with properly named columns
         predict_params: a dict of prediction parameters
         """ 
+        print("THIS IS  predict_params: ", predict_params)
+        print("THIS IS  the type of predict_params: ", type(predict_params))
         feat_columns = self.dataframe.columns[self.dataframe.columns.get_loc("feat0"):]
         X = self.dataframe.loc[:,feat_columns].values
         ### shuffling features
@@ -241,7 +245,7 @@ class Simulation(object):
         y_pred = self.hamiltonian_summary.pred_phase[boolean_mask].values
         self.accuracy["hamiltonian_test"] = accuracy_score(y_true,y_pred)
                  
-    def run_simulation(self, n_experiments=1, start_n=0, fit_params=None, shuffle_rows = True, pred_params=None, random_features = False, store_in_lists=False, save_eigenvector=False, save_hamiltonian=True, save_accuracy=True, save_model=False):
+    def run_simulation(self, n_experiments=1, start_n=0, fit_params=None, shuffle_rows = True, pred_params=None, random_features = False, store_in_lists=False, save_eigenvector=False, save_hamiltonian=True, save_accuracy=True, save_models=False):
         """
         Fits a machine learning algorithm to training data and writes result of simulation to disk
         
@@ -256,7 +260,7 @@ class Simulation(object):
[…]

### 2020-03-07 paper/main.tex
Simulations done. Next step: write results template

--- 2020-01-18 1901.01963/main.tex
@@
 The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector-ensembling procedure.
-We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from lattice data in real space and show how the Gini impurity of ensembles of lattice eigenvectors can be used to retrieve a topological signal detailing how topological information is distributed along the lattice.
-The discovery of local Gini topological signals from the analysis of data from several thousand SSH systems illustrates how machine learning can advance the research and discovery of new quantum materials with exotic properties that may power future technological applications such as quantum computing.
+We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed along the lattice.
+The discovery of Shannon entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as quantum computing.
 \end{abstract}
@@
 
-The advantage of using tree-based methods to learn from local eigenvector data is that their use of entropy-based cost functions (such as mixture entropy or Gini impurity) makes it much easier to trace the localization of relevant information along the features of a data set.
-We use this advantage to recover a topological signal quantifying the amount of topological information available from each lattice site as measured by normalized reduction in Gini impurity.
+The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
+This makes it much easier to trace the localization of relevant information along the features of a data set.
+Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
 This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
@@
 
-The topological signals presented for the first time in this work provide a clear illustration of how machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
+The Shannon information entropy signals presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
 
@@
 A detailed description of the algorithm is found in the section \textbf{The eigenvector-ensembling algorithm} in the Supplementary Material.
-Here we present results for the numerical experiments we performed with it.
-We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (figure \ref{ssh2}).
+Here we present results of the numerical experiments we performed with it.
+We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called ssh\_1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called ssh\_2, figure \ref{ssh2}).
 
 In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
-The goal in each experiment is to recover the corresponding phase diagram in 2D (i.e.
-two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
+The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
 

### 2020-03-07 2_results/data_analysis.py

@@ -1,776 +1,0 @@
-import numpy as np
-import pandas as pd
-import os
-import matplotlib.pyplot as plt
-import graphviz
-from itertools import filterfalse
-from importlib import reload
-from itertools import chain
-from sklearn.tree import export_graphviz
-from sklearn.tree import DecisionTreeClassifier
-from sklearn.ensemble import RandomForestClassifier
-from sklearn.metrics import accuracy_score
-from sklearn.base import clone
-from tqdm import tqdm
-from joblib import load
-from matplotlib.colors import ListedColormap
-from matplotlib.colors import LinearSegmentedColormap
-from collections import defaultdict
-#import json
-import csv
-
-############### Defining some color maps
-###Reds_alpha
-ncolors = 256
-color_array = plt.get_cmap('Reds')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Reds_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-
-###Oranges_alpha
-ncolors = 256
-color_array = plt.get_cmap('Oranges')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Oranges_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-
-### Greens_alpha
-ncolors = 256
-color_array = plt.get_cmap('Greens')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Greens_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-### Blues_alpha
-ncolors = 256
-color_array = plt.get_cmap('Blues')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Blues_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-##########
-
-class Experiment(object):
-    """
-    A class to perform data analysis on machine learning experiments.
-    """
-
-    def __init__(self, simulation_dir, experiment_name):
-        """
[…]

### 2020-03-07 2_results/prediction_grids.py

@@ -1,772 +1,0 @@
-import numpy as np
-import pandas as pd
-import os
-import matplotlib.pyplot as plt
-import graphviz
-from itertools import filterfalse
-from importlib import reload
-from itertools import chain
-from sklearn.tree import export_graphviz
-from sklearn.tree import DecisionTreeClassifier
-from sklearn.ensemble import RandomForestClassifier
-from sklearn.metrics import accuracy_score
-from sklearn.base import clone
-from tqdm import tqdm
-from joblib import load
-from matplotlib.colors import ListedColormap
-from matplotlib.colors import LinearSegmentedColormap
-from collections import defaultdict
-#import json
-import csv
-#import seaborn
-
-### Defining some color maps
-###Reds_alpha
-ncolors = 256
-color_array = plt.get_cmap('Reds')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Reds_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-
-###Oranges_alpha
-ncolors = 256
-color_array = plt.get_cmap('Oranges')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Oranges_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-
-### Greens_alpha
-ncolors = 256
-color_array = plt.get_cmap('Greens')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Greens_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-### Blues_alpha
-ncolors = 256
-color_array = plt.get_cmap('Blues')(range(ncolors))
-# change alpha values
-color_array[:,-1] = np.linspace(0.0,1.0,ncolors)
-# create a colormap object
-map_object = LinearSegmentedColormap.from_list(name='Blues_alpha',colors=color_array)
-plt.register_cmap(cmap=map_object)
-
-class Experiment(object):
-    """
-    A class to perform data analysis on machine learning experiments.
-    """
-
-    def __init__(self, simulation_dir, experiment_name):
-        """
[…]

### 2020-05-05 paper/main.tex
Preparing to run simulations with fewer features

@@
 The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector-ensembling procedure.
-We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed along the lattice.
-The discovery of Shannon entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as quantum computing.
+We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
+The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
 \end{abstract}
@@
 
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
+The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
 This makes it much easier to trace the localization of relevant information along the features of a data set.
@@
 This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
-To our knowledge this is the first time that a signal describing the localization of topological information in condensed matter systems is presented in the literature.
+To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
 
@@
 \centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{ssh1.png}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{ssh2.png}}
+\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh1.png}}\quad
+\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh2.png}}
 \caption{Phase diagrams in parameter space.
@@
 Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiments 1 and 2 as seen from parameter space.
-The accuracy statistics presented in the following subsections and probability heatmaps shown in figure \ref{heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-The probability heatmaps shown in figure \ref{heatmaps} faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
+The accuracy statistics presented in the following subsections and probability heatmaps shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
+The recovered probability heatmaps faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
 
@@
 \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{fig1a-6561-100-train_val_test_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{fig1a-6561-100-train_winding_labels_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{fig1a-6561-100-prediction_grid_0.png}}
+\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 1 as seen from 2D parameter space.
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{fig1b-6561-100-train_val_test_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{fig1b-6561-100-train_winding_labels_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{fig1b-6561-100-prediction_grid_0.png}}
+\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 2 as seen from 2D parameter space.
@@
 The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g.
-information entropy or Gini impurity \cite{friedman2001elements}).
+Shannon information entropy or Gini impurity \cite{friedman2001elements}).
 By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 and experiment 2 we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only 6 lattice sites $S_1$ = (1, 2, 4, 51, 52, 54) corresponding to the two sharp peaks seen in figure \ref{feature_importances1} contributed more than 70\% of total reduction in Shannon entropy.
-Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by 18 lattice sites $S_2$ = (1, 2, 3, 4, 5, 6, 47, 49, 50, 51, 52, 54, 95, 96, 97, 98, 99, 100) located at the three peaks in figure \ref{feature_importances2}.
+For experiment 1, only 6 lattice sites $S_1$ = (1, 2, 4, 51, 52, 54) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed more than 70\% of total reduction in Shannon entropy.
+Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by 18 lattice sites $S_2$ = (1, 2, 3, 4, 5, 6, 47, 49, 50, 51, 52, 54, 95, 96, 97, 98, 99, 100) located at the three peaks in figure \ref{feature_importances_ssh2}.
 
@@
 \centering
-\subfigure[]{\label{heatmap:a}\includegraphics[width=.50\textwidth]{fig1a-6561-100-simulation_merged_winding_grid.png}}
-\subfigure[]{\label{heatmap:b}\includegraphics[width=.49\textwidth]{fig1b-6561-100-simulation_merged_winding_grid.png}}
-\caption{Probability heatmaps learned from real space eigenvector data.
-Heatmaps were averaged across all 100 iterations in both experiments.
-(a) The probability heatmap learned in experiment 1 shows the probability that a Hamiltonian in the grid has winding number equal to 1.
-(b) The probability heatmap learned in experiment 2 is a superposition of individual probability heatmaps learned for each winding number $W$ = -1, 0, 1 and 2.}
-\label{heatmaps}
+\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
+\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1.
+Heatmaps were averaged across all 100 iterations of the experiment.
+(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
+(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
+(c) The phase diagram resulting from heatmaps (a) and (b).}
+\label{ssh1_heatmaps}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_-1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_2_sim.png}}
+\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
+\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2.
+Heatmaps were averaged across all 100 iterations of the experiment.
+(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to -1.
+(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
+(c) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
+(d) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 2.
+(e) The phase diagram resulting from heatmaps (a)-(d).}
+\label{ssh2_heatmaps}
 \end{figure}
@@
 An advantage of using data from real space is that it enables us to investigate how topological information is distributed in the system.
-This was demonstrated by the Gini topological signals recovered from the Gini impurity of ensembles of eigenvectors in each experiment.
+This was demonstrated by the information entropy signatures recovered from the Shannon entropy of ensembles of eigenvectors in each experiment.
 The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.
 
-We should remark on the subtleties of the Gini topological signals.
+We should remark on the subtleties of the information entropy signatures presented here.
 Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, these importances actually express a global property of the whole lattice.
-Therefore, a lattice site that appears unimportant in a Gini topological signal may not be unimportant or void of topological information by itself.
-To give a concrete example, reduction in Gini impurity tends to be distributed among highly correlated variables.
-This implies that if only a single variable in a highly correlated subset is used, it will likely inherit most of the reduction in Gini impurity from the other variables in the subset.
-In this regard the Gini topological signals presented here express a summary of relations between lattice sites and are therefore intrinsically global.
+Therefore, a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
+To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
+This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other lattice sites in the subset.
+In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
 Furthermore, it should be emphasized that these signals were recovered from the analysis of data from several thousand SSH systems in each experiment and therefore they are not a property of a single SSH lattice.
@@
 
-We performed several tests on the Gini topological signals.
+We performed several tests on the information entropy signatures.
 By rerunning each experiment with longer lattices (i.e.
-increasing the number of unit cells) we have verified that the Gini topological signals in figures \ref{feature_importances1} and \ref{feature_importances2} appear to converge to well defined continuous density functions in the macroscopic limit.
-The macroscopic limit of Gini topological signals may be an important signature of topological systems and thus merits further theoretical investigation.
-A detailed discussion of this point is presented in the section \textbf{Gini topological signals in the macroscopic limit} in the Supplementary Material.
+increasing the number of unit cells) we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
+The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further theoretical investigation.
+A detailed discussion of this point is presented in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
 
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given that topological signals such as the ones shown in figures \ref{feature_importances1} and \ref{feature_importances2} are measured in terms of quantities that have actual physical meaning such as mixture entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
-Whether there is any relationship between local topological markers and the entropy of mixing or the Gini impurity of the ensemble of eigenvectors is left for speculation.
+Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
+Whether there is any relationship between local topological markers and the information entropy of the ensemble of eigenvectors is left for speculation.
 
@@
 \centering
-\subfigure[]{\label{feature_importances1}\includegraphics[width=0.49\textwidth]{fig1a-6561-100-feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances2}\includegraphics[width=0.49\textwidth]{fig1b-6561-100-feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions studied in the paper.
+\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_feature_importances.png}}\quad
+\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
+\caption{Information entropy signatures of the topological phase transitions from experiments 1 and 2.
 (a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for more than 70\% of reduction in information entropy.
@@
   \centering
-  \includegraphics[width=.37\textwidth]{model.pdf}
+  \includegraphics[width=.37\textwidth]{./phase_diagrams/ssh_model.pdf}
   \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
@@
   \centering
-  \includegraphics[width=.37\textwidth]{winding.png}
+  \includegraphics[width=.37\textwidth]{./phase_diagrams/winding.png}
   \caption{Winding number.
@@
 
-\begin{figure}
-\centering
-\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{fig1a-6561-less-simulation_merged_winding_grid.png}}
-\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{fig1b-6561-less-simulation_merged_winding_grid.png}}
-\caption{Probability heatmaps learned from most relevant lattice sites.
-(a) Probability heatmap learned in experiment 1 using only lattice sites $S_1$.
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{fig1a-6561-less-simulation_merged_winding_grid.png}}
+%\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{fig1b-6561-less-simulation_merged_winding_grid.png}}
+%\caption{Probability heatmaps learned from most relevant lattice sites.
+(a) Probability heatmap learned in experiment 1 using only lattice %sites $S_1$.
 (b) Probability heatmap learned in experiment 2 using only lattice sites $S_2$.}
-\label{less_feat}
-\end{figure}
+%\label{less_feat}
+%\end{figure}
 
@@
 
-\subsection*{Gini topological signals in the macroscopic limit}
+\subsection*{Information entropy signatures in the macroscopic limit}
 
-A natural question that comes to mind regarding the Gini topological signals presented here is whether these signals are artifacts of the numerical procedure used to generate them.
+A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
 
@@
 Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive.
-Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the Gini topological signals is lattice size.
+Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the information entropy signatures is lattice size.
 
@@
 Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
-Here we present the Gini topological signals obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{newtopsig1} and \ref{newtopsig2}).
-These Gini topological signals were generated in exactly the same way as the Gini topological signals obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
+Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{newtopsig1} and \ref{newtopsig2}).
+These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
 
-It is clear from figures \ref{newtopsig1} and \ref{newtopsig2} that the patterns seen with 50 unit cells (figures \ref{feature_importances1} and \ref{feature_importances2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
+It is clear from figures \ref{newtopsig1} and \ref{newtopsig2} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
 
-Figures \ref{newtopsig1} and \ref{newtopsig2} suggest that the Gini topological signals presented here can be viewed as topological mass functions along the lattices.
-In the limit of an infinite chain, the cumulative Gini topological distribution function (or cumulative Gini topological distribution for short) $F_G(x)$ associated with a Gini topological signal will be given by the integral of a Gini topological density function (or Gini topological density for short) $\rho_G$($x$),
+Figures \ref{newtopsig1} and \ref{newtopsig2} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
+In the limit of an infinite chain, the cumulative entropy distribution $F_S(x)$ associated with a Shannon information entropy signal will be given by the integral of an entropy density function $\rho_S$($x$),
 
@@
 \label{entropy_dens}
-F_G(x) = \int_{0}^x\rho_G(x')dx'
+F_S(x) = \int_{0}^x\rho_S(x')dx'
 \end{equation}
@@
 For open boundary conditions, the spatial coordinate $x$ is defined in the closed interval [0,1]).
-In this continuum limit, a Gini topological signal will be given by the Gini topological density $\rho_G(x)$.
-Figures \ref{cdf1} and \ref{cdf2} show the cumulative Gini topological distributions corresponding to the Gini topological signals in figures \ref{newtopsig1} and \ref{newtopsig2}.
+In this continuum limit, an information entropy signature will be given by the entropy density function $\rho_S(x)$.
+Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{newtopsig1} and \ref{newtopsig2}.
 
-The results presented in this article suggest that the macroscopic limit $\rho_G(x)$ of Gini topological signals may have strong theoretical interest and pave new roads to the investigation of topological materials.
+The results presented in this article suggest that the macroscopic limit $\rho_S(x)$ of the information entropy signatures may have strong theoretical interest and pave new roads to the investigation of topological materials.
 
@@
 \centering
-\subfigure[]{\label{newtopsig1-70}\includegraphics[width=.32\textwidth]{fig1a-6561-140-feature_importances}}
-\subfigure[]{\label{newtopsig1-90}\includegraphics[width=.32\textwidth]{fig1a-6561-180-feature_importances}}
-\subfigure[]{\label{newtopsig1-110}\includegraphics[width=.32\textwidth]{fig1a-6561-220-feature_importances}}
-\caption{Gini topological signals obtained for experiment 1 with higher lattice sizes.
-(a) Gini topological signal for 70 unit cells.
-(b) Gini topological signal for 90 unit cells.
-(c) Gini topological signal for 110 unit cells.}
-\label{newtopsig1}
+\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_feature_importances.png}}
+\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh1_longer_lattices}
 \end{figure}
@@
 \centering
-\subfigure[]{\label{newtopsig2-70}\includegraphics[width=.32\textwidth]{fig1b-6561-140-feature_importances}}
-\subfigure[]{\label{newtopsig2-90}\includegraphics[width=.32\textwidth]{fig1b-6561-180-feature_importances}}
-\subfigure[]{\label{newtopsig2-110}\includegraphics[width=.32\textwidth]{fig1b-6561-220-feature_importances}}
-\caption{Gini topological signals obtained for experiment 2 with higher lattice sizes.
-(a) Gini topological signal for 70 unit cells.
-(b) Gini topological signal for 90 unit cells.
-(c) Gini topological signal for 110 unit cells.}
-\label{newtopsig2}
+\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_feature_importances.png}}
+\caption{Information entropy signature obtained for experiment 2 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh2_longer_lattices}
 \end{figure}
@@
 \centering
-\subfigure[]{\label{cdf1-70}\includegraphics[width=.32\textwidth]{fig1a-6561-140-cumulative_feature_importances-newer}}
-\subfigure[]{\label{cdf1-90}\includegraphics[width=.32\textwidth]{fig1a-6561-180-cumulative_feature_importances-newer}}
-\subfigure[]{\label{cdf1-110}\includegraphics[width=.32\textwidth]{fig1a-6561-220-cumulative_feature_importances-newer}}
-\caption{Cumulative Gini topological distributions (CGTDs) for higher lattice sizes in experiment 1.
-(a) CGTD for 70 unit cells.
-(b) CGTD for 90 unit cells.
-(c) CGTD for 110 unit cells.
-The two visible leaps in the cumulative Gini topological distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
+\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
+(a) Cumulative entropy distribution for 70 unit cells.
+(b) Cumulative entropy distribution for 90 unit cells.
+(c) Cumulative entropy distribution for 110 unit cells.
+The two visible leaps in the cumulative entropy distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
 \label{cdf1}
@@
 \centering
-\subfigure[]{\label{cdf2-70}\includegraphics[width=.32\textwidth]{fig1b-6561-140-cumulative_feature_importances-newer}}
-\subfigure[]{\label{cdf2-90}\includegraphics[width=.32\textwidth]{fig1b-6561-180-cumulative_feature_importances-newer}}
-\subfigure[]{\label{cdf2-110}\includegraphics[width=.32\textwidth]{fig1b-6561-220-cumulative_feature_importances-newer}}
-\caption{Cumulative Gini topological distributions (CGTDs) for higher lattice sizes in experiment 2.
-(a) CGTD for 70 unit cells.
-(b) CGTD for 90 unit cells.
-(c) CGTD for 110 unit cells.
-Here the leaps in the cumulative Gini topological distributions are less pronounced than in experiment 1, but still noticeable.
+\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
+\caption{Cumulative entropy distributions distributions for higher lattice sizes in experiment 2.
+(a) Cumulative entropy distributions for 70 unit cells.
+(b) Cumulative entropy distributions for 90 unit cells.
+(c) Cumulative entropy distributions for 110 unit cells.
+Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable.
 The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case with 50 unit cells.}

### 2020-05-05 3_simulation_with_less_features/simulation.py
Prparing to run simulation with fewer lattices

@@ -1,0 +1,461 @@
+import numpy as np
+import pandas as pd
+import os
+import matplotlib.pyplot as plt
+import graphviz
+from itertools import filterfalse
+from importlib import reload
+from itertools import chain
+from sklearn.tree import export_graphviz
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.metrics import accuracy_score
+from sklearn.base import clone
+from tqdm import tqdm
+from joblib import dump
+import csv
+import papermill as pm
+
+### Simulation directories
+SIMULATIONS_DIR = "/home/rio/ssh_simulations"
+# ssh1 simulations
+SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
+SSH1_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_100_6561")
+SSH1_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_140_6561")
+SSH1_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_180_6561")
+SSH1_PERIODIC_LESS_220_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_220_6561")
+# ssh2 simulations
+SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
+SSH2_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_100_6561")
+SSH2_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_140_6561")
+SSH2_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_180_6561")
+SSH2_PERIODIC_LESS_220_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_220_6561")
+
+### Generating simulation directories
+generate_dirs = [SIMULATIONS_DIR,
[…]

### 2020-05-05 4_results_with_less_features/simulation_results.py
Generated figures for less features

@@ -1,0 +1,900 @@
+import numpy as np
+import pandas as pd
+import os
+import matplotlib.pyplot as plt
+import graphviz
+from itertools import filterfalse
+from importlib import reload
+from itertools import chain
+from sklearn.tree import export_graphviz
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.metrics import accuracy_score
+from sklearn.base import clone
+from tqdm import tqdm
+from joblib import load
+from matplotlib.colors import ListedColormap
+from matplotlib.colors import LinearSegmentedColormap
+from collections import defaultdict
+#import json
+import csv
+
+### Simulation directories
+SIMULATIONS_DIR = "/home/rio/ssh_simulations"
+# ssh1 simulations
+SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
+SSH1_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_100_6561")
+SSH1_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_140_6561")
+SSH1_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_180_6561")
+SSH1_PERIODIC_LESS_220_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_220_6561")
+# ssh2 simulations
+SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
+SSH2_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_100_6561")
+SSH2_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_140_6561")
+SSH2_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_180_6561")
[…]

### 2020-05-06 5_paper/main.tex
Added figures for less sites to paper

--- 2020-05-05 paper/main.tex
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only 6 lattice sites $S_1$ = (1, 2, 4, 51, 52, 54) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed more than 70\% of total reduction in Shannon entropy.
-Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by 18 lattice sites $S_2$ = (1, 2, 3, 4, 5, 6, 47, 49, 50, 51, 52, 54, 95, 96, 97, 98, 99, 100) located at the three peaks in figure \ref{feature_importances_ssh2}.
+For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed more than 70\% of total reduction in Shannon entropy.
+Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
 
@@
 
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only the most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S_1$, mean accuracies were 97.1\% for training eigenvectors, 94.5\% for validation eigenvectors and 78.6\% for test eigenvectors.
-Mean accuracies obtained from eigenvector-ensembling were 98.9\% for training Hamiltonians, 98.5\% for validation Hamiltonians and 98.9\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S_2$ were 99.9\% for training eigenvectors, 96.0\% for validation eigenvectors and 63.7\% for test eigenvectors.
-Eigenvector-ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.6\% for validation Hamiltonians and 90.4\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data is still possible even for small subsets of lattice sites.
+To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
+In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
+Mean accuracies obtained from eigenvector-ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
+
+Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
+Eigenvector-ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
+
+These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
 We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
@@
 
-%\begin{figure}
-%\centering
-%\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{fig1a-6561-less-simulation_merged_winding_grid.png}}
-%\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{fig1b-6561-less-simulation_merged_winding_grid.png}}
-%\caption{Probability heatmaps learned from most relevant lattice sites.
-(a) Probability heatmap learned in experiment 1 using only lattice %sites $S_1$.
-(b) Probability heatmap learned in experiment 2 using only lattice sites $S_2$.}
-%\label{less_feat}
-%\end{figure}
+\begin{figure}
+\centering
+\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{./ssh1/periodic_less_100_6561/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{./ssh2/periodic_less_100_6561/merge_imshow_winding_grids_sim.png}}
+\caption{Phase diagrams learned from most relevant lattice sites.
+(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1 = (0, 50, 51, 99)$.
+The test set accuracy achieved using only the four lattice sites in $S'_1$ was approximately 95\%.
+(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2 = (0, 1, 3, 48, 50, 51, 96, 98, 99)$.
+The test set accuracy achieved using only the nine lattice sites in $S'_2$ was approximately 74\%.}
+\label{less_feat}
+\end{figure}
 

### 2020-05-06 5_paper/main.tex
Made small changes and revised paper

@@
 \begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems in real lattice space.
-The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector-ensembling procedure.
-We combine our algorithm with decision trees to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
+We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems from bulk data in real lattice space.
+The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
+We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
 The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
@@
 Our paper extends this task to the case of learning topological phase diagrams from input data in real space.
-Strikingly, we find that information localized on a few lattice sites in real space is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector-ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
+Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
+
+To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
 The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We demonstrate its effectiveness by combining it with decision trees to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
+We demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
 
@@
 
-The eigenvector-ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-A detailed description of the algorithm is found in the section \textbf{The eigenvector-ensembling algorithm} in the Supplementary Material.
+The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
+A detailed description of the algorithm is found in the section \textbf{The eigenvector ensembling algorithm} in the Supplementary Material.
 Here we present results of the numerical experiments we performed with it.
-We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called ssh\_1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called ssh\_2, figure \ref{ssh2}).
+We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
 
@@
 
-When generating these Hamiltonians we applied periodic boundary conditions to eliminate border effects.
+When generating the Hamiltonians we applied periodic boundary conditions to eliminate border effects.
 This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.
+The choice of periodic boundary conditions also implies that the information recovered from real space data comes from the bulk of the topological systems considered and therefore provides strong evidence for the existence of topological signatures in the bulk of such systems.
 
@@
 76.2\%) were used to compute validation scores at each iteration.
-These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from out of the test set were used for training at each iteration.
+These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
 The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
@@
 The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (98.1\%), validation eigenvectors (96.4\%) and test eigenvectors (79.4\%).
+In particular, we report mean accuracies on training eigenvectors (98.2\%), validation eigenvectors (96.4\%) and test eigenvectors (78.8\%).
 Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.3\% for test Hamiltonians.
+These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
+
+The probability heatmaps and phase diagram learned by the combination of decision trees with eigenvector ensembling used in experiment 1 are shown in figure \ref{ssh1_heatmaps}.
 
@@
 (b) Distribution of winding numbers in the training set.
-(c) Phase prediction grid learned from real space.}
+(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
 \label{figexp1_exp}
@@
 This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 50 decision trees.
+For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 25 decision trees.
 Our data set consisted of 1040 (15.8\%) test Hamiltonians.
@@
 
-Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.4\% for validation eigenvectors and 67.4\% for test eigenvectors.
-Mean accuracies resulting from eigenvector-ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 87.9\% for test Hamiltonians.
-The large accuracy gain achieved by eigenvector-ensembling in the test set (going from 67.4\% eigenvector accuracy to 87.9\% Hamiltonian accuracy) attests to its power.
+Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.1\% for validation eigenvectors and 66.4\% for test eigenvectors.
+Mean accuracies resulting from eigenvector ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 88.2\% for test Hamiltonians.
+The large accuracy gain achieved by eigenvector ensembling in the test set (going from 66.4\% eigenvector accuracy to 88.2\% Hamiltonian accuracy) attests to its power.
+
+The probability heatmaps and phase diagram learned by the combination of random forests with eigenvector ensembling used in experiment 2 are shown in figure \ref{ssh2_heatmaps}.
 
@@
 (b) Distribution of winding numbers in the training set.
-(c) Phase prediction grid learned from real space.}
+(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
 \label{figexp2_exp}
@@
 
-We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
+We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
+Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
 
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed more than 70\% of total reduction in Shannon entropy.
-Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
 
 Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector-ensembling algorithm.
+They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
 We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
@@
 To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector-ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector-ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
+In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy in experiment 1), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
+Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
+
+Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy in experiment 2) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
+Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
 
@@
 To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other lattice sites in the subset.
+This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites in the subset.
 In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
@@
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
+Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as Shannon information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
 Whether there is any relationship between local topological markers and the information entropy of the ensemble of eigenvectors is left for speculation.
 
-The eigenvector-ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
+The eigenvector ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
 This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
@@
 \caption{Information entropy signatures of the topological phase transitions from experiments 1 and 2.
-(a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for more than 70\% of reduction in information entropy.
+(a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
 These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2, the three visible peaks account for more than 30\% of reduction in information entropy.
-These three peaks are located on lattice sites $S_2$.}
+(b) In experiment 2, the three visible peaks account for approximately 30\% of reduction in information entropy.
+These three peaks are located along lattice sites $S_2$.}
 \label{feature_importances}
@@
 \caption{Phase diagrams learned from most relevant lattice sites.
-(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1 = (0, 50, 51, 99)$.
-The test set accuracy achieved using only the four lattice sites in $S'_1$ was approximately 95\%.
-(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2 = (0, 1, 3, 48, 50, 51, 96, 98, 99)$.
-The test set accuracy achieved using only the nine lattice sites in $S'_2$ was approximately 74\%.}
+(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99).
+The accuracy achieved for Hamiltonians in the test set using only the four lattice sites in $S'_1$ was approximately 95\%.
+(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99).
+The accuracy achieved for Hamiltonians in the test set using only the nine lattice sites in $S'_2$ was approximately 74\%.}
 \label{less_feat}
@@
 
-These conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
 Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \citesupp{rifai2011manifold}).
@@
 
-\subsection*{The eigenvector-ensembling algorithm}
-
-We describe here in detail each step of the eigenvector-ensembling algorithm.
+\subsection*{The eigenvector ensembling algorithm}
+
+We describe here in detail each step of the eigenvector ensembling algorithm.
 \vspace{.3cm}
@@
 These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} here we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
+\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
 More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
@@
 This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the class probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each class.
-\item[5)] \textbf{Bootstrapping:} We refine the class probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
+In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
+\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
 The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
@@
 
-The eigenvector-ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
+The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
 Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
 
-Artifacts resulting from randomization in the eigenvector-ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
+Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
 As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
-The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector-ensembling algorithm.
+The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector ensembling algorithm.
 
@@
 Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
-Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{newtopsig1} and \ref{newtopsig2}).
+Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}).
 These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
 
-It is clear from figures \ref{newtopsig1} and \ref{newtopsig2} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
-
-Figures \ref{newtopsig1} and \ref{newtopsig2} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
+
+Figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
 In the limit of an infinite chain, the cumulative entropy distribution $F_S(x)$ associated with a Shannon information entropy signal will be given by the integral of an entropy density function $\rho_S$($x$),
@@
 In this continuum limit, an information entropy signature will be given by the entropy density function $\rho_S(x)$.
-Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{newtopsig1} and \ref{newtopsig2}.
+Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}.
 
@@
 \subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_feature_importances.png}}
-\caption{Information entropy signature obtained for experiment 2 with higher lattice sizes.
+\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
 (a) Information entropy signature for 70 unit cells.
@@
 \subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
-\caption{Cumulative entropy distributions distributions for higher lattice sizes in experiment 2.
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
 (a) Cumulative entropy distributions for 70 unit cells.
@@
 Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable.
-The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case with 50 unit cells.}
+The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case of 50 unit cells.}
 \label{cdf2}

### 2020-05-07 6_prb/main.tex
Adding prb template

--- 2020-05-06 5_paper/main.tex
@@
-\documentclass[fleqn,10pt]{wlscirep}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphics, subfigure}
+%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
+\documentclass[10pt]{revtex4-1}
+\usepackage{graphicx}
+\usepackage{nicefrac}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{amsmath} 
+\usepackage{subfigure}
+\usepackage{multirow} 
+\usepackage{tabularx} 
+\usepackage{array}
+\usepackage{units}
+\usepackage{tensor} 
+\usepackage{braket}
+\usepackage{bm}
+\usepackage{hyperref}
 \usepackage[resetlabels, labeled]{multibib}
@@
 
+\renewcommand{\Re}{\operatorname{{\mathrm Re}}}
+\renewcommand{\Im}{\operatorname{{\mathrm Im}}}
+\newcommand{\tr}{\operatorname{{\mathrm tr}}}
+
+\newcommand{\hc}{^{\dagger}}
+\newcommand{\ad}{\operatorname{{\mathrm ad}}}
+\newcommand{\adn}{\ad_{\hat n}}
+\newcommand{\adx}{\ad_{\hat x}}
+\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
+\newcommand{\adp}{\ad_{\hat p}}
+\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
+\newcommand{\inbk}[1]{\left[ #1 \right]}
+\newcommand{\inbr}[1]{\left\{ #1 \right\}}
+\newcommand{\inp}[1]{\left( #1 \right)}
+\newcommand{\pd}{\partial}
+\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
+\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional
+                                %derivative
+
+\begin{document}
+\nocite{*}
+
 \title{Machine learning topological phases in real space}
 
-\author[1,2*]{N. L. Holanda}
-\author[2,3+]{M. A. R. Griffith}
-\affil[1]{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
-\affil[2]{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud, 150, Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affil[3]{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
+\author{N. L. Holanda}
+\email{linneuholanda@gmail.com, linneu@cbpf.br}
+\affiliation{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
+\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
 
-\affil[*]{linneu@cbpf.br}
+\author{M. A. S. Griffith}
+\email{griffithphys@gmail.com}
+\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
+\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
 
-\affil[+]{griffithphys@gmail.com}
+\date{\today }
 
@@
 \end{abstract}
-\begin{document}
-\nocite{*}
 
-\flushbottom
 \maketitle
-% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
-%
-%  Click the title above to edit the author information and abstract
-%
-\thispagestyle{empty}
-
-%\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
 
@@
 
-\begin{thebibliography}{10}
-\urlstyle{rm}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem{RevModPhys.82.3045}
-\bibinfo{author}{Hasan, M.~Z.} \& \bibinfo{author}{Kane, C.~L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Colloquium: Topological
-  insulators}}.
-\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
-  \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{3045--3067}
-  (\bibinfo{year}{2010}).
-
-\bibitem{CONTINENTINO2017A1}
-\bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological phase transitions}}.
-\newblock {\emph{\JournalTitle{Physica B: Condensed Matter}}}
-  \textbf{\bibinfo{volume}{505}}, \bibinfo{pages}{A1 -- A2}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.95.094509}
-\bibinfo{author}{Puel, T.~O.}, \bibinfo{author}{Sacramento, P.~D.} \&
-  \bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{$4\ensuremath{\pi}$ josephson
-  currents in junctions of hybridized multiband superconductors}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{95}},
-  \bibinfo{pages}{094509} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevE.97.012107}
-\bibinfo{author}{Griffith, M.~A.} \& \bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Casimir amplitudes in topological
-  quantum phase transitions}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. E}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{012107} (\bibinfo{year}{2018}).
-
-\bibitem{ryu2010topological}
-\bibinfo{author}{Ryu, S.}, \bibinfo{author}{Schnyder, A.~P.},
-  \bibinfo{author}{Furusaki, A.} \& \bibinfo{author}{Ludwig, A.~W.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological insulators and
-  superconductors: tenfold way and dimensional hierarchy}}.
-\newblock {\emph{\JournalTitle{New Journal of Physics}}}
-  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{065010}
-  (\bibinfo{year}{2010}).
-
-\bibitem{atala2013direct}
-\bibinfo{author}{Atala, M.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Direct measurement of the zak phase
-  in topological bloch bands}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{9}},
-  \bibinfo{pages}{795} (\bibinfo{year}{2013}).
-
-\bibitem{Stuhl1514}
-\bibinfo{author}{Stuhl, B.~K.}, \bibinfo{author}{Lu, H.-I.},
-  \bibinfo{author}{Aycock, L.~M.}, \bibinfo{author}{Genkina, D.} \&
-  \bibinfo{author}{Spielman, I.~B.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Visualizing edge states with an
-  atomic bose gas in the quantum hall regime}}.
-\newblock {\emph{\JournalTitle{Science}}} \textbf{\bibinfo{volume}{349}},
-  \bibinfo{pages}{1514--1518} (\bibinfo{year}{2015}).
-
-\bibitem{leder2016real}
-\bibinfo{author}{Leder, M.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Real-space imaging of a
-  topologically protected edge state with ultracold atoms in an
-  amplitude-chirped optical lattice}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13112} (\bibinfo{year}{2016}).
-
-\bibitem{goldman2016topological}
-\bibinfo{author}{Goldman, N.}, \bibinfo{author}{Budich, J.} \&
-  \bibinfo{author}{Zoller, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological quantum matter with
-  ultracold gases in optical lattices}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
-  \bibinfo{pages}{639} (\bibinfo{year}{2016}).
-
-\bibitem{meier2016observation}
-\bibinfo{author}{Meier, E.~J.}, \bibinfo{author}{An, F.~A.} \&
-  \bibinfo{author}{Gadway, B.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observation of the topological
-  soliton state in the su--schrieffer--heeger model}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13986} (\bibinfo{year}{2016}).
-
-\bibitem{hafezi2013imaging}
-\bibinfo{author}{Hafezi, M.}, \bibinfo{author}{Mittal, S.},
-  \bibinfo{author}{Fan, J.}, \bibinfo{author}{Migdall, A.} \&
-  \bibinfo{author}{Taylor, J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Imaging topological edge states in
-  silicon photonics}}.
-\newblock {\emph{\JournalTitle{Nature Photonics}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1001} (\bibinfo{year}{2013}).
-
-\bibitem{lu2016topological}
-\bibinfo{author}{Lu, L.}, \bibinfo{author}{Joannopoulos, J.~D.} \&
-  \bibinfo{author}{Solja{\v{c}}i{\'c}, M.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological states in photonic
-  systems}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
-  \bibinfo{pages}{626} (\bibinfo{year}{2016}).
-
-\bibitem{PhysRevX.5.031011}
-\bibinfo{author}{Peano, V.}, \bibinfo{author}{Brendel, C.},
-  \bibinfo{author}{Schmidt, M.} \& \bibinfo{author}{Marquardt, F.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological phases of sound and
-  light}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
-  \bibinfo{pages}{031011} (\bibinfo{year}{2015}).
-
-\bibitem{kitagawa2012observation}
-\bibinfo{author}{Kitagawa, T.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observation of topologically
-  protected bound states in photonic quantum walks}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{882} (\bibinfo{year}{2012}).
-
-\bibitem{cardano2016statistical}
-\bibinfo{author}{Cardano, F.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Statistical moments of quantum-walk
-  dynamics reveal topological quantum transitions}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{11439} (\bibinfo{year}{2016}).
-
-\bibitem{PhysRevX.7.031023}
-\bibinfo{author}{Flurin, E.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observing topological invariants
-  using quantum walks in superconducting circuits}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
-  \bibinfo{pages}{031023} (\bibinfo{year}{2017}).
-
-\bibitem{soluyanov2015type}
-\bibinfo{author}{Soluyanov, A.~A.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Type-ii weyl semimetals}}.
-\newblock {\emph{\JournalTitle{Nature}}} \textbf{\bibinfo{volume}{527}},
-  \bibinfo{pages}{495} (\bibinfo{year}{2015}).
-
-\bibitem{PhysRevX.5.031013}
-\bibinfo{author}{Lv, B.~Q.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Experimental discovery of weyl
-  semimetal taas}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
-  \bibinfo{pages}{031013} (\bibinfo{year}{2015}).
-
-\bibitem{PhysRevLett.42.1698}
-\bibinfo{author}{Su, W.~P.}, \bibinfo{author}{Schrieffer, J.~R.} \&
-  \bibinfo{author}{Heeger, A.~J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Solitons in polyacetylene}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{1698--1701}
-  (\bibinfo{year}{1979}).
-
-\bibitem{maffei2018topological}
-\bibinfo{author}{Maffei, M.}, \bibinfo{author}{Dauphin, A.},
-  \bibinfo{author}{Cardano, F.}, \bibinfo{author}{Lewenstein, M.} \&
-  \bibinfo{author}{Massignan, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological characterization of
-  chiral models through their long time dynamics}}.
-\newblock {\emph{\JournalTitle{New Journal of Physics}}}
-  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{013023}
-  (\bibinfo{year}{2018}).
-
-\bibitem{RevModPhys.73.681}
-\bibinfo{author}{Heeger, A.~J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Nobel lecture: Semiconducting and
-  metallic polymers: The fourth generation of polymeric materials}}.
-\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
-  \textbf{\bibinfo{volume}{73}}, \bibinfo{pages}{681--700}
-  (\bibinfo{year}{2001}).
-
-\bibitem{kane2014topological}
-\bibinfo{author}{Kane, C.} \& \bibinfo{author}{Lubensky, T.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological boundary modes in
-  isostatic lattices}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{10}},
-  \bibinfo{pages}{39} (\bibinfo{year}{2014}).
-
-\bibitem{Chen13004}
-\bibinfo{author}{Chen, B. G.-g.}, \bibinfo{author}{Upadhyaya, N.} \&
-  \bibinfo{author}{Vitelli, V.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Nonlinear conduction via solitons
-  in a topological mechanical insulator}}.
-\newblock {\emph{\JournalTitle{Proceedings of the National Academy of
-  Sciences}}} \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{13004--13009}
-  (\bibinfo{year}{2014}).
-
-\bibitem{carrasquilla2017machine}
-\bibinfo{author}{Carrasquilla, J.} \& \bibinfo{author}{Melko, R.~G.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of
-  matter}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
-  \bibinfo{pages}{431} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevX.7.031038}
-\bibinfo{author}{Ch'ng, K.}, \bibinfo{author}{Carrasquilla, J.},
-  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Khatami, E.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of strongly
-  correlated fermions}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
-  \bibinfo{pages}{031038} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.94.195105}
-\bibinfo{author}{Wang, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Discovering phase transitions with
-  unsupervised learning}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{94}},
-  \bibinfo{pages}{195105} (\bibinfo{year}{2016}).
-
-\bibitem{broecker2017machine}
-\bibinfo{author}{Broecker, P.}, \bibinfo{author}{Carrasquilla, J.},
-  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Trebst, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning quantum phases of
-  matter beyond the fermion sign problem}}.
-\newblock {\emph{\JournalTitle{Scientific reports}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{8823} (\bibinfo{year}{2017}).
-
-\bibitem{van2017learning}
-\bibinfo{author}{Van~Nieuwenburg, E.~P.}, \bibinfo{author}{Liu, Y.-H.} \&
-  \bibinfo{author}{Huber, S.~D.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Learning phase transitions by
-  confusion}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
-  \bibinfo{pages}{435} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevLett.120.066401}
-\bibinfo{author}{Zhang, P.}, \bibinfo{author}{Shen, H.} \&
-  \bibinfo{author}{Zhai, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
-  invariants with neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{066401}
-  (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.98.085402}
-\bibinfo{author}{Sun, N.}, \bibinfo{author}{Yi, J.}, \bibinfo{author}{Zhang,
-  P.}, \bibinfo{author}{Shen, H.} \& \bibinfo{author}{Zhai, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning topological
-  invariants of band insulators}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{98}},
-  \bibinfo{pages}{085402} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.97.174435}
-\bibinfo{author}{Suchsland, P.} \& \bibinfo{author}{Wessel, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Parameter diagnostics of phases and
-  phase transition learning by neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{174435} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevLett.118.216401}
-\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Quantum loop topography for machine
-  learning}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{216401}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevLett.120.257204}
-\bibinfo{author}{Venderley, J.}, \bibinfo{author}{Khemani, V.} \&
-  \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning out-of-equilibrium
-  phases of matter}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{257204}
-  (\bibinfo{year}{2018}).
-
-\bibitem{ohtsuki2017deep}
-\bibinfo{author}{Ohtsuki, T.} \& \bibinfo{author}{Ohtsuki, T.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning the quantum phase
-  transitions in random electron systems: Applications to three dimensions}}.
-\newblock {\emph{\JournalTitle{Journal of the Physical Society of Japan}}}
-  \textbf{\bibinfo{volume}{86}}, \bibinfo{pages}{044708}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.97.205110}
-\bibinfo{author}{Yoshioka, N.}, \bibinfo{author}{Akagi, Y.} \&
-  \bibinfo{author}{Katsura, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Learning disordered topological
-  phases by statistical recovery of symmetry}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{205110} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.96.195145}
-\bibinfo{author}{Deng, D.-L.}, \bibinfo{author}{Li, X.} \&
-  \bibinfo{author}{Das~Sarma, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
-  states}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
-  \bibinfo{pages}{195145} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.97.134109}
-\bibinfo{author}{Huembeli, P.}, \bibinfo{author}{Dauphin, A.} \&
-  \bibinfo{author}{Wittek, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Identifying quantum phase
-  transitions with adversarial neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{134109} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.97.115453}
-\bibinfo{author}{Carvalho, D.}, \bibinfo{author}{Garc\'{\i}a-Mart\'{\i}nez,
-  N.~A.}, \bibinfo{author}{Lado, J.~L.} \&
-  \bibinfo{author}{Fern\'andez-Rossier, J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Real-space mapping of topological
-  invariants using artificial neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{115453} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.96.245119}
-\bibinfo{author}{Zhang, Y.}, \bibinfo{author}{Melko, R.~G.} \&
-  \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning ${\mathbb{z}}_{2}$
-  quantum spin liquids with quasiparticle statistics}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
-  \bibinfo{pages}{245119} (\bibinfo{year}{2017}).
-
-\bibitem{rodriguez2018identifying}
-\bibinfo{author}{Rodriguez-Nieva, J.~F.} \& \bibinfo{author}{Scheurer, M.~S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Identifying topological order via
-  unsupervised machine learning}}.
-\newblock {\emph{\JournalTitle{arXiv preprint arXiv:1805.05961}}}
-  (\bibinfo{year}{2018}).
-
-\bibitem{breiman2017classification}
-\bibinfo{author}{Breiman, L.}, \bibinfo{author}{Friedman, J.},
-  \bibinfo{author}{Stone, C.~J.} \& \bibinfo{author}{Olshen, R.~A.}
-\newblock \emph{\bibinfo{title}{Classification and regression trees}}
-  (\bibinfo{publisher}{Chapman and Hall/CRC, London, UK},
-  \bibinfo{year}{1984}).
-
-\bibitem{Breiman2001}
-\bibinfo{author}{Breiman, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Random forests}}.
-\newblock {\emph{\JournalTitle{Machine Learning}}}
-  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{5--32} (\bibinfo{year}{2001}).
-
-\bibitem{friedman2001elements}
-\bibinfo{author}{Friedman, J.}, \bibinfo{author}{Hastie, T.} \&
-  \bibinfo{author}{Tibshirani, R.}
-\newblock \emph{\bibinfo{title}{The elements of statistical learning}}
-  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2001}).
-
-\bibitem{PhysRevB.84.241106}
-\bibinfo{author}{Bianco, R.} \& \bibinfo{author}{Resta, R.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Mapping topological order in
-  coordinate space}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{84}},
-  \bibinfo{pages}{241106} (\bibinfo{year}{2011}).
-
-\bibitem{caio2019topological}
-\bibinfo{author}{Caio, M.~D.}, \bibinfo{author}{M{\"o}ller, G.},
-  \bibinfo{author}{Cooper, N.~R.} \& \bibinfo{author}{Bhaseen, M.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological marker currents in
-  chern insulators}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \bibinfo{pages}{1}
-  (\bibinfo{year}{2019}).
-
-\bibitem{carlsson2009topology}
-\bibinfo{author}{Carlsson, G.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topology and data}}.
-\newblock {\emph{\JournalTitle{Bulletin of the American Mathematical Society}}}
-  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{255--308}
-  (\bibinfo{year}{2009}).
-
-\bibitem{wasserman2018topological}
-\bibinfo{author}{Wasserman, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological data analysis}}.
-\newblock {\emph{\JournalTitle{Annual Review of Statistics and Its
-  Application}}} \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{501--532}
-  (\bibinfo{year}{2018}).
-
-\bibitem{wang2005adaptive}
-\bibinfo{author}{Wang, J.}, \bibinfo{author}{Zhang, Z.} \&
-  \bibinfo{author}{Zha, H.}
-\newblock \bibinfo{title}{Adaptive manifold learning}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in neural information
-  processing systems}}, \bibinfo{pages}{1473--1480} (\bibinfo{year}{2005}).
-
-\bibitem{lin2008riemannian}
-\bibinfo{author}{Lin, T.} \& \bibinfo{author}{Zha, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Riemannian manifold learning}}.
-\newblock {\emph{\JournalTitle{IEEE Transactions on Pattern Analysis and
-  Machine Intelligence}}} \textbf{\bibinfo{volume}{30}},
-  \bibinfo{pages}{796--809} (\bibinfo{year}{2008}).
-
-\bibitem{belkin2003problems}
-\bibinfo{author}{Belkin, M.}
-\newblock \emph{\bibinfo{title}{Problems of learning on manifolds}}
-  (\bibinfo{publisher}{The University of Chicago, Chicago, IL, USA},
-  \bibinfo{year}{2003}).
-
-\end{thebibliography}
-
 \section*{Acknowledgements}
@@
 
-Correspondence and requests for materials should be addressed to N. L. Holanda.
+Correspondence and requests for materials should be addressed to N.
+L.
+Holanda.
+The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
 
@@
 \vspace{.3cm}
-\begin{enumerate}[topsep=0pt, partopsep=0pt]
+\begin{enumerate}%[topsep=0pt, partopsep=0pt]
 \item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
@@
 
-\newpage
-\begin{thebibliography}{1}
-\urlstyle{rm}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem{asboth2016short}
-\bibinfo{author}{Asb{\'o}th, J.~K.}, \bibinfo{author}{Oroszl{\'a}ny, L.} \&
-  \bibinfo{author}{P{\'a}lyi, A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{A short course on topological
-  insulators}}.
-\newblock {\emph{\JournalTitle{Lecture notes in physics}}}
-  \textbf{\bibinfo{volume}{919}} (\bibinfo{year}{2016}).
-
-\bibitem{goodfellow2016deep}
-\bibinfo{author}{Goodfellow, I.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Courville, A.}
-\newblock \emph{\bibinfo{title}{Deep learning}} (\bibinfo{publisher}{MIT press,
-  Cambridge, MA, USA}, \bibinfo{year}{2016}).
-
-\bibitem{bishop2006pattern}
-\bibinfo{author}{Bishop, C.~M.}
-\newblock \emph{\bibinfo{title}{Pattern recognition and machine learning}}
-  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2006}).
-
-\bibitem{cayton2005algorithms}
-\bibinfo{author}{Cayton, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Algorithms for manifold learning}}.
-\newblock {\emph{\JournalTitle{Univ. of California at San Diego Tech. Rep}}}
-  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{1} (\bibinfo{year}{2005}).
-
-\bibitem{narayanan2010sample}
-\bibinfo{author}{Narayanan, H.} \& \bibinfo{author}{Mitter, S.}
-\newblock \bibinfo{title}{Sample complexity of testing the manifold
-  hypothesis}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{1786--1794} (\bibinfo{year}{2010}).
-
-\bibitem{rifai2011manifold}
-\bibinfo{author}{Rifai, S.}, \bibinfo{author}{Dauphin, Y.~N.},
-  \bibinfo{author}{Vincent, P.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Muller, X.}
-\newblock \bibinfo{title}{The manifold tangent classifier}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{2294--2302} (\bibinfo{year}{2011}).
-
-\end{thebibliography}
 \end{document}

### 2020-05-07 6_prb/main.tex
Working on bibtex
Generated prb document with correct bibtex file

@@
 \usepackage[resetlabels, labeled]{multibib}
-\newcites{supp}{References}
+%\newcites{supp}{References}
 
@@
 
+\bibliography{bibl}{}
+%\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
+
 \section*{Acknowledgements}
@@
 
-The SSH model \citesupp{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
+The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
 This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
@@
 
-In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \citesupp{goodfellow2016deep}.
+In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
 Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
@@
 
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \citesupp{bishop2006pattern}.
+The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \cite{bishop2006pattern}.
 It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
 
-These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
-Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \citesupp{rifai2011manifold}).
+These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
 As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}).
@@
 
+%\newpage
+%\bibliographystylesupp{ieeetr}
+%\bibliographysupp{supp}
+
 \end{document}

### 2020-05-08 7_prb_submission/article/article.tex
Submitted to prb

--- 2020-05-07 6_prb/main.tex
@@
 \affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
+\affiliation{Departamento de Ci\^{e}ncias Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
 
@@
 
-These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
+These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{peng2016experimental}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
 Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.
@@
 
-\bibliography{bibl}{}
-%\bibliographystyle{plain}
-\bibliographystyle{ieeetr}
+\begin{thebibliography}{10}
+
+\bibitem{RevModPhys.82.3045}
+M.~Z. Hasan and C.~L. Kane, ``Colloquium: Topological insulators,'' {\em Rev.
+  Mod. Phys.}, vol.~82, pp.~3045--3067, Nov 2010.
+
+\bibitem{CONTINENTINO2017A1}
+M.~A. Continentino, ``Topological phase transitions,'' {\em Physica B:
+  Condensed Matter}, vol.~505, pp.~A1 -- A2, 2017.
+
+\bibitem{PhysRevB.95.094509}
+T.~O. Puel, P.~D. Sacramento, and M.~A. Continentino, ``$4\ensuremath{\pi}$
+  josephson currents in junctions of hybridized multiband superconductors,''
+  {\em Phys. Rev. B}, vol.~95, p.~094509, Mar 2017.
+
+\bibitem{PhysRevE.97.012107}
+M.~A. Griffith and M.~A. Continentino, ``Casimir amplitudes in topological
+  quantum phase transitions,'' {\em Phys. Rev. E}, vol.~97, p.~012107, Jan
+  2018.
+
+\bibitem{ryu2010topological}
+S.~Ryu, A.~P. Schnyder, A.~Furusaki, and A.~W. Ludwig, ``Topological insulators
+  and superconductors: tenfold way and dimensional hierarchy,'' {\em New
+  Journal of Physics}, vol.~12, no.~6, p.~065010, 2010.
+
+\bibitem{atala2013direct}
+M.~Atala, M.~Aidelsburger, J.~T. Barreiro, D.~Abanin, T.~Kitagawa, E.~Demler,
+  and I.~Bloch, ``Direct measurement of the zak phase in topological bloch
+  bands,'' {\em Nature Physics}, vol.~9, no.~12, p.~795, 2013.
+
+\bibitem{Stuhl1514}
+B.~K. Stuhl, H.-I. Lu, L.~M. Aycock, D.~Genkina, and I.~B. Spielman,
+  ``Visualizing edge states with an atomic bose gas in the quantum hall
+  regime,'' {\em Science}, vol.~349, no.~6255, pp.~1514--1518, 2015.
+
+\bibitem{leder2016real}
+M.~Leder, C.~Grossert, L.~Sitta, M.~Genske, A.~Rosch, and M.~Weitz,
+  ``Real-space imaging of a topologically protected edge state with ultracold
+  atoms in an amplitude-chirped optical lattice,'' {\em Nature communications},
+  vol.~7, p.~13112, 2016.
+
+\bibitem{goldman2016topological}
+N.~Goldman, J.~Budich, and P.~Zoller, ``Topological quantum matter with
+  ultracold gases in optical lattices,'' {\em Nature Physics}, vol.~12, no.~7,
+  p.~639, 2016.
+
+\bibitem{meier2016observation}
+E.~J. Meier, F.~A. An, and B.~Gadway, ``Observation of the topological soliton
+  state in the su--schrieffer--heeger model,'' {\em Nature communications},
+  vol.~7, p.~13986, 2016.
+
+\bibitem{hafezi2013imaging}
+M.~Hafezi, S.~Mittal, J.~Fan, A.~Migdall, and J.~Taylor, ``Imaging topological
+  edge states in silicon photonics,'' {\em Nature Photonics}, vol.~7, no.~12,
+  p.~1001, 2013.
+
+\bibitem{rechtsman2013photonic}
+M.~C. Rechtsman, J.~M. Zeuner, Y.~Plotnik, Y.~Lumer, D.~Podolsky, F.~Dreisow,
+  S.~Nolte, M.~Segev, and A.~Szameit, ``Photonic floquet topological
+  insulators,'' {\em Nature}, vol.~496, no.~7444, p.~196, 2013.
+
+\bibitem{lu2016topological}
+L.~Lu, J.~D. Joannopoulos, and M.~Solja{\v{c}}i{\'c}, ``Topological states in
+  photonic systems,'' {\em Nature Physics}, vol.~12, no.~7, p.~626, 2016.
+
+\bibitem{PhysRevX.5.031011}
+V.~Peano, C.~Brendel, M.~Schmidt, and F.~Marquardt, ``Topological phases of
+  sound and light,'' {\em Phys. Rev. X}, vol.~5, p.~031011, Jul 2015.
+
+\bibitem{peng2016experimental}
+Y.-G. Peng, C.-Z. Qin, D.-G. Zhao, Y.-X. Shen, X.-Y. Xu, M.~Bao, H.~Jia, and
+  X.-F. Zhu, ``Experimental demonstration of anomalous floquet topological
+  insulator for sound,'' {\em Nature communications}, vol.~7, p.~13368, 2016.
+
+\bibitem{kitagawa2012observation}
+T.~Kitagawa, M.~A. Broome, A.~Fedrizzi, M.~S. Rudner, E.~Berg, I.~Kassal,
+  A.~Aspuru-Guzik, E.~Demler, and A.~G. White, ``Observation of topologically
+  protected bound states in photonic quantum walks,'' {\em Nature
+  communications}, vol.~3, p.~882, 2012.
+
+\bibitem{cardano2016statistical}
+F.~Cardano, M.~Maffei, F.~Massa, B.~Piccirillo, C.~De~Lisio, G.~De~Filippis,
+  V.~Cataudella, E.~Santamato, and L.~Marrucci, ``Statistical moments of
+  quantum-walk dynamics reveal topological quantum transitions,'' {\em Nature
+  communications}, vol.~7, p.~11439, 2016.
+
+\bibitem{PhysRevX.7.031023}
+E.~Flurin, V.~V. Ramasesh, S.~Hacohen-Gourgy, L.~S. Martin, N.~Y. Yao, and
+  I.~Siddiqi, ``Observing topological invariants using quantum walks in
+  superconducting circuits,'' {\em Phys. Rev. X}, vol.~7, p.~031023, Aug 2017.
+
+\bibitem{soluyanov2015type}
+A.~A. Soluyanov, D.~Gresch, Z.~Wang, Q.~Wu, M.~Troyer, X.~Dai, and B.~A.
+  Bernevig, ``Type-ii weyl semimetals,'' {\em Nature}, vol.~527, no.~7579,
+  p.~495, 2015.
+
+\bibitem{PhysRevX.5.031013}
+B.~Q. Lv, H.~M. Weng, B.~B. Fu, X.~P. Wang, H.~Miao, J.~Ma, P.~Richard, X.~C.
+  Huang, L.~X. Zhao, G.~F. Chen, Z.~Fang, X.~Dai, T.~Qian, and H.~Ding,
+  ``Experimental discovery of weyl semimetal taas,'' {\em Phys. Rev. X},
+  vol.~5, p.~031013, Jul 2015.
+
+\bibitem{PhysRevLett.42.1698}
+W.~P. Su, J.~R. Schrieffer, and A.~J. Heeger, ``Solitons in polyacetylene,''
+  {\em Phys. Rev. Lett.}, vol.~42, pp.~1698--1701, Jun 1979.
+
+\bibitem{maffei2018topological}
+M.~Maffei, A.~Dauphin, F.~Cardano, M.~Lewenstein, and P.~Massignan,
+  ``Topological characterization of chiral models through their long time
+  dynamics,'' {\em New Journal of Physics}, vol.~20, no.~1, p.~013023, 2018.
+
+\bibitem{RevModPhys.73.681}
+A.~J. Heeger, ``Nobel lecture: Semiconducting and metallic polymers: The fourth
+  generation of polymeric materials,'' {\em Rev. Mod. Phys.}, vol.~73,
+  pp.~681--700, Sep 2001.
+
+\bibitem{kane2014topological}
+C.~Kane and T.~Lubensky, ``Topological boundary modes in isostatic lattices,''
+  {\em Nature Physics}, vol.~10, no.~1, p.~39, 2014.
+
+\bibitem{Chen13004}
+B.~G.-g. Chen, N.~Upadhyaya, and V.~Vitelli, ``Nonlinear conduction via
+  solitons in a topological mechanical insulator,'' {\em Proceedings of the
+  National Academy of Sciences}, vol.~111, no.~36, pp.~13004--13009, 2014.
+
+\bibitem{carrasquilla2017machine}
+J.~Carrasquilla and R.~G. Melko, ``Machine learning phases of matter,'' {\em
+  Nature Physics}, vol.~13, no.~5, p.~431, 2017.
+
+\bibitem{PhysRevX.7.031038}
+K.~Ch'ng, J.~Carrasquilla, R.~G. Melko, and E.~Khatami, ``Machine learning
+  phases of strongly correlated fermions,'' {\em Phys. Rev. X}, vol.~7,
+  p.~031038, Aug 2017.
+
+\bibitem{PhysRevB.94.195105}
+L.~Wang, ``Discovering phase transitions with unsupervised learning,'' {\em
+  Phys. Rev. B}, vol.~94, p.~195105, Nov 2016.
+
+\bibitem{broecker2017machine}
+P.~Broecker, J.~Carrasquilla, R.~G. Melko, and S.~Trebst, ``Machine learning
+  quantum phases of matter beyond the fermion sign problem,'' {\em Scientific
+  reports}, vol.~7, no.~1, p.~8823, 2017.
+
+\bibitem{van2017learning}
+E.~P. Van~Nieuwenburg, Y.-H. Liu, and S.~D. Huber, ``Learning phase transitions
+  by confusion,'' {\em Nature Physics}, vol.~13, no.~5, p.~435, 2017.
+
+\bibitem{PhysRevLett.120.066401}
+P.~Zhang, H.~Shen, and H.~Zhai, ``Machine learning topological invariants with
+  neural networks,'' {\em Phys. Rev. Lett.}, vol.~120, p.~066401, Feb 2018.
+
+\bibitem{PhysRevB.98.085402}
+N.~Sun, J.~Yi, P.~Zhang, H.~Shen, and H.~Zhai, ``Deep learning topological
+  invariants of band insulators,'' {\em Phys. Rev. B}, vol.~98, p.~085402, Aug
+  2018.
+
+\bibitem{PhysRevB.97.174435}
+P.~Suchsland and S.~Wessel, ``Parameter diagnostics of phases and phase
+  transition learning by neural networks,'' {\em Phys. Rev. B}, vol.~97,
+  p.~174435, May 2018.
+
+\bibitem{PhysRevLett.120.257204}
+J.~Venderley, V.~Khemani, and E.-A. Kim, ``Machine learning out-of-equilibrium
+  phases of matter,'' {\em Phys. Rev. Lett.}, vol.~120, p.~257204, Jun 2018.
+
+\bibitem{PhysRevB.97.205110}
+N.~Yoshioka, Y.~Akagi, and H.~Katsura, ``Learning disordered topological phases
+  by statistical recovery of symmetry,'' {\em Phys. Rev. B}, vol.~97,
+  p.~205110, May 2018.
+
+\bibitem{PhysRevB.96.195145}
+D.-L. Deng, X.~Li, and S.~Das~Sarma, ``Machine learning topological states,''
+  {\em Phys. Rev. B}, vol.~96, p.~195145, Nov 2017.
+
+\bibitem{PhysRevB.97.134109}
+P.~Huembeli, A.~Dauphin, and P.~Wittek, ``Identifying quantum phase transitions
+  with adversarial neural networks,'' {\em Phys. Rev. B}, vol.~97, p.~134109,
+  Apr 2018.
+
+\bibitem{PhysRevB.97.115453}
+D.~Carvalho, N.~A. Garc\'{\i}a-Mart\'{\i}nez, J.~L. Lado, and
+  J.~Fern\'andez-Rossier, ``Real-space mapping of topological invariants using
+  artificial neural networks,'' {\em Phys. Rev. B}, vol.~97, p.~115453, Mar
+  2018.
+
+\bibitem{PhysRevB.96.245119}
+Y.~Zhang, R.~G. Melko, and E.-A. Kim, ``Machine learning ${\mathbb{z}}_{2}$
+  quantum spin liquids with quasiparticle statistics,'' {\em Phys. Rev. B},
+  vol.~96, p.~245119, Dec 2017.
+
+\bibitem{rodriguez2018identifying}
+J.~F. Rodriguez-Nieva and M.~S. Scheurer, ``Identifying topological order via
+  unsupervised machine learning,'' {\em arXiv preprint arXiv:1805.05961}, 2018.
+
+\bibitem{breiman2017classification}
+L.~Breiman, J.~Friedman, C.~J. Stone, and R.~A. Olshen, {\em Classification and
+  regression trees}.
+\newblock Chapman and Hall/CRC, 1984.
+
+\bibitem{Breiman2001}
+L.~Breiman, ``Random forests,'' {\em Machine Learning}, vol.~45, pp.~5--32, Oct
+  2001.
+
+\bibitem{friedman2001elements}
+J.~Friedman, T.~Hastie, and R.~Tibshirani, {\em The elements of statistical
+  learning}.
+\newblock Springer New York, NY, USA:, 2001.
+
+\bibitem{PhysRevB.84.241106}
+R.~Bianco and R.~Resta, ``Mapping topological order in coordinate space,'' {\em
+  Phys. Rev. B}, vol.~84, p.~241106, Dec 2011.
+
+\bibitem{caio2019topological}
+M.~D. Caio, G.~M{\"o}ller, N.~R. Cooper, and M.~Bhaseen, ``Topological marker
+  currents in chern insulators,'' {\em Nature Physics}, p.~1, 2019.
+
+\bibitem{carlsson2009topology}
+G.~Carlsson, ``Topology and data,'' {\em Bulletin of the American Mathematical
+  Society}, vol.~46, no.~2, pp.~255--308, 2009.
+
+\bibitem{wasserman2018topological}
+L.~Wasserman, ``Topological data analysis,'' {\em Annual Review of Statistics
+  and Its Application}, vol.~5, pp.~501--532, 2018.
+
+\bibitem{wang2005adaptive}
+J.~Wang, Z.~Zhang, and H.~Zha, ``Adaptive manifold learning,'' in {\em Advances
+  in neural information processing systems}, pp.~1473--1480, 2005.
+
+\bibitem{lin2008riemannian}
+T.~Lin and H.~Zha, ``Riemannian manifold learning,'' {\em IEEE Transactions on
+  Pattern Analysis and Machine Intelligence}, vol.~30, no.~5, pp.~796--809,
+  2008.
+
+\bibitem{belkin2003problems}
+M.~Belkin, {\em Problems of learning on manifolds}.
+\newblock The University of Chicago, 2003.
+
+\end{thebibliography}
 
@@
 
-\newpage
-
-\begin{figure}
-  \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/ssh_model.pdf}
-  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
-\label{fig:model}
-\end{figure}
-
-\begin{figure}%[h!]
-  \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/winding.png}
-  \caption{Winding number.
-The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point.
-Picture credits: Jim Belk, public domain.}
-\label{fig:winding}
-\end{figure}
-
-\section*{Supplementary Material}
-\subsection*{The SSH model}
-\label{sshapp}
-
-The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
-This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
-This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
-\begin{equation}
-\label{SSH}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-where the column vector
-\begin{equation*}
-\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
-\end{equation*}
-contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
-\begin{equation*}
-\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
-\end{equation*}
-contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
-Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.
-
-The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
-We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics.
-As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
-\begin{equation}\label{hmatrix}
-H(t_1,t_2,T_1,T_2)=\left(
-  \begin{array}{cccccc}
-    0 & t_1 & 0 & T_1 & 0 & \cdots \\
-    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
-    0 & t_2 & 0 & t_1 & 0 & \cdots\\
-    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
-    0 & T_2 & 0 & t_2 &  0& \cdots\\
-    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
-  \end{array}
-  \right)_{N \times N}.
-\end{equation}
-Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
-Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.
-
-The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
-This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
-This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system.
-In the particular case of the SSH model, the topological invariant used to classify the topological phases is the winding number.
-
-The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
-It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative).
-Figure \ref{fig:winding} shows several closed, oriented curves and their winding numbers computed with respect to a given point.
-
-An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
-This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a very challenging task.
-
-For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
-\begin{equation}\label{winding_number}
-W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
-\end{equation}
-where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\hat{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
-Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure \ref{fig:phasediagrams}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{./ssh1/periodic_less_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{./ssh2/periodic_less_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Phase diagrams learned from most relevant lattice sites.
-(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99).
-The accuracy achieved for Hamiltonians in the test set using only the four lattice sites in $S'_1$ was approximately 95\%.
-(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99).
-The accuracy achieved for Hamiltonians in the test set using only the nine lattice sites in $S'_2$ was approximately 74\%.}
-\label{less_feat}
-\end{figure}
-
-\subsection*{Learning topological phases from real space data}
-
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
-
-Our reasoning goes as follows.
-First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
-Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space.
-Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.
-
-In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
-Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
-\begin{equation}
-\label{localconstancy}
-W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
-\end{equation}
-
-That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure \ref{fig:phasediagrams}, where we draw phase diagrams of SSH models with first-neighbor (figure \ref{ssh1}) and first- and second-neighbor (figure \ref{ssh2}) hoppings.
-In figure \ref{ssh1} for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
-Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.
-
-It does not immediately follow, however, that the same strategy will be successful in real space.
-Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,
-
-\begin{equation}
-\label{parameter_to_real}
-\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
-\end{equation}
-where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
-The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.
-
-This fact is well illustrated by the numerical experiments discussed in the article.
-Although it may seem from figures \ref{figexp1_exp:b} and \ref{figexp2_exp:b} in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
-In such high-dimensional spaces, the data should be much sparser.
-
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \cite{bishop2006pattern}.
-It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
-
-These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
-Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
-As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}).
-In this sense, key topological information can be said to be localized on few lattice sites.
-
-\subsection*{The eigenvector ensembling algorithm}
-
-We describe here in detail each step of the eigenvector ensembling algorithm.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
-\vspace{.3cm}
-In this work we implemented the eigenvector ensembling algorithm with Python's Scikit tools.
-
-\subsection*{Information entropy signatures in the macroscopic limit}
-
-A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
-
-The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
-Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
-
-Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
-As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
-The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector ensembling algorithm.
-
-There are still artifacts that might arise from the hyperparameters used to generate the data.
-These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space).
-Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive.
-Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the information entropy signatures is lattice size.
-
-All results presented in the article were obtained for lattices with 50 unit cells.
-Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
-Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}).
-These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
-
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
-
-Figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
-In the limit of an infinite chain, the cumulative entropy distribution $F_S(x)$ associated with a Shannon information entropy signal will be given by the integral of an entropy density function $\rho_S$($x$),
-
-\begin{equation}
-\label{entropy_dens}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
-\end{equation}
-where $x$ $\in$ [0,1] is a spatial coordinate along the lattice (being strict, our use of periodic boundary conditions implies that the coordinate $x$ should be defined in the quotient space $[0,1]/R$, where $R$ is the equivalence relation in [0,1] defining the unit circle $S^1$, i.e.
-$x$ $R$ $x'$ if and only if $x$ = $x'$ or ($x$,$x'$) $\in$ \{(0,1), (1,0)\}.
-For open boundary conditions, the spatial coordinate $x$ is defined in the closed interval [0,1]).
-In this continuum limit, an information entropy signature will be given by the entropy density function $\rho_S(x)$.
-Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}.
-
-The results presented in this article suggest that the macroscopic limit $\rho_S(x)$ of the information entropy signatures may have strong theoretical interest and pave new roads to the investigation of topological materials.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_feature_importances.png}}
-\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
-(a) Information entropy signature for 70 unit cells.
-(b) Information entropy signature for 90 unit cells.
-(c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh1_longer_lattices}
-\end{figure}
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_feature_importances.png}}
-\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
-(a) Information entropy signature for 70 unit cells.
-(b) Information entropy signature for 90 unit cells.
-(c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh2_longer_lattices}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
-(a) Cumulative entropy distribution for 70 unit cells.
-(b) Cumulative entropy distribution for 90 unit cells.
-(c) Cumulative entropy distribution for 110 unit cells.
-The two visible leaps in the cumulative entropy distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
-\label{cdf1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
-(a) Cumulative entropy distributions for 70 unit cells.
-(b) Cumulative entropy distributions for 90 unit cells.
-(c) Cumulative entropy distributions for 110 unit cells.
-Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable.
-The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case of 50 unit cells.}
-\label{cdf2}
-\end{figure}
-
 %\newpage

### 2020-05-09 5_paper/main.tex
Added github reference to paper
Updated email in paper
Fine adjustments in 8_prb_submission

@@
 \usepackage{graphics, subfigure}
-\usepackage[resetlabels, labeled]{multibib}
-\newcites{supp}{References}
+%\usepackage[resetlabels, labeled]{multibib}
+%\newcites{supp}{References}
 
@@
 
-\affil[*]{linneu@cbpf.br}
+\affil[*]{linneuholanda@gmail.com, linneu@cbpf.br}
 
@@
 
-\begin{thebibliography}{10}
-\urlstyle{rm}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem{RevModPhys.82.3045}
-\bibinfo{author}{Hasan, M.~Z.} \& \bibinfo{author}{Kane, C.~L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Colloquium: Topological
-  insulators}}.
-\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
-  \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{3045--3067}
-  (\bibinfo{year}{2010}).
-
-\bibitem{CONTINENTINO2017A1}
-\bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological phase transitions}}.
-\newblock {\emph{\JournalTitle{Physica B: Condensed Matter}}}
-  \textbf{\bibinfo{volume}{505}}, \bibinfo{pages}{A1 -- A2}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.95.094509}
-\bibinfo{author}{Puel, T.~O.}, \bibinfo{author}{Sacramento, P.~D.} \&
-  \bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{$4\ensuremath{\pi}$ josephson
-  currents in junctions of hybridized multiband superconductors}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{95}},
-  \bibinfo{pages}{094509} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevE.97.012107}
-\bibinfo{author}{Griffith, M.~A.} \& \bibinfo{author}{Continentino, M.~A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Casimir amplitudes in topological
-  quantum phase transitions}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. E}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{012107} (\bibinfo{year}{2018}).
-
-\bibitem{ryu2010topological}
-\bibinfo{author}{Ryu, S.}, \bibinfo{author}{Schnyder, A.~P.},
-  \bibinfo{author}{Furusaki, A.} \& \bibinfo{author}{Ludwig, A.~W.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological insulators and
-  superconductors: tenfold way and dimensional hierarchy}}.
-\newblock {\emph{\JournalTitle{New Journal of Physics}}}
-  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{065010}
-  (\bibinfo{year}{2010}).
-
-\bibitem{atala2013direct}
-\bibinfo{author}{Atala, M.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Direct measurement of the zak phase
-  in topological bloch bands}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{9}},
-  \bibinfo{pages}{795} (\bibinfo{year}{2013}).
-
-\bibitem{Stuhl1514}
-\bibinfo{author}{Stuhl, B.~K.}, \bibinfo{author}{Lu, H.-I.},
-  \bibinfo{author}{Aycock, L.~M.}, \bibinfo{author}{Genkina, D.} \&
-  \bibinfo{author}{Spielman, I.~B.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Visualizing edge states with an
-  atomic bose gas in the quantum hall regime}}.
-\newblock {\emph{\JournalTitle{Science}}} \textbf{\bibinfo{volume}{349}},
-  \bibinfo{pages}{1514--1518} (\bibinfo{year}{2015}).
-
-\bibitem{leder2016real}
-\bibinfo{author}{Leder, M.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Real-space imaging of a
-  topologically protected edge state with ultracold atoms in an
-  amplitude-chirped optical lattice}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13112} (\bibinfo{year}{2016}).
-
-\bibitem{goldman2016topological}
-\bibinfo{author}{Goldman, N.}, \bibinfo{author}{Budich, J.} \&
-  \bibinfo{author}{Zoller, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological quantum matter with
-  ultracold gases in optical lattices}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
-  \bibinfo{pages}{639} (\bibinfo{year}{2016}).
-
-\bibitem{meier2016observation}
-\bibinfo{author}{Meier, E.~J.}, \bibinfo{author}{An, F.~A.} \&
-  \bibinfo{author}{Gadway, B.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observation of the topological
-  soliton state in the su--schrieffer--heeger model}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{13986} (\bibinfo{year}{2016}).
-
-\bibitem{hafezi2013imaging}
-\bibinfo{author}{Hafezi, M.}, \bibinfo{author}{Mittal, S.},
-  \bibinfo{author}{Fan, J.}, \bibinfo{author}{Migdall, A.} \&
-  \bibinfo{author}{Taylor, J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Imaging topological edge states in
-  silicon photonics}}.
-\newblock {\emph{\JournalTitle{Nature Photonics}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1001} (\bibinfo{year}{2013}).
-
-\bibitem{lu2016topological}
-\bibinfo{author}{Lu, L.}, \bibinfo{author}{Joannopoulos, J.~D.} \&
-  \bibinfo{author}{Solja{\v{c}}i{\'c}, M.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological states in photonic
-  systems}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{12}},
-  \bibinfo{pages}{626} (\bibinfo{year}{2016}).
-
-\bibitem{PhysRevX.5.031011}
-\bibinfo{author}{Peano, V.}, \bibinfo{author}{Brendel, C.},
-  \bibinfo{author}{Schmidt, M.} \& \bibinfo{author}{Marquardt, F.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological phases of sound and
-  light}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
-  \bibinfo{pages}{031011} (\bibinfo{year}{2015}).
-
-\bibitem{kitagawa2012observation}
-\bibinfo{author}{Kitagawa, T.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observation of topologically
-  protected bound states in photonic quantum walks}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{882} (\bibinfo{year}{2012}).
-
-\bibitem{cardano2016statistical}
-\bibinfo{author}{Cardano, F.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Statistical moments of quantum-walk
-  dynamics reveal topological quantum transitions}}.
-\newblock {\emph{\JournalTitle{Nature communications}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{11439} (\bibinfo{year}{2016}).
-
-\bibitem{PhysRevX.7.031023}
-\bibinfo{author}{Flurin, E.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Observing topological invariants
-  using quantum walks in superconducting circuits}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
-  \bibinfo{pages}{031023} (\bibinfo{year}{2017}).
-
-\bibitem{soluyanov2015type}
-\bibinfo{author}{Soluyanov, A.~A.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Type-ii weyl semimetals}}.
-\newblock {\emph{\JournalTitle{Nature}}} \textbf{\bibinfo{volume}{527}},
-  \bibinfo{pages}{495} (\bibinfo{year}{2015}).
-
-\bibitem{PhysRevX.5.031013}
-\bibinfo{author}{Lv, B.~Q.} \emph{et~al.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Experimental discovery of weyl
-  semimetal taas}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{5}},
-  \bibinfo{pages}{031013} (\bibinfo{year}{2015}).
-
-\bibitem{PhysRevLett.42.1698}
-\bibinfo{author}{Su, W.~P.}, \bibinfo{author}{Schrieffer, J.~R.} \&
-  \bibinfo{author}{Heeger, A.~J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Solitons in polyacetylene}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{1698--1701}
-  (\bibinfo{year}{1979}).
-
-\bibitem{maffei2018topological}
-\bibinfo{author}{Maffei, M.}, \bibinfo{author}{Dauphin, A.},
-  \bibinfo{author}{Cardano, F.}, \bibinfo{author}{Lewenstein, M.} \&
-  \bibinfo{author}{Massignan, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological characterization of
-  chiral models through their long time dynamics}}.
-\newblock {\emph{\JournalTitle{New Journal of Physics}}}
-  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{013023}
-  (\bibinfo{year}{2018}).
-
-\bibitem{RevModPhys.73.681}
-\bibinfo{author}{Heeger, A.~J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Nobel lecture: Semiconducting and
-  metallic polymers: The fourth generation of polymeric materials}}.
-\newblock {\emph{\JournalTitle{Rev. Mod. Phys.}}}
-  \textbf{\bibinfo{volume}{73}}, \bibinfo{pages}{681--700}
-  (\bibinfo{year}{2001}).
-
-\bibitem{kane2014topological}
-\bibinfo{author}{Kane, C.} \& \bibinfo{author}{Lubensky, T.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological boundary modes in
-  isostatic lattices}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{10}},
-  \bibinfo{pages}{39} (\bibinfo{year}{2014}).
-
-\bibitem{Chen13004}
-\bibinfo{author}{Chen, B. G.-g.}, \bibinfo{author}{Upadhyaya, N.} \&
-  \bibinfo{author}{Vitelli, V.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Nonlinear conduction via solitons
-  in a topological mechanical insulator}}.
-\newblock {\emph{\JournalTitle{Proceedings of the National Academy of
-  Sciences}}} \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{13004--13009}
-  (\bibinfo{year}{2014}).
-
-\bibitem{carrasquilla2017machine}
-\bibinfo{author}{Carrasquilla, J.} \& \bibinfo{author}{Melko, R.~G.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of
-  matter}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
-  \bibinfo{pages}{431} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevX.7.031038}
-\bibinfo{author}{Ch'ng, K.}, \bibinfo{author}{Carrasquilla, J.},
-  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Khatami, E.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning phases of strongly
-  correlated fermions}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. X}}} \textbf{\bibinfo{volume}{7}},
-  \bibinfo{pages}{031038} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.94.195105}
-\bibinfo{author}{Wang, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Discovering phase transitions with
-  unsupervised learning}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{94}},
-  \bibinfo{pages}{195105} (\bibinfo{year}{2016}).
-
-\bibitem{broecker2017machine}
-\bibinfo{author}{Broecker, P.}, \bibinfo{author}{Carrasquilla, J.},
-  \bibinfo{author}{Melko, R.~G.} \& \bibinfo{author}{Trebst, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning quantum phases of
-  matter beyond the fermion sign problem}}.
-\newblock {\emph{\JournalTitle{Scientific reports}}}
-  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{8823} (\bibinfo{year}{2017}).
-
-\bibitem{van2017learning}
-\bibinfo{author}{Van~Nieuwenburg, E.~P.}, \bibinfo{author}{Liu, Y.-H.} \&
-  \bibinfo{author}{Huber, S.~D.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Learning phase transitions by
-  confusion}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \textbf{\bibinfo{volume}{13}},
-  \bibinfo{pages}{435} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevLett.120.066401}
-\bibinfo{author}{Zhang, P.}, \bibinfo{author}{Shen, H.} \&
-  \bibinfo{author}{Zhai, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
-  invariants with neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{066401}
-  (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.98.085402}
-\bibinfo{author}{Sun, N.}, \bibinfo{author}{Yi, J.}, \bibinfo{author}{Zhang,
-  P.}, \bibinfo{author}{Shen, H.} \& \bibinfo{author}{Zhai, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning topological
-  invariants of band insulators}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{98}},
-  \bibinfo{pages}{085402} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.97.174435}
-\bibinfo{author}{Suchsland, P.} \& \bibinfo{author}{Wessel, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Parameter diagnostics of phases and
-  phase transition learning by neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{174435} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevLett.118.216401}
-\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Quantum loop topography for machine
-  learning}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{216401}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevLett.120.257204}
-\bibinfo{author}{Venderley, J.}, \bibinfo{author}{Khemani, V.} \&
-  \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning out-of-equilibrium
-  phases of matter}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. Lett.}}}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{257204}
-  (\bibinfo{year}{2018}).
-
-\bibitem{ohtsuki2017deep}
-\bibinfo{author}{Ohtsuki, T.} \& \bibinfo{author}{Ohtsuki, T.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Deep learning the quantum phase
-  transitions in random electron systems: Applications to three dimensions}}.
-\newblock {\emph{\JournalTitle{Journal of the Physical Society of Japan}}}
-  \textbf{\bibinfo{volume}{86}}, \bibinfo{pages}{044708}
-  (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.97.205110}
-\bibinfo{author}{Yoshioka, N.}, \bibinfo{author}{Akagi, Y.} \&
-  \bibinfo{author}{Katsura, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Learning disordered topological
-  phases by statistical recovery of symmetry}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{205110} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.96.195145}
-\bibinfo{author}{Deng, D.-L.}, \bibinfo{author}{Li, X.} \&
-  \bibinfo{author}{Das~Sarma, S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning topological
-  states}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
-  \bibinfo{pages}{195145} (\bibinfo{year}{2017}).
-
-\bibitem{PhysRevB.97.134109}
-\bibinfo{author}{Huembeli, P.}, \bibinfo{author}{Dauphin, A.} \&
-  \bibinfo{author}{Wittek, P.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Identifying quantum phase
-  transitions with adversarial neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{134109} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.97.115453}
-\bibinfo{author}{Carvalho, D.}, \bibinfo{author}{Garc\'{\i}a-Mart\'{\i}nez,
-  N.~A.}, \bibinfo{author}{Lado, J.~L.} \&
-  \bibinfo{author}{Fern\'andez-Rossier, J.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Real-space mapping of topological
-  invariants using artificial neural networks}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{97}},
-  \bibinfo{pages}{115453} (\bibinfo{year}{2018}).
-
-\bibitem{PhysRevB.96.245119}
-\bibinfo{author}{Zhang, Y.}, \bibinfo{author}{Melko, R.~G.} \&
-  \bibinfo{author}{Kim, E.-A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Machine learning ${\mathbb{z}}_{2}$
-  quantum spin liquids with quasiparticle statistics}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{96}},
-  \bibinfo{pages}{245119} (\bibinfo{year}{2017}).
-
-\bibitem{rodriguez2018identifying}
-\bibinfo{author}{Rodriguez-Nieva, J.~F.} \& \bibinfo{author}{Scheurer, M.~S.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Identifying topological order via
-  unsupervised machine learning}}.
-\newblock {\emph{\JournalTitle{arXiv preprint arXiv:1805.05961}}}
-  (\bibinfo{year}{2018}).
-
-\bibitem{breiman2017classification}
-\bibinfo{author}{Breiman, L.}, \bibinfo{author}{Friedman, J.},
-  \bibinfo{author}{Stone, C.~J.} \& \bibinfo{author}{Olshen, R.~A.}
-\newblock \emph{\bibinfo{title}{Classification and regression trees}}
-  (\bibinfo{publisher}{Chapman and Hall/CRC, London, UK},
-  \bibinfo{year}{1984}).
-
-\bibitem{Breiman2001}
-\bibinfo{author}{Breiman, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Random forests}}.
-\newblock {\emph{\JournalTitle{Machine Learning}}}
-  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{5--32} (\bibinfo{year}{2001}).
-
-\bibitem{friedman2001elements}
-\bibinfo{author}{Friedman, J.}, \bibinfo{author}{Hastie, T.} \&
-  \bibinfo{author}{Tibshirani, R.}
-\newblock \emph{\bibinfo{title}{The elements of statistical learning}}
-  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2001}).
-
-\bibitem{PhysRevB.84.241106}
-\bibinfo{author}{Bianco, R.} \& \bibinfo{author}{Resta, R.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Mapping topological order in
-  coordinate space}}.
-\newblock {\emph{\JournalTitle{Phys. Rev. B}}} \textbf{\bibinfo{volume}{84}},
-  \bibinfo{pages}{241106} (\bibinfo{year}{2011}).
-
-\bibitem{caio2019topological}
-\bibinfo{author}{Caio, M.~D.}, \bibinfo{author}{M{\"o}ller, G.},
-  \bibinfo{author}{Cooper, N.~R.} \& \bibinfo{author}{Bhaseen, M.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological marker currents in
-  chern insulators}}.
-\newblock {\emph{\JournalTitle{Nature Physics}}} \bibinfo{pages}{1}
-  (\bibinfo{year}{2019}).
-
-\bibitem{carlsson2009topology}
-\bibinfo{author}{Carlsson, G.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topology and data}}.
-\newblock {\emph{\JournalTitle{Bulletin of the American Mathematical Society}}}
-  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{255--308}
-  (\bibinfo{year}{2009}).
-
-\bibitem{wasserman2018topological}
-\bibinfo{author}{Wasserman, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Topological data analysis}}.
-\newblock {\emph{\JournalTitle{Annual Review of Statistics and Its
-  Application}}} \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{501--532}
-  (\bibinfo{year}{2018}).
-
-\bibitem{wang2005adaptive}
-\bibinfo{author}{Wang, J.}, \bibinfo{author}{Zhang, Z.} \&
-  \bibinfo{author}{Zha, H.}
-\newblock \bibinfo{title}{Adaptive manifold learning}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in neural information
-  processing systems}}, \bibinfo{pages}{1473--1480} (\bibinfo{year}{2005}).
-
-\bibitem{lin2008riemannian}
-\bibinfo{author}{Lin, T.} \& \bibinfo{author}{Zha, H.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Riemannian manifold learning}}.
-\newblock {\emph{\JournalTitle{IEEE Transactions on Pattern Analysis and
-  Machine Intelligence}}} \textbf{\bibinfo{volume}{30}},
-  \bibinfo{pages}{796--809} (\bibinfo{year}{2008}).
-
-\bibitem{belkin2003problems}
-\bibinfo{author}{Belkin, M.}
-\newblock \emph{\bibinfo{title}{Problems of learning on manifolds}}
-  (\bibinfo{publisher}{The University of Chicago, Chicago, IL, USA},
-  \bibinfo{year}{2003}).
-
-\end{thebibliography}
+\bibliography{bibl}{}
+%\bibliographystyle{plain}
+%\bibliographystyle{ieeetr}
 
@@
 
-\newpage
-\begin{thebibliography}{1}
-\urlstyle{rm}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
+%\newpage
+%\bibliographystylesupp{naturemag-doi}
+%\bibliographysupp{supp}
 
-\bibitem{asboth2016short}
-\bibinfo{author}{Asb{\'o}th, J.~K.}, \bibinfo{author}{Oroszl{\'a}ny, L.} \&
-  \bibinfo{author}{P{\'a}lyi, A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{A short course on topological
-  insulators}}.
-\newblock {\emph{\JournalTitle{Lecture notes in physics}}}
-  \textbf{\bibinfo{volume}{919}} (\bibinfo{year}{2016}).
-
-\bibitem{goodfellow2016deep}
-\bibinfo{author}{Goodfellow, I.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Courville, A.}
-\newblock \emph{\bibinfo{title}{Deep learning}} (\bibinfo{publisher}{MIT press,
-  Cambridge, MA, USA}, \bibinfo{year}{2016}).
-
-\bibitem{bishop2006pattern}
-\bibinfo{author}{Bishop, C.~M.}
-\newblock \emph{\bibinfo{title}{Pattern recognition and machine learning}}
-  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2006}).
-
-\bibitem{cayton2005algorithms}
-\bibinfo{author}{Cayton, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Algorithms for manifold learning}}.
-\newblock {\emph{\JournalTitle{Univ. of California at San Diego Tech. Rep}}}
-  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{1} (\bibinfo{year}{2005}).
-
-\bibitem{narayanan2010sample}
-\bibinfo{author}{Narayanan, H.} \& \bibinfo{author}{Mitter, S.}
-\newblock \bibinfo{title}{Sample complexity of testing the manifold
-  hypothesis}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{1786--1794} (\bibinfo{year}{2010}).
-
-\bibitem{rifai2011manifold}
-\bibinfo{author}{Rifai, S.}, \bibinfo{author}{Dauphin, Y.~N.},
-  \bibinfo{author}{Vincent, P.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Muller, X.}
-\newblock \bibinfo{title}{The manifold tangent classifier}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{2294--2302} (\bibinfo{year}{2011}).
-
-\end{thebibliography}
 \end{document}

### 2020-05-09 __init__.py

@@ -1,12 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Editor Spyder
-
-Este é um arquivo de script temporário.
-"""
-#import sys
-#print("path: ", sys.path)
-#from scripts.preprocessing import *
-#from scripts.simulation import *
-#from scripts.simulation_results import *
-

### 2020-05-09 0_preprocessing/run_template.py
Cleaning directories

@@ -1,44 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Mar  3 17:23:25 2020
-
-@author: linneu
-"""
-
-
-import papermill as pm
-from tqdm import tqdm
-import os
-
-WDIR = "/home/linneu/ml_topological_phases_in_real_space/0_preprocessing"
-os.chdir(WDIR)
-
-template = "preprocessing_template.ipynb"
-parameters = {"allowed_windings":[0,1], "epsilon":0.01, "to_csv":True}
-kernel_name = "ml_top_phases"
-grid_folders_csv_names_outputs = [("/home/linneu/ssh_grids/ssh1/periodic_100_6561", "/home/linneu/ssh_csvs/ssh1/periodic_100_6561.csv","preprocessing_output_periodic_100_6561.ipynb"),\
-                             ("/home/linneu/ssh_grids/ssh1/periodic_140_6561", "/home/linneu/ssh_csvs/ssh1/periodic_140_6561.csv","preprocessing_output_periodic_140_6561.ipynb"),\
-                             ("/home/linneu/ssh_grids/ssh1/periodic_180_6561", "/home/linneu/ssh_csvs/ssh1/periodic_180_6561.csv","preprocessing_output_periodic_180_6561.ipynb"),\
-                             ("/home/linneu/ssh_grids/ssh1/periodic_220_6561", "/home/linneu/ssh_csvs/ssh1/periodic_220_6561.csv","preprocessing_output_periodic_220_6561.ipynb")\
-                             ]
-    
-def execute_notebook(template,output_file,parameters,kernel_name,grid_folder,csv_name):
-    
-    parameters["grid_folder"]=grid_folder
-    parameters["csv_name"]=csv_name
-    nb = pm.execute_notebook(template,
-                        output_file,
-                        parameters=parameters,
-                        kernel_name=kernel_name)
-    #nbs = []
-    #nbs.append(nb)
-    return nb
-
-nbs = {}
-for grid_folder, csv_name, output_file in tqdm(grid_folders_csv_names_outputs):
-    filename = csv_name.split(".")[0].split("/")[-1]
-    nbs[filename] = execute_notebook(template,output_file,parameters,kernel_name,grid_folder,csv_name)
-    
-
-    

### 2020-06-21 8_prb_submission/1_reply_referee/reply_referee.tex
Generated template of reply to referee

%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
\documentclass[10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{tabularx} 
\usepackage{array}
\usepackage{units}
\usepackage{tensor} 
\usepackage{braket}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage[resetlabels, labeled]{multibib}
%\newcites{supp}{References}

\renewcommand{\Re}{\operatorname{{\mathrm Re}}}
\renewcommand{\Im}{\operatorname{{\mathrm Im}}}
\newcommand{\tr}{\operatorname{{\mathrm tr}}}

\newcommand{\hc}{^{\dagger}}
\newcommand{\ad}{\operatorname{{\mathrm ad}}}
\newcommand{\adn}{\ad_{\hat n}}
\newcommand{\adx}{\ad_{\hat x}}
\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
\newcommand{\adp}{\ad_{\hat p}}
\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
\newcommand{\inbk}[1]{\left[ #1 \right]}
\newcommand{\inbr}[1]{\left\{ #1 \right\}}
\newcommand{\inp}[1]{\left( #1 \right)}
\newcommand{\pd}{\partial}
\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative

\newcounter{quoter}
\setcounter{quoter}{0}
\renewcommand*{\thequoter}{%
  %\textbf{%
  %  \ifnum\value{custom}<1000 0\fi
  %  \ifnum\value{custom}<100 0\fi
  %  \ifnum\value{custom}<10 0\fi
  %  \arabic{custom}%
  \textbf{[\arabic{quoter}]}
  }%

\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
\newcommand{\citequote}[1]{\ref{#1}}

\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}

%\stepcounter{quote}
%\refstepcounter{quote}

\begin{document}
\section{Reply to the first referee }
\section{Reply to the second referee}
Dear referee,

we appreciate the valuable insigths on how to improve our article that you have provided us. Below we address each of the points you emphasized separately, as they were written in your reply. We quote the issues raised by you in purple, and highlight in boldface the points that we thought were particularly relevant.

\subsection{Major}

\textcolor{antiquefuchsia}{I am not sure about the novelty and generality of their method. For
example, \textbf{their pipeline cannot work for complex experimental physical
systems, where the Hamiltonian could be unknown}\genquote{pipeline_not_work}. Moreover, the authors
state that it is sufficient to use the input data in real space to
predict the topological phase with high accuracy. \textbf{It is not clear to
me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of
using the input data in real space instead of the Hamiltonian in
wavevector space. \textbf{I expect the evidence to indicate that their method
is superior or comparable to any other method}\genquote{superior_comparable}. It is worth mentioning
that the author already discussed \textbf{the motivations for developing a
data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological
phases from real space data" section. However, these arguments should
be pointed carefully in the "Introduction" section.}

\vspace{0.25cm}
\citequote{pipeline_not_work} Mention the possibility of using incomplete information with eigenvector ensembling.

\citequote{sufficient_accuracy} ...

\citequote{superior_comparable} Mention trends in model explainability as well as performance scores.

\citequote{motif_real_space}We agree that the motivation for using real space data to study topological phase transitions should be placed in the introduction. We have therefore moved the first paragraph of the section "Learning topological phases from real space data" to the introduction.

\vspace{0.5cm}
\textcolor{antiquefuchsia}{I am not sure which crucial problems their algorithm can solve that
was not possible before with machine learning. Furthermore, along with
the emerging research of unsupervised learning methods in realizing
the topological phases, \textbf{why should the supervised learning method be
focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript,
where I do not see the proposal's advantages, I would prefer the
\textbf{unsupervised approaches that could grasp information from a given
system without knowing their phases}\genquote{unsupervised_approaches}. In my opinion, a proper intrinsic
route for understanding physical systems without much information on
the dynamics of the system will lead to significant future
developments and a better understanding of physic systems.}

\vspace{0.25cm}
\citequote{unsupervised_learning} Mention semi-supervised learning, model explainability.

\citequote{unsupervised_approaches} Mention Hamiltonian compression, of unsupervised learning through dimensional reduction.

\vspace{0.5cm}
\textcolor{antiquefuchsia}{The details of \textbf{the eigenvector ensembling algorithm should be
addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material. What is
the specific algorithm used in the paper to train on eigenvectors? I
think it is important even if the readers are not familiar with some
ML techniques. Some readers in physics may find it difficult to
understand some ML technical terms such as bootstrapping, training and
validation, test sets, etc. In addition, \textbf{I expect proof of what
"physics" their method captures and why the eigenvector can play an
important role in characterizing the topological phase}\genquote{eigenvector_physics}. If this
physical interpretability is not mentioned, it is very difficult to
see the contribution of the method in physics.}

\vspace{0.25cm}
\citequote{eigenvector_ensembling_alg} We have moved the section "The eigenvector ensembling algorithm" to the main paper. The issue of specifying the particular learning algorithms used was also addressed.

\citequote{eigenvector_physics} One of the strongest points of the paper is to introduce model explainability tools from machine learning in physics. The need to use eigenvectors is that they encode all the physical information from a system. The paper paves the way for new theoretical investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.

\vspace{0.5cm}
\textcolor{antiquefuchsia}{The authors made efforts to analyze how the algorithm was able to
recover the Hamiltonians' global property in the "Information Entropy
Signatures" section. The authors state that learning topological
phases from local real-space data in bulk is still possible even for
small subsets of lattice sites, then refer us to the section "Learning
topological phases from real space data" in the Supplementary
Material. The authors mention on page 4 of the Supplementary Material
that \textbf{"key topological information can be said to be localized on a few
lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
However, I fail to understand the physical insights behind it. Without
the proper explanation, \textbf{it is difficult to see the effectiveness of
their method or verify the method with a more complex model}\genquote{more_complex_model} instead of
the simple SSH form.}

\vspace{0.25cm}
\citequote{key_top} Move this sentence to main paper.

\citequote{more_complex_model} Add FFT of entropy signatures? Mention entropic uncertainty? Talk about information gain? Mention that interpretability in ML is often challenging and a fast evolving field. Furthermore, eigenvector ensembling can always be used as a preprocessing step to other ML models, such as in semi supervised learning tasks. 
\end{document}

### 2020-06-21 8_prb_submission/1_reply_referee/article/article.tex
Generated template of reply to referee

--- 2020-05-07 6_prb/main.tex
@@
 \documentclass[10pt]{revtex4-1}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{graphicx}
@@
 \usepackage[resetlabels, labeled]{multibib}
-\newcites{supp}{References}
+\usepackage{xcolor}
+%\newcites{supp}{References}
 
@@
 Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
+
+The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
+\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+disordered systems in condensed matter) do not have.
+Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
+We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
 
@@
 
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{56}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Hasan}\ and\ \citenamefont
+  {Kane}(2010)}]{RevModPhys.82.3045}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Hasan}}\ and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
+  {Kane}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {3045}
+  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Continentino}(2017)}]{CONTINENTINO2017A1}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physica B: Condensed Matter}\ }\textbf {\bibinfo {volume} {505}},\ \bibinfo
+  {pages} {A1 } (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Puel}\ \emph {et~al.}(2017)\citenamefont {Puel},
+  \citenamefont {Sacramento},\ and\ \citenamefont
+  {Continentino}}]{PhysRevB.95.094509}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~O.}\ \bibnamefont
+  {Puel}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
+  {Sacramento}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {094509}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Griffith}\ and\ \citenamefont
+  {Continentino}(2018)}]{PhysRevE.97.012107}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Griffith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {012107}
+  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ryu}\ \emph {et~al.}(2010)\citenamefont {Ryu},
+  \citenamefont {Schnyder}, \citenamefont {Furusaki},\ and\ \citenamefont
+  {Ludwig}}]{ryu2010topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ryu}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont {Schnyder}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Furusaki}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont {Ludwig}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {New Journal of
+  Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {065010}
+  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Atala}\ \emph {et~al.}(2013)\citenamefont {Atala},
+  \citenamefont {Aidelsburger}, \citenamefont {Barreiro}, \citenamefont
+  {Abanin}, \citenamefont {Kitagawa}, \citenamefont {Demler},\ and\
+  \citenamefont {Bloch}}]{atala2013direct}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Atala}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Aidelsburger}},
+  \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont {Barreiro}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Abanin}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Kitagawa}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Bloch}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
+  {9}},\ \bibinfo {pages} {795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stuhl}\ \emph {et~al.}(2015)\citenamefont {Stuhl},
+  \citenamefont {Lu}, \citenamefont {Aycock}, \citenamefont {Genkina},\ and\
+  \citenamefont {Spielman}}]{Stuhl1514}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~K.}\ \bibnamefont
+  {Stuhl}}, \bibinfo {author} {\bibfnamefont {H.-I.}\ \bibnamefont {Lu}},
+  \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont {Aycock}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Genkina}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {I.~B.}\ \bibnamefont {Spielman}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {349}},\ \bibinfo {pages} {1514} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Leder}\ \emph {et~al.}(2016)\citenamefont {Leder},
+  \citenamefont {Grossert}, \citenamefont {Sitta}, \citenamefont {Genske},
+  \citenamefont {Rosch},\ and\ \citenamefont {Weitz}}]{leder2016real}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Leder}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Grossert}},
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sitta}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Genske}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Rosch}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {13112} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goldman}\ \emph {et~al.}(2016)\citenamefont
+  {Goldman}, \citenamefont {Budich},\ and\ \citenamefont
+  {Zoller}}]{goldman2016topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Goldman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Budich}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
+  }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {639} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Meier}\ \emph {et~al.}(2016)\citenamefont {Meier},
+  \citenamefont {An},\ and\ \citenamefont {Gadway}}]{meier2016observation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
+  {Meier}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {An}}, \
+  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  communications}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {13986}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hafezi}\ \emph {et~al.}(2013)\citenamefont {Hafezi},
+  \citenamefont {Mittal}, \citenamefont {Fan}, \citenamefont {Migdall},\ and\
+  \citenamefont {Taylor}}]{hafezi2013imaging}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Hafezi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mittal}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Fan}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Migdall}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Taylor}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Photonics}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {1001} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Lu}\ \emph {et~al.}(2016)\citenamefont {Lu},
+  \citenamefont {Joannopoulos},\ and\ \citenamefont
+  {Solja{\v{c}}i{\'c}}}]{lu2016topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Lu}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+  {Joannopoulos}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Solja{\v{c}}i{\'c}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {626} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peano}\ \emph {et~al.}(2015)\citenamefont {Peano},
+  \citenamefont {Brendel}, \citenamefont {Schmidt},\ and\ \citenamefont
+  {Marquardt}}]{PhysRevX.5.031011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Peano}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Brendel}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Schmidt}}, \ and\
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marquardt}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
+  {\bibinfo {volume} {5}},\ \bibinfo {pages} {031011} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2012)\citenamefont
+  {Kitagawa}, \citenamefont {Broome}, \citenamefont {Fedrizzi}, \citenamefont
+  {Rudner}, \citenamefont {Berg}, \citenamefont {Kassal}, \citenamefont
+  {Aspuru-Guzik}, \citenamefont {Demler},\ and\ \citenamefont
+  {White}}]{kitagawa2012observation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Broome}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Fedrizzi}},
+  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Kassal}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~G.}\
+  \bibnamefont {White}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature communications}\ }\textbf {\bibinfo {volume} {3}},\
+  \bibinfo {pages} {882} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cardano}\ \emph {et~al.}(2016)\citenamefont
+  {Cardano}, \citenamefont {Maffei}, \citenamefont {Massa}, \citenamefont
+  {Piccirillo}, \citenamefont {De~Lisio}, \citenamefont {De~Filippis},
+  \citenamefont {Cataudella}, \citenamefont {Santamato},\ and\ \citenamefont
+  {Marrucci}}]{cardano2016statistical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Cardano}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maffei}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Massa}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Piccirillo}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {De~Lisio}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {De~Filippis}}, \bibinfo {author}
+  {\bibfnamefont {V.}~\bibnamefont {Cataudella}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Santamato}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Marrucci}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {11439} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Flurin}\ \emph {et~al.}(2017)\citenamefont {Flurin},
+  \citenamefont {Ramasesh}, \citenamefont {Hacohen-Gourgy}, \citenamefont
+  {Martin}, \citenamefont {Yao},\ and\ \citenamefont
+  {Siddiqi}}]{PhysRevX.7.031023}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Flurin}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
+  {Ramasesh}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Hacohen-Gourgy}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
+  {Martin}}, \bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont {Yao}}, \
+  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Siddiqi}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
+  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {031023} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Soluyanov}\ \emph {et~al.}(2015)\citenamefont
+  {Soluyanov}, \citenamefont {Gresch}, \citenamefont {Wang}, \citenamefont
+  {Wu}, \citenamefont {Troyer}, \citenamefont {Dai},\ and\ \citenamefont
+  {Bernevig}}]{soluyanov2015type}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
+  {Soluyanov}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gresch}},
+  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {Q.}~\bibnamefont {Wu}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Troyer}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Dai}}, \ and\ \bibinfo {author} {\bibfnamefont {B.~A.}\
+  \bibnamefont {Bernevig}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {527}},\ \bibinfo {pages}
+  {495} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lv}\ \emph {et~al.}(2015)\citenamefont {Lv},
+  \citenamefont {Weng}, \citenamefont {Fu}, \citenamefont {Wang}, \citenamefont
+  {Miao}, \citenamefont {Ma}, \citenamefont {Richard}, \citenamefont {Huang},
+  \citenamefont {Zhao}, \citenamefont {Chen}, \citenamefont {Fang},
+  \citenamefont {Dai}, \citenamefont {Qian},\ and\ \citenamefont
+  {Ding}}]{PhysRevX.5.031013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~Q.}\ \bibnamefont
+  {Lv}}, \bibinfo {author} {\bibfnamefont {H.~M.}\ \bibnamefont {Weng}},
+  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Fu}}, \bibinfo
+  {author} {\bibfnamefont {X.~P.}\ \bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Miao}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ma}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Richard}}, \bibinfo {author} {\bibfnamefont {X.~C.}\ \bibnamefont {Huang}},
+  \bibinfo {author} {\bibfnamefont {L.~X.}\ \bibnamefont {Zhao}}, \bibinfo
+  {author} {\bibfnamefont {G.~F.}\ \bibnamefont {Chen}}, \bibinfo {author}
+  {\bibfnamefont {Z.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Dai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Qian}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
+  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {031013} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Su}\ \emph {et~al.}(1979)\citenamefont {Su},
+  \citenamefont {Schrieffer},\ and\ \citenamefont
+  {Heeger}}]{PhysRevLett.42.1698}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~P.}\ \bibnamefont
+  {Su}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Schrieffer}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Heeger}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1698} (\bibinfo {year}
+  {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},
+  \citenamefont {Dauphin}, \citenamefont {Cardano}, \citenamefont
+  {Lewenstein},\ and\ \citenamefont {Massignan}}]{maffei2018topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Maffei}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Cardano}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Massignan}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
+  {\bibinfo {volume} {20}},\ \bibinfo {pages} {013023} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heeger}(2001)}]{RevModPhys.73.681}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Heeger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {681}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kane}\ and\ \citenamefont
+  {Lubensky}(2014)}]{kane2014topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Kane}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Lubensky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {39}
+  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
+  \citenamefont {Upadhyaya},\ and\ \citenamefont {Vitelli}}]{Chen13004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.-g.}\
+  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Upadhyaya}}, \ and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Vitelli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
+  {volume} {111}},\ \bibinfo {pages} {13004} (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carrasquilla}\ and\ \citenamefont
+  {Melko}(2017)}]{carrasquilla2017machine}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Carrasquilla}}\ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Melko}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {431}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ch'ng}\ \emph {et~al.}(2017)\citenamefont {Ch'ng},
+  \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\ \citenamefont
+  {Khatami}}]{PhysRevX.7.031038}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Ch'ng}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Carrasquilla}},
+  \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \ and\
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Khatami}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
+  {\bibinfo {volume} {7}},\ \bibinfo {pages} {031038} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}(2016)}]{PhysRevB.94.195105}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Wang}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {195105}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Broecker}\ \emph {et~al.}(2017)\citenamefont
+  {Broecker}, \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\
+  \citenamefont {Trebst}}]{broecker2017machine}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Broecker}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Carrasquilla}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Melko}}, \ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Trebst}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Scientific reports}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
+  {8823} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Van~Nieuwenburg}\ \emph {et~al.}(2017)\citenamefont
+  {Van~Nieuwenburg}, \citenamefont {Liu},\ and\ \citenamefont
+  {Huber}}]{van2017learning}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
+  {Van~Nieuwenburg}}, \bibinfo {author} {\bibfnamefont {Y.-H.}\ \bibnamefont
+  {Liu}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Huber}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {435}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2018)\citenamefont {Zhang},
+  \citenamefont {Shen},\ and\ \citenamefont {Zhai}}]{PhysRevLett.120.066401}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {120}},\ \bibinfo {pages} {066401} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
+  \citenamefont {Yi}, \citenamefont {Zhang}, \citenamefont {Shen},\ and\
+  \citenamefont {Zhai}}]{PhysRevB.98.085402}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Yi}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Zhang}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {98}},\ \bibinfo {pages} {085402} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Suchsland}\ and\ \citenamefont
+  {Wessel}(2018)}]{PhysRevB.97.174435}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Suchsland}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Wessel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {174435}
+  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont
+  {Kim}(2017)}]{PhysRevLett.118.216401}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont
+  {Kim}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. Lett.}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {216401}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Venderley}\ \emph {et~al.}(2018)\citenamefont
+  {Venderley}, \citenamefont {Khemani},\ and\ \citenamefont
+  {Kim}}]{PhysRevLett.120.257204}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Venderley}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Khemani}},
+  \ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {120}},\ \bibinfo {pages} {257204} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ohtsuki}\ and\ \citenamefont
+  {Ohtsuki}(2017)}]{ohtsuki2017deep}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ohtsuki}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ohtsuki}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo {volume}
+  {86}},\ \bibinfo {pages} {044708} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Yoshioka}\ \emph {et~al.}(2018)\citenamefont
+  {Yoshioka}, \citenamefont {Akagi},\ and\ \citenamefont
+  {Katsura}}]{PhysRevB.97.205110}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Yoshioka}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Akagi}}, \
+  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Katsura}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {205110} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2017)\citenamefont {Deng},
+  \citenamefont {Li},\ and\ \citenamefont {Das~Sarma}}]{PhysRevB.96.195145}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.-L.}\ \bibnamefont
+  {Deng}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}}, \ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf
+  {\bibinfo {volume} {96}},\ \bibinfo {pages} {195145} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huembeli}\ \emph {et~al.}(2018)\citenamefont
+  {Huembeli}, \citenamefont {Dauphin},\ and\ \citenamefont
+  {Wittek}}]{PhysRevB.97.134109}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Huembeli}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wittek}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {134109} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carvalho}\ \emph {et~al.}(2018)\citenamefont
+  {Carvalho}, \citenamefont {Garc\'{\i}a-Mart\'{\i}nez}, \citenamefont {Lado},\
+  and\ \citenamefont {Fern\'andez-Rossier}}]{PhysRevB.97.115453}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Carvalho}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
+  {Garc\'{\i}a-Mart\'{\i}nez}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
+  \bibnamefont {Lado}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Fern\'andez-Rossier}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {97}},\ \bibinfo {pages} {115453} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2017)\citenamefont {Zhang},
+  \citenamefont {Melko},\ and\ \citenamefont {Kim}}]{PhysRevB.96.245119}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {245119} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rodriguez-Nieva}\ and\ \citenamefont
+  {Scheurer}(2018)}]{rodriguez2018identifying}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+  {Rodriguez-Nieva}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\
+  \bibnamefont {Scheurer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {arXiv preprint arXiv:1805.05961}\ } (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
+  {Breiman}, \citenamefont {Friedman}, \citenamefont {Stone},\ and\
+  \citenamefont {Olshen}}]{breiman2017classification}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Breiman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},
+  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Stone}}, \ and\
+  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Olshen}},\
+  }\href@noop {} {\emph {\bibinfo {title} {Classification and regression
+  trees}}}\ (\bibinfo  {publisher} {Chapman and Hall/CRC, London, UK},\
+  \bibinfo {year} {1984})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Breiman}(2001)}]{Breiman2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Breiman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Machine Learning}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {5}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
+  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
+  {Tibshirani}}]{friedman2001elements}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
+  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
+  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
+  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
+  {year} {2001})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
+  {Resta}(2011)}]{PhysRevB.84.241106}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Bianco}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Resta}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {241106} (\bibinfo
+  {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Caio}\ \emph {et~al.}(2019)\citenamefont {Caio},
+  \citenamefont {M{\"o}ller}, \citenamefont {Cooper},\ and\ \citenamefont
+  {Bhaseen}}]{caio2019topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
+  {Caio}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {M{\"o}ller}},
+  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Cooper}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bhaseen}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ ,\ \bibinfo
+  {pages} {1}} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carlsson}(2009)}]{carlsson2009topology}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Carlsson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Bulletin of the American Mathematical Society}\ }\textbf {\bibinfo {volume}
+  {46}},\ \bibinfo {pages} {255} (\bibinfo {year} {2009})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wasserman}(2018)}]{wasserman2018topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Wasserman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Annual Review of Statistics and Its Application}\ }\textbf {\bibinfo
+  {volume} {5}},\ \bibinfo {pages} {501} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2005)\citenamefont {Wang},
+  \citenamefont {Zhang},\ and\ \citenamefont {Zha}}]{wang2005adaptive}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\ }in\ \href@noop
+  {} {\emph {\bibinfo {booktitle} {Advances in neural information processing
+  systems}}}\ (\bibinfo {year} {2005})\ pp.\ \bibinfo {pages}
+  {1473--1480}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lin}\ and\ \citenamefont
+  {Zha}(2008)}]{lin2008riemannian}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Lin}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Transactions
+  on Pattern Analysis and Machine Intelligence}\ }\textbf {\bibinfo {volume}
+  {30}},\ \bibinfo {pages} {796} (\bibinfo {year} {2008})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Belkin}(2003)}]{belkin2003problems}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Belkin}},\ }\href@noop {} {\emph {\bibinfo {title} {Problems of learning on
+  manifolds}}}\ (\bibinfo  {publisher} {The University of Chicago, Chicago, IL,
+  USA},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
+  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
+  {P{\'a}lyi}}]{asboth2016short}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
+  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
+  {Courville}}]{goodfellow2016deep}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
+  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
+  {publisher} {MIT press, Cambridge, MA, USA},\ \bibinfo {year}
+  {2016})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
+  machine learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\
+  \bibinfo {year} {2006})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
+  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
+  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
+  {Mitter}(2010)}]{narayanan2010sample}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
+  Neural Information Processing Systems}}}\ (\bibinfo {year} {2010})\ pp.\
+  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
+  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
+  and\ \citenamefont {Muller}}]{rifai2011manifold}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {Advances in Neural Information Processing Systems}}}\
+  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
+
 \section*{Acknowledgements}
@@
 
-\newpage
-
-\begin{figure}
-  \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/ssh_model.pdf}
-  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
-\label{fig:model}
-\end{figure}
-
-\begin{figure}%[h!]
-  \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/winding.png}
-  \caption{Winding number.
-The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point.
-Picture credits: Jim Belk, public domain.}
-\label{fig:winding}
-\end{figure}
-
-\section*{Supplementary Material}
-\subsection*{The SSH model}
-\label{sshapp}
-
-The SSH model \citesupp{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
-This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
-This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
-\begin{equation}
-\label{SSH}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-where the column vector
-\begin{equation*}
-\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
-\end{equation*}
-contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
-\begin{equation*}
-\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
-\end{equation*}
-contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
-Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.
-
-The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
-We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics.
-As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
-\begin{equation}\label{hmatrix}
-H(t_1,t_2,T_1,T_2)=\left(
-  \begin{array}{cccccc}
-    0 & t_1 & 0 & T_1 & 0 & \cdots \\
-    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
-    0 & t_2 & 0 & t_1 & 0 & \cdots\\
-    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
-    0 & T_2 & 0 & t_2 &  0& \cdots\\
-    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
-  \end{array}
-  \right)_{N \times N}.
-\end{equation}
-Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
-Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.
-
-The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
-This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
-This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system.
-In the particular case of the SSH model, the topological invariant used to classify the topological phases is the winding number.
-
-The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
-It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative).
-Figure \ref{fig:winding} shows several closed, oriented curves and their winding numbers computed with respect to a given point.
-
-An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
-This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a very challenging task.
-
-For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
-\begin{equation}\label{winding_number}
-W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
-\end{equation}
-where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\hat{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
-Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure \ref{fig:phasediagrams}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{./ssh1/periodic_less_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{./ssh2/periodic_less_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Phase diagrams learned from most relevant lattice sites.
-(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99).
-The accuracy achieved for Hamiltonians in the test set using only the four lattice sites in $S'_1$ was approximately 95\%.
-(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99).
-The accuracy achieved for Hamiltonians in the test set using only the nine lattice sites in $S'_2$ was approximately 74\%.}
-\label{less_feat}
-\end{figure}
-
-\subsection*{Learning topological phases from real space data}
-
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
-
-Our reasoning goes as follows.
-First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
-Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space.
-Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.
-
-In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \citesupp{goodfellow2016deep}.
-Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
-\begin{equation}
-\label{localconstancy}
-W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
-\end{equation}
-
-That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure \ref{fig:phasediagrams}, where we draw phase diagrams of SSH models with first-neighbor (figure \ref{ssh1}) and first- and second-neighbor (figure \ref{ssh2}) hoppings.
-In figure \ref{ssh1} for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
-Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.
-
-It does not immediately follow, however, that the same strategy will be successful in real space.
-Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,
-
-\begin{equation}
-\label{parameter_to_real}
-\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
-\end{equation}
-where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
-The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.
-
-This fact is well illustrated by the numerical experiments discussed in the article.
-Although it may seem from figures \ref{figexp1_exp:b} and \ref{figexp2_exp:b} in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
-In such high-dimensional spaces, the data should be much sparser.
-
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \citesupp{bishop2006pattern}.
-It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
-
-These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
-Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \citesupp{rifai2011manifold}).
-As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}).
-In this sense, key topological information can be said to be localized on few lattice sites.
-
-\subsection*{The eigenvector ensembling algorithm}
-
-We describe here in detail each step of the eigenvector ensembling algorithm.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
-\vspace{.3cm}
-In this work we implemented the eigenvector ensembling algorithm with Python's Scikit tools.
-
-\subsection*{Information entropy signatures in the macroscopic limit}
-
-A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
-
-The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
-Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
-
-Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
-As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
-The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector ensembling algorithm.
-
-There are still artifacts that might arise from the hyperparameters used to generate the data.
-These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space).
-Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive.
-Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the information entropy signatures is lattice size.
-
-All results presented in the article were obtained for lattices with 50 unit cells.
-Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
-Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}).
-These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
-
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
-
-Figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
-In the limit of an infinite chain, the cumulative entropy distribution $F_S(x)$ associated with a Shannon information entropy signal will be given by the integral of an entropy density function $\rho_S$($x$),
-
-\begin{equation}
-\label{entropy_dens}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
-\end{equation}
-where $x$ $\in$ [0,1] is a spatial coordinate along the lattice (being strict, our use of periodic boundary conditions implies that the coordinate $x$ should be defined in the quotient space $[0,1]/R$, where $R$ is the equivalence relation in [0,1] defining the unit circle $S^1$, i.e.
-$x$ $R$ $x'$ if and only if $x$ = $x'$ or ($x$,$x'$) $\in$ \{(0,1), (1,0)\}.
-For open boundary conditions, the spatial coordinate $x$ is defined in the closed interval [0,1]).
-In this continuum limit, an information entropy signature will be given by the entropy density function $\rho_S(x)$.
-Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}.
-
-The results presented in this article suggest that the macroscopic limit $\rho_S(x)$ of the information entropy signatures may have strong theoretical interest and pave new roads to the investigation of topological materials.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_feature_importances.png}}
-\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
-(a) Information entropy signature for 70 unit cells.
-(b) Information entropy signature for 90 unit cells.
-(c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh1_longer_lattices}
-\end{figure}
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_feature_importances.png}}
-\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
-(a) Information entropy signature for 70 unit cells.
-(b) Information entropy signature for 90 unit cells.
-(c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh2_longer_lattices}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
-(a) Cumulative entropy distribution for 70 unit cells.
-(b) Cumulative entropy distribution for 90 unit cells.
-(c) Cumulative entropy distribution for 110 unit cells.
-The two visible leaps in the cumulative entropy distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
-\label{cdf1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
-(a) Cumulative entropy distributions for 70 unit cells.
-(b) Cumulative entropy distributions for 90 unit cells.
-(c) Cumulative entropy distributions for 110 unit cells.
-Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable.
-The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case of 50 unit cells.}
-\label{cdf2}
-\end{figure}
-
 \end{document}

### 2020-06-21 8_prb_submission/1_reply_referee/supplementary/supplementary.tex
Generated template of reply to referee

--- 2020-05-07 6_prb/main.tex
@@
 \nocite{*}
-
-\title{Machine learning topological phases in real space}
-
-\author{N. L. Holanda}
-\email{linneuholanda@gmail.com, linneu@cbpf.br}
-\affiliation{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-
-\author{M. A. S. Griffith}
-\email{griffithphys@gmail.com}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
-
-\date{\today }
-
-\begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems from bulk data in real lattice space.
-The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
-We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
-The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
-\end{abstract}
-
-\maketitle
-
-\section*{Introduction}
-
-The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}.
-These materials feature previously unthought-of traits like bulk insulation coupled with metallic conductance at the surface and the splitting of currents according to spin orientation.
-Adding to that, these properties are protected by non-trivial topology that renders them robust to many sources of perturbation like thermal noise.
-Such characteristics make them promising candidates to being the cornerstone of 21st century technologies like spintronics and quantum computing.
-
-These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
-Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.
-
-The SSH model is the simplest tight-binding model that exhibits a topological phase transition.
-As such, it can be viewed as the \emph{Drosophila} of the field, providing a simple framework for testing new techniques.
-The model can be expressed in terms of creation and annihilation operators by the Hamiltonian
-\begin{equation}
-\label{SSH_ham}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-and describes e.g.
-the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material).
-The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.
-
-Many recent papers have explored the possibility of treating the general problem of determining phase transition boundaries of physical systems as machine learning tasks \cite{carrasquilla2017machine}$^-$\cite{rodriguez2018identifying}.
-In the particular case of topological phase transitions, the usual approach for supervised learning is to generate a data set $\big(H_1(k), W_1\big)$, ..., $\big(H_n(k), W_n\big)$ whose inputs are representations of Hamiltonians in wavevector space $H_i(k)$ and targets are their corresponding topological invariants $W_i$ (for the SSH model the topological invariant is the winding number).
-Our paper extends this task to the case of learning topological phase diagrams from input data in real space.
-Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
-The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
-
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
-This makes it much easier to trace the localization of relevant information along the features of a data set.
-Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
-To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-
-The Shannon information entropy signals presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh1.png}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh2.png}}
-\caption{Phase diagrams in parameter space.
-a) SSH model with first-neighbor hoppings $t_1$ and $t_2$.
-The (red) regions with winding number $W$ = 0 are trivial, while the (blue) regions with winding number $W$ = 1 are topologically non-trivial.
-b) SSH model with first ($t_1$ and $t_2$) and second ($T_1$ and $T_2$) nearest-neighbor hoppings.
-In this article we set $t_1$ = $t_2$ = 1 and renamed the variables $T_1$ $\rightarrow$ $t_1$, $T_2$ $\rightarrow$ $t_2$ for convenience.
-The (orange) region with winding number $W$ = 0 is trivial while the others with winding numbers $W$ = -1, $W$ = 1 and $W$ = 2 (red, green and blue respectively) are topologically non-trivial.}
-\label{fig:phasediagrams}
-\end{figure}
-
-\section*{Numerical experiments}
-
-The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-A detailed description of the algorithm is found in the section \textbf{The eigenvector ensembling algorithm} in the Supplementary Material.
-Here we present results of the numerical experiments we performed with it.
-We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
-
-In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
-The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
-
-This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the allowed winding number values.
-Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
-The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
-
-When generating the Hamiltonians we applied periodic boundary conditions to eliminate border effects.
-This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.
-The choice of periodic boundary conditions also implies that the information recovered from real space data comes from the bulk of the topological systems considered and therefore provides strong evidence for the existence of topological signatures in the bulk of such systems.
-
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiments 1 and 2 as seen from parameter space.
-The accuracy statistics presented in the following subsections and probability heatmaps shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-The recovered probability heatmaps faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
-
-\subsection*{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-
-Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
-These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
-Our algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
-
-The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (98.2\%), validation eigenvectors (96.4\%) and test eigenvectors (78.8\%).
-Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
-
-The probability heatmaps and phase diagram learned by the combination of decision trees with eigenvector ensembling used in experiment 1 are shown in figure \ref{ssh1_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 1 as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
-\label{figexp1_exp}
-\end{figure}
-
-\subsection*{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{exp2}
-
-This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 25 decision trees.
-Our data set consisted of 1040 (15.8\%) test Hamiltonians.
-The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving 2761 (42.1\%) training Hamiltonians and 2760 (42.1\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (17.9\%), $W$ = 0 (32.5\%), $W$ = 1 (32.3\%) and $W$ = 2 (17.3\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (36.3\%), $W$ = 0 (11.1\%), $W$ = 1 (12.7\%) and $W$ = 2 (39.9\%).
-
-Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.1\% for validation eigenvectors and 66.4\% for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 88.2\% for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from 66.4\% eigenvector accuracy to 88.2\% Hamiltonian accuracy) attests to its power.
-
-The probability heatmaps and phase diagram learned by the combination of random forests with eigenvector ensembling used in experiment 2 are shown in figure \ref{ssh2_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 2 as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
-\label{figexp2_exp}
-\end{figure}
-
-\section*{Information entropy signatures}
-
-We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
-
-The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g.
-Shannon information entropy or Gini impurity \cite{friedman2001elements}).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 and experiment 2 we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
-These signals are the information entropy signatures of each topological phase transition.
-
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for experiments 1 and 2.
-They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-
-Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
-
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy in experiment 1), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy in experiment 2) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1.
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(c) The phase diagram resulting from heatmaps (a) and (b).}
-\label{ssh1_heatmaps}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2.
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to -1.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(c) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(d) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 2.
-(e) The phase diagram resulting from heatmaps (a)-(d).}
-\label{ssh2_heatmaps}
-\end{figure}
-
-\section*{Discussion}
-
-Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have implemented a data-driven approach to the search for new topological materials bypassing the use of wavevector space data.
-
-The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to wavevector space methods.
-
-An advantage of using data from real space is that it enables us to investigate how topological information is distributed in the system.
-This was demonstrated by the information entropy signatures recovered from the Shannon entropy of ensembles of eigenvectors in each experiment.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.
-
-We should remark on the subtleties of the information entropy signatures presented here.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, these importances actually express a global property of the whole lattice.
-Therefore, a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
-To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites in the subset.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
-Furthermore, it should be emphasized that these signals were recovered from the analysis of data from several thousand SSH systems in each experiment and therefore they are not a property of a single SSH lattice.
-They are rather a pattern that emerges from correlating topological phase with lattice eigenvector data for several SSH systems.
-
-We performed several tests on the information entropy signatures.
-By rerunning each experiment with longer lattices (i.e.
-increasing the number of unit cells) we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further theoretical investigation.
-A detailed discussion of this point is presented in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
-
-Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as Shannon information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
-Whether there is any relationship between local topological markers and the information entropy of the ensemble of eigenvectors is left for speculation.
-
-The eigenvector ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
-This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
-It is therefore expected that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
-
-One final comment should be made about the flourishing relationship between physics and machine learning.
-In this work we have demonstrated how a machine learning approach can provide new insights into complex physical phenomena of current interest.
-The other direction of this relationship (physics enhancing understanding in machine learning) is equally important.
-As the need for ever more powerful machine learning algorithms continues to grow, the development of mathematical frameworks for understanding general data spaces (i.e., a physics of data) will be of crucial relevance.
-This pursuit is seen in many theoretical works investigating the intriguing connections between geometry, topology and data \cite{carlsson2009topology}$^-$\cite{belkin2003problems}.
-The detailed study of data generated by physical models with non-trivial geometrical and topological properties such as the SSH model may provide invaluable insights into the structure and shape of real world high-dimensional data, since these models usually underscore well known mathematical frameworks behind the data generating process, a feature that is often absent from machine learning applications.
-Thus, far from being restricted to applications in physics, the study of the topological and geometrical properties of data sets generated by physical models will also be of great value to the machine learning and artificial intelligence communities.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions from experiments 1 and 2.
-(a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2, the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located along lattice sites $S_2$.}
-\label{feature_importances}
-\end{figure}
-
-\bibliography{bibl}{}
-%\bibliographystyle{plain}
-\bibliographystyle{ieeetr}
-
-\section*{Acknowledgements}
-
-We thank S.
-E.
-Rowley, J.
-F.
-de Oliveira, T.
-Micklitz and M.
-A.
-Continentino for insightful discussions and S.
-E.
-Rowley for carefully reading the manuscript and suggesting improvements.
-N.
-L.
-Holanda acknowledges financial support from CENPES/Petrobr\'as/CBPF.
-M.
-A.
-R.
-Griffith acknowledges financial support from Capes.
-N.
-L.
-Holanda is grateful to the Theory of Condensed Matter and Quantum Materials groups at the Cavendish Laboratory and the Quantum Information Group at CBPF.
-
-\section*{Author contributions}
-
-Both authors of this work contributed equally to its realization at all stages.
-
-\section*{Competing financial interests}
-
-The authors declare no competing financial or non-financial interests.
-
-\section*{Additional information}
-
-Correspondence and requests for materials should be addressed to N.
-L.
-Holanda.
-The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
-
-\newpage
 
@@
 where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\hat{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
-Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure \ref{fig:phasediagrams}.
+Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure 1 in the article.
+%\ref{fig:phasediagrams}.
 
@@
 
-That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure \ref{fig:phasediagrams}, where we draw phase diagrams of SSH models with first-neighbor (figure \ref{ssh1}) and first- and second-neighbor (figure \ref{ssh2}) hoppings.
-In figure \ref{ssh1} for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
+That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure 1 in the article %\ref{fig:phasediagrams}, 
+where we draw phase diagrams of SSH models with first-neighbor (figure 1(a)) and first- and second-neighbor (figure 1(b)) hoppings.
+In figure 1(a) for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
 Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.
@@
 This fact is well illustrated by the numerical experiments discussed in the article.
-Although it may seem from figures \ref{figexp1_exp:b} and \ref{figexp2_exp:b} in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
+Although it may seem from figures 2(b) and 3(b) (from the article) in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
 In such high-dimensional spaces, the data should be much sparser.
@@
 
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b)) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
 
@@
 
+\begin{thebibliography}{10}
+\bibitem{asboth2016short}
+J.~K. Asb{\'o}th, L.~Oroszl{\'a}ny, and A.~P{\'a}lyi, ``A short course on
+  topological insulators,'' {\em Lecture notes in physics}, vol.~919, 2016.
+
+\bibitem{goodfellow2016deep}
+I.~Goodfellow, Y.~Bengio, and A.~Courville, {\em Deep learning}.
+\newblock MIT press, Cambridge, MA, USA, 2016.
+
+\bibitem{bishop2006pattern}
+C.~M. Bishop, {\em Pattern recognition and machine learning}.
+\newblock Springer New York, NY, USA, 2006.
+
+\bibitem{cayton2005algorithms}
+L.~Cayton, ``Algorithms for manifold learning,'' {\em Univ. of California at
+  San Diego Tech. Rep}, vol.~12, no.~1-17, p.~1, 2005.
+
+\bibitem{narayanan2010sample}
+H.~Narayanan and S.~Mitter, ``Sample complexity of testing the manifold
+  hypothesis,'' in {\em Advances in Neural Information Processing Systems},
+  pp.~1786--1794, 2010.
+
+\bibitem{rifai2011manifold}
+S.~Rifai, Y.~N. Dauphin, P.~Vincent, Y.~Bengio, and X.~Muller, ``The manifold
+  tangent classifier,'' in {\em Advances in Neural Information Processing
+  Systems}, pp.~2294--2302, 2011.
+\end{thebibliography}
+
 \end{document}

### 2020-06-22 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Moved eigenvector ensembling algorithm section to main text in article_with_comments

--- 2020-06-21 8_prb_submission/1_reply_referee/article/article.tex
@@
 \newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
-\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional
-                                %derivative
+\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative
+
+\newcounter{quoter}
+\setcounter{quoter}{0}
+\renewcommand*{\thequoter}{%
+  %\textbf{%
+  %  \ifnum\value{custom}<1000 0\fi
+  %  \ifnum\value{custom}<100 0\fi
+  %  \ifnum\value{custom}<10 0\fi
+  %  \arabic{custom}%
+  \textbf{[\arabic{quoter}]}
+  }%
+
+\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
+\newcommand{\citequote}[1]{\ref{#1}}
+
+\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
 
 \begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Comments referee %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Reply to the first referee }
+\section*{Reply to the second referee}
+Dear referee,
+
+we appreciate the valuable insights on how to improve our article that you have provided us with.
+Below we address each of the emphasized points separately, as they were written in the reply that was sent back to us.
+We quote the issues raised in italic, and highlight in boldface the points that we thought were particularly relevant.
+
+\subsection*{Major}
+
+\emph{I am not sure about the novelty and generality of their method. For
+example, \textbf{their pipeline cannot work for complex experimental physical
+systems, where the Hamiltonian could be unknown}\genquote{pipeline_not_work}. Moreover, the authors
+state that it is sufficient to use the input data in real space to
+predict the topological phase with high accuracy. \textbf{It is not clear to
+me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of
+using the input data in real space instead of the Hamiltonian in
+wavevector space. \textbf{I expect the evidence to indicate that their method
+is superior or comparable to any other method}\genquote{superior_comparable}. It is worth mentioning
+that the author already discussed \textbf{the motivations for developing a
+data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological
+phases from real space data" section. However, these arguments should
+be pointed carefully in the "Introduction" section.}
+
+\vspace{0.25cm}
+\citequote{pipeline_not_work} Mention the possibility of using incomplete information with eigenvector ensembling.
+
+\citequote{sufficient_accuracy} ...
+
+\citequote{superior_comparable} Mention trends in model explainability as well as performance scores.
+
+\textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data driven approach based on real space data should be in the Introduction.
+We have therefore moved the first paragraph of the section "Learning topological phases from real space data" that addresses this issue to the Introduction.}
+
+\vspace{0.5cm}
+\emph{I am not sure which crucial problems their algorithm can solve that
+was not possible before with machine learning. Furthermore, along with
+the emerging research of unsupervised learning methods in realizing
+the topological phases, \textbf{why should the supervised learning method be
+focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript,
+where I do not see the proposal's advantages, I would prefer the
+\textbf{unsupervised approaches that could grasp information from a given
+system without knowing their phases}\genquote{unsupervised_approaches}. In my opinion, a proper intrinsic
+route for understanding physical systems without much information on
+the dynamics of the system will lead to significant future
+developments and a better understanding of physic systems.}
+
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{unsupervised_learning}, \citequote{unsupervised_approaches} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
+The most straightforward way to do this is by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
+This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the entropic uncertainty relations included in this new version of the article.
+It should be noted, however, that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
+This point is now explicitly mentioned in this new version of the paper, in the last paragraph of the section "THE EIGENVECTOR ENSEMBLING ALGORITHM" which was moved to the main body of the paper.}
+
+\citequote{unsupervised_approaches} Mention Hamiltonian compression, of unsupervised learning through dimensional reduction.
+
+\vspace{0.5cm}
+\emph{The details of \textbf{the eigenvector ensembling algorithm should be
+addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material. What is
+the specific algorithm used in the paper to train on eigenvectors? I
+think it is important even if the readers are not familiar with some
+ML techniques. Some readers in physics may find it difficult to
+understand some ML technical terms such as bootstrapping, training and
+validation, test sets, etc. In addition, \textbf{I expect proof of what
+"physics" their method captures and why the eigenvector can play an
+important role in characterizing the topological phase}\genquote{eigenvector_physics}. If this
+physical interpretability is not mentioned, it is very difficult to
+see the contribution of the method in physics.}
+
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{eigenvector_ensembling_alg} We have moved the section "The eigenvector ensembling algorithm" to the main paper.
+The issue of specifying the particular learning algorithms used was also addressed in the same section.}
+
+\citequote{eigenvector_physics} One of the strongest points of the paper is to introduce model explainability tools from machine learning in physics.
+The need to use eigenvectors is that they encode all the physical information from a system.
+The paper paves the way for new theoretical investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
+
+\vspace{0.5cm}
+\emph{The authors made efforts to analyze how the algorithm was able to
+recover the Hamiltonians' global property in the "Information Entropy
+Signatures" section. The authors state that learning topological
+phases from local real-space data in bulk is still possible even for
+small subsets of lattice sites, then refer us to the section "Learning
+topological phases from real space data" in the Supplementary
+Material. The authors mention on page 4 of the Supplementary Material
+that \textbf{"key topological information can be said to be localized on a few
+lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
+However, I fail to understand the physical insights behind it. Without
+the proper explanation, \textbf{it is difficult to see the effectiveness of
+their method or verify the method with a more complex model}\genquote{more_complex_model} instead of
+the simple SSH form.}
+
+\vspace{0.25cm}
+\citequote{key_top} Move this sentence to main paper.
+
+\citequote{more_complex_model} Add FFT of entropy signatures?
+Mention entropic uncertainty?
+Talk about information gain?
+Mention that interpretability in ML is often challenging and a fast evolving field.
+Furthermore, eigenvector ensembling can always be used as a preprocessing step to other ML models, such as in semi supervised learning tasks.
+
+\subsection*{Minor}
+
+\emph{The authors state in the abstract that "model explainability in
+machine learning can advance the research of exotic quantum materials
+with properties that may power future technological applications such
+as qubit engineering for quantum computing." \textbf{Could you explain a bit
+more about properties that may power future quantum computing?}\genquote{quantum_comp}}
+
+\vspace{0.25cm}
+\citequote{quantum_comp} Insert comments about topological qubits?
+
+\vspace{0.5cm}
+\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single
+iterations of experiments 1 and 2 as seen from parameter space". \textbf{What
+are the experiments 1 and 2?}\genquote{experiments_1_2}}
+
+\vspace{0.25cm}
+\citequote{experiments_1_2} Experiments 1 and 2 were mentioned as subtitles to the sections.
+
+\vspace{0.5cm}
+\emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
+such as "the accuracy" and "the probability heatmap," "eigenvector
+accuracy," and "Hamiltonian accuracy."}
+
+\vspace{0.25cm}
+\citequote{evaluation_metrics}
+
+\vspace{0.5cm}
+\emph{I prefer to \textbf{put the definition of information entropy signatures in
+the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
+
+\vspace{0.25cm}
+\citequote{inf_entropy_sig}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\pagebreak
+
 \nocite{*}
@@
 
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+\textcolor{blue}{The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
 disordered systems in condensed matter) do not have.
 Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
+We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.}\citequote{motif_real_space}
 
@@
 
-The Shannon information entropy signals presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
+\textcolor{blue}{The topological signals recovered from the analysis of real space eigenvector data can be further theoretically explored as information entropy mass functions along the lattices in real space.
+By computing their Fourier transform, we retrieve similar information entropy mass functions in wavevector space.
+These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
+We use the Bialynicki-Birula-Mycielski inequality to bound the localizability of Shannon information entropy in topological phase transitions.}   \cite{xxxx}
+
+\textcolor{blue}{As of yet model explainability is one of the topics at the forefront of machine learning research that has been little explored by the physics community working at the interface between the two disciplines}\citequote{unsupervised_learning}.
+The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
 
@@
 \end{figure}
+
+\section*{The eigenvector ensembling algorithm}\citequote{eigenvector_ensembling_alg}
+
+\textcolor{blue}{
+We describe here in detail each step of the eigenvector ensembling algorithm as implemented is this article.
+\vspace{.3cm}
+\begin{enumerate}%[topsep=0pt, partopsep=0pt]
+\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
+These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
+\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
+More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
+We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
+\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$.
+Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
+Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
+\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
+This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
+In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
+\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
+The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
+\end{enumerate}
+\vspace{.3cm}
+In step 3) we used the implementations of decision trees and random forest classifiers from Python's Scikit-learn module.
+As mentioned in the Introduction, the choice of these particular algorithms is based on their powerful and accessible model explainability capabilities.
+This choice was made in conformity with our main purpose in this work, which is to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
+Nevertheless, the steps above are flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}\citequote{unsupervised_learning}
 
@@
 \end{figure}
+
+\citequote{motif_real_space}
 

### 2020-06-24 8_prb_submission/1_reply_referee/reply_referee.tex
Generated template of reply to referee
Added comments about sampling and dimensionality reduction

@@
 \begin{document}
-\section{Reply to the first referee }
-\section{Reply to the second referee}
+\section*{Reply to the first referee }
+\section*{Reply to the second referee}
 Dear referee,
 
-we appreciate the valuable insigths on how to improve our article that you have provided us.
-Below we address each of the points you emphasized separately, as they were written in your reply.
-We quote the issues raised by you in purple, and highlight in boldface the points that we thought were particularly relevant.
+we appreciate the valuable insights on how to improve our article that you have provided us with.
+Below we address each of the emphasized points separately, as they were written in the reply that was sent back to us.
+We quote the issues raised in italic, and highlight in boldface the points that we thought were particularly relevant.
 
-\subsection{Major}
+\subsection*{Major}
 
-\textcolor{antiquefuchsia}{I am not sure about the novelty and generality of their method. For
+\emph{I am not sure about the novelty and generality of their method. For
 example, \textbf{their pipeline cannot work for complex experimental physical
@@
 
-\citequote{motif_real_space}We agree that the motivation for using real space data to study topological phase transitions should be placed in the introduction.
-We have therefore moved the first paragraph of the section "Learning topological phases from real space data" to the introduction.
+\citequote{motif_real_space} We have therefore moved the first paragraph of the section "Learning topological phases from real space data" to the introduction.
 
 \vspace{0.5cm}
-\textcolor{antiquefuchsia}{I am not sure which crucial problems their algorithm can solve that
+\emph{I am not sure which crucial problems their algorithm can solve that
 was not possible before with machine learning. Furthermore, along with
@@
 \vspace{0.5cm}
-\textcolor{antiquefuchsia}{The details of \textbf{the eigenvector ensembling algorithm should be
+\emph{The details of \textbf{the eigenvector ensembling algorithm should be
 addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material. What is
@@
 \vspace{0.5cm}
-\textcolor{antiquefuchsia}{The authors made efforts to analyze how the algorithm was able to
+\emph{The authors made efforts to analyze how the algorithm was able to
 recover the Hamiltonians' global property in the "Information Entropy
@@
 Furthermore, eigenvector ensembling can always be used as a preprocessing step to other ML models, such as in semi supervised learning tasks.
+
+\subsection*{Minor}
+
+\emph{The authors state in the abstract that "model explainability in
+machine learning can advance the research of exotic quantum materials
+with properties that may power future technological applications such
+as qubit engineering for quantum computing." \textbf{Could you explain a bit
+more about properties that may power future quantum computing?}\genquote{quantum_comp}}
+
+\vspace{0.25cm}
+\citequote{quantum_comp} Insert comments about topological qubits?
+
+\vspace{0.5cm}
+\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single
+iterations of experiments 1 and 2 as seen from parameter space". \textbf{What
+are the experiments 1 and 2?}\genquote{experiments_1_2}}
+
+\vspace{0.25cm}
+\citequote{experiments_1_2} Experiments 1 and 2 were mentioned as subtitles to the sections.
+
+\vspace{0.5cm}
+\emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
+such as "the accuracy" and "the probability heatmap," "eigenvector
+accuracy," and "Hamiltonian accuracy."}
+
+\vspace{0.25cm}
+\citequote{evaluation_metrics}
+
+\vspace{0.5cm}
+\emph{I prefer to \textbf{put the definition of information entropy signatures in
+the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
+
+\vspace{0.25cm}
+\citequote{inf_entropy_sig}
+
 \end{document}

### 2020-06-24 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Added comments about sampling and dimensionality reduction

@@
 
-\emph{I am not sure about the novelty and generality of their method. For
-example, \textbf{their pipeline cannot work for complex experimental physical
-systems, where the Hamiltonian could be unknown}\genquote{pipeline_not_work}. Moreover, the authors
+\emph{\textbf{I am not sure about the novelty and generality of their method.}\genquote{pipeline_not_work} For
+example, their pipeline cannot work for complex experimental physical
+systems, where the Hamiltonian could be unknown. Moreover, the authors
 state that it is sufficient to use the input data in real space to
@@
 \vspace{0.25cm}
-\citequote{pipeline_not_work} Mention the possibility of using incomplete information with eigenvector ensembling.
+\textcolor{blue}{\citequote{pipeline_not_work} We can think of several use cases for the eigenvector ensembling procedure outlined in the paper.
+Among these, we emphasize its applicability in tackling the so-called "curse of dimensionality" that plagues many problems in condensed matter and statistical physics.
+In the paper, we have demonstrated an application in which the dimensionality of an SSH lattice can be greatly reduced in so far as its topological properties are concerned, simply by extracting the most relevant lattice sites in its information entropy signature.
+Similar feature extraction and dimensionality reduction procedures are often employed in machine learning applications and are surely to become the norm in data-driven physics.
+The eigenvector ensembling algorithm can thus be viewed as a general framework in this direction.
+Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
+We have added a paragraph to the \textbf{Discussion} section outlining these possibilities.
+As for the novelty of the method, the eigenvector ensembling algorithm together with the explainability powers of decision trees allowed us to rigorously investigate the information entropy of topological phase transitions.
+To our knowledge, our work pioneers the discovery of new concepts in physics through model explainability in machine learning.
+}
 
@@
 \textcolor{blue}{\citequote{unsupervised_learning}, \citequote{unsupervised_approaches} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
-The most straightforward way to do this is by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
+We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
 This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the entropic uncertainty relations included in this new version of the article.
 It should be noted, however, that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in the last paragraph of the section "THE EIGENVECTOR ENSEMBLING ALGORITHM" which was moved to the main body of the paper.}
+This point is now explicitly mentioned in this new version of the paper, in the last paragraph of the section "The eigenvector ensembling algorithm" which was moved from the Supplementary Material to the main paper.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool, and therefore many current }
 
@@
 \textcolor{blue}{\citequote{eigenvector_ensembling_alg} We have moved the section "The eigenvector ensembling algorithm" to the main paper.
-The issue of specifying the particular learning algorithms used was also addressed in the same section.}
-
-\citequote{eigenvector_physics} One of the strongest points of the paper is to introduce model explainability tools from machine learning in physics.
+The issue of specifying the particular learning algorithms used to train on eigenvectors was also addressed in the same section.}
+
+\citequote{eigenvector_physics} One of the main themes of the paper is to use model explainability tools from machine learning in to arrive at new concepts in physics.
 The need to use eigenvectors is that they encode all the physical information from a system.
@@
 \vspace{0.25cm}
-\citequote{key_top} Move this sentence to main paper.
+\textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
+We have therefore moved it to the final patragraph of the section "Information entropy signatures" in the main text.}
 
@@
 These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.}\citequote{key_top} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
 
@@
 This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
-It is therefore expected that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+
+\textcolor{blue}{As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
+This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
+An approach based on eigenvector ensembling can be of use in such situations both as a dimensionality reduction tool and as a sampling strategy.
+The first case was illustrated in this work, where it was shown that relevant topological information of SSH systems can be retrieved from few sites in a lattice, which can be exploited as a dimensionality reduction strategy.
+The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
+Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.}\citequote{pipeline_not_work}  We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
 

### 2020-06-25 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Added more corrections

@@
 lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
-However, I fail to understand the physical insights behind it. Without
-the proper explanation, \textbf{it is difficult to see the effectiveness of
-their method or verify the method with a more complex model}\genquote{more_complex_model} instead of
+However, \textbf{I fail to understand the physical insights behind it}\genquote{physical_insights}. Without
+the proper explanation, it is difficult to see the effectiveness of
+their method or verify the method with a more complex model instead of
 the simple SSH form.}
@@
 
-\citequote{more_complex_model} Add FFT of entropy signatures?
+\citequote{physical_insights} Add FFT of entropy signatures?
 Mention entropic uncertainty?
@@
 Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.}\citequote{motif_real_space}
+The data-driven approach described in this article addresses these issues.
+In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems} \citequote{motif_real_space}
+
+%We develop here an alternative data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
+%\citequote{motif_real_space}
 
@@
 
-\textcolor{blue}{The topological signals recovered from the analysis of real space eigenvector data can be further theoretically explored as information entropy mass functions along the lattices in real space.
+\textcolor{blue}{The topological signals recovered from the analysis of real space eigenvector data are then further theoretically explored as information entropy mass functions along the lattices in real space.
 By computing their Fourier transform, we retrieve similar information entropy mass functions in wavevector space.
 These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
-We use the Bialynicki-Birula-Mycielski inequality to bound the localizability of Shannon information entropy in topological phase transitions.}   \cite{xxxx}
+We use the Bialynicki-Birula-Mycielski inequality to bound the localizability of Shannon information entropy in topological phase transitions.}  \citequote{eigenvector_physics}, \citequote{physical_insights}
 
 \textcolor{blue}{As of yet model explainability is one of the topics at the forefront of machine learning research that has been little explored by the physics community working at the interface between the two disciplines}\citequote{unsupervised_learning}.
-The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
+The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.\citequote{pipeline_not_work}
 
@@
 \textcolor{blue}{
-We describe here in detail each step of the eigenvector ensembling algorithm as implemented is this article.
+The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
+We describe here in detail each of these steps as they were implemented in this work.
 \vspace{.3cm}
@@
 \item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
+More explicitly, assume our hopping parameters vector $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
 We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$.
+\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will provide $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$ to our data set.
 Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
@@
 The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
+\end{enumerate}}
+
 \vspace{.3cm}
-In step 3) we used the implementations of decision trees and random forest classifiers from Python's Scikit-learn module.
-As mentioned in the Introduction, the choice of these particular algorithms is based on their powerful and accessible model explainability capabilities.
-This choice was made in conformity with our main purpose in this work, which is to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the steps above are flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}\citequote{unsupervised_learning}
+\textcolor{blue}{In step 3) we used the implementations of decision trees and random forests from Python's scikit-learn module}\citequote{eigenvector_ensembling_alg}
 
@@
 
-The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-A detailed description of the algorithm is found in the section \textbf{The eigenvector ensembling algorithm} in the Supplementary Material.
-Here we present results of the numerical experiments we performed with it.
-We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
+We performed two numerical experiments with the eigenvector ensembling algorithm.
+The first experiment deals with the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), while the second experiment uses the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
 
@@
 This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the allowed winding number values.
+For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the correct winding number values.
 Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
 The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
+
+\textcolor{blue}{As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
+These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all eigenvectors (or Hamiltonians).
+Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy}
 
@@
 The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
-Our algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
+\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model as implemented in the scikit-learn Python module \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
 
@@
 These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
+\textcolor{blue}{When compared with the baseline test accuracy of 55.2\% of a system that predicts the whole test set as having winding number $W=1$, the accuracy of 99.1\% on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} \citequote{sufficient_accuracy}
 
@@
 Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.}\citequote{pipeline_not_work}  We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+
+\textcolor{blue}{Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
+In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
+This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
+Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}\citequote{unsupervised_learning}
 

### 2020-06-25 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Further comments

@@
 Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
-We have added a paragraph to the \textbf{Discussion} section outlining these possibilities.
-As for the novelty of the method, the eigenvector ensembling algorithm together with the explainability powers of decision trees allowed us to rigorously investigate the information entropy of topological phase transitions.
+We have added a paragraph to the section \textbf{Discussion} outlining these possibilities.
+As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
 To our knowledge, our work pioneers the discovery of new concepts in physics through model explainability in machine learning.
+We have added a last paragraph to the introduction emphasizing this point.
 }
 
-\citequote{sufficient_accuracy} ...
-
-\citequote{superior_comparable} Mention trends in model explainability as well as performance scores.
+\textcolor{blue}{\citequote{sufficient_accuracy}, \citequote{superior_comparable} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
+This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
+We have added a paragraph to the section \textbf{Numerical experiments} to emphasize the use of this baseline.
+As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
+Rev.
+Lett.
+120, 066401, where neural networks were trained on wavevector space data in a similar supervised learning task.
+This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.}
 
@@
 Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool, and therefore many current }
-
-\citequote{unsupervised_approaches} Mention Hamiltonian compression, of unsupervised learning through dimensional reduction.
 
@@
 
-\textcolor{blue}{As of yet model explainability is one of the topics at the forefront of machine learning research that has been little explored by the physics community working at the interface between the two disciplines}\citequote{unsupervised_learning}.
 The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.\citequote{pipeline_not_work}
 
+\textcolor{blue}{As of yet model explainability is one of the topics at the forefront of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
+By tying together contemporary concepts in physics (topological phase transitions and information theory) to a topic at the edge of machine learning research (model explainability) we hope to append the latter to the growing list of machine learning tools at physcists' disposal.
+}\citequote{pipeline_not_work}
 \begin{figure}
@@
 These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all eigenvectors (or Hamiltonians).
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy}
+Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
 
@@
 The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.
+
+\textcolor{blue}{The accuracy scores obtained in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
+This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information can most readily be recovered from in the SSH lattices investigated.}\citequote{superior_comparable}
 

### 2020-06-27 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Next thing to update: the eigenvector ensembling algorithm section

@@
 \textcolor{blue}{\citequote{pipeline_not_work} We can think of several use cases for the eigenvector ensembling procedure outlined in the paper.
-Among these, we emphasize its applicability in tackling the so-called "curse of dimensionality" that plagues many problems in condensed matter and statistical physics.
+Among these, we emphasize its applicability in dealing with the so-called "curse of dimensionality" that plagues many problems in condensed matter and statistical physics.
 In the paper, we have demonstrated an application in which the dimensionality of an SSH lattice can be greatly reduced in so far as its topological properties are concerned, simply by extracting the most relevant lattice sites in its information entropy signature.
@@
 As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
-To our knowledge, our work pioneers the discovery of new concepts in physics through model explainability in machine learning.
-We have added a last paragraph to the introduction emphasizing this point.
+Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the Shannon entropy signature and the information entropy uncertainty relations for topological phase transitions presented here for the first time.
+We have added a paragraph to the \textbf{Introduction} emphasizing this point.
 }
@@
 This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.}
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
+In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+Rev.
+Research 2, 023283,  whose theme is model interpretability of single-layer feedforward neural networks trained to recognize phase transitions of some topological condensed matter systems.
+When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties of the training data, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomenon underlying the data, which is the main purpose of our work.
+}
 
 \textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data driven approach based on real space data should be in the Introduction.
-We have therefore moved the first paragraph of the section "Learning topological phases from real space data" that addresses this issue to the Introduction.}
+We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the Supplementary Material that addresses this issue to the Introduction.}
 
@@
 It should be noted, however, that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in the last paragraph of the section "The eigenvector ensembling algorithm" which was moved from the Supplementary Material to the main paper.
-Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool, and therefore many current }
+This point is now explicitly mentioned in this new version of the paper, in another paragraph added to the section \textbf{Discussion}.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool in data-driven physics, which by itself is an unsupervised learning task.}
 
@@
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{eigenvector_ensembling_alg} We have moved the section "The eigenvector ensembling algorithm" to the main paper.
+\textcolor{blue}{\citequote{eigenvector_ensembling_alg} We have moved the section \textbf{The eigenvector ensembling algorithm} from the Supplementary Material to the main paper.
 The issue of specifying the particular learning algorithms used to train on eigenvectors was also addressed in the same section.}
 
-\citequote{eigenvector_physics} One of the main themes of the paper is to use model explainability tools from machine learning in to arrive at new concepts in physics.
-The need to use eigenvectors is that they encode all the physical information from a system.
+\citequote{eigenvector_physics} In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy signature for topological phase transitions in SSH.
+The advantage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian encode all the physical information of the particular system in terms of local components in real space.
+In fact, the use of eigenvectors play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
+In the majority of the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
 The paper paves the way for new theoretical investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
@@
 
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
+The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired patterns in the data.
 This makes it much easier to trace the localization of relevant information along the features of a data set.
 Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
+This is a highly non-trivial proposition since the topological phase of a system is a global property of the system as a whole emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
 To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
@@
 These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
-We use the Bialynicki-Birula-Mycielski inequality to bound the localizability of Shannon information entropy in topological phase transitions.}  \citequote{eigenvector_physics}, \citequote{physical_insights}
+This allows us to establish the Bialynicki-Birula-Mycielski inequality as an uncertainty principle for the localizability of Shannon information entropy in topological phase transitions.}  \citequote{eigenvector_physics}, \citequote{physical_insights}
 
@@
 
-\textcolor{blue}{As of yet model explainability is one of the topics at the forefront of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
-By tying together contemporary concepts in physics (topological phase transitions and information theory) to a topic at the edge of machine learning research (model explainability) we hope to append the latter to the growing list of machine learning tools at physcists' disposal.
+\textcolor{blue}{As of yet model explainability\cite{https://ieeexplore.ieee.org/abstract/document/8631448?casa_token=ENOe4-VIc7kAAAAA:Tp8Aatj9Rx-9UcbOXtLbqNhG33nAt7_LEb-pG4-NC6wnQacmyRn0NqF4rrs2JGIDjgUgCNDLJaY, https://ieeexplore.ieee.org/abstract/document/8400040, https://ieeexplore.ieee.org/abstract/document/9007737} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines (this is also emphasized in \cite{https://arxiv.org/abs/1912.10057}).
+This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were already known.
+By proposing new concepts from the analysis of data from physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
 }\citequote{pipeline_not_work}
@@
 This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information can most readily be recovered from in the SSH lattices investigated.}\citequote{superior_comparable}
+
+\textcolor{blue}{We should also compare our results to those obtained in \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some physical systems.
+In that paper, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed correspond to known physical quantities that are relevant to the problems at hand.
+This should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems at hand.
+In our paper we prefer the term "model explainability", as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
+While the nuances in the meanings of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}\citequote{superior_comparable}
 

### 2020-06-27 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Stopped at issue 9.

@@
 \textcolor{blue}{\citequote{eigenvector_ensembling_alg}  We have moved the section \textbf{The eigenvector ensembling algorithm} from the Supplementary Material to the main paper.
-The issue of specifying the particular learning algorithms used to train on eigenvectors was also addressed in the same section.}
-
-\citequote{eigenvector_physics} In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy signature for topological phase transitions in SSH.
-The advantage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian encode all the physical information of the particular system in terms of local components in real space.
-In fact, the use of eigenvectors play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
-In the majority of the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
-The paper paves the way for new theoretical investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
+The issue of specifying the particular learning algorithms used to train on eigenvectors is addressed in the subsections for each SSH experiment (see subsections \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees} and \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}).
+In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module.}
+
+\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
+Therefore, by expressing a data set of eigenvectors on a suitable choice of basis (which in this paper is the real space basis), we are able to investigate properties of a family of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
+Thus the use of eigenvectors greatly facilitates the exploration of model explainability techniques in data-driven physics applications while at the same time not leading to a loss of information from the systems being investigated.
+As to the physics being captured by our procedure, we emphasize that the Shannon entropy signatures of topological phase transitions demonstrated in our paper are physically interpretable in terms of entropic uncertainty relations which ultimately lead to the development of an uncertainty principle limiting the localizability of topological phase transitions.
+This topic is explored in the new section \textbf{Entropic uncertainty relations}.}
+
+%While there may surely be other ways to achieve a similar result, using eigenvectors as input data is fairly straightforward and, as we have %demonstrated, as we have demonstrated tage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian %encode all the physical information of the particular system in terms of local components in real space.
+In fact, the use of eigenvectors %play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
+In the majority of %the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses %track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
+The paper paves the way for new theoretical %investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
+%In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy %signature and its corresponding entropic uncertainty relation for topological phase transitions in SSH systems.
+}
 
@@
 \vspace{.3cm}
-\textcolor{blue}{In step 3) we used the implementations of decision trees and random forests from Python's scikit-learn module}\citequote{eigenvector_ensembling_alg}
+\textcolor{blue}{Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
+The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
+The intuition that eigenvectors can be used in replacement to raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$, }
+\begin{equation}
+\label{eigen_decomposition}
+H = \sum_{i=1}^{N}\lambda^{(i)} \ket{\mathbf{v}^{(i)}}\bra{\mathbf{v}^{(i)}}
+\end{equation}
+where $\lambda^{(i)}$ \textcolor{blue}{is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
+It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
+By expressing the eigenvectors in a basis suitable to a particular problem (e.g.
+the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
+Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.}
+
+%\textcolor{blue}{In step 3) we used the implementations of decision trees and random forests from Python's scikit-learn module}\citequote{eigenvector_ensembling_alg}
 
@@
 The recovered probability heatmaps faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
+
+\textbf{blue}{The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit}.}
 
@@
 The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model as implemented in the scikit-learn Python module \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
+\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
 

### 2020-06-29 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Starting code on entropic uncertainty

@@
 When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
-While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties of the training data, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomenon underlying the data, which is the main purpose of our work.
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.
 }
 
-\textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data driven approach based on real space data should be in the Introduction.
-We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the Supplementary Material that addresses this issue to the Introduction.}
+\textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data-driven approach based on real space should be in the Introduction.
+We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the \textbf{Introduction}.}
 
@@
 It should be noted, however, that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in another paragraph added to the section \textbf{Discussion}.
-Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool in data-driven physics, which by itself is an unsupervised learning task.}
+This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{Discussion}.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool in data-driven physics, which by itself is an unsupervised learning task and can serve as a preprocessing step to further applications of machine learning to physics.}
 

### 2020-06-30 2_results/simulation_results.py
Coding Fourier transform of topological signals

@@ -1,4 +1,5 @@
 import numpy as np
+from scipy.fft import fft, rfft, fftfreq
 import pandas as pd
 import os
 import matplotlib.pyplot as plt
@@ -542,6 +543,7 @@ class ExperimentEnsemble(object):
         ### feature importances
         self.feature_importance = None
         self.cumulative_feature_importance = None
+        self.fourier_feature_importance = None
           
     def reset_current_experiment(self):
         """
@@ -663,6 +665,28 @@ class ExperimentEnsemble(object):
             with open(os.path.join(self.simulation_dir, "cumulative_feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
                 w.writerows(self.cumulative_feature_importance.items())
+                
+    def compute_fourier_feature_importance(self, fft="real", save_to_disk=False):
+        lattice_sites, feature_importance = zip(*self.feature_importance.items()) 
+        lattice_sites = np.array(lattice_sites)
+        feature_importance = np.array(feature_importance)
+        arg_sort = np.argsort(lattice_sites)
+        #lattice_sites = lattice_sites[arg_sort]
+        print("arg_sort: ", arg_sort)
+        print("lattice_sites: ", lattice_sites)
+        print("feature_importance: ", feature_importance)
+        feature_importance = feature_importance[arg_sort]
+        if fft == "real":
+            fourier_feature_importance = rfft(feature_importance)
+        self.fourier_feature_importance = dict(zip(lattice_sites,fourier_feature_importance))
+        self.cumulative_fourier_feature_importance = dict(zip(lattice_sites, np.cumsum(fourier_feature_importance)))
+        if save_to_disk:
+            with open(os.path.join(self.simulation_dir, "fourier_feature_importance.csv"), 'w') as f:  
+                w = csv.writer(f)
+                w.writerows(self.fourier_feature_importance.items())
+            with open(os.path.join(self.simulation_dir, "cumulative_feature_importance.csv"), 'w') as f:  
+                w = csv.writer(f)
+                w.writerows(self.cumulative_fourier_feature_importance.items())
 
     def create_plot(self, fig_params, xlabel_params, ylabel_params, title_params, xlim_params={}, ylim_params={}, xticks_params ={}, yticks_params={}):
         """
@@ -788,7 +812,7 @@ class ExperimentEnsemble(object):
         if len(savefig_params) > 0:
             plt.savefig(**savefig_params)  
 
[…]

### 2020-06-30 2_results/simulation_results.py
Generated feature importance pictures in fourier space in 0_results_template.ipynb

@@ -544,6 +544,7 @@ class ExperimentEnsemble(object):
         self.feature_importance = None
         self.cumulative_feature_importance = None
         self.fourier_feature_importance = None
+        self.cumulative_fourier_feature_importance = None
           
     def reset_current_experiment(self):
         """
@@ -666,7 +667,7 @@ class ExperimentEnsemble(object):
                 w = csv.writer(f)
                 w.writerows(self.cumulative_feature_importance.items())
                 
-    def compute_fourier_feature_importance(self, fft="real", save_to_disk=False):
+    def compute_fourier_feature_importance(self, save_to_disk=False):
         lattice_sites, feature_importance = zip(*self.feature_importance.items()) 
         lattice_sites = np.array(lattice_sites)
         feature_importance = np.array(feature_importance)
@@ -675,16 +676,17 @@ class ExperimentEnsemble(object):
         print("arg_sort: ", arg_sort)
         print("lattice_sites: ", lattice_sites)
         print("feature_importance: ", feature_importance)
-        feature_importance = feature_importance[arg_sort]
-        if fft == "real":
-            fourier_feature_importance = rfft(feature_importance)
+        #feature_importance = feature_importance[arg_sort]
+        #sqrt_feature_importance = np.sqrt(feature_importance)
+        #fourier_sqrt_feature_importance = fft(sqrt_feature_importance)
+        fourier_feature_importance = 1/(len(feature_importance))*np.power(np.absolute( fft(np.sqrt(feature_importance)) ),2)
         self.fourier_feature_importance = dict(zip(lattice_sites,fourier_feature_importance))
         self.cumulative_fourier_feature_importance = dict(zip(lattice_sites, np.cumsum(fourier_feature_importance)))
         if save_to_disk:
             with open(os.path.join(self.simulation_dir, "fourier_feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
                 w.writerows(self.fourier_feature_importance.items())
-            with open(os.path.join(self.simulation_dir, "cumulative_feature_importance.csv"), 'w') as f:  
+            with open(os.path.join(self.simulation_dir, "cumulative_fourier_feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
                 w.writerows(self.cumulative_fourier_feature_importance.items())
 
@@ -851,13 +853,17 @@ class ExperimentEnsemble(object):
             plt.savefig(**savefig_params)
         #plt.bar(importances)
 
[…]

### 2020-06-30 2_results/simulation_results.py
Generated feature importance pictures in fourier space in 0_results_template.ipynb

@@ -673,9 +673,9 @@ class ExperimentEnsemble(object):
         feature_importance = np.array(feature_importance)
         arg_sort = np.argsort(lattice_sites)
         #lattice_sites = lattice_sites[arg_sort]
-        print("arg_sort: ", arg_sort)
-        print("lattice_sites: ", lattice_sites)
-        print("feature_importance: ", feature_importance)
+        #print("arg_sort: ", arg_sort)
+        #print("lattice_sites: ", lattice_sites)
+        #print("feature_importance: ", feature_importance)
         #feature_importance = feature_importance[arg_sort]
         #sqrt_feature_importance = np.sqrt(feature_importance)
         #fourier_sqrt_feature_importance = fft(sqrt_feature_importance)

### 2020-07-01 2_results/simulation_results.py
Starting to write section on entropic uncertainty

@@ -545,6 +545,8 @@ class ExperimentEnsemble(object):
         self.cumulative_feature_importance = None
         self.fourier_feature_importance = None
         self.cumulative_fourier_feature_importance = None
+        self.feature_importance_statistics = {}
+        self.fourier_feature_importance_statistics = {}
           
     def reset_current_experiment(self):
         """
@@ -689,6 +691,35 @@ class ExperimentEnsemble(object):
             with open(os.path.join(self.simulation_dir, "cumulative_fourier_feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
                 w.writerows(self.cumulative_fourier_feature_importance.items())
+         
+    def compute_feature_importance_statistics(self,save_to_disk=False):
+        ### statistics in real space
+        x, rho_x = zip(*self.feature_importance.items())
+        arg_sort = np.argsort(x)
+        N = len(x)
+        x, rho_x = (1/N*np.array(x))[arg_sort], (np.array(rho_x))[arg_sort]
+        x_mean = np.dot(x,rho_x)
+        x_var = np.dot(np.power(x-x_mean,2),rho_x)
+        x_std = np.sqrt(x_var)
+        x_shannon= -np.dot(rho_x, np.log(rho_x))
+        self.feature_importance_statistics = {"mean": x_mean, "var": x_var, "std": x_std, "shannon": x_shannon}
+        ### statistics in wavevector space
+        p, rho_p = zip(*self.fourier_feature_importance.items())
+        arg_sort = np.argsort(p)
+        N = len(p)
+        p, rho_p = (1/N*np.array(p))[arg_sort], (np.array(rho_p))[arg_sort]
+        p_mean = np.dot(p,rho_p)
+        p_var = np.dot(np.power(p-p_mean,2),rho_p)
+        p_std = np.sqrt(p_var)
+        p_shannon = -np.dot(rho_p, np.log(rho_p))
+        self.fourier_feature_importance_statistics = {"mean": p_mean, "var": p_var, "std": p_std, "shannon": p_shannon}
+        if save_to_disk:
+            with open(os.path.join(self.simulation_dir, "feature_importance_statistics.csv"), 'w') as f:  
+                w = csv.writer(f)
+                w.writerows(self.feature_importance_statistics.items())
+            with open(os.path.join(self.simulation_dir, "fourier_feature_importance_statistics.csv"), 'w') as f:  
+                w = csv.writer(f)
[…]

### 2020-07-01 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Started writing section on uncertainty relations

@@
 \textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
-We have therefore moved it to the final patragraph of the section "Information entropy signatures" in the main text.}
+We have therefore moved it to the final patragraph of the section \textbf{Information entropy signatures} in the main text.}
 
@@
 \end{figure}
+
+\section*{Uncertainty relations}
+In this section we explore some theoretical possibilities that arise from the information entropy signatures presented in the previous section.
+The discussion presented here is complemented by the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
+
+We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
+macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
+By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by
+
+\begin{equation}
+\label{entropy_density}
+F_S(x) = \int_{0}^x\rho_S(x')dx'
+\end{equation}
+
+where $x \in [0,1]$ is a spatial coordinate along the lattice and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
+
+Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
+
+\begin{equation}
+\label{shannon_wave_function}
+\rho_S(x) = |\psi_S(x)|^2,
+\end{equation}
+the amount of topological information available from a single lattice site then being computed by Born's rule,
+
+\begin{equation}
+\label{born_rule_spatial}
+\rho_S(x_i) = |\braket{x_i|\psi_S}|^2, \qquad i=0,\dots,N-1.
+\end{equation}
+
+The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues for investigation.
+Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform
+\begin{equation}
+\label{fourier_shannon_wave_function}
+\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
+\end{equation}
+from which the Shannon information entropy density function can be computed in wavevector space,
+\begin{equation}
+\label{shannon_wave_function_wavevector_space}
+\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
+\end{equation}
+In possession of this quantum formalism, we may write two canonical uncertainty relations binding together the real space and wavevector space information entropy density functions \ref{shannon_wave_function} and \ref{shannon_wave_function_wavevector_space} for topological phase transitions:
+\begin{enumerate}
+\item[i)] \emph{The Heisenberg uncertainty principle}
+\begin{equation}
+\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi} \quad
+\end{equation}
+and 
+\item[ii)] \emph{The Hirschman entropic uncertainty}
+\begin{equation}
+H[\rho_S] + H[\hat{\rho}_S] \geq \log\Big(\frac{e}{2}\Big). \quad
+\end{equation}
+\end{enumerate}
 

### 2020-07-02 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Finished section information entropy signatures in the macroscopic space

@@
 
-\section*{Uncertainty relations}
-In this section we explore some theoretical possibilities that arise from the information entropy signatures presented in the previous section.
-The discussion presented here is complemented by the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
+\section*{Information entropy signatures in the macroscopic limit}
+In this final section we explore theoretical possibilities that arise from the information entropy signatures presented in the previous section.
+The discussion presented here is complemented by the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
@@
 \end{equation}
-In possession of this quantum formalism, we may write two canonical uncertainty relations binding together the real space and wavevector space information entropy density functions \ref{shannon_wave_function} and \ref{shannon_wave_function_wavevector_space} for topological phase transitions:
+
+Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have 
+\begin{subequations}
+\label{statistics}
+\begin{equation}
+\label{mean}
+\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
+\end{equation}
+\begin{equation}
+\label{variance}
+\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
+\end{equation}
+\begin{equation}
+\label{entropy}
+H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx
+\end{equation}
+\end{subequations}
+
+In possession of this quantum formalism, we may write two canonical uncertainty relations binding together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space} for topological phase transitions:
+
 \begin{enumerate}
-\item[i)] \emph{The Heisenberg uncertainty principle}
+\item[i)] \emph{the Heisenberg uncertainty principle}
 \begin{equation}
-\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi} \quad
+\label{heisenberg}
+\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad
 \end{equation}
 and 
-\item[ii)] \emph{The Hirschman entropic uncertainty}
+\item[ii)] \emph{the Hirschman entropic uncertainty}
 \begin{equation}
-H[\rho_S] + H[\hat{\rho}_S] \geq \log\Big(\frac{e}{2}\Big). \quad
+\label{hirschman}
+H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
 \end{equation}
 \end{enumerate}
+
+Equations \eqref{entropy_density}-\eqref{hirschman} provide a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
+In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} provide rigorous measures of localizability of topological phase transitions in SSH systems based on information theory.
+
+Given that our analysis has now come full circle back to theoretical physics, we leave the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
@@
 
-\textcolor{blue}{We should also compare our results to those obtained in \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some physical systems.
+\textcolor{blue}{This paper should also contrasted with \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some physical systems.
 In that paper, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed correspond to known physical quantities that are relevant to the problems at hand.
-This should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems at hand.
+We agree that such tasks should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
 In our paper we prefer the term "model explainability", as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
@@
 A detailed discussion of this point is presented in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
+
+\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, passing through proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between the two disciplines can be enriching in both ways.
+}
 

### 2020-07-03 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Writing section emergent information entropy wave functions

--- 2020-06-29 8_prb_submission/1_reply_referee/article_with_comments/article.tex
@@
 Thus the use of eigenvectors greatly facilitates the exploration of model explainability techniques in data-driven physics applications while at the same time not leading to a loss of information from the systems being investigated.
-As to the physics being captured by our procedure, we emphasize that the Shannon entropy signatures of topological phase transitions demonstrated in our paper are physically interpretable in terms of entropic uncertainty relations which ultimately lead to the development of an uncertainty principle limiting the localizability of topological phase transitions.
-This topic is explored in the new section \textbf{Entropic uncertainty relations}.}
+As to the physics being captured by our procedure, see the answer to the issue \citequote{physical_insights}.}
 
@@
 \textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
-We have therefore moved it to the final patragraph of the section "Information entropy signatures" in the main text.}
-
-\citequote{physical_insights} Add FFT of entropy signatures?
-Mention entropic uncertainty?
-Talk about information gain?
-Mention that interpretability in ML is often challenging and a fast evolving field.
-Furthermore, eigenvector ensembling can always be used as a preprocessing step to other ML models, such as in semi supervised learning tasks.
+We have therefore moved it to the final patragraph of the section \textbf{Information entropy signatures} in the main text.}
+
+\citequote{physical_insights} We have added the new section \textbf{Emergent information entropy wave functions} in which we interpret an information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinit lattice.
+Therefore, the paper now performs a full cycle of data-driven physics, as we propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), use model explainability to extract new, previously unknown properties of the SSH systems (the information entropy signatures) and finally interpret these new properties in the light of theoretical physics.
+It is important to point that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the known relevant patterns associated with specific physical phenomena.
+Our paper goes beyond this task as we use machine learning and model explainability to discover new properties of the physical systems under consideration and (with the addition of this new section) map these previously unknown properties into new theoretical  constructs.
 
@@
 \vspace{0.25cm}
-\citequote{experiments_1_2} Experiments 1 and 2 were mentioned as subtitles to the sections.
+\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
+The designation "experiment 1" is used to abbreviate the subsection \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
+Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.
 
@@
 
-\section*{Introduction}
-
+\section{Introduction}
+\label{introduction}
 The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}.
@@
 
-\section*{The eigenvector ensembling algorithm}\citequote{eigenvector_ensembling_alg}
-
+\section{The eigenvector ensembling algorithm}\citequote{eigenvector_ensembling_alg}
+\label{the_eigenvector_ensembling_algorithm}
 \textcolor{blue}{
@@
 
-\section*{Numerical experiments}
-
+\section{Numerical experiments}
+\label{numerical_experiments}
 We performed two numerical experiments with the eigenvector ensembling algorithm.
@@
 
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiments 1 and 2 as seen from parameter space.
+Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
 The accuracy statistics presented in the following subsections and probability heatmaps shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
@@
 
-\subsection*{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-
+\subsection{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
+\label{experiment_1}
 Our test set in this experiment contained 1005 Hamiltonians (approx.
@@
 \subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 1 as seen from 2D parameter space.
+\caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
 (a) Train/validation/test split.
@@
 
-\subsection*{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{exp2}
+\subsection{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
+\label{experiment_2}
 
@@
 \subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 2 as seen from 2D parameter space.
+\caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
 (a) Train/validation/test split.
@@
 
-\section*{Information entropy signatures}
+\section{Information entropy signatures}
+\label{information_entropy_signatures}
 
@@
 Shannon information entropy or Gini impurity \cite{friedman2001elements}).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 and experiment 2 we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
+By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
 These signals are the information entropy signatures of each topological phase transition.
 
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for experiments 1 and 2.
+The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for each experiment.
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-
-Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them.
+For experiment 1 (section \ref{experiment_1}), only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+
+\textcolor{blue}{We should remark on the subtleties of the information entropy signatures presented here.
+Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
+In the next section, where we develop a quantum formalism for the information entropy signatures discovered in this section, these seemingly antagonistic conceptions shall be harmonized.
+What is important to emphasize at this point is that the information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.}
+
+\textcolor{blue}{To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
+This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
+The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
+In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.}
+
+%Another important point to be emphasized is that these signals were recovered from the analysis of data from several thousand SSH systems in %each experiment and therefore they are not a property of a single SSH lattice.
+They are rather a pattern that emerges from correlating %topological winding numbers with lattice eigenvector data for several SSH systems.
+
+\textcolor{blue}{Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
+In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
 They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
-
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy in experiment 1), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
+The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
+
+%The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further %theoretical investigation.
+This is pursued in the next section.
+We present the information entropy signatures for longer lattices in the %section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
+
+To see if learning the topological phases can be achieved efficiently by employing simpler models we reran each experiment using only a small subset of most relevant lattice sites.
+In our rerun of experiment 1 (section \ref{experiment_1}) using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
 Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
 
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy in experiment 2) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
+Mean accuracies for our rerun of experiment 2 (section \ref{experiment_2}) using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
 Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
@@
 \subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1.
+\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
 Heatmaps were averaged across all 100 iterations of the experiment.
@@
 \subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2.
+\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
 Heatmaps were averaged across all 100 iterations of the experiment.
@@
 
-\section*{Discussion}
+\textcolor{blue}{
+\section{Emergent information entropy wave functions}
+\label{emergent_information_entropy_wave_functions}
+}
+\textcolor{blue}{
+The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
+In this final section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
+Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
+The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
+
+\textcolor{blue}{
+We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
+macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
+By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by}
+
+\begin{equation}
+\label{entropy_density}
+F_S(x) = \int_{0}^x\rho_S(x')dx'
+\end{equation}
+where $x \in [0,1]$ is a spatial coordinate along the lattice and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
+
+\textcolor{blue}{
+Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
+}
+\begin{equation}
+\label{shannon_wave_function}
+\rho_S(x) = |\psi_S(x)|^2,
+\end{equation}
+the amount of topological information available from a single point in the continuous 1D string then being expressed in bra-ket notation by Born's rule,
+
+\begin{equation}
+\label{born_rule_spatial}
+\rho_S(x) = |\braket{x|\psi_S}|^2.
+\end{equation}
+
+\textcolor{blue}{
+The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues for theoretical investigation.
+Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+}
+
+\textcolor{blue}{
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
+\begin{equation}
+\label{fourier_shannon_wave_function}
+\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
+\end{equation}
+\textcolor{blue}{
+from which the Shannon information entropy density function can be computed in wavevector space,}
+\begin{equation}
+\label{shannon_wave_function_wavevector_space}
+\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
+\end{equation}
+\textcolor{blue}{
+Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have }
+\begin{subequations}
+\label{statistics}
+\begin{equation}
+\label{mean}
+\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
+\end{equation}
+\begin{equation}
+\label{variance}
+\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
+\end{equation}
+\begin{equation}
+\label{entropy}
+H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx,
+\end{equation}
+\end{subequations}
+\textcolor{blue}{
+with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H[\hat{\rho_S}]$ in terms of $k$ and $\hat{\rho}$.}
+
+\textcolor{blue}{
+In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}: }
+
+\begin{enumerate}
+\item[i)] \emph{the Heisenberg uncertainty principle}
+\begin{equation}
+\label{heisenberg}
+\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad \text{and }
+\end{equation}
+\item[ii)] \emph{the Hirschman entropic uncertainty}
+\begin{equation}
+\label{hirschman}
+H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
+\end{equation}
+\end{enumerate}
+
+\textcolor{blue}{
+The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
+In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} demonstrate the existence of a trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
+}
+
+\textcolor{blue}{
+Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D continuous string is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the whole SSH system.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
+Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
+}
+
+\textcolor{blue}{
+Given that our analysis has now come full circle back to theoretical physics, we leave the task of numerically exploring the equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
+}
+
+\section{Discussion}
+\label{discussion}
 
 Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have implemented a data-driven approach to the search for new topological materials bypassing the use of wavevector space data.
+Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
 
@@
 
-An advantage of using data from real space is that it enables us to investigate how topological information is distributed in the system.
-This was demonstrated by the information entropy signatures recovered from the Shannon entropy of ensembles of eigenvectors in each experiment.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.
-
-\textcolor{blue}{The accuracy scores obtained in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information can most readily be recovered from in the SSH lattices investigated.}\citequote{superior_comparable}
-
-\textcolor{blue}{We should also compare our results to those obtained in \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some physical systems.
+As we have seen, the use of real space data enabled us to investigate how topological information is distributed in SSH systems.
+This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment and led us to the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
+The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
+
+\textcolor{blue}{The accuracy scores obtained in the numerical experiments of section \ref{numerical_experiments} were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
+This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}\citequote{superior_comparable}
+
+\textcolor{blue}{This paper should also be contrasted with \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
 In that paper, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed correspond to known physical quantities that are relevant to the problems at hand.
-This should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems at hand.
+We agree that such tasks should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
 In our paper we prefer the term "model explainability", as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
@@
 
-We should remark on the subtleties of the information entropy signatures presented here.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, these importances actually express a global property of the whole lattice.
-Therefore, a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
-To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites in the subset.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
-Furthermore, it should be emphasized that these signals were recovered from the analysis of data from several thousand SSH systems in each experiment and therefore they are not a property of a single SSH lattice.
-They are rather a pattern that emerges from correlating topological phase with lattice eigenvector data for several SSH systems.
-
-We performed several tests on the information entropy signatures.
-By rerunning each experiment with longer lattices (i.e.
-increasing the number of unit cells) we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further theoretical investigation.
-A detailed discussion of this point is presented in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
+\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, passing through proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between the two disciplines can be enriching in both ways.
+}
 
@@
 \subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions from experiments 1 and 2.
-(a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
+\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
+(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
 These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2, the three visible peaks account for approximately 30\% of reduction in information entropy.
+(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
 These three peaks are located along lattice sites $S_2$.}

### 2020-07-03 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Writing section emergent information entropy wave functions
Move comparisons of accuracy scores to the numerical experiments section

@@
 This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
-In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.}
+
+\textcolor{blue}{\citequote{superior_comparable}In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
 Rev.
@@
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{unsupervised_learning}, \citequote{unsupervised_approaches} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
+\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
 We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
-This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the entropic uncertainty relations included in this new version of the article.
-It should be noted, however, that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
+This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the new section \textbf{Emergent information entropy wave functions} added to this new version of the article.}
+
+\textcolor{blue}{\citequote{unsupervised_approaches} Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
 This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{Discussion}.
@@
 
-\citequote{physical_insights} We have added the new section \textbf{Emergent information entropy wave functions} in which we interpret an information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinit lattice.
-Therefore, the paper now performs a full cycle of data-driven physics, as we propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), use model explainability to extract new, previously unknown properties of the SSH systems (the information entropy signatures) and finally interpret these new properties in the light of theoretical physics.
-It is important to point that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the known relevant patterns associated with specific physical phenomena.
-Our paper goes beyond this task as we use machine learning and model explainability to discover new properties of the physical systems under consideration and (with the addition of this new section) map these previously unknown properties into new theoretical  constructs.
+\textcolor{blue}{\citequote{physical_insights} We have added the new section \textbf{Emergent information entropy wave functions} in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinit lattice.
+Therefore, the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures) and finally iii) interpret these new properties in the light of theoretical physics.}
+
+\textcolor{blue}{We find it noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
+Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
 
@@
 \vspace{0.25cm}
-\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
+\textcolor{blue}{\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
 The designation "experiment 1" is used to abbreviate the subsection \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
-Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.
+Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.}
 
@@
 \vspace{0.25cm}
-\citequote{evaluation_metrics}
+\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{Numerical experiments}.}
 
@@
 \vspace{0.25cm}
-\citequote{inf_entropy_sig}
+\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
 
@@
 \textcolor{blue}{As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
-These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all eigenvectors (or Hamiltonians).
+These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
 Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
@@
 Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
-The accuracy statistics presented in the following subsections and probability heatmaps shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-The recovered probability heatmaps faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
+The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
+\textcolor{blue}{Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ = 100 experiments.
+The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps}.
+As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
 
@@
 \end{equation}
-where $x \in [0,1]$ is a spatial coordinate along the lattice and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
+where $x \in [0,1]$ is a spatial coordinate along the continuous lattice (which we shall call from now on string, to emphasize its continuity as opposed to a discrete lattice) and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
 
@@
 \end{equation}
-the amount of topological information available from a single point in the continuous 1D string then being expressed in bra-ket notation by Born's rule,
+the amount of topological information available from a single point in the string then being expressed in bra-ket notation by Born's rule,
 
@@
 The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
-In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} demonstrate the existence of a trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
+In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
 }
@@
 
-As we have seen, the use of real space data enabled us to investigate how topological information is distributed in SSH systems.
+As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
 This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment and led us to the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.

### 2020-07-03 8_prb_submission/1_reply_referee/article_with_comments/article.tex
More or less rounded version to resubmit

@@
 \textcolor{blue}{
-The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues for theoretical investigation.
+The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
 Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
@@
 \textcolor{blue}{
-from which the Shannon information entropy density function can be computed in wavevector space,}
+from which the Shannon information entropy density function in wavevector space can be computed,}
 \begin{equation}
@@
 \textcolor{blue}{
-Given that our analysis has now come full circle back to theoretical physics, we leave the task of numerically exploring the equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
+Given that our analysis has now come full circle back to theoretical physics, the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 }
@@
 Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
+
+\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching in to both disciplines.
+}
 
@@
 \textcolor{blue}{This paper should also be contrasted with \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
-In that paper, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed correspond to known physical quantities that are relevant to the problems at hand.
-We agree that such tasks should indeed be called "model interpretability", as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
-In our paper we prefer the term "model explainability", as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the meanings of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}\citequote{superior_comparable}
+In \cite{ml_interpretability}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
+We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
+In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
+While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}\citequote{superior_comparable}
+
+Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
+Given the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of Shannon information entropy, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Whether there is any relationship between the local topological markers detailed in \cite{PhysRevB.84.241106,caio2019topological} and the information entropy of the ensemble of eigenvectors discussed here is left for speculation.
 
@@
 }
-
-Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as Shannon information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
-Whether there is any relationship between local topological markers and the information entropy of the ensemble of eigenvectors is left for speculation.
 

### 2020-07-03 2_results/results_template_parameters.py
Generated feature importances in fourier space

@@ -139,7 +139,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "fig_params": {"figsize": [12,12]}, 
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
     "ylabel_params": {"ylabel": "reduction in information entropy (%)", "fontsize": 24},
-    "title_params": {"label": "Information entropy signature - SSH 1", "fontsize": 24},
+    "title_params": {"label": "Information entropy signature (real space) - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
     "xticks_params": {"ticks": [int(i) for i in np.linspace(0,int(chain_length)-1,10).astype(int)], "fontsize": 24},
@@ -158,7 +158,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "fig_params": {"figsize": [12,12]},
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
     "ylabel_params": {"ylabel": "cumulative reduction in information entropy (%)", "fontsize": 24},
-    "title_params": {"label": "Cumulative information entropy signature - SSH 1", "fontsize": 24},
+    "title_params": {"label": "Cumulative information entropy signature (real space) - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
     "xticks_params": {"ticks": [int(i) for i in np.linspace(0,int(chain_length)-1,10).astype(int)], "fontsize": 24},
@@ -167,7 +167,46 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     #cumulative_features_path_to_save = "/home/linneu/ml_topological_phases_in_real_space/paper/ssh1/periodic_100_6561/cumulative_feature_importances.png"
     "savefig_params": {"fname": os.path.join(figs_dir,"plot_cumulative_feature_importances.png")},
      },
-    }   
+   
+    ### Plotting fourier feature importances with plot_feature_importances
+    "plot_fourier_feature_importances_params": {
+    "n_features": None,
+    "fourier": True,
+    "plot": "bar",
+    "plot_params": {"color": "palevioletred", "width": 0.7},
+    "hist_precision": 1000,
+    "fig_params": {"figsize": [12,12]}, 
+    "xlabel_params": {"xlabel": "reciprocal lattice site", "fontsize": 24},
[…]

### 2020-07-03 2_results/simulation_results.py

@@ -36,7 +36,7 @@ SSH2_PERIODIC_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"perio
 SSH2_PERIODIC_220_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_220_6561")
 
 ### Paper directory
-FIGURES_DIR = "/home/rio/ml_topological_phases_in_real_space/paper"
+FIGURES_DIR = "/home/rio/ml_topological_phases_in_real_space/5_paper"
 # ssh1 figures
 SSH1_FIGURES_DIR = os.path.join(FIGURES_DIR,"ssh1")
 SSH1_PERIODIC_100_6561_FIGURES_DIR = os.path.join(SSH1_FIGURES_DIR,"periodic_100_6561")
@@ -543,8 +543,10 @@ class ExperimentEnsemble(object):
         ### feature importances
         self.feature_importance = None
         self.cumulative_feature_importance = None
+        self.real_psi = None
         self.fourier_feature_importance = None
         self.cumulative_fourier_feature_importance = None
+        self.fourier_psi = None
         self.feature_importance_statistics = {}
         self.fourier_feature_importance_statistics = {}
           
@@ -661,6 +663,7 @@ class ExperimentEnsemble(object):
             non_sorted_args = np.arange(len(mean_feature_importance))
             self.feature_importance = dict(zip(non_sorted_args, mean_feature_importance))
             self.cumulative_feature_importance = dict(zip(non_sorted_args, np.cumsum(mean_feature_importance) ) )
+        self.real_psi = {k:np.sqrt(v) for k,v in self.feature_importance.items()}
         if save_to_disk:
             with open(os.path.join(self.simulation_dir, "feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
@@ -668,12 +671,17 @@ class ExperimentEnsemble(object):
             with open(os.path.join(self.simulation_dir, "cumulative_feature_importance.csv"), 'w') as f:  
                 w = csv.writer(f)
                 w.writerows(self.cumulative_feature_importance.items())
+            with open(os.path.join(self.simulation_dir, "real_psi.csv"), 'w') as f:  
+                w = csv.writer(f)
+                w.writerows(self.real_psi.items())
                 
     def compute_fourier_feature_importance(self, save_to_disk=False):
-        lattice_sites, feature_importance = zip(*self.feature_importance.items()) 
[…]

### 2020-07-05 8_prb_submission/1_reply_referee/article_with_comments/article.tex
Writing section topological feature engineering

@@
 The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
-In this final section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
+In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
 Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
@@
 \textcolor{blue}{
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
+\begin{equation}
+\label{fourier_shannon_wave_function}
+\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
+\end{equation}
+\textcolor{blue}{
+from which the Shannon information entropy density function in wavevector space can be computed,}
+\begin{equation}
+\label{shannon_wave_function_wavevector_space}
+\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
+\end{equation}
+
+\textcolor{blue}{
 The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
@@
 
-\textcolor{blue}{
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
-\begin{equation}
-\label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
-\end{equation}
-\textcolor{blue}{
-from which the Shannon information entropy density function in wavevector space can be computed,}
-\begin{equation}
-\label{shannon_wave_function_wavevector_space}
-\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
-\end{equation}
 \textcolor{blue}{
@@
 }
+
+\section{Topological feature engineering}
+\label{topological_feature_engineering}
+
+In this last section, we show how the theoretical formalism sketched in section \ref{emergent_information_entropy_wave_functions} can be used to instigate yet another round of machine learning.
+As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of an SSH system can be largely decreased with little loss of information.
+Perhaps more interesting, nonetheless, are the possibilities that the information entropy signatures in real and wavevector space offer when used complementarily.
+Here we explore the engineering of new topological features in real space.
+
+The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the real space information entropy wave functions are real.
+The discretized version of equation \eqref{fourier_shannon_wave_function},
+\begin{equation}
+\label{discrete_fourier_transform}
+\hat{\psi}_S[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}\psi_S[m]e^{-i\frac{2\pi}{N}nm}
+\end{equation}
+which is simply the Discrete Fourier Transform (DFT) formula for digital signals, will accomplish this.
+After computing the norm of each component of the resulting discrete information entropy wave function $\hat{\psi}_S[n]$, we recover the information entropy signatures in wavevector space shown in figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2}.
+
+Contrary to their real space counterparts, the wavevector space information entropy signatures are highly localized, which by itself does not come as a surprise.
+This gives us an opportunity to engineer new features in real space that carry more relevant topological information than the simpler strategy of selecting the most important lattice sites in a real space information entropy signature.
+We may write equation \ref{discrete_fourier_transform} in matrix form as
+\begin{equation}
+\label{dft}
+\hat{\mathbf{\psi}}_S = \frac{1}{\sqrt{N}} \mathbf{\mathcal{F}}_{N}\mathbf{\psi}_S
+\end{equation}
+where we have used the Sylvester DFT matrix
+\begin{equation}
+\label{sylvester_dft}
+\mathbf{\mathcal{F}}_{N} = \begin{bmatrix}
+\omega_N^{0\cdot 0} & \omega_N^{0\cdot 1} & \omega_N^{0\cdot 2} &... & \omega_N^{0\cdot (N-1)}\\
+\omega_N^{1\cdot 0} & \omega_N^{1\cdot 1} & \omega_N^{1\cdot 2} &... & \omega_N^{1\cdot (N-1)}\\
+\omega_N^{2\cdot 0} & \omega_N^{2\cdot 1} & \omega_N^{2\cdot 2} &... & \omega_N^{2\cdot (N-1)}\\
+\vdots & \vdots & \vdots & \cdots & \vdots\\ 
+\omega_N^{(N-1)\cdot 0} & \omega_N^{(N-1)\cdot 1} & \omega_N^{(N-1)\cdot 2} &... & \omega_N^{(N-1)\cdot (N-1)}\\
+\end{bmatrix}, \quad \text{with} \quad \omega_N = e^{-i\frac{2\pi}{N}}.
+\end{equation}
+
+When trying to engineer informative global topological features in real space, the information entropy signatures in wavevector space provide good hints of where to start.
+Figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} show us that in both numerical experiments the zeroth component in wave vector space is the most important  for learning the topological phases, contributing about 49\% of reduction in information entropy in experiment 1 (section \ref{experiment_1}) and 95\% in experiment 2 (section \ref{experiment_2}).
+Let $x[m]$ be an eigenvector in real space.
+We can use equation \eqref{dft} to compute its wavevector space representation $k[n]$ and in particular its zeroth component,
+\begin{equation}
+\label{k_0} 
+k[0] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m].
+\end{equation}
+Equation \eqref{k_0} indicates that simply knowing the sum of components of the eigenvectors in real space may provide key information about the topological phases of SSH Hamiltonians.
+To visually examine this proposition, we can draw histograms
+
+The next most relevant components in wavevector space in both numerical experiments are the symmetric pair (2,98), which together reduce approximately 10\% of information entropy in experiment 1 (section \ref{experiment_1}) and 2.5\% in experiment 2 (section \ref{experiment_2}).
+The pair (2,98) in wavevector space leads us to another real space engineered feature,
+\begin{equation}
+\label{k_2_98} 
+\frac{k[2]+k[98]}{\sqrt{2}} = \sqrt{\frac{2}{N}}\sum_{m=0}^{N-1}x[m]\cos(2m\omega_N).
+\end{equation}
+
+The two engineered features, $k[0]$ and $\frac{k[2]+k[98]}{\sqrt{2}}$
+
+\begin{equation}
+\label{matrix_discrete_fourier_transform}
+\begin{bmatrix}
+\hat{\psi}_S[0] \\
+\hat{\psi}_S[1] \\
+\vdots \\
+\hat{\psi}_S[N-1]
+\end{bmatrix} = \frac{1}{\sqrt{N}}\begin{bmatrix}
+1 & 1 & 1 &... & 1\\
+1 & W_N & W_N^2 &... &W_N^{N-1}\\
+1 & W_N^2 & W_N^4 &... & W_N^{2(N-1)}\\
+\vdots & \vdots & \vdots & \cdots & \vdots\\ 
+1 & W_N^{N-1} & W_N^{2(N-1)} & \cdots & W_N^{(N-1)^2}    
+\end{bmatrix}
+\begin{bmatrix}
+\psi_S[0] \\
+\psi_S[1] \\
+\vdots \\
+\psi_S[N-1]
+\end{bmatrix}
+\end{equation}
+
+Let us define a discrete wavevector space unit pulse as
+
+\begin{equation}
+\label{wavevector_unit_impulse}
+\hat{\delta}^{(m)}_n = \hat{\delta}[n-m] =
+\begin{cases}
+    1, & \text{if } n=m\\
+    0,              & \text{otherwise}.
+\end{cases}
+\end{equation}
+
+Then equation \eqref{discrete_fourier_transform} yields
+
+\begin{equation}
+\label{fourier_wavevector_unit_impulse}
+\hat{\delta}^{(m)}_n = \hat{\delta}[n-m] =
+\begin{cases}
+ \frac{1}{\sqrt{N}}\sum_{l=0}^{N-1}x[l]e^{-\frac{2\pi i}{N} nl}, & \text{if } n=m\\
+    0,              & \text{otherwise}
+\end{cases}
+\end{equation}
+Let us consider the Inverse Discrete Fourier Transform (IDFT) formula, which allows us to invert equation
+
+ \eqref{discrete_fourier_transform}
+
+\begin{equation}
+\label{inverse_discrete_fourier_transform}
+\psi_S[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}\hat{\psi}_S[m]e^{\frac{2\pi i}{N} mn}.
+\end{equation}
+
+In both figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2}, the main mode in wavevector space
+
+ main mode of the wavevector space information entropy signatures, which is
 
@@
 \label{feature_importances}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{\label{fourier_feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_fourier_feature_importances.png}}\quad
+\subfigure[]{\label{fourier_feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_fourier_feature_importances.png}}\quad
+\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
+(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
+These two peaks correspond to the lattice sites $S_1$.
+(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
+These three peaks are located along lattice sites $S_2$.}
+\label{fourier_feature_importances}
 \end{figure}

### 2020-07-06 08_arxiv/main.tex
Coded simulations with fourier engineered features

--- 2020-05-05 paper/main.tex
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only 6 lattice sites $S_1$ = (1, 2, 4, 51, 52, 54) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed more than 70\% of total reduction in Shannon entropy.
-Similarly, more than 30\% of total reduction in the Shannon entropy of eigenvector data from experiment 2 was achieved by 18 lattice sites $S_2$ = (1, 2, 3, 4, 5, 6, 47, 49, 50, 51, 52, 54, 95, 96, 97, 98, 99, 100) located at the three peaks in figure \ref{feature_importances_ssh2}.
+For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
 
 Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector-ensembling algorithm.
+They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
 We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
 
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only the most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S_1$, mean accuracies were 97.1\% for training eigenvectors, 94.5\% for validation eigenvectors and 78.6\% for test eigenvectors.
-Mean accuracies obtained from eigenvector-ensembling were 98.9\% for training Hamiltonians, 98.5\% for validation Hamiltonians and 98.9\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S_2$ were 99.9\% for training eigenvectors, 96.0\% for validation eigenvectors and 63.7\% for test eigenvectors.
-Eigenvector-ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.6\% for validation Hamiltonians and 90.4\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data is still possible even for small subsets of lattice sites.
+To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
+In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy in experiment 1), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
+Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
+
+Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy in experiment 2) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
+Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
+
+These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
 We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
@@
 
+\bibitem{asboth2016short}
+\bibinfo{author}{Asb{\'o}th, J.~K.}, \bibinfo{author}{Oroszl{\'a}ny, L.} \&
+  \bibinfo{author}{P{\'a}lyi, A.}
+\newblock \bibinfo{journal}{\bibinfo{title}{A short course on topological
+  insulators}}.
+\newblock {\emph{\JournalTitle{Lecture notes in physics}}}
+  \textbf{\bibinfo{volume}{919}} (\bibinfo{year}{2016}).
+
+\bibitem{goodfellow2016deep}
+\bibinfo{author}{Goodfellow, I.}, \bibinfo{author}{Bengio, Y.} \&
+  \bibinfo{author}{Courville, A.}
+\newblock \emph{\bibinfo{title}{Deep learning}} (\bibinfo{publisher}{MIT press,
+  Cambridge, MA, USA}, \bibinfo{year}{2016}).
+
+\bibitem{bishop2006pattern}
+\bibinfo{author}{Bishop, C.~M.}
+\newblock \emph{\bibinfo{title}{Pattern recognition and machine learning}}
+  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2006}).
+
+\bibitem{cayton2005algorithms}
+\bibinfo{author}{Cayton, L.}
+\newblock \bibinfo{journal}{\bibinfo{title}{Algorithms for manifold learning}}.
+\newblock {\emph{\JournalTitle{Univ. of California at San Diego Tech. Rep}}}
+  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{1} (\bibinfo{year}{2005}).
+
+\bibitem{narayanan2010sample}
+\bibinfo{author}{Narayanan, H.} \& \bibinfo{author}{Mitter, S.}
+\newblock \bibinfo{title}{Sample complexity of testing the manifold
+  hypothesis}.
+\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
+  Processing Systems}}, \bibinfo{pages}{1786--1794} (\bibinfo{year}{2010}).
+
+\bibitem{rifai2011manifold}
+\bibinfo{author}{Rifai, S.}, \bibinfo{author}{Dauphin, Y.~N.},
+  \bibinfo{author}{Vincent, P.}, \bibinfo{author}{Bengio, Y.} \&
+  \bibinfo{author}{Muller, X.}
+\newblock \bibinfo{title}{The manifold tangent classifier}.
+\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
+  Processing Systems}}, \bibinfo{pages}{2294--2302} (\bibinfo{year}{2011}).
+
 \end{thebibliography}
+%\bibliographystyle{plain}
+%\bibliographystyle{ieeetr}
 
@@
 
-%\begin{figure}
-%\centering
-%\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{fig1a-6561-less-simulation_merged_winding_grid.png}}
-%\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{fig1b-6561-less-simulation_merged_winding_grid.png}}
-%\caption{Probability heatmaps learned from most relevant lattice sites.
-(a) Probability heatmap learned in experiment 1 using only lattice %sites $S_1$.
-(b) Probability heatmap learned in experiment 2 using only lattice sites $S_2$.}
-%\label{less_feat}
-%\end{figure}
+\begin{figure}
+\centering
+\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{./ssh1/periodic_less_100_6561/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{./ssh2/periodic_less_100_6561/merge_imshow_winding_grids_sim.png}}
+\caption{Phase diagrams learned from most relevant lattice sites.
+(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99).
+The accuracy achieved for Hamiltonians in the test set using only the four lattice sites in $S'_1$ was approximately 95\%.
+(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99).
+The accuracy achieved for Hamiltonians in the test set using only the nine lattice sites in $S'_2$ was approximately 74\%.}
+\label{less_feat}
+\end{figure}
 
@@
 
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \citesupp{bishop2006pattern}.
+The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \cite{bishop2006pattern}.
 It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
 
-These conflicting facets of our learning problem are harmonized by the manifold hypothesis \citesupp{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
-Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \citesupp{rifai2011manifold}).
+These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
 As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}).
@@
 
-\newpage
-\begin{thebibliography}{1}
-\urlstyle{rm}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem{asboth2016short}
-\bibinfo{author}{Asb{\'o}th, J.~K.}, \bibinfo{author}{Oroszl{\'a}ny, L.} \&
-  \bibinfo{author}{P{\'a}lyi, A.}
-\newblock \bibinfo{journal}{\bibinfo{title}{A short course on topological
-  insulators}}.
-\newblock {\emph{\JournalTitle{Lecture notes in physics}}}
-  \textbf{\bibinfo{volume}{919}} (\bibinfo{year}{2016}).
-
-\bibitem{goodfellow2016deep}
-\bibinfo{author}{Goodfellow, I.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Courville, A.}
-\newblock \emph{\bibinfo{title}{Deep learning}} (\bibinfo{publisher}{MIT press,
-  Cambridge, MA, USA}, \bibinfo{year}{2016}).
-
-\bibitem{bishop2006pattern}
-\bibinfo{author}{Bishop, C.~M.}
-\newblock \emph{\bibinfo{title}{Pattern recognition and machine learning}}
-  (\bibinfo{publisher}{Springer New York, NY, USA}, \bibinfo{year}{2006}).
-
-\bibitem{cayton2005algorithms}
-\bibinfo{author}{Cayton, L.}
-\newblock \bibinfo{journal}{\bibinfo{title}{Algorithms for manifold learning}}.
-\newblock {\emph{\JournalTitle{Univ. of California at San Diego Tech. Rep}}}
-  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{1} (\bibinfo{year}{2005}).
-
-\bibitem{narayanan2010sample}
-\bibinfo{author}{Narayanan, H.} \& \bibinfo{author}{Mitter, S.}
-\newblock \bibinfo{title}{Sample complexity of testing the manifold
-  hypothesis}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{1786--1794} (\bibinfo{year}{2010}).
-
-\bibitem{rifai2011manifold}
-\bibinfo{author}{Rifai, S.}, \bibinfo{author}{Dauphin, Y.~N.},
-  \bibinfo{author}{Vincent, P.}, \bibinfo{author}{Bengio, Y.} \&
-  \bibinfo{author}{Muller, X.}
-\newblock \bibinfo{title}{The manifold tangent classifier}.
-\newblock In \emph{\bibinfo{booktitle}{Advances in Neural Information
-  Processing Systems}}, \bibinfo{pages}{2294--2302} (\bibinfo{year}{2011}).
-
-\end{thebibliography}
+%\newpage
+%\bibliographystylesupp{naturemag-doi}
+%\bibliographysupp{supp}
+
 \end{document}

### 2020-07-06 05_simulation_with_engineered_features/simulation.py

@@ -1,0 +1,508 @@
+import numpy as np
+import pandas as pd
+import os
+import matplotlib.pyplot as plt
+import graphviz
+from itertools import filterfalse
+from importlib import reload
+from itertools import chain
+from sklearn.tree import export_graphviz
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.metrics import accuracy_score
+from sklearn.base import clone
+from tqdm import tqdm
+from joblib import dump
+import csv
+import papermill as pm
+
+### Simulation directories
+SIMULATIONS_DIR = "/home/rio/ssh_simulations"
+# ssh1 simulations with fourier engineered features
+SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
+SSH1_PERIODIC_ENGINEERED_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_100_6561")
+SSH1_PERIODIC_ENGINEERED_140_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_140_6561")
+SSH1_PERIODIC_ENGINEERED_180_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_180_6561")
+SSH1_PERIODIC_ENGINEERED_220_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_220_6561")
+# ssh2 simulations
+SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
+SSH2_PERIODIC_ENGINEERED_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_engineered_100_6561")
+SSH2_PERIODIC_ENGINEERED_140_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_engineered_140_6561")
+SSH2_PERIODIC_ENGINEERED_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_engineered_180_6561")
[…]

### 2020-07-06 06_results_with_engineered_features/results_template_parameters.py

@@ -1,0 +1,343 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Mar 10 19:23:54 2020
+
+@author: linneu
+"""
+import os
+import numpy as np
+from simulation_results import *
+
+def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name="0", n_experiments=None, load_hamiltonian_summary=False, base_simulations_dir="/home/rio/ssh_simulations/ssh1",
+                        base_figs_dir="/home/rio/ml_topological_phases_in_real_space/paper/ssh1"):
+    
+    if not os.path.isdir(base_figs_dir):
+        os.mkdir(base_figs_dir)
+    figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    if not os.path.isdir(figs_dir):
+        os.mkdir(figs_dir)    
+    simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    
+    #########################################################################
+    ################### Results from a single experiment ####################
+    #########################################################################
+    
+    parameters = { 
+    ### Visualizing train/val/test splits with scatter_train_val_test
+    "scatter_train_val_test_params": {
+    "fig_params":{"figsize": [6,6]}, 
+    "val_params": {"marker": "s", "s": 64, "alpha": 0.2, "color": "salmon", "label": "val"},
+    "test_params": {"marker": "s", "s": 64, "alpha": 0.5, "color": "royalblue", "label": "test"},
+    "train_params": {"marker": "o", "s": 3, "alpha": 1, "color": "green", "label": "train"},
+    "legend_params": {"framealpha": 0.8, "loc": "upper right", "fontsize": 16},
+    "xlabel_params": {"xlabel": "$t_2$", "fontsize": 24},
+    "ylabel_params": {"ylabel": "$t_1$", "fontsize": 24},
+    "title_params": {},
+    "xlim_params": {"left": -2, "right": 2},
+    "ylim_params": {"bottom": -2, "top": 2},
+    "xticks_params": {"fontsize": 14},
+    "yticks_params": {"fontsize": 14},
+    "tight_params": {},
+    "savefig_params": {"fname": os.path.join(figs_dir,"scatter_train_val_test_experiment_{}.png".format(experiment_name))},
+     },
[…]

### 2020-07-07 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
Finishing section topological feature engineering and topological data compression

--- 2020-07-05 8_prb_submission/1_reply_referee/article_with_comments/article.tex
@@
 
-\section{Topological feature engineering}
+\section{Topological feature engineering and data compression}
 \label{topological_feature_engineering}
 
-In this last section, we show how the theoretical formalism sketched in section \ref{emergent_information_entropy_wave_functions} can be used to instigate yet another round of machine learning.
+In this last section, we show how the theoretical formalism sketched in section \ref{emergent_information_entropy_wave_functions} can be used to instigate yet another round of machine learning, with a flavor of data compression.
 As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of an SSH system can be largely decreased with little loss of information.
-Perhaps more interesting, nonetheless, are the possibilities that the information entropy signatures in real and wavevector space offer when used complementarily.
-Here we explore the engineering of new topological features in real space.
+Nevertheless, given that the topological phase of a SSH lattice is a global property and not a local one, it is expected that simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological information.
+Here we explore the engineering of new global topological features in real space, and how these global features lead to an effective compression of topological information.
 
@@
 
-Contrary to their real space counterparts, the wavevector space information entropy signatures are highly localized, which by itself does not come as a surprise.
-This gives us an opportunity to engineer new features in real space that carry more relevant topological information than the simpler strategy of selecting the most important lattice sites in a real space information entropy signature.
-We may write equation \ref{discrete_fourier_transform} in matrix form as
+Contrary to their real space counterparts, the wavevector space information entropy signatures are highly localized, which indicates that most of the topological information can be traced to a subset of wavevector modes.
+In fact, in figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} the reduction in information entropy is concentraded mostly on even wavevector modes.
+Furthermore, the wavevector space information entropy signatures are approximately even-symmetric with respect to the wavevector modes at 0 and $\frac{N}{2}$, a consequence of the fact that they are obtained as the DFT of a real signal with periodic boundary conditions.
+
+These (appproximate) symmetries of the topological signatures can guide us through engineering of new topological features from real space coordinates.
+Indeed, it is easy to verify that the DFT of a real signal $x[m]$ that is even-symmetric around 0 and $\frac{N}{2}$ is given by the Discrete Cosine Transform (DCT),
+\begin{equation}
+\label{DCT}
+\hat{x}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\Big(\frac{\pi}{M-1}nm\Big), \quad n=0,\dots,M-1, 
+\end{equation}
+where $M = \frac{N}{2}+1$.
+
+The DCT is often employed in several applications of Digital Signal Processing such as audio and image processing and, most importantly here, data compression.
+As equation \eqref{DCT} shows, the DCT profits from redundance of information in a real, even-symmetric signal, allowing us to write a signal of length $N$ in terms of $M = \frac{N}{2}+1$ features.
+
+We further reduce the number of engineered topological features by taking only even values of $n$ in the left-hand side of equation \eqref{DCT}.
+This is done in agreement with the observation that the information entropy signatures in figure \ref{fourier_feature_importances} are strongly localized on even wavevector modes.
+This leads us to our desired topological features,
+\begin{equation}
+\hat{x}[n] = x[0] + x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\Big(\frac{2\pi}{M-1}nm\Big), \quad n=0,\dots,\frac{M-1}{2}.
+\end{equation}
+
+ %the DFT of a real eigenvector $x[m]$\eqref{discrete_fourier_transform} o \eqref{in figures \ref{fourier_feature_importances_ssh1} and %\ref{fourier_feature_importances_ssh2}.
+This gives us an opportunity to engineer new features in real space that carry more relevant %topological information than the simpler strategy of selecting the most important lattice sites in a real space information entropy %signature.
+We may write equation \eqref{discrete_fourier_transform} in matrix form as
 \begin{equation}
@@
 Let $x[m]$ be an eigenvector in real space.
-We can use equation \eqref{dft} to compute its wavevector space representation $k[n]$ and in particular its zeroth component,
-\begin{equation}
-\label{k_0} 
-k[0] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m].
-\end{equation}
-Equation \eqref{k_0} indicates that simply knowing the sum of components of the eigenvectors in real space may provide key information about the topological phases of SSH Hamiltonians.
-To visually examine this proposition, we can draw histograms
-
-The next most relevant components in wavevector space in both numerical experiments are the symmetric pair (2,98), which together reduce approximately 10\% of information entropy in experiment 1 (section \ref{experiment_1}) and 2.5\% in experiment 2 (section \ref{experiment_2}).
+We can use equation \eqref{dft} to compute its wavevector space representation $\hat{k}[n]$ and in particular its zeroth component,
+\begin{equation}
+\label{x_hat_0} 
+\hat{x}[0] = \hat{k}[0] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m].
+\end{equation}
+Equation \eqref{x_hat_0} amounts to taking the sum of components of the eigenvectors in real space as a first engineered topological feature. 
+%may provide key information about the topological phases of SSH Hamiltonians. To visually examine this proposition, we can draw histograms %-----
+
+Now let us consider the symmetric pairs $(m,N-m)$, with $m$ even.
+As figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} indicate, these pairs concentrate the remaining relevant topological information from the SSH systems investigated here.
+We can therefore engineer the topological features
+
+\begin{equation}
+\label{x_hat_m} 
+\hat{x}[n] = \frac{k[2n]+k[N-2n]}{2} = \sqrt{\frac{1}{N}}\sum_{m=1}^{\frac{N}{2}-1}x[2m]\cos(2mn\omega_N), \quad n = 1, 2, \cdots, \frac{N}{2}-1.
+\end{equation}
+
+Putting the engineered topological features from equations \eqref{x_hat_0} and \eqref{x_hat_m} together, we obtain a compressed version of the real space eigenvectors,
+
+These  which together reduce approximately 10\% of information entropy in experiment 1 (section \ref{experiment_1}) and 2.5\% in experiment 2 (section \ref{experiment_2}).
 The pair (2,98) in wavevector space leads us to another real space engineered feature,
 \begin{equation}
-\label{k_2_98} 
-\frac{k[2]+k[98]}{\sqrt{2}} = \sqrt{\frac{2}{N}}\sum_{m=0}^{N-1}x[m]\cos(2m\omega_N).
+\label{k_m} 
+\frac{k[m]+k[N-m]}{\sqrt{2}} = \sqrt{\frac{2}{N}}\sum_{m=0}^{N-1}x[m]\cos(2m\omega_N).
 \end{equation}

### 2020-07-08 05_simulation_with_engineered_features/simulation.py
Running code with feature engineering

@@ -18,31 +18,43 @@ import papermill as pm
 
 ### Simulation directories
 SIMULATIONS_DIR = "/home/rio/ssh_simulations"
+
 # ssh1 simulations with fourier engineered features
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
-SSH1_PERIODIC_ENGINEERED_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_100_6561")
-SSH1_PERIODIC_ENGINEERED_140_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_140_6561")
-SSH1_PERIODIC_ENGINEERED_180_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_180_6561")
-SSH1_PERIODIC_ENGINEERED_220_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_engineered_220_6561")
+# N = 100
+SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
+SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
+SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
+SSH1_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
+SSH1_PERIODIC_5TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_5th_scenario_100_6561")
+
 # ssh2 simulations
 SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
[…]

### 2020-07-09 05_simulation_with_engineered_features/simulation.py
Code ready to run several scenarios

@@ -27,6 +27,10 @@ SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIO
 SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
 SSH1_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
 SSH1_PERIODIC_5TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_5th_scenario_100_6561")
+SSH1_PERIODIC_6TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_6th_scenario_100_6561")
+SSH1_PERIODIC_7TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_7th_scenario_100_6561")
+SSH1_PERIODIC_8TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_8th_scenario_100_6561")
+SSH1_PERIODIC_9TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_9th_scenario_100_6561")
 
 # ssh2 simulations
 SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
@@ -36,6 +40,10 @@ SSH2_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIO
 SSH2_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
 SSH2_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
[…]

### 2020-07-13 06_results _with_engineered_features/results_template_parameters.py
Generated results for scenarios 1-9

@@ -1,0 +1,424 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Mar 10 19:23:54 2020
+
+@author: linneu
+"""
+import os
+import numpy as np
+from simulation_results import *
+
+def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name="0", n_experiments=None, load_hamiltonian_summary=False, base_simulations_dir="/home/rio/ssh_simulations/ssh1",
+                        base_figs_dir="/home/rio/ml_topological_phases_in_real_space/paper/ssh1"):
+    
+    if not os.path.isdir(base_figs_dir):
+        os.mkdir(base_figs_dir)
+    figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    if not os.path.isdir(figs_dir):
+        os.mkdir(figs_dir)    
+    simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    
+    #figures_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    
+    #########################################################################
+    ################### Results from a single experiment ####################
+    #########################################################################
+    
+    parameters = { 
+    ### Visualizing train/val/test splits with scatter_train_val_test
+    "scatter_train_val_test_params": {
+    "fig_params":{"figsize": [6,6]}, 
+    "val_params": {"marker": "s", "s": 64, "alpha": 0.2, "color": "salmon", "label": "val"},
+    "test_params": {"marker": "s", "s": 64, "alpha": 0.5, "color": "royalblue", "label": "test"},
+    "train_params": {"marker": "o", "s": 3, "alpha": 1, "color": "green", "label": "train"},
+    "legend_params": {"framealpha": 0.8, "loc": "upper right", "fontsize": 16},
+    "xlabel_params": {"xlabel": "$t_2$", "fontsize": 24},
+    "ylabel_params": {"ylabel": "$t_1$", "fontsize": 24},
+    "title_params": {},
+    "xlim_params": {"left": -2, "right": 2},
+    "ylim_params": {"bottom": -2, "top": 2},
+    "xticks_params": {"fontsize": 14},
+    "yticks_params": {"fontsize": 14},
+    "tight_params": {},
[…]

### 2020-07-13 06_results _with_engineered_features/simulation_results.py

@@ -1,0 +1,1020 @@
+import numpy as np
+from scipy.fft import fft, rfft, fftfreq
+import pandas as pd
+import os
+import matplotlib.pyplot as plt
+import graphviz
+from itertools import filterfalse
+from importlib import reload
+from itertools import chain
+from sklearn.tree import export_graphviz
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.metrics import accuracy_score
+from sklearn.base import clone
+from tqdm import tqdm
+from joblib import load
+from matplotlib.colors import ListedColormap
+from matplotlib.colors import LinearSegmentedColormap
+from collections import defaultdict
+#import json
+import csv
+
+### Simulation directories
+SIMULATIONS_DIR = "/home/rio/ssh_simulations"
+# ssh1 simulations with engineered features
+SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
+SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
+SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
+SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
+SSH1_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
+SSH1_PERIODIC_5TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_5th_scenario_100_6561")
+SSH1_PERIODIC_6TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_6th_scenario_100_6561")
[…]

### 2020-07-14 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
Writing table with results

@@
 
-\textcolor{blue}{
-\section{Emergent information entropy wave functions}
-\label{emergent_information_entropy_wave_functions}
-}
-\textcolor{blue}{
-The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
-In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
-Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
-The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-\textcolor{blue}{
-We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
-macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
-By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by}
-
-\begin{equation}
-\label{entropy_density}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
-\end{equation}
-where $x \in [0,1]$ is a spatial coordinate along the continuous lattice (which we shall call from now on string, to emphasize its continuity as opposed to a discrete lattice) and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
-
-\textcolor{blue}{
-Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
-}
-\begin{equation}
-\label{shannon_wave_function}
-\rho_S(x) = |\psi_S(x)|^2,
-\end{equation}
-the amount of topological information available from a single point in the string then being expressed in bra-ket notation by Born's rule,
-
-\begin{equation}
-\label{born_rule_spatial}
-\rho_S(x) = |\braket{x|\psi_S}|^2.
-\end{equation}
-
-\textcolor{blue}{
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
-\begin{equation}
-\label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
-\end{equation}
-\textcolor{blue}{
-from which the Shannon information entropy density function in wavevector space can be computed,}
-\begin{equation}
-\label{shannon_wave_function_wavevector_space}
-\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
-\end{equation}
-
-\textcolor{blue}{
-The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
-Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
-}
-
-\textcolor{blue}{
-Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have }
-\begin{subequations}
-\label{statistics}
-\begin{equation}
-\label{mean}
-\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
-\end{equation}
-\begin{equation}
-\label{variance}
-\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
-\end{equation}
-\begin{equation}
-\label{entropy}
-H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx,
-\end{equation}
-\end{subequations}
-\textcolor{blue}{
-with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H[\hat{\rho_S}]$ in terms of $k$ and $\hat{\rho}$.}
-
-\textcolor{blue}{
-In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}: }
-
-\begin{enumerate}
-\item[i)] \emph{the Heisenberg uncertainty principle}
-\begin{equation}
-\label{heisenberg}
-\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad \text{and }
-\end{equation}
-\item[ii)] \emph{the Hirschman entropic uncertainty}
-\begin{equation}
-\label{hirschman}
-H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
-\end{equation}
-\end{enumerate}
-
-\textcolor{blue}{
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
-In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
-}
-
-\textcolor{blue}{
-Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D continuous string is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the whole SSH system.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
-Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
-}
-
-\textcolor{blue}{
-Given that our analysis has now come full circle back to theoretical physics, the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-}
-
 \section{Topological feature engineering and data compression}
@@
 
-In this last section, we show how the theoretical formalism sketched in section \ref{emergent_information_entropy_wave_functions} can be used to instigate yet another round of machine learning, with a flavor of data compression.
-As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of an SSH system can be largely decreased with little loss of information.
-Nevertheless, given that the topological phase of a SSH lattice is a global property and not a local one, it is expected that simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an effective compression of topological information.
-
-The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the real space information entropy wave functions are real.
-The discretized version of equation \eqref{fourier_shannon_wave_function},
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from an information-theoretic perspective, in particular as related to data compression.
+As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
+Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
+Here we show how the symmetries in the real space information entropy signatures in figure \ref{feature_importances} can be exploited to engineer new global topological features, leading to an effective compression of topological information.
+
+%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
+Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
+
+%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
+
+Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
 \begin{equation}
 \label{discrete_fourier_transform}
-\hat{\psi}_S[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}\psi_S[m]e^{-i\frac{2\pi}{N}nm}
-\end{equation}
-which is simply the Discrete Fourier Transform (DFT) formula for digital signals, will accomplish this.
-After computing the norm of each component of the resulting discrete information entropy wave function $\hat{\psi}_S[n]$, we recover the information entropy signatures in wavevector space shown in figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2}.
+\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
+\end{equation}
+Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
+The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
+\begin{equation}
+\label{hermitian_symmetry}
+\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
+\end{equation}
+where  we have used the notation $\overline{k} = k \mod N$.
+
+Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
+In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
+This leads us to the Discrete Cosine Transform (DCT) topological features,
+\begin{equation}
+\label{DCT}
+\hat{x}_{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
+\end{equation}
+where $M = \frac{N}{2}+1$.
+The second path capitalizes on the fact that de imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
+\begin{equation}
+\label{DST}
+\hat{x}_{s}[n+1] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
+\end{equation} 
+where $M = \frac{N}{2}-1$.
+
+We ran several numerical experiments to evaluate how the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST} perform.
+The results obtained in each experiment are listed in table \ref{numerical_results}.
+These numerical experiments differed both on which topological features were used (whether DCT or DST topological features), as well as which features in real space were used to compute the engineered topological features.
+The results obtained in the numerical experiments of section \ref{numerical_experiments} are also listed in table \ref{numerical_results} for the sake of reference.
+
+\begin{table}
+ \begin{tabular}{||c c c c c||} 
+ \hline
+ SSH system & Real space feat. & Wavevector space feat. & Val. Hamiltonian acc. & Test Hamiltonian acc. \\ % [0.5ex] 
+ \hline\hline
+ 1 & All & None & 1 & 0.991 \\ 
+ \hline
+ 1 & $\mathcal{S}_1$ & None & 0.985 & 0.985\\
+ \hline
+ 1 & $\mathcal{S}'_1$ & None & 0.985 & 0.986\\
+ \hline
+ 1 & DCT & DCT & 0.997 & 0.989 \\
+ \hline
+ 1 & DST & DST & --- & --- \\
+ \hline
+ 1 & $\mathcal{S}_1$ & $\mathcal{E}_1$ & --- & --- \\ 
+ \hline
+ 1 & $\mathcal{S'}_1$ & $\mathcal{E}'_1$ & --- & --- \\ 
+ \hline
+ 1 & $\mathcal{S}_1$ & $\mathcal{O}_1$ & --- & --- \\ 
+ \hline
+ 1 & $\mathcal{S'}_1$ & $\mathcal{O}'_1$ & --- & --- \\ 
+ \hline
+ 2 & All & None & --- & --- \\ 
+ \hline
+ 2 & $\mathcal{S}_2$ & --- & --- & ---\\
+ \hline
+ 2 & $\mathcal{S}'_2$ & --- & --- & ---\\
+ \hline
+ 2 & DCT & DCT & --- & --- \\
+ \hline
+ 2 & DST & DST & --- & --- \\
+ \hline
+ 2 & $\mathcal{S}_2$ & $\mathcal{E}_2$ & --- & --- \\ 
+ \hline
+ 2 & $\mathcal{S'}_2$ & $\mathcal{E}'_2$ & --- & --- \\ 
+ \hline
+ 2 & $\mathcal{S}_2$ & $\mathcal{O}_2$ & --- & --- \\ 
+ \hline
+ 2 & $\mathcal{S'}_2$ & $\mathcal{O}'_2$ & --- & --- \\ 
+ \hline
+
+ \end{tabular}
+\caption{\label{numerical_results}Your caption.}
+\end{table}
+
+Guaranteed to have Hermitian symmetry with respect to the lattice site at $\frac{N}{2}$. Furthermore, given that the lattices were closed with periodic boundary conditions, the   
+%After computing the norm of each component of the resulting discrete information entropy wave function $\hat{\psi}_S[n]$, we recover the %information entropy signatures in wavevector space shown in figures \ref{fourier_feature_importances_ssh1} and %%\ref{fourier_feature_importances_ssh2}.
 
@@
  main mode of the wavevector space information entropy signatures, which is
+
+\textcolor{blue}{
+\section{Emergent information entropy wave functions}
+\label{emergent_information_entropy_wave_functions}
+}
+\textcolor{blue}{
+The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
+In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
+Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
+The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
+
+\textcolor{blue}{
+We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
+macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
+By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by}
+
+\begin{equation}
+\label{entropy_density}
+F_S(x) = \int_{0}^x\rho_S(x')dx'
+\end{equation}
+where $x \in [0,1]$ is a spatial coordinate along the continuous lattice (which we shall call from now on string, to emphasize its continuity as opposed to a discrete lattice) and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
+
+\textcolor{blue}{
+Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
+}
+\begin{equation}
+\label{shannon_wave_function}
+\rho_S(x) = |\psi_S(x)|^2,
+\end{equation}
+the amount of topological information available from a single point in the string then being expressed in bra-ket notation by Born's rule,
+
+\begin{equation}
+\label{born_rule_spatial}
+\rho_S(x) = |\braket{x|\psi_S}|^2.
+\end{equation}
+
+\textcolor{blue}{
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
+\begin{equation}
+\label{fourier_shannon_wave_function}
+\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
+\end{equation}
+\textcolor{blue}{
+from which the Shannon information entropy density function in wavevector space can be computed,}
+\begin{equation}
+\label{shannon_wave_function_wavevector_space}
+\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
+\end{equation}
+
+\textcolor{blue}{
+The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
+Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+}
+
+\textcolor{blue}{
+Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have }
+\begin{subequations}
+\label{statistics}
+\begin{equation}
+\label{mean}
+\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
+\end{equation}
+\begin{equation}
+\label{variance}
+\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
+\end{equation}
+\begin{equation}
+\label{entropy}
+H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx,
+\end{equation}
+\end{subequations}
+\textcolor{blue}{
+with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H[\hat{\rho_S}]$ in terms of $k$ and $\hat{\rho}$.}
+
+\textcolor{blue}{
+In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}: }
+
+\begin{enumerate}
+\item[i)] \emph{the Heisenberg uncertainty principle}
+\begin{equation}
+\label{heisenberg}
+\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad \text{and }
+\end{equation}
+\item[ii)] \emph{the Hirschman entropic uncertainty}
+\begin{equation}
+\label{hirschman}
+H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
+\end{equation}
+\end{enumerate}
+
+\textcolor{blue}{
+The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
+In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
+}
+
+\textcolor{blue}{
+Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D continuous string is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the whole SSH system.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
+Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
+}
+
+\textcolor{blue}{
+Given that our analysis has now come full circle back to theoretical physics, the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
+}
 

### 2020-07-15 05_simulation_with_engineered_features/simulation.py
implemented DST

@@ -170,6 +170,7 @@ class Simulation(object):
         self.fourier_mode = fourier_mode
         self.fourier_features_to_use = fourier_features_to_use
         self.fourier_real = fourier_real
+        #print("This is fourier_ real: ", fourier_real)
         self.fourier_normalize = fourier_normalize
         self.fourier_fillna = fourier_fillna
         self.omega = None
@@ -214,12 +215,24 @@ class Simulation(object):
             self.fourier_operator[:,[0,-1]] = 1/2*self.fourier_operator[:,[0,-1]]
             fourier_features_array = np.dot(self.dataframe.loc[:,self.features].values[:,real_space_features_to_use], self.fourier_operator)
             feature_name = "dct_feat"
-        
+        elif self.fourier_mode == "dst":
+            if self.features_to_use is None:
+                real_space_features_to_use = range(0,self.n_features//2-1)
+            else:
+                real_space_features_to_use = [f for f in range(self.n_features//2-1) if f in self.features_to_use]
+            if self.fourier_features_to_use is None:
+                self.fourier_features_to_use = range(0,self.n_features//2-1)
+            #M = self.n_features//2+1
+            self.omega = np.pi/(self.n_features//2)
+            self.fourier_operator =  np.array([[2*1j*np.sin(self.omega*((m+1)*(n+1))) for n in self.fourier_features_to_use] for m in                                                                                                       real_space_features_to_use])
+            #self.fourier_operator[:,[0,-1]] = 1/2*self.fourier_operator[:,[0,-1]]
+            fourier_features_array = np.dot(self.dataframe.loc[:,self.features].values[:,real_space_features_to_use], self.fourier_operator)
+            feature_name = "dst_feat"
         if self.fourier_real == "real":
             fourier_features_array = np.real(fourier_features_array)
         elif self.fourier_real == "imag":
+            #print("Making comeplex!")
             fourier_features_array = np.imag(fourier_features_array)
-        
         if self.fourier_normalize:
             norms = np.linalg.norm(fourier_features_array,axis=1)
             norms=np.reshape(norms,(-1,1))
@@ -281,7 +294,9 @@ class Simulation(object):
             if self.fourier_mode == "dft":
                 first_feat_name = "dft_feat0" 
             elif self.fourier_mode == "dct":
-                first_feat_name = "dct_feat0" 
+                first_feat_name = "dct_feat0"
[…]

### 2020-07-16 05_simulation_with_engineered_features/simulation.py
Generated table for SSH 1 systems

@@ -15,6 +15,7 @@ from tqdm import tqdm
 from joblib import dump
 import csv
 import papermill as pm
+import json
 
 ### Simulation directories
 SIMULATIONS_DIR = "/home/rio/ssh_simulations"
@@ -22,6 +23,7 @@ SIMULATIONS_DIR = "/home/rio/ssh_simulations"
 # ssh1 simulations with fourier engineered features
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
 # N = 100
+SSH1_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
 SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
 SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
 SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
@@ -35,6 +37,7 @@ SSH1_PERIODIC_9TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIO
 # ssh2 simulations
 SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
 # N = 100
+SSH2_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
 SSH2_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
 SSH2_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
[…]

### 2020-07-16 06_results _with_engineered_features/simulation_results.py

@@ -19,11 +19,13 @@ from matplotlib.colors import LinearSegmentedColormap
 from collections import defaultdict
 #import json
 import csv
+import json
 
 ### Simulation directories
 SIMULATIONS_DIR = "/home/rio/ssh_simulations"
 # ssh1 simulations with engineered features
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
+SSH1_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
 SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
 SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
 SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
@@ -36,6 +38,7 @@ SSH1_PERIODIC_9TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIO
 
 # ssh2 simulations with engineered features
 SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
+SSH2_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
 SSH2_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
 SSH2_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
[…]

### 2020-07-16 06_results_with_engineered_features_deprecated/results_template_parameters.py

@@ -1,343 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Mar 10 19:23:54 2020
-
-@author: linneu
-"""
-import os
-import numpy as np
-from simulation_results import *
-
-def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name="0", n_experiments=None, load_hamiltonian_summary=False, base_simulations_dir="/home/rio/ssh_simulations/ssh1",
-                        base_figs_dir="/home/rio/ml_topological_phases_in_real_space/paper/ssh1"):
-    
-    if not os.path.isdir(base_figs_dir):
-        os.mkdir(base_figs_dir)
-    figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
-    if not os.path.isdir(figs_dir):
-        os.mkdir(figs_dir)    
-    simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
-    
-    #########################################################################
-    ################### Results from a single experiment ####################
-    #########################################################################
-    
-    parameters = { 
-    ### Visualizing train/val/test splits with scatter_train_val_test
-    "scatter_train_val_test_params": {
-    "fig_params":{"figsize": [6,6]}, 
-    "val_params": {"marker": "s", "s": 64, "alpha": 0.2, "color": "salmon", "label": "val"},
-    "test_params": {"marker": "s", "s": 64, "alpha": 0.5, "color": "royalblue", "label": "test"},
-    "train_params": {"marker": "o", "s": 3, "alpha": 1, "color": "green", "label": "train"},
-    "legend_params": {"framealpha": 0.8, "loc": "upper right", "fontsize": 16},
-    "xlabel_params": {"xlabel": "$t_2$", "fontsize": 24},
-    "ylabel_params": {"ylabel": "$t_1$", "fontsize": 24},
-    "title_params": {},
-    "xlim_params": {"left": -2, "right": 2},
-    "ylim_params": {"bottom": -2, "top": 2},
-    "xticks_params": {"fontsize": 14},
-    "yticks_params": {"fontsize": 14},
-    "tight_params": {},
-    "savefig_params": {"fname": os.path.join(figs_dir,"scatter_train_val_test_experiment_{}.png".format(experiment_name))},
-     },
[…]

### 2020-07-16 06_results_with_engineered_features_deprecated/simulation_results.py

@@ -1,900 +1,0 @@
-import numpy as np
-import pandas as pd
-import os
-import matplotlib.pyplot as plt
-import graphviz
-from itertools import filterfalse
-from importlib import reload
-from itertools import chain
-from sklearn.tree import export_graphviz
-from sklearn.tree import DecisionTreeClassifier
-from sklearn.ensemble import RandomForestClassifier
-from sklearn.metrics import accuracy_score
-from sklearn.base import clone
-from tqdm import tqdm
-from joblib import load
-from matplotlib.colors import ListedColormap
-from matplotlib.colors import LinearSegmentedColormap
-from collections import defaultdict
-#import json
-import csv
-
-### Simulation directories
-SIMULATIONS_DIR = "/home/rio/ssh_simulations"
-# ssh1 simulations
-SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
-SSH1_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_100_6561")
-SSH1_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_140_6561")
-SSH1_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_180_6561")
-SSH1_PERIODIC_LESS_220_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_less_220_6561")
-# ssh2 simulations
-SSH2_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh2")
-SSH2_PERIODIC_LESS_100_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_100_6561")
-SSH2_PERIODIC_LESS_140_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_140_6561")
-SSH2_PERIODIC_LESS_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_less_180_6561")
[…]

### 2020-07-18 05_simulation_with_engineered_features/simulation.py
Running all simulations again

@@ -17,65 +17,76 @@ import csv
 import papermill as pm
 import json
 
-### Simulation directories
+######## Simulation directories
 SIMULATIONS_DIR = "/home/rio/ssh_simulations"
 
-# ssh1 simulations with fourier engineered features
+#### ssh1 simulations 
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
-# N = 100
-SSH1_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
-SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
-SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
-SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
-SSH1_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
-SSH1_PERIODIC_5TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_5th_scenario_100_6561")
-SSH1_PERIODIC_6TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_6th_scenario_100_6561")
-SSH1_PERIODIC_7TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_7th_scenario_100_6561")
-SSH1_PERIODIC_8TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_8th_scenario_100_6561")
[…]

### 2020-07-18 06_results _with_engineered_features/results_template_parameters.py

@@ -14,10 +14,14 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     
     if not os.path.isdir(base_figs_dir):
         os.mkdir(base_figs_dir)
-    figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    #figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    figs_dir = os.path.join(base_figs_dir,ssh_type)
     if not os.path.isdir(figs_dir):
         os.mkdir(figs_dir)    
-    simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    #simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    simulation_dir = os.path.join(base_simulations_dir,ssh_type) 
+    print("figs_dir: ", figs_dir)
+    print("simulation_dir: ", simulation_dir)
     
     #figures_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
     
@@ -221,11 +225,12 @@ def get_parameters_ssh2(ssh_type, chain_length, n_hamiltonians, experiment_name=
     
     if not os.path.isdir(base_figs_dir):
         os.mkdir(base_figs_dir)
-    figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    #figs_dir = os.path.join(base_figs_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians))
+    figs_dir = os.path.join(base_figs_dir,ssh_type)
     if not os.path.isdir(figs_dir):
         os.mkdir(figs_dir)    
-    simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
-    
+    #simulation_dir = os.path.join(base_simulations_dir,"{}_{}_{}".format(ssh_type,chain_length,n_hamiltonians)) 
+    simulation_dir = os.path.join(base_simulations_dir,ssh_type) 
     #########################################################################
     ################### Results from a single experiment ####################
     #########################################################################

### 2020-07-18 06_results _with_engineered_features/simulation_results.py

@@ -21,114 +21,145 @@ from collections import defaultdict
 import csv
 import json
 
-### Simulation directories
+######## Simulation directories
 SIMULATIONS_DIR = "/home/rio/ssh_simulations"
-# ssh1 simulations with engineered features
+#### ssh1 simulations 
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
-SSH1_PERIODIC_0TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_0th_scenario_100_6561")
-SSH1_PERIODIC_1ST_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_1st_scenario_100_6561")
-SSH1_PERIODIC_2ND_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_2nd_scenario_100_6561")
-SSH1_PERIODIC_3RD_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_3rd_scenario_100_6561")
-SSH1_PERIODIC_4TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_4th_scenario_100_6561")
-SSH1_PERIODIC_5TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_5th_scenario_100_6561")
-SSH1_PERIODIC_6TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_6th_scenario_100_6561")
-SSH1_PERIODIC_7TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_7th_scenario_100_6561")
-SSH1_PERIODIC_8TH_SCENARIO_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_8th_scenario_100_6561")
[…]

### 2020-07-18 05_simulation_with_engineered_features/simulation.py
Ran simulations of real space, dct and dst

@@ -23,46 +23,46 @@ SIMULATIONS_DIR = "/home/rio/ssh_simulations"
 #### ssh1 simulations 
 SSH1_SIMULATIONS_DIR = os.path.join(SIMULATIONS_DIR,"ssh1")
 ## N = 100 simulation directories
-SSH1_PERIODIC_100_6561_SIMULATION_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_100_6561")
+SSH1_PERIODIC_100_6561_SIMULATIONS_DIR = os.path.join(SSH1_SIMULATIONS_DIR,"periodic_100_6561")
 # Real space simulation directories
-SSH1_REAL_SPACE_ALL_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATION_DIR,"real_space_all_sites")
-SSH1_REAL_SPACE_BEST_04_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATION_DIR,"real_space_best_04_sites")
+SSH1_REAL_SPACE_ALL_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATIONS_DIR,"real_space_all_sites")
+SSH1_REAL_SPACE_BEST_04_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATIONS_DIR,"real_space_best_04_sites")
 # DFT space 
-SSH1_DFT_ALL_WAVEVECTOR_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATION_DIR,"dft_all_wavevector_sites")
-SSH1_DFT_BEST_04_WAVEVECTOR_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATION_DIR,"dft_best_04_wavevector_sites")
-SSH1_DFT_BEST_04_WAVEVECTOR_SITES_FROM_BEST_04_REAL_SPACE_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATION_DIR,"dft_best_04_wavevector_sites_from_best_04_real_space_sites")
+SSH1_DFT_ALL_WAVEVECTOR_SITES = os.path.join(SSH1_PERIODIC_100_6561_SIMULATIONS_DIR,"dft_all_wavevector_sites")
[…]

### 2020-07-18 06_results _with_engineered_features/simulation_results.py

@@ -153,7 +153,7 @@ SSH2_DFT_BEST_12_WAVEVECTOR_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dft_best_12_wavev
 SSH2_DFT_BEST_12_WAVEVECTOR_SITES_FROM_BEST_12_REAL_SPACE_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dft_best_12_wavevector_sites_from_best_12_real_space_sites_results_notebook.ipynb"
 ## DCT
 SSH2_DCT_ALL_WAVEVECTOR_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dct_all_wavevector_sites_results_notebook.ipynb"
-SSH2_DCT_BEST_12_WAVEVECTOR_SITES_RESULTS_NOTEBOOKS = "zzz_ssh2_dct_best_12_wavevector_sites_results_notebook.ipynb"
+SSH2_DCT_BEST_12_WAVEVECTOR_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dct_best_12_wavevector_sites_results_notebook.ipynb"
 SSH2_DCT_BEST_12_WAVEVECTOR_SITES_FROM_BEST_12_REAL_SPACE_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dct_best_12_wavevector_sites_from_best_12_real_space_sites_results_notebook.ipynb"
 ## DST
 SSH2_DST_ALL_WAVEVECTOR_SITES_RESULTS_NOTEBOOK = "zzz_ssh2_dst_all_wavevector_sites_results_notebook.ipynb"

### 2020-07-19 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
Added table with results to paper

@@
 \usepackage{xcolor}
+\usepackage{bbm}
 %\newcites{supp}{References}
@@
 
-\section{Topological feature engineering and data compression}
+\section{Topological feature engineering and lattice compression}
 \label{topological_feature_engineering}
@@
 \label{DCT}
-\hat{x}_{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
+\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
 \end{equation}
@@
 \label{DST}
-\hat{x}_{s}[n+1] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
+\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
 \end{equation} 
@@
 
-We ran several numerical experiments to evaluate how the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST} perform.
-The results obtained in each experiment are listed in table \ref{numerical_results}.
-These numerical experiments differed both on which topological features were used (whether DCT or DST topological features), as well as which features in real space were used to compute the engineered topological features.
+The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
+the sites $0 \leq j \leq \frac{N}{2}$.
+This is due to the fact that each equation assumes that the real space eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
+While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
+Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
+
+The topological feature engineering strategies described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
+As equations \eqref{DCT} and \eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
+
+We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
+The accuracy scores obtained in each experiment are listed in table \ref{numerical_results}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
+
+The lattice compression strategies tested in this work were: i) learning topological phases from only a subset of the real space lattice sites; ii) learning topological phases from the DCT or DST engineered features of equations; iii) learning topologcal phases from a fraction of the DCT or DST topological features and iv) learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
+
+In strategy \emph{i)} the lattice sites used in the SSH1 and SSH2 systems were
+\begin{equation}
+\label{lattice_subsets}
+\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
+\end{equation}
+Note that for the nearest-neighbor SSH system $\mathcal{S}_1$ correspond to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
+Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
+In table \ref{numerical results}, the features used in strategy \emph{i)} are referred to as $X_{\mathcal{S}_1}$ and $X_{\mathcal{S}_2}$, according to the SSH system they relate to.
+
+In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
+These features are denoted in table \ref{numerical_results} by $\hat{X}^c_1$, $\hat{X}^s_1$, $\hat{X}^c_2$, $\hat{X}^s_2$ according to which set of topological features and SSH systems they refer to.
+
+Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH1 and SSH2 systems,
+\begin{equation}
+\label{DCT_subsets}
+\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
+\end{equation}
+and the DST topological features,
+\begin{equation}
+\label{DCT_subsets}
+\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
+\end{equation}
+The features in strategy \emph{iii)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{O}_2}$ according to the topological features and wavevector sites used with each SSH system.
+
+The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
+It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
+Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
+Mathematically, we can expess the topological features used in strategy \emph{iv)} as follows:
+\begin{equation}
+\label{DCT_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \mathbbm{1}_{\mathcal{S}}[0]x[0] + (-1)^n\mathbbm{1}_{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
+\end{equation}
+\begin{equation}
+\label{DST_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}.
+\end{equation}
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, i.e.
+$\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
+The features engineered in strategy \emph{iv)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH systems, type of topological features used as well as which features in real and wavevector space were used to compute them.
+
+The lattice compression strategies  These numerical experiments differed both on which topological features were used (whether DCT or DST topological features), as well as which features in real space were used to compute the engineered topological features.
 The results obtained in the numerical experiments of section \ref{numerical_experiments} are also listed in table \ref{numerical_results} for the sake of reference.
@@
 \begin{table}
- \begin{tabular}{||c c c c c||} 
+ \begin{tabular}{||c c c c c c||} 
  \hline
- SSH system & Real space feat. & Wavevector space feat. & Val. Hamiltonian acc. & Test Hamiltonian acc. \\ % [0.5ex] 
+SSH     &Features                                      & Eigenvector val.    & Eigenvector test      & Hamiltonian val.    & Hamiltonian test \\ % [0.5ex] 
  \hline\hline
- 1 & All & None & 1 & 0.991 \\ 
+        &                                              &                    &                 &                    &                      \\
+1       & $X_1$                                        & 0.964              & 0.790           & 1                  & 0.992                \\  
 \hline
- 1 & $\mathcal{S}_1$ & None & 0.985 & 0.985\\
+1       & $X_{\mathcal{S}_1}$                          & 0.944              & 0.776           & 0.985              & 0.990                \\
 \hline
- 1 & $\mathcal{S}'_1$ & None & 0.985 & 0.986\\
+1       & $\hat{X}^c_1$                                & 0.952              & 0.737           & 0.998              & 0.992                \\
 \hline
- 1 & DCT & DCT & 0.997 & 0.989 \\
+1       & $\hat{X}^c_{\mathcal{E}_1}$                  & 0.828              & 0.607           & 0.998              & 0.919                \\
 \hline
- 1 & DST & DST & --- & --- \\
+1       & $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$    & 0.944              & 0.818           & 0.985              & 0.993                \\
 \hline
- 1 & $\mathcal{S}_1$ & $\mathcal{E}_1$ & --- & --- \\ 
+1       & $\hat{X}^s_1$                                & 0.953              & 0.731           & 0.991              & 0.986                \\
 \hline
- 1 & $\mathcal{S'}_1$ & $\mathcal{E}'_1$ & --- & --- \\ 
+1       & $\hat{X}^s_{\mathcal{O}_1}$                  & 0.694              & 0.542           & 0.709              & 0.480                \\
 \hline
- 1 & $\mathcal{S}_1$ & $\mathcal{O}_1$ & --- & --- \\ 
+1       & $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$    & 0.946              & 0.782           & 0.985              & 0.940                \\
 \hline
- 1 & $\mathcal{S'}_1$ & $\mathcal{O}'_1$ & --- & --- \\ 
+2       & $X_2$                                        & 0.971              & 0.663           & 0.997              & 0.880                \\  
 \hline
- 2 & All & None & --- & --- \\ 
+2       & $X_{\mathcal{S}_2}$                          & 0.959              & 0.617           & 0.996              & 0.863                \\
 \hline
- 2 & $\mathcal{S}_2$ & --- & --- & ---\\
+2       & $\hat{X}^c_2$                                & 0.974              & 0.690           & 0.998              & 0.886                \\
 \hline
- 2 & $\mathcal{S}'_2$ & --- & --- & ---\\
+2       & $\hat{X}^c_{\mathcal{E}_2}$                  & 0.899              & 0.536           & 0.995              & 0.790                \\
 \hline
- 2 & DCT & DCT & --- & --- \\
+2       & $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$    & 0.900              & 0.503           & 0.996              & 0.767                \\
 \hline
- 2 & DST & DST & --- & --- \\
+2       & $\hat{X}^s_2$                                & 0.974              & 0.688           & 0.997              & 0.890                \\
 \hline
- 2 & $\mathcal{S}_2$ & $\mathcal{E}_2$ & --- & --- \\ 
+2       & $\hat{X}^s_{\mathcal{O}_2}$                  & 0.904              & 0.553           & 0.992              & 0.743                \\
 \hline
- 2 & $\mathcal{S'}_2$ & $\mathcal{E}'_2$ & --- & --- \\ 
- \hline
- 2 & $\mathcal{S}_2$ & $\mathcal{O}_2$ & --- & --- \\ 
- \hline
- 2 & $\mathcal{S'}_2$ & $\mathcal{O}'_2$ & --- & --- \\ 
- \hline
-
+2       & $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$    & 0.820              & 0.413           & 0.994              & 0.590                \\
+        &                                              &                    &                 &                    &                      \\
+\hline\hline
  \end{tabular}
@@
 \end{table}
-
-Guaranteed to have Hermitian symmetry with respect to the lattice site at $\frac{N}{2}$. Furthermore, given that the lattices were closed with periodic boundary conditions, the   
-%After computing the norm of each component of the resulting discrete information entropy wave function $\hat{\psi}_S[n]$, we recover the %information entropy signatures in wavevector space shown in figures \ref{fourier_feature_importances_ssh1} and %%\ref{fourier_feature_importances_ssh2}.
-
-Contrary to their real space counterparts, the wavevector space information entropy signatures are highly localized, which indicates that most of the topological information can be traced to a subset of wavevector modes.
-In fact, in figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} the reduction in information entropy is concentraded mostly on even wavevector modes.
-Furthermore, the wavevector space information entropy signatures are approximately even-symmetric with respect to the wavevector modes at 0 and $\frac{N}{2}$, a consequence of the fact that they are obtained as the DFT of a real signal with periodic boundary conditions.
-
-These (appproximate) symmetries of the topological signatures can guide us through engineering of new topological features from real space coordinates.
-Indeed, it is easy to verify that the DFT of a real signal $x[m]$ that is even-symmetric around 0 and $\frac{N}{2}$ is given by the Discrete Cosine Transform (DCT),
-\begin{equation}
-\label{DCT}
-\hat{x}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\Big(\frac{\pi}{M-1}nm\Big), \quad n=0,\dots,M-1, 
-\end{equation}
-where $M = \frac{N}{2}+1$.
-
-The DCT is often employed in several applications of Digital Signal Processing such as audio and image processing and, most importantly here, data compression.
-As equation \eqref{DCT} shows, the DCT profits from redundance of information in a real, even-symmetric signal, allowing us to write a signal of length $N$ in terms of $M = \frac{N}{2}+1$ features.
-
-We further reduce the number of engineered topological features by taking only even values of $n$ in the left-hand side of equation \eqref{DCT}.
-This is done in agreement with the observation that the information entropy signatures in figure \ref{fourier_feature_importances} are strongly localized on even wavevector modes.
-This leads us to our desired topological features,
-\begin{equation}
-\hat{x}[n] = x[0] + x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\Big(\frac{2\pi}{M-1}nm\Big), \quad n=0,\dots,\frac{M-1}{2}.
-\end{equation}
-
- %the DFT of a real eigenvector $x[m]$\eqref{discrete_fourier_transform} o \eqref{in figures \ref{fourier_feature_importances_ssh1} and %\ref{fourier_feature_importances_ssh2}.
-This gives us an opportunity to engineer new features in real space that carry more relevant %topological information than the simpler strategy of selecting the most important lattice sites in a real space information entropy %signature.
-We may write equation \eqref{discrete_fourier_transform} in matrix form as
-\begin{equation}
-\label{dft}
-\hat{\mathbf{\psi}}_S = \frac{1}{\sqrt{N}} \mathbf{\mathcal{F}}_{N}\mathbf{\psi}_S
-\end{equation}
-where we have used the Sylvester DFT matrix
-\begin{equation}
-\label{sylvester_dft}
-\mathbf{\mathcal{F}}_{N} = \begin{bmatrix}
-\omega_N^{0\cdot 0} & \omega_N^{0\cdot 1} & \omega_N^{0\cdot 2} &... & \omega_N^{0\cdot (N-1)}\\
-\omega_N^{1\cdot 0} & \omega_N^{1\cdot 1} & \omega_N^{1\cdot 2} &... & \omega_N^{1\cdot (N-1)}\\
-\omega_N^{2\cdot 0} & \omega_N^{2\cdot 1} & \omega_N^{2\cdot 2} &... & \omega_N^{2\cdot (N-1)}\\
-\vdots & \vdots & \vdots & \cdots & \vdots\\ 
-\omega_N^{(N-1)\cdot 0} & \omega_N^{(N-1)\cdot 1} & \omega_N^{(N-1)\cdot 2} &... & \omega_N^{(N-1)\cdot (N-1)}\\
-\end{bmatrix}, \quad \text{with} \quad \omega_N = e^{-i\frac{2\pi}{N}}.
-\end{equation}
-
-When trying to engineer informative global topological features in real space, the information entropy signatures in wavevector space provide good hints of where to start.
-Figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} show us that in both numerical experiments the zeroth component in wave vector space is the most important  for learning the topological phases, contributing about 49\% of reduction in information entropy in experiment 1 (section \ref{experiment_1}) and 95\% in experiment 2 (section \ref{experiment_2}).
-Let $x[m]$ be an eigenvector in real space.
-We can use equation \eqref{dft} to compute its wavevector space representation $\hat{k}[n]$ and in particular its zeroth component,
-\begin{equation}
-\label{x_hat_0} 
-\hat{x}[0] = \hat{k}[0] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m].
-\end{equation}
-Equation \eqref{x_hat_0} amounts to taking the sum of components of the eigenvectors in real space as a first engineered topological feature. 
-%may provide key information about the topological phases of SSH Hamiltonians. To visually examine this proposition, we can draw histograms %-----
-
-Now let us consider the symmetric pairs $(m,N-m)$, with $m$ even.
-As figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2} indicate, these pairs concentrate the remaining relevant topological information from the SSH systems investigated here.
-We can therefore engineer the topological features
-
-\begin{equation}
-\label{x_hat_m} 
-\hat{x}[n] = \frac{k[2n]+k[N-2n]}{2} = \sqrt{\frac{1}{N}}\sum_{m=1}^{\frac{N}{2}-1}x[2m]\cos(2mn\omega_N), \quad n = 1, 2, \cdots, \frac{N}{2}-1.
-\end{equation}
-
-Putting the engineered topological features from equations \eqref{x_hat_0} and \eqref{x_hat_m} together, we obtain a compressed version of the real space eigenvectors,
-
-These  which together reduce approximately 10\% of information entropy in experiment 1 (section \ref{experiment_1}) and 2.5\% in experiment 2 (section \ref{experiment_2}).
-The pair (2,98) in wavevector space leads us to another real space engineered feature,
-\begin{equation}
-\label{k_m} 
-\frac{k[m]+k[N-m]}{\sqrt{2}} = \sqrt{\frac{2}{N}}\sum_{m=0}^{N-1}x[m]\cos(2m\omega_N).
-\end{equation}
-
-The two engineered features, $k[0]$ and $\frac{k[2]+k[98]}{\sqrt{2}}$
-
-\begin{equation}
-\label{matrix_discrete_fourier_transform}
-\begin{bmatrix}
-\hat{\psi}_S[0] \\
-\hat{\psi}_S[1] \\
-\vdots \\
-\hat{\psi}_S[N-1]
-\end{bmatrix} = \frac{1}{\sqrt{N}}\begin{bmatrix}
-1 & 1 & 1 &... & 1\\
-1 & W_N & W_N^2 &... &W_N^{N-1}\\
-1 & W_N^2 & W_N^4 &... & W_N^{2(N-1)}\\
-\vdots & \vdots & \vdots & \cdots & \vdots\\ 
-1 & W_N^{N-1} & W_N^{2(N-1)} & \cdots & W_N^{(N-1)^2}    
-\end{bmatrix}
-\begin{bmatrix}
-\psi_S[0] \\
-\psi_S[1] \\
-\vdots \\
-\psi_S[N-1]
-\end{bmatrix}
-\end{equation}
-
-Let us define a discrete wavevector space unit pulse as
-
-\begin{equation}
-\label{wavevector_unit_impulse}
-\hat{\delta}^{(m)}_n = \hat{\delta}[n-m] =
-\begin{cases}
-    1, & \text{if } n=m\\
-    0,              & \text{otherwise}.
-\end{cases}
-\end{equation}
-
-Then equation \eqref{discrete_fourier_transform} yields
-
-\begin{equation}
-\label{fourier_wavevector_unit_impulse}
-\hat{\delta}^{(m)}_n = \hat{\delta}[n-m] =
-\begin{cases}
- \frac{1}{\sqrt{N}}\sum_{l=0}^{N-1}x[l]e^{-\frac{2\pi i}{N} nl}, & \text{if } n=m\\
-    0,              & \text{otherwise}
-\end{cases}
-\end{equation}
-Let us consider the Inverse Discrete Fourier Transform (IDFT) formula, which allows us to invert equation
-
- \eqref{discrete_fourier_transform}
-
-\begin{equation}
-\label{inverse_discrete_fourier_transform}
-\psi_S[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}\hat{\psi}_S[m]e^{\frac{2\pi i}{N} mn}.
-\end{equation}
-
-In both figures \ref{fourier_feature_importances_ssh1} and \ref{fourier_feature_importances_ssh2}, the main mode in wavevector space
-
- main mode of the wavevector space information entropy signatures, which is
 
@@
 
-\begin{figure}
-\centering
-\subfigure[]{\label{fourier_feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_fourier_feature_importances.png}}\quad
-\subfigure[]{\label{fourier_feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_fourier_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{fourier_feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
+%\subfigure[]{\label{fourier_feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
+%\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section %%\ref{numerical_experiments}.
+(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for %approximately 70\% of reduction in information entropy.
 These two peaks correspond to the lattice sites $S_1$.
 (b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located along lattice sites $S_2$.}
-\label{fourier_feature_importances}
-\end{figure}
+These three peaks are located %along lattice sites $S_2$.}
+%\label{fourier_feature_importances}
+%\end{figure}
 

### 2020-07-20 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
Inserting commands in latex document

@@
 \usepackage{bbm}
+\usepackage{xfp}
 %\newcites{supp}{References}
+
+%\def\basiceval#1{\the\numexpr#1\relax}
 
@@
 \newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative
+
+%ssh1
+
+%Our test set in this experiment contained 1005 Hamiltonians (approx.
+15.3\% of all data).
+Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx.
+8.5\%) and 5000 (approx.
+76.2\%) were used to compute validation scores at each iteration.
+%These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration.
+The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
+The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$.
+\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
+
+%\documentclass{article}
+%\usepackage{xfp}
+
+%\begin{document}
+
+%\fpeval{31/45}
+
+%\fpeval{round(31/45,5)}
+
+%\end{document}
+
+%%%%%% Numerical experiments parameters
+\newcommand\nPrec{2}    % precision digits
+\newcommand\accPrec{4}  % precision digits for accuracy scores
+\newcommand\nHam{6561}  % total number of hamiltonians
+\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
+\newcommand\nExp{100}   % number of experiments
+%%%%%%%%%%%%%%% ssh1 experiments
+\newcommand\sshOneTrainNHam{556}
+\newcommand\sshOneValNHam{5000}
+\newcommand\sshOneTestNHam{1005}
+\newcommand\sshOneTrainValWindZeroNHam{2822} %number of winding = 0 in train+val set
+\newcommand\sshOneTrainValWindOneNHam{2734}  %number of winding = 1 in train+val set
+\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
+\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
+%%% real space accuracies
+\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
+\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
+\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
+\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
+\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
+\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
+%%% x1 features table entries 
+\newcommand\xOne{$X_1$}
+\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
+\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
+\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
+\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
+%%% x_S1 features table entries  
+\newcommand\xSOne{$X_{\mathcal{S}_1}$}
+\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
+\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
+\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
+\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
+\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
+\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
+%%% x^c_1 features table entries  
+\newcommand\xcOne{$\hat{X}^c_1$}
+\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
+\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
+\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
+\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
+\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
+\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
+%%% x^cE_1 features table entries  
+\newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
+\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
+\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
+\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
+\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
+\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
+\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
+%%% x^cSE_1 features table entries  
+\newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
+\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
+\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
+\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
+\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
+\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
+\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
+%%% x^s_1 features table entries  
+\newcommand\xsOne{$\hat{X}^s_1$}
+\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
+\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
+\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
+\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
+\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
+\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
+%%% x^SO_1 features table entries  
+\newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
+\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
+\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
+\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
+\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
+\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
+\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
+%%% x^SSO_1 features table entries  
+\newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
+\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
+\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
+\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
+\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
+\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
+\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}
+
+% real space best 04 accuracies
+%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       
+%\newcommand\sshOneEigenValAcc{0.96392276}         
+%\newcommand\sshOneEigenTestAcc{0.78966836492891}       
+%\newcommand\sshOneHamTrainAcc{1.0}             
+%\newcommand\sshOneHamValAcc{1.0}               
+%\newcommand\sshOneHamTestAcc{0.9918720379146919}
+
+%ssh2
+\newcommand\sshTwoTrainNHam{2761}
+\newcommand\sshTwoValNHam{2760}
+\newcommand\sshTwoTestNHam{1040}
+
+\newcommand\sshTwoTrainValWindMinusOneNHam{988} %number of winding = -1 in train+val set
+\newcommand\sshTwoTrainValWindZeroNHam{1795} %number of winding = 0 in train+val set
+\newcommand\sshTwoTrainValWindOneNHam{1781}  %number of winding = 1 in train+val set
+\newcommand\sshTwoTrainValWindTwoNHam{957}   %number of winding = 2 in train+val set
+
+\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
+\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
+\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
+\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set
+
+\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
+\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
+\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
+\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
+\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
+\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
+
+\newcommand\nEst{25}   % number of estimators in random forest
 
@@
 
-In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
+In each experiment our grid consisted of \nHam\ Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
 The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
@@
 This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the correct winding number values.
+For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = \epsilonValue$ around the correct winding number values.
 Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
@@
 Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
-The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-\textcolor{blue}{Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ = 100 experiments.
+The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
+\textcolor{blue}{Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ experiments.
 The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps}.
@@
 \label{experiment_1}
-Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
+Our test set in this experiment contained \sshOneTestNHam\ Hamiltonians (approx.
+\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}\% of all data).
+Of the remaining \fpeval{\sshOneTrainNHam+\sshOneValNHam} Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
+\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}\%) and \sshOneValNHam\ (approx.
+\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}\%) were used to compute validation scores at each iteration.
 These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
+The composition of the train + validation set for this experiment was \fpeval{round(\sshOneTrainValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}\% of Hamiltonians with winding number $W$ = 0 and \fpeval{round(\sshOneTrainValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}\% with winding number $W$ = 1.
+The composition of the test set was \fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% of Hamiltonians with winding number $W$ = 0 and \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% with winding number $W=1$.
 \textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
@@
 The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (98.2\%), validation eigenvectors (96.4\%) and test eigenvectors (78.8\%).
+In particular, we report mean accuracies on training eigenvectors (\fpeval{round(\sshOneEigenTrainAcc,\accPrec)}), validation eigenvectors (\fpeval{round(\sshOneEigenValAcc,\accPrec)}) and test eigenvectors (\fpeval{round(\sshOneEigenTestAcc,\accPrec)}).
 Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
-\textcolor{blue}{When compared with the baseline test accuracy of 55.2\% of a system that predicts the whole test set as having winding number $W=1$, the accuracy of 99.1\% on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} \citequote{sufficient_accuracy}
+These were \fpeval{round(\sshOneHamTrainAcc,\accPrec)} for training Hamiltonians, \fpeval{round(\sshOneHamValAcc,\accPrec)} for validation Hamiltonians and \fpeval{round(\sshOneHamTestAcc,\accPrec)}  for test Hamiltonians.
+\textcolor{blue}{When compared with the baseline test accuracy of \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)} of a system that predicts the whole test set as having winding number $W=1$, the accuracy of \fpeval{round(\sshOneHamTestAcc,\accPrec)} on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} \citequote{sufficient_accuracy}
 
@@
 This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 25 decision trees.
-Our data set consisted of 1040 (15.8\%) test Hamiltonians.
-The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving 2761 (42.1\%) training Hamiltonians and 2760 (42.1\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (17.9\%), $W$ = 0 (32.5\%), $W$ = 1 (32.3\%) and $W$ = 2 (17.3\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (36.3\%), $W$ = 0 (11.1\%), $W$ = 1 (12.7\%) and $W$ = 2 (39.9\%).
-
-Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.1\% for validation eigenvectors and 66.4\% for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 88.2\% for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from 66.4\% eigenvector accuracy to 88.2\% Hamiltonian accuracy) attests to its power.
+For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with \nEst\ decision trees.
+Our data set consisted of \sshTwoTestNHam\ (\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}\%) test Hamiltonians.
+The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}\%) training Hamiltonians and \sshTwoValNHam\ (\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}\%) validation Hamiltonians.
+The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\fpeval{round(\sshTwoTrainValWindMinusOneNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%), $W$ = 0 (\fpeval{round(\sshTwoTrainValWindZeroNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%), $W$ = 1 (\fpeval{round(\sshTwoTrainValWindOneNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%) and $W$ = 2 (\fpeval{round(\sshTwoTrainValWindTwoNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%).
+The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%), $W$ = 0 (\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%), $W$ = 1 (\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%) and $W$ = 2 (\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%).
+
+Mean accuracies across \nExp\ repetitions of experiment 2 were \fpeval{round(\sshTwoEigenTrainAcc,\accPrec)} for training eigenvectors, \fpeval{round(\sshTwoEigenValAcc,\accPrec)} for validation eigenvectors and \fpeval{round(\sshTwoEigenTestAcc,\accPrec)} for test eigenvectors.
+Mean accuracies resulting from eigenvector ensembling were \fpeval{round(\sshTwoHamTrainAcc,\accPrec)} for training Hamiltonians, \fpeval{round(\sshTwoHamValAcc,\accPrec)} for validation Hamiltonians and \fpeval{round(\sshTwoHamTestAcc,\accPrec)} for test Hamiltonians.
+The large accuracy gain achieved by eigenvector ensembling in the test set (going from \fpeval{round(\sshTwoEigenTestAcc,\accPrec)} eigenvector accuracy to \fpeval{round(\sshTwoHamTestAcc,\accPrec)} Hamiltonian accuracy) attests to its power.
+The effectiveness of eigenvector ensembling is also evident from the much worse performance (\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
 
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1 (section \ref{experiment_1}), only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+For experiment 1 (section \ref{experiment_1}), only six lattice sites (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites(0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
 
@@
 
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran each experiment using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 (section \ref{experiment_1}) using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 (section \ref{experiment_2}) using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.}\citequote{key_top} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+%To see if learning the topological phases can be achieved efficiently by employing simpler models we reran each experiment using only a small %subset of most relevant lattice sites.
+In our rerun of experiment 1 (section \ref{experiment_1}) using only lattice sites $S'_1$ = (0, 50, %51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy), mean accuracies were 97.0\% for training %eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
+Mean accuracies obtained from eigenvector ensembling were %99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
+
+%Mean accuracies for our rerun of experiment 2 (section \ref{experiment_2}) using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, %99) (which contributed approximately 20 \% of total reduction in Shannon information entropy) were 99.9\% for training eigenvectors, 87.7\% %for validation eigenvectors and 47.3\% for test eigenvectors.
+Eigenvector ensembling yields mean accuracies of 100\% for training %Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
 
@@
 \begin{equation}
-\label{DCT_subsets}
+\label{DST_subsets}
 \mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
@@
 $\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
-The features engineered in strategy \emph{iv)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH systems, type of topological features used as well as which features in real and wavevector space were used to compute them.
-
-The lattice compression strategies  These numerical experiments differed both on which topological features were used (whether DCT or DST topological features), as well as which features in real space were used to compute the engineered topological features.
-The results obtained in the numerical experiments of section \ref{numerical_experiments} are also listed in table \ref{numerical_results} for the sake of reference.
+The features engineered in strategy \emph{iv)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH system, type of topological features used as well as which features in real and wavevector space were used to engineer them.
+
+The results shown in table \ref{numerical_results} carry some important surprises.
+For example, the topological phase transition boundaries of SSH-1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores in the .
+The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ produce accuracy scores at near the same level as using the whole lattice.
+
+Even more striking is the performance achieved by the DCT topological features $\hat{X}^c_{\mathcal{S},\mathcal{E}}$ defined in equation \eqref{DCT_very_compressed}.
+For SSH-1 systems, they perform on par with using the full set of real space features $X_1$, while for SSH-2 systems a small loss in accuracy is incurred.
+
+Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features versus DST topological features.
+The latter seems to have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features $\hat{X}^s_{\mathcal{S},\mathcal{O}}$ in both SSH-1 and SSH-2 systems.
+This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
+
+The accuracy scores obtained with the real space features $X_{\mathcal{S}_\alpha}$ and the DCT topological features $\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
+\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.}\citequote{key_top} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
 
 \begin{table}
- \begin{tabular}{||c c c c c c||} 
+ \begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
  \hline
-SSH     &Features                                      & Eigenvector val.    & Eigenvector test      & Hamiltonian val.    & Hamiltonian test \\ % [0.5ex] 
+SSH systems &Features                              &Val. eigenvectors  &Test eigenvectors  &Val. Hamiltonians          &Test Hamiltonians  \\  
  \hline\hline
             &                                              &               &                    &                      &                   \\
-1       & $X_1$                                        & 0.964              & 0.790           & 1                  & 0.992                \\  
+1           &\xOne                                         &\xOneEigVal    &\xOneEigTest        &\xOneHamVal           &\xOneHamTest       \\
 \hline
-1       & $X_{\mathcal{S}_1}$                          & 0.944              & 0.776           & 0.985              & 0.990                \\
+1           &\xSOne                                        &\xSOneEigVal   &\xSOneEigTest       &\xSOneHamVal          &\xSOneHamVal       \\
 \hline
-1       & $\hat{X}^c_1$                                & 0.952              & 0.737           & 0.998              & 0.992                \\
+1           &\xcOne                                        &\xcOneEigVal   &\xcOneEigTest       &\xcOneHamVal          &\xcOneHamTest      \\
 \hline
-1       & $\hat{X}^c_{\mathcal{E}_1}$                  & 0.828              & 0.607           & 0.998              & 0.919                \\
+1           &\xcEOne                                       &\xcEOneEigVal  &\xcEOneEigTest      &\xcEOneHamVal         &\xcEOneHamTest     \\
 \hline
-1       & $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$    & 0.944              & 0.818           & 0.985              & 0.993                \\
+1           &\xcSEOne                                      &\xcSEOneEigVal &\xcSEOneEigTest     &\xcSEOneHamVal        &\xcSEOneHamTest    \\
 \hline
-1       & $\hat{X}^s_1$                                & 0.953              & 0.731           & 0.991              & 0.986                \\
+1           &\xsOne                                        &\xsOneEigVal   &\xsOneEigTest       &\xsOneHamVal          &\xsOneHamTest      \\
 \hline
-1       & $\hat{X}^s_{\mathcal{O}_1}$                  & 0.694              & 0.542           & 0.709              & 0.480                \\
+1           &\xsOOne                                       &\xsOOneEigVal  &\xsOOneEigTest      &\xsOOneHamVal         &\xsOOneHamTest     \\
 \hline
-1       & $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$    & 0.946              & 0.782           & 0.985              & 0.940                \\
+1           &\xsSOOne                                      &\xsSOOneEigVal &\xsSOOneEigTest      &\xsSOOneHamVal       &\xsSOOneHamTest    \\
 \hline
@@
 2           & $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$    & 0.820              & 0.413           & 0.994                & 0.590             \\
-        &                                              &                    &                 &                    &                      \\
+            &                                              &                    &                 &                                          \\
 \hline\hline
  \end{tabular}
-\caption{\label{numerical_results}Your caption.}
+
+\caption{\label{numerical_results}ACCURACY SCORES OF NUMERICAL EXPERIMENTS.
+The features used to train the decision trees (SSH-1) or random forests (SSH-2) in the numerical experiments with SSH-$\alpha$ systems were as follows.
+Real space features: all real space lattice sites ($X_\alpha$) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ ($X_{\mathcal{S}_{\alpha}}$) (equation \eqref{lattice_subsets}).
+DCT topological features: all DCT topological features $\hat{X}^c_\alpha$ (equation \eqref{DCT}); DCT topological features from subset $\hat{X}^c_{\mathcal{E}_\alpha}$ (equation \eqref{DCT_subsets}; DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ ($\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$) (equation \eqref{DCT_very_compressed}).
+DST topological features: all DST topological features $\hat{X}^s_\alpha$ (equation \eqref{DST}); DST topological features from subset $\hat{X}^s_{\mathcal{O}_\alpha}$ (equation \eqref{DST_subsets}; DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ ($\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$) (equation \eqref{DST_very_compressed}).
+}
 \end{table}
@@
 
-\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching in to both disciplines.
+\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
 }
@@
 As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
-This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment and led us to the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
+This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment executed in section \ref{numerical_experiments} and led us to the new topological features of section \ref{topological_feature_engineering} and the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
 The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
 
-\textcolor{blue}{The accuracy scores obtained in the numerical experiments of section \ref{numerical_experiments} were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
+\textcolor{blue}{The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
 This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}\citequote{superior_comparable}
@@
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of Shannon information entropy, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of Shannon information entropy given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
 Whether there is any relationship between the local topological markers detailed in \cite{PhysRevB.84.241106,caio2019topological} and the information entropy of the ensemble of eigenvectors discussed here is left for speculation.
-
-\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, passing through proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between the two disciplines can be enriching in both ways.
-}
 

### 2020-07-21 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
Finished letter to referee. Now reviewing paper.

@@
 \usepackage{xfp}
+\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
+\usepackage{booktabs}
+\renewcommand{\figurename}{Figure}
+\renewcommand{\tablename}{Table}
+\renewcommand{\thetable}{\arabic{table}}
+%\captionsetup{justification=raggedright, singlelinecheck = false}
+%\usepackage{makecell}
+%\usepackage{cellspace}
+
 %\newcites{supp}{References}
@@
 \newcommand\nExp{100}   % number of experiments
+%%%table commands
+%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
+\newcommand{\tableRow}[1]{\\[#1 cm]}
+\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
+\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
+\newcommand\tableRowEnd{\tableRow{0.15}}
+%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
+%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
+%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
+%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
+%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
+%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
+\newcommand\SSHSys{SSH systems}         
+\newcommand\Feat{Features}              
+\newcommand\ValEig{Val. eigenvectors}   
+\newcommand\TestEig{Test eigenvectors}  
+\newcommand\ValHam{Val. Hamiltonians}   
+\newcommand\TestHam{Test Hamiltonians}
+
 %%%%%%%%%%%%%%% ssh1 experiments
@@
 
-% real space best 04 accuracies
-%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       
-%\newcommand\sshOneEigenValAcc{0.96392276}         
-%\newcommand\sshOneEigenTestAcc{0.78966836492891}       
-%\newcommand\sshOneHamTrainAcc{1.0}             
-%\newcommand\sshOneHamValAcc{1.0}               
-%\newcommand\sshOneHamTestAcc{0.9918720379146919}
-
 %ssh2
@@
 \newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
+
+%%% x2 features table entries 
+\newcommand\xTwo{$X_2$}
+\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
+\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
+\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
+\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
+\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
+%%% x_S2 features table entries  
+\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
+\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
+\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
+\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
+\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
+\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
+%%% x^c_2 features table entries  
+\newcommand\xcTwo{$\hat{X}^c_2$}
+\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
+\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
+\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
+\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
+\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
+%%% x^cO_2 features table entries  
+\newcommand\xcOTwo{$\hat{X}^c_{\mathcal{O}_2}$}
+\newcommand\xcOTwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
+\newcommand\xcOTwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
+\newcommand\xcOTwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
+\newcommand\xcOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcOTwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
+\newcommand\xcOTwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
+
+%%% x^cSO_2 features table entries  
+\newcommand\xcSOTwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{O}_2}$}
+\newcommand\xcSOTwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
+\newcommand\xcSOTwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
+\newcommand\xcSOTwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
+\newcommand\xcSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcSOTwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
+\newcommand\xcSOTwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
+%%% x^s_2 features table entries  
+\newcommand\xsTwo{$\hat{X}^s_2$}
+\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
+\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
+\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
+\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
+\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
+%%% x^SO_2 features table entries  
+\newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
+\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
+\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
+\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
+\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
+\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
+%%% x^SSO_2 features table entries  
+\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
+\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
+\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
+\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
+\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
+\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
 
@@
 
-we appreciate the valuable insights on how to improve our article that you have provided us with.
-Below we address each of the emphasized points separately, as they were written in the reply that was sent back to us.
-We quote the issues raised in italic, and highlight in boldface the points that we thought were particularly relevant.
+we appreciate the valuable insights on how to improve our article that you have provided us.
+These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical results.
+
+These new results have been added to the paper in the form of two new sections: \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
+The eigenvector ensembling algorithm}.
+The section \textbf{VII.
+Discussion} has been extended to include comments on some of the issues that were raised.
+The sections are now numbered for clarity.
+
+Below we address each of the raised issues separately, as they were written in the reply that was sent back to us.
+We quote the raised issues in italic, and highlight in bold the points that we thought were particularly relevant and guided us in the improvement of the manuscript.
+The answers to each of the major points are written in blue.
 
@@
 \emph{\textbf{I am not sure about the novelty and generality of their method.}\genquote{pipeline_not_work} For
-example, their pipeline cannot work for complex experimental physical
-systems, where the Hamiltonian could be unknown. Moreover, the authors
-state that it is sufficient to use the input data in real space to
-predict the topological phase with high accuracy. \textbf{It is not clear to
-me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of
-using the input data in real space instead of the Hamiltonian in
-wavevector space. \textbf{I expect the evidence to indicate that their method
-is superior or comparable to any other method}\genquote{superior_comparable}. It is worth mentioning
-that the author already discussed \textbf{the motivations for developing a
-data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological
-phases from real space data" section. However, these arguments should
-be pointed carefully in the "Introduction" section.}
+example, their pipeline cannot work for complex experimental physical systems, where the Hamiltonian could be unknown. Moreover, the authors
+state that it is sufficient to use the input data in real space to predict the topological phase with high accuracy. \textbf{It is not clear to
+me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of using the input data in real space instead of the Hamiltonian in wavevector space.
+\textbf{I expect the evidence to indicate that their method is superior or comparable to any other method}\genquote{superior_comparable}.
+It is worth mentioning that the author already discussed \textbf{the motivations for developing a
+data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological phases from real space data" section.
+However, these arguments should be pointed carefully in the "Introduction" section.}
 
@@
 Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
-We have added a paragraph to the section \textbf{Discussion} outlining these possibilities.
+We have added a paragraph to the section \textbf{VII.
+Discussion} outlining these possibilities.
 As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
-Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the Shannon entropy signature and the information entropy uncertainty relations for topological phase transitions presented here for the first time.
-We have added a paragraph to the \textbf{Introduction} emphasizing this point.
+Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data and the Shannon information entropy signature and uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have added a paragraph to the section \textbf{I.
+Introduction} emphasizing these new results.
 }
 
-\textcolor{blue}{\citequote{sufficient_accuracy}, \citequote{superior_comparable} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
+\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
 This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
-We have added a paragraph to the section \textbf{Numerical experiments} to emphasize the use of this baseline.
-As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
+We have added a paragraph to the section \textbf{III.
+Numerical experiments} to emphasize the use of this baseline.}
+
+\textcolor{blue}{\citequote{superior_comparable} As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
 Rev.
@@
 This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.}
-
-\textcolor{blue}{\citequote{superior_comparable}In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
+In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
 Rev.
@@
 When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
-While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.
-}
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
 
 \textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data-driven approach based on real space should be in the Introduction.
-We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the \textbf{Introduction}.}
+We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the section \textbf{I.
+Introduction} in the main paper.}
 
 \vspace{0.5cm}
-\emph{I am not sure which crucial problems their algorithm can solve that
-was not possible before with machine learning. Furthermore, along with
-the emerging research of unsupervised learning methods in realizing
-the topological phases, \textbf{why should the supervised learning method be
-focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript,
-where I do not see the proposal's advantages, I would prefer the
-\textbf{unsupervised approaches that could grasp information from a given
-system without knowing their phases}\genquote{unsupervised_approaches}. In my opinion, a proper intrinsic
-route for understanding physical systems without much information on
-the dynamics of the system will lead to significant future
-developments and a better understanding of physic systems.}
+\emph{I am not sure which crucial problems their algorithm can solve that was not possible before with machine learning.
+Furthermore, along with the emerging research of unsupervised learning methods in realizing the topological phases, \textbf{why should the supervised learning method be focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript, where I do not see the proposal's advantages, I would prefer the \textbf{unsupervised approaches that could grasp information from a given system without knowing their phases}\genquote{unsupervised_approaches}.
+In my opinion, a proper intrinsic route for understanding physical systems without much information on
+the dynamics of the system will lead to significant future developments and a better understanding of physic systems.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
-We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
-This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the new section \textbf{Emergent information entropy wave functions} added to this new version of the article.}
-
-\textcolor{blue}{\citequote{unsupervised_approaches} Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{Discussion}.
-Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool in data-driven physics, which by itself is an unsupervised learning task and can serve as a preprocessing step to further applications of machine learning to physics.}
+\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
+We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of information entropy as loss function provides a clear way to measure feature importance.
+This is compounded by the fact that information entropy plays a very important role in information theory and physics, as is evidenced in the new section \textbf{VI.
+Emergent information entropy wave functions} added to this new version of the article.}
+
+\textcolor{blue}{\citequote{unsupervised_approaches} The new section \textbf{V.
+Topological feature engineering and lattice compression} shows how unsupervised learning can be performed with eigenvector ensembling using tree based methods as learning algorithms.
+In fact, two of the main tasks under the broad umbrella of unsupervised learning are exactly those: dimensionality reduction and feature engineering.
+Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
+This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{VII.
+Discussion}.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used as a powerful dimensionality reduction tool in other, unrelated data-driven or numerical physics tasks, which by itself is another example of unsupervised learning and can serve as a preprocessing step to further applications of machine learning to physics.}
 
 \vspace{0.5cm}
-\emph{The details of \textbf{the eigenvector ensembling algorithm should be
-addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material. What is
-the specific algorithm used in the paper to train on eigenvectors? I
-think it is important even if the readers are not familiar with some
-ML techniques. Some readers in physics may find it difficult to
-understand some ML technical terms such as bootstrapping, training and
-validation, test sets, etc. In addition, \textbf{I expect proof of what
-"physics" their method captures and why the eigenvector can play an
-important role in characterizing the topological phase}\genquote{eigenvector_physics}. If this
-physical interpretability is not mentioned, it is very difficult to
-see the contribution of the method in physics.}
+\emph{The details of \textbf{the eigenvector ensembling algorithm should be addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material.
+What is the specific algorithm used in the paper to train on eigenvectors?
+I think it is important even if the readers are not familiar with some ML techniques.
+Some readers in physics may find it difficult to understand some ML technical terms such as bootstrapping, training and validation, test sets, etc.
+In addition, \textbf{I expect proof of what "physics" their method captures and why the eigenvector can play an important role in characterizing the topological phase}\genquote{eigenvector_physics}.
+If this physical interpretability is not mentioned, it is very difficult to see the contribution of the method in physics.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  We have moved the section \textbf{The eigenvector ensembling algorithm} from the Supplementary Material to the main paper.
+\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  The section \textbf{II.
+The eigenvector ensembling algorithm} has been moved from the Supplementary Material to the main paper.
 The issue of specifying the particular learning algorithms used to train on eigenvectors is addressed in the subsections for each SSH experiment (see subsections \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees} and \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}).
-In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module.}
-
-\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
+In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module used to run the numerical experiments in the paper.}
+
+\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{II.
+The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
 Therefore, by expressing a data set of eigenvectors on a suitable choice of basis (which in this paper is the real space basis), we are able to investigate properties of a family of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
@@
 \vspace{0.5cm}
-\emph{The authors made efforts to analyze how the algorithm was able to
-recover the Hamiltonians' global property in the "Information Entropy
-Signatures" section. The authors state that learning topological
-phases from local real-space data in bulk is still possible even for
-small subsets of lattice sites, then refer us to the section "Learning
-topological phases from real space data" in the Supplementary
-Material. The authors mention on page 4 of the Supplementary Material
-that \textbf{"key topological information can be said to be localized on a few
-lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
-However, \textbf{I fail to understand the physical insights behind it}\genquote{physical_insights}. Without
-the proper explanation, it is difficult to see the effectiveness of
-their method or verify the method with a more complex model instead of
-the simple SSH form.}
+\emph{The authors made efforts to analyze how the algorithm was able to recover the Hamiltonians' global property in the "Information Entropy
+Signatures" section. The authors state that learning topological phases from local real-space data in bulk is still possible even for
+small subsets of lattice sites, then refer us to the section "Learning topological phases from real space data" in the Supplementary
+Material.
+The authors mention on page 4 of the Supplementary Material that \textbf{"key topological information can be said to be localized on a few lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
+However, \textbf{I fail to understand the physical insights behind it}\genquote{physical_insights}.
+Without the proper explanation, it is difficult to see the effectiveness of
+their method or verify the method with a more complex model instead of the simple SSH form.}
 
@@
 \textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
-We have therefore moved it to the final patragraph of the section \textbf{Information entropy signatures} in the main text.}
-
-\textcolor{blue}{\citequote{physical_insights} We have added the new section \textbf{Emergent information entropy wave functions} in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinit lattice.
-Therefore, the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures) and finally iii) interpret these new properties in the light of theoretical physics.}
-
-\textcolor{blue}{We find it noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
-Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
+We have therefore moved it to the final patragraph of the section \textbf{V.
+Topological feature engineering and lattice compression} in the main text.}
+
+\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), iii) generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
+Topological feature engineering and lattice compression},  and finally iv) interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
+Emergent information entropy wave functions}, in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinite lattice.}
+
+\textcolor{blue}{It is noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
+Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{VI.
+Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
 
@@
 
-\emph{The authors state in the abstract that "model explainability in
-machine learning can advance the research of exotic quantum materials
-with properties that may power future technological applications such
-as qubit engineering for quantum computing." \textbf{Could you explain a bit
-more about properties that may power future quantum computing?}\genquote{quantum_comp}}
+\emph{The authors state in the abstract that "model explainability in machine learning can advance the research of exotic quantum materials
+with properties that may power future technological applications such as qubit engineering for quantum computing." \textbf{Could you explain a bit more about properties that may power future quantum computing?}\genquote{quantum_comp}}
 
 \vspace{0.25cm}
-\citequote{quantum_comp} Insert comments about topological qubits?
+\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
 
 \vspace{0.5cm}
-\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single
-iterations of experiments 1 and 2 as seen from parameter space". \textbf{What
-are the experiments 1 and 2?}\genquote{experiments_1_2}}
+\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single iterations of experiments 1 and 2 as seen from parameter space".
+\textbf{What are the experiments 1 and 2?}\genquote{experiments_1_2}}
 
@@
 \textcolor{blue}{\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
-The designation "experiment 1" is used to abbreviate the subsection \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
-Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.}
+The designation "experiment 1" is used to abbreviate the subsection \textbf{III.A Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
+Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{III.B Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.}
 
@@
 \emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
-such as "the accuracy" and "the probability heatmap," "eigenvector
-accuracy," and "Hamiltonian accuracy."}
+such as "the accuracy" and "the probability heatmap," "eigenvector accuracy," and "Hamiltonian accuracy."}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{Numerical experiments}.}
+\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{III.
+Numerical experiments}.
+Furthermore, the new section \textbf{V.
+Topological feature engineering and lattice compression} contains a summary of accuracy scores obtained in all numerical experiments performed in the paper.}
 
 \vspace{0.5cm}
-\emph{I prefer to \textbf{put the definition of information entropy signatures in
-the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
+\emph{I prefer to \textbf{put the definition of information entropy signatures in the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
+\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{VI.
+Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
 
@@
 \email{linneuholanda@gmail.com, linneu@cbpf.br}
-\affiliation{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
+\affiliation{Integrated Quantum Materials, Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
 \affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
@@
 \begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems from bulk data in real lattice space.
+We develop a supervised machine learning algorithm that is able to learn topological phases of finite condensed matter systems from bulk data in real lattice space.
 The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
 We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
+We further use insights obtained from these information entropy signatures to engineer global topological features from real space lattice data that still carry most of the topological information in the lattice, while greatly diminishing the size of feature space, thus effectively amounting to a topological lattice compression.
+Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which allows us to establish Heisenberg and Hirschman uncertainty relations for topological phase transitions.
 The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
@@
 We describe here in detail each of these steps as they were implemented in this work.
+For a comprehensive introduction to the concepts referenced in the steps below, we recommend the book \cite{friedman2001elements}.
 \vspace{.3cm}
@@
 
+%\newcommand\SSHSys{\thead{SSH systems}}
+%\newcommand\Feat{\thead{Features}}
+%\newcommand\ValEig{\thead{Val. eigenvectors}}
+%\newcommand\TestEig{\thead{Test eigenvectors}}
+%\newcommand\ValHam{\thead{Val. Hamiltonians}}
+%\newcommand\TestHam{\thead{Test Hamiltonians}}
+
 \begin{table}
+\label{numerical_results}
 \begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
- \hline
-SSH systems &Features                              &Val. eigenvectors  &Test eigenvectors  &Val. Hamiltonians          &Test Hamiltonians  \\  
- \hline\hline
-            &                                              &               &                    &                      &                   \\
-1           &\xOne                                         &\xOneEigVal    &\xOneEigTest        &\xOneHamVal           &\xOneHamTest       \\
-\hline
-1           &\xSOne                                        &\xSOneEigVal   &\xSOneEigTest       &\xSOneHamVal          &\xSOneHamVal       \\
-\hline
-1           &\xcOne                                        &\xcOneEigVal   &\xcOneEigTest       &\xcOneHamVal          &\xcOneHamTest      \\
-\hline
-1           &\xcEOne                                       &\xcEOneEigVal  &\xcEOneEigTest      &\xcEOneHamVal         &\xcEOneHamTest     \\
-\hline
-1           &\xcSEOne                                      &\xcSEOneEigVal &\xcSEOneEigTest     &\xcSEOneHamVal        &\xcSEOneHamTest    \\
-\hline
-1           &\xsOne                                        &\xsOneEigVal   &\xsOneEigTest       &\xsOneHamVal          &\xsOneHamTest      \\
-\hline
-1           &\xsOOne                                       &\xsOOneEigVal  &\xsOOneEigTest      &\xsOOneHamVal         &\xsOOneHamTest     \\
-\hline
-1           &\xsSOOne                                      &\xsSOOneEigVal &\xsSOOneEigTest      &\xsSOOneHamVal       &\xsSOOneHamTest    \\
-\hline
-2           & $X_2$                                        & 0.971              & 0.663           & 0.997                & 0.880             \\
-\hline
-2           & $X_{\mathcal{S}_2}$                          & 0.959              & 0.617           & 0.996                & 0.863             \\
-\hline
-2           & $\hat{X}^c_2$                                & 0.974              & 0.690           & 0.998                & 0.886             \\
-\hline
-2           & $\hat{X}^c_{\mathcal{E}_2}$                  & 0.899              & 0.536           & 0.995                & 0.790             \\
-\hline
-2           & $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$    & 0.900              & 0.503           & 0.996                & 0.767             \\
-\hline
-2           & $\hat{X}^s_2$                                & 0.974              & 0.688           & 0.997                & 0.890             \\
-\hline
-2           & $\hat{X}^s_{\mathcal{O}_2}$                  & 0.904              & 0.553           & 0.992                & 0.743             \\
-\hline
-2           & $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$    & 0.820              & 0.413           & 0.994                & 0.590             \\
-            &                                              &                    &                 &                                          \\
-\hline\hline
+%\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.} \label{numerical_results}
+%\begin{table}[th]
+%\caption{An Example of a Table}
+%\centering\label{table_example}
+%\begin{tabular}{|Sc*{9}{c|}}
+\toprule
+\SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd 
+\midrule
+%                     &                  &                   &                   &                     &                   \tableRow{0.3}
+1                     &\xOne             &\xOneEigVal        &\xOneEigTest       &\xOneHamVal          &\xOneHamTest       \tableRowEnd
+1                     &\xSOne            &\xSOneEigVal       &\xSOneEigTest      &\xSOneHamVal         &\xSOneHamVal       \tableRowEnd
+1                     &\xcOne            &\xcOneEigVal       &\xcOneEigTest      &\xcOneHamVal         &\xcOneHamTest      \tableRowEnd
+1                     &\xcEOne           &\xcEOneEigVal      &\xcEOneEigTest     &\xcEOneHamVal        &\xcEOneHamTest     \tableRowEnd
+1                     &\xcSEOne          &\xcSEOneEigVal     &\xcSEOneEigTest    &\xcSEOneHamVal       &\xcSEOneHamTest    \tableRowEnd
+1                     &\xsOne            &\xsOneEigVal       &\xsOneEigTest      &\xsOneHamVal         &\xsOneHamTest      \tableRowEnd
+1                     &\xsOOne           &\xsOOneEigVal      &\xsOOneEigTest     &\xsOOneHamVal        &\xsOOneHamTest     \tableRowEnd
+1                     &\xsSOOne          &\xsSOOneEigVal     &\xsSOOneEigTest    &\xsSOOneHamVal       &\xsSOOneHamTest    \tableRowEnd
+2                     &\xTwo             &\xTwoEigVal        &\xTwoEigTest       &\xTwoHamVal          &\xTwoHamTest       \tableRowEnd
+2                     &\xSTwo            &\xSTwoEigVal       &\xSTwoEigTest      &\xSTwoHamVal         &\xSTwoHamVal       \tableRowEnd
+2                     &\xcTwo            &\xcTwoEigVal       &\xcTwoEigTest      &\xcTwoHamVal         &\xcTwoHamTest      \tableRowEnd
+2                     &\xcOTwo           &\xcOTwoEigVal      &\xcOTwoEigTest     &\xcOTwoHamVal        &\xcOTwoHamTest     \tableRowEnd
+2                     &\xcSOTwo          &\xcSOTwoEigVal     &\xcSOTwoEigTest    &\xcSOTwoHamVal       &\xcSOTwoHamTest    \tableRowEnd
+2                     &\xsTwo            &\xsTwoEigVal       &\xsTwoEigTest      &\xsTwoHamVal         &\xsTwoHamTest      \tableRowEnd
+2                     &\xsOTwo           &\xsOTwoEigVal      &\xsOTwoEigTest     &\xsOTwoHamVal        &\xsOTwoHamTest     \tableRowEnd
+2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
+\bottomrule
 \end{tabular}
-
-\caption{\label{numerical_results}ACCURACY SCORES OF NUMERICAL EXPERIMENTS.
+\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.
 The features used to train the decision trees (SSH-1) or random forests (SSH-2) in the numerical experiments with SSH-$\alpha$ systems were as follows.
@@
 
+\textcolor{blue}{
 The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to wavevector space methods.
+Such systems usually break translational symmetry and therefore are not amenable to canonical wavevector space methods.
+Thus, the discovery and engineering of topological features from real space data as demonstrated in this work carries great promise to the theoretical investigation of these systems.
+}
+
+\textcolor{blue}{
+Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
+On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy of information is a necessary commodity to ensure error-correction within the system.
+We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
+}
 

### 2020-07-21 07_paper/article.tex
Generating final version in directory 07_paper

--- 2020-07-21 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Comments referee %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Reply to the first referee }
-\section*{Reply to the second referee}
-Dear referee,
-
-we appreciate the valuable insights on how to improve our article that you have provided us.
-These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical results.
-
-These new results have been added to the paper in the form of two new sections: \textbf{V.
-Topological feature engineering and lattice compression} and \textbf{VI.
-Emergent information entropy wave functions}.
-We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
-The eigenvector ensembling algorithm}.
-The section \textbf{VII.
-Discussion} has been extended to include comments on some of the issues that were raised.
-The sections are now numbered for clarity.
-
-Below we address each of the raised issues separately, as they were written in the reply that was sent back to us.
-We quote the raised issues in italic, and highlight in bold the points that we thought were particularly relevant and guided us in the improvement of the manuscript.
-The answers to each of the major points are written in blue.
-
-\subsection*{Major}
-
-\emph{\textbf{I am not sure about the novelty and generality of their method.}\genquote{pipeline_not_work} For
-example, their pipeline cannot work for complex experimental physical systems, where the Hamiltonian could be unknown. Moreover, the authors
-state that it is sufficient to use the input data in real space to predict the topological phase with high accuracy. \textbf{It is not clear to
-me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of using the input data in real space instead of the Hamiltonian in wavevector space.
-\textbf{I expect the evidence to indicate that their method is superior or comparable to any other method}\genquote{superior_comparable}.
-It is worth mentioning that the author already discussed \textbf{the motivations for developing a
-data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological phases from real space data" section.
-However, these arguments should be pointed carefully in the "Introduction" section.}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{pipeline_not_work} We can think of several use cases for the eigenvector ensembling procedure outlined in the paper.
-Among these, we emphasize its applicability in dealing with the so-called "curse of dimensionality" that plagues many problems in condensed matter and statistical physics.
-In the paper, we have demonstrated an application in which the dimensionality of an SSH lattice can be greatly reduced in so far as its topological properties are concerned, simply by extracting the most relevant lattice sites in its information entropy signature.
-Similar feature extraction and dimensionality reduction procedures are often employed in machine learning applications and are surely to become the norm in data-driven physics.
-The eigenvector ensembling algorithm can thus be viewed as a general framework in this direction.
-Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
-We have added a paragraph to the section \textbf{VII.
-Discussion} outlining these possibilities.
-As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
-Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data and the Shannon information entropy signature and uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
-Topological feature engineering and lattice compression} and \textbf{VI.
-Emergent information entropy wave functions}.
-We have added a paragraph to the section \textbf{I.
-Introduction} emphasizing these new results.
-}
-
-\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
-This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
-We have added a paragraph to the section \textbf{III.
-Numerical experiments} to emphasize the use of this baseline.}
-
-\textcolor{blue}{\citequote{superior_comparable} As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
-Rev.
-Lett.
-120, 066401, where neural networks were trained on wavevector space data in a similar supervised learning task.
-This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
-In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
-Rev.
-Research 2, 023283,  whose theme is model interpretability of single-layer feedforward neural networks trained to recognize phase transitions of some topological condensed matter systems.
-When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
-While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
-
-\textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data-driven approach based on real space should be in the Introduction.
-We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the section \textbf{I.
-Introduction} in the main paper.}
-
-\vspace{0.5cm}
-\emph{I am not sure which crucial problems their algorithm can solve that was not possible before with machine learning.
-Furthermore, along with the emerging research of unsupervised learning methods in realizing the topological phases, \textbf{why should the supervised learning method be focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript, where I do not see the proposal's advantages, I would prefer the \textbf{unsupervised approaches that could grasp information from a given system without knowing their phases}\genquote{unsupervised_approaches}.
-In my opinion, a proper intrinsic route for understanding physical systems without much information on
-the dynamics of the system will lead to significant future developments and a better understanding of physic systems.}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
-We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of information entropy as loss function provides a clear way to measure feature importance.
-This is compounded by the fact that information entropy plays a very important role in information theory and physics, as is evidenced in the new section \textbf{VI.
-Emergent information entropy wave functions} added to this new version of the article.}
-
-\textcolor{blue}{\citequote{unsupervised_approaches} The new section \textbf{V.
-Topological feature engineering and lattice compression} shows how unsupervised learning can be performed with eigenvector ensembling using tree based methods as learning algorithms.
-In fact, two of the main tasks under the broad umbrella of unsupervised learning are exactly those: dimensionality reduction and feature engineering.
-Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{VII.
-Discussion}.
-Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used as a powerful dimensionality reduction tool in other, unrelated data-driven or numerical physics tasks, which by itself is another example of unsupervised learning and can serve as a preprocessing step to further applications of machine learning to physics.}
-
-\vspace{0.5cm}
-\emph{The details of \textbf{the eigenvector ensembling algorithm should be addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material.
-What is the specific algorithm used in the paper to train on eigenvectors?
-I think it is important even if the readers are not familiar with some ML techniques.
-Some readers in physics may find it difficult to understand some ML technical terms such as bootstrapping, training and validation, test sets, etc.
-In addition, \textbf{I expect proof of what "physics" their method captures and why the eigenvector can play an important role in characterizing the topological phase}\genquote{eigenvector_physics}.
-If this physical interpretability is not mentioned, it is very difficult to see the contribution of the method in physics.}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  The section \textbf{II.
-The eigenvector ensembling algorithm} has been moved from the Supplementary Material to the main paper.
-The issue of specifying the particular learning algorithms used to train on eigenvectors is addressed in the subsections for each SSH experiment (see subsections \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees} and \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}).
-In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module used to run the numerical experiments in the paper.}
-
-\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{II.
-The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
-Therefore, by expressing a data set of eigenvectors on a suitable choice of basis (which in this paper is the real space basis), we are able to investigate properties of a family of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
-Thus the use of eigenvectors greatly facilitates the exploration of model explainability techniques in data-driven physics applications while at the same time not leading to a loss of information from the systems being investigated.
-As to the physics being captured by our procedure, see the answer to the issue \citequote{physical_insights}.}
-
-%While there may surely be other ways to achieve a similar result, using eigenvectors as input data is fairly straightforward and, as we have %demonstrated, as we have demonstrated tage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian %encode all the physical information of the particular system in terms of local components in real space.
-In fact, the use of eigenvectors %play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
-In the majority of %the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses %track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
-The paper paves the way for new theoretical %investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
-%In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy %signature and its corresponding entropic uncertainty relation for topological phase transitions in SSH systems.
-}
-
-\vspace{0.5cm}
-\emph{The authors made efforts to analyze how the algorithm was able to recover the Hamiltonians' global property in the "Information Entropy
-Signatures" section. The authors state that learning topological phases from local real-space data in bulk is still possible even for
-small subsets of lattice sites, then refer us to the section "Learning topological phases from real space data" in the Supplementary
-Material.
-The authors mention on page 4 of the Supplementary Material that \textbf{"key topological information can be said to be localized on a few lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
-However, \textbf{I fail to understand the physical insights behind it}\genquote{physical_insights}.
-Without the proper explanation, it is difficult to see the effectiveness of
-their method or verify the method with a more complex model instead of the simple SSH form.}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
-We have therefore moved it to the final patragraph of the section \textbf{V.
-Topological feature engineering and lattice compression} in the main text.}
-
-\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), iii) generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
-Topological feature engineering and lattice compression},  and finally iv) interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
-Emergent information entropy wave functions}, in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinite lattice.}
-
-\textcolor{blue}{It is noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
-Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{VI.
-Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
-
-\subsection*{Minor}
-
-\emph{The authors state in the abstract that "model explainability in machine learning can advance the research of exotic quantum materials
-with properties that may power future technological applications such as qubit engineering for quantum computing." \textbf{Could you explain a bit more about properties that may power future quantum computing?}\genquote{quantum_comp}}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
-
-\vspace{0.5cm}
-\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single iterations of experiments 1 and 2 as seen from parameter space".
-\textbf{What are the experiments 1 and 2?}\genquote{experiments_1_2}}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
-The designation "experiment 1" is used to abbreviate the subsection \textbf{III.A Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
-Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{III.B Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.}
-
-\vspace{0.5cm}
-\emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
-such as "the accuracy" and "the probability heatmap," "eigenvector accuracy," and "Hamiltonian accuracy."}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{III.
-Numerical experiments}.
-Furthermore, the new section \textbf{V.
-Topological feature engineering and lattice compression} contains a summary of accuracy scores obtained in all numerical experiments performed in the paper.}
-
-\vspace{0.5cm}
-\emph{I prefer to \textbf{put the definition of information entropy signatures in the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
-
-\vspace{0.25cm}
-\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{VI.
-Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\pagebreak
-
 \nocite{*}
@@
 The data-driven approach described in this article addresses these issues.
-In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems} \citequote{motif_real_space}
+In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems} %\citequote{motif_real_space}
 
@@
 These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
-This allows us to establish the Bialynicki-Birula-Mycielski inequality as an uncertainty principle for the localizability of Shannon information entropy in topological phase transitions.}  \citequote{eigenvector_physics}, \citequote{physical_insights}
-
-The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.\citequote{pipeline_not_work}
-
-\textcolor{blue}{As of yet model explainability\cite{https://ieeexplore.ieee.org/abstract/document/8631448?casa_token=ENOe4-VIc7kAAAAA:Tp8Aatj9Rx-9UcbOXtLbqNhG33nAt7_LEb-pG4-NC6wnQacmyRn0NqF4rrs2JGIDjgUgCNDLJaY, https://ieeexplore.ieee.org/abstract/document/8400040, https://ieeexplore.ieee.org/abstract/document/9007737} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines (this is also emphasized in \cite{https://arxiv.org/abs/1912.10057}).
+This allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of Shannon information entropy in topological phase transitions.}  %\citequote{eigenvector_physics}, \citequote{physical_insights}
+
+The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+
+\textcolor{blue}{As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
 This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were already known.
 By proposing new concepts from the analysis of data from physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
-}\citequote{pipeline_not_work}
+}%\citequote{pipeline_not_work}
 \begin{figure}
@@
 
-\section{The eigenvector ensembling algorithm}\citequote{eigenvector_ensembling_alg}
+\section{The eigenvector ensembling algorithm}%\citequote{eigenvector_ensembling_alg}
 \label{the_eigenvector_ensembling_algorithm}
@@
 These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
+Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}%\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
 
@@
 
-\textbf{blue}{The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit}.}
+\textcolor{blue}{The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module.} %\cite{scikit}
 
@@
 The composition of the test set was \fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% of Hamiltonians with winding number $W$ = 0 and \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
+\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.%\citequote{eigenvector_ensembling_alg}
 
@@
 These were \fpeval{round(\sshOneHamTrainAcc,\accPrec)} for training Hamiltonians, \fpeval{round(\sshOneHamValAcc,\accPrec)} for validation Hamiltonians and \fpeval{round(\sshOneHamTestAcc,\accPrec)}  for test Hamiltonians.
-\textcolor{blue}{When compared with the baseline test accuracy of \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)} of a system that predicts the whole test set as having winding number $W=1$, the accuracy of \fpeval{round(\sshOneHamTestAcc,\accPrec)} on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} \citequote{sufficient_accuracy}
+\textcolor{blue}{When compared with the baseline test accuracy of \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)} of a system that predicts the whole test set as having winding number $W=1$, the accuracy of \fpeval{round(\sshOneHamTestAcc,\accPrec)} on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} %\citequote{sufficient_accuracy}
 
@@
 \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
+\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
+\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
@@
 \centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim.png}}
 \caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
@@
 \centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim.png}}
+\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim.png}}
 \caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
@@
 
-\section{Topological feature engineering and lattice compression}
-\label{topological_feature_engineering}
-
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from an information-theoretic perspective, in particular as related to data compression.
-As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
-Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
-Here we show how the symmetries in the real space information entropy signatures in figure \ref{feature_importances} can be exploited to engineer new global topological features, leading to an effective compression of topological information.
-
-%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
-
-%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
-
-Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
-\begin{equation}
-\label{discrete_fourier_transform}
-\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
-\end{equation}
-Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
-The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
-\begin{equation}
-\label{hermitian_symmetry}
-\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
-\end{equation}
-where  we have used the notation $\overline{k} = k \mod N$.
-
-Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
-In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
-This leads us to the Discrete Cosine Transform (DCT) topological features,
-\begin{equation}
-\label{DCT}
-\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
-\end{equation}
-where $M = \frac{N}{2}+1$.
-The second path capitalizes on the fact that de imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
-\begin{equation}
-\label{DST}
-\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
-\end{equation} 
-where $M = \frac{N}{2}-1$.
-
-The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
-the sites $0 \leq j \leq \frac{N}{2}$.
-This is due to the fact that each equation assumes that the real space eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
-While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
-Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
-
-The topological feature engineering strategies described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
-As equations \eqref{DCT} and \eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
-
-We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
-The accuracy scores obtained in each experiment are listed in table \ref{numerical_results}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
-
-The lattice compression strategies tested in this work were: i) learning topological phases from only a subset of the real space lattice sites; ii) learning topological phases from the DCT or DST engineered features of equations; iii) learning topologcal phases from a fraction of the DCT or DST topological features and iv) learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
-
-In strategy \emph{i)} the lattice sites used in the SSH1 and SSH2 systems were
-\begin{equation}
-\label{lattice_subsets}
-\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
-\end{equation}
-Note that for the nearest-neighbor SSH system $\mathcal{S}_1$ correspond to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{numerical results}, the features used in strategy \emph{i)} are referred to as $X_{\mathcal{S}_1}$ and $X_{\mathcal{S}_2}$, according to the SSH system they relate to.
-
-In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
-These features are denoted in table \ref{numerical_results} by $\hat{X}^c_1$, $\hat{X}^s_1$, $\hat{X}^c_2$, $\hat{X}^s_2$ according to which set of topological features and SSH systems they refer to.
-
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH1 and SSH2 systems,
-\begin{equation}
-\label{DCT_subsets}
-\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
-\end{equation}
-and the DST topological features,
-\begin{equation}
-\label{DST_subsets}
-\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
-\end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{O}_2}$ according to the topological features and wavevector sites used with each SSH system.
-
-The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
-It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
-Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
-Mathematically, we can expess the topological features used in strategy \emph{iv)} as follows:
-\begin{equation}
-\label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \mathbbm{1}_{\mathcal{S}}[0]x[0] + (-1)^n\mathbbm{1}_{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
-\end{equation}
-\begin{equation}
-\label{DST_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}.
-\end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, i.e.
-$\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
-The features engineered in strategy \emph{iv)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH system, type of topological features used as well as which features in real and wavevector space were used to engineer them.
-
-The results shown in table \ref{numerical_results} carry some important surprises.
-For example, the topological phase transition boundaries of SSH-1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores in the .
-The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ produce accuracy scores at near the same level as using the whole lattice.
-
-Even more striking is the performance achieved by the DCT topological features $\hat{X}^c_{\mathcal{S},\mathcal{E}}$ defined in equation \eqref{DCT_very_compressed}.
-For SSH-1 systems, they perform on par with using the full set of real space features $X_1$, while for SSH-2 systems a small loss in accuracy is incurred.
-
-Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features versus DST topological features.
-The latter seems to have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features $\hat{X}^s_{\mathcal{S},\mathcal{O}}$ in both SSH-1 and SSH-2 systems.
-This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
-
-The accuracy scores obtained with the real space features $X_{\mathcal{S}_\alpha}$ and the DCT topological features $\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.}\citequote{key_top} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
-
-%\newcommand\SSHSys{\thead{SSH systems}}
-%\newcommand\Feat{\thead{Features}}
-%\newcommand\ValEig{\thead{Val. eigenvectors}}
-%\newcommand\TestEig{\thead{Test eigenvectors}}
-%\newcommand\ValHam{\thead{Val. Hamiltonians}}
-%\newcommand\TestHam{\thead{Test Hamiltonians}}
-
 \begin{table}
-\label{numerical_results}
 \begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
@@
 \end{tabular}
-\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.
-The features used to train the decision trees (SSH-1) or random forests (SSH-2) in the numerical experiments with SSH-$\alpha$ systems were as follows.
+\caption{\label{accuracy_scores}Accuracy scores of numerical experiments.
+The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH-$\alpha$ systems were as follows.
 Real space features: all real space lattice sites ($X_\alpha$) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ ($X_{\mathcal{S}_{\alpha}}$) (equation \eqref{lattice_subsets}).
@@
 
+\section{Topological feature engineering and lattice compression}
+\label{topological_feature_engineering}
+
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from an information-theoretic perspective, in particular as related to data compression.
+As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
+Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
+Here we show how the symmetries in the real space information entropy signatures in figure \ref{feature_importances} can be exploited to engineer new global topological features, leading to an effective compression of topological information.
+
+%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
+Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
+
+%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
+
+Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
+\begin{equation}
+\label{discrete_fourier_transform}
+\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
+\end{equation}
+Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
+The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
+\begin{equation}
+\label{hermitian_symmetry}
+\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
+\end{equation}
+where  we have used the notation $\overline{k} = k \mod N$.
+
+Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
+In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
+This leads us to the Discrete Cosine Transform (DCT) topological features,
+\begin{equation}
+\label{DCT}
+\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
+\end{equation}
+where $M = \frac{N}{2}+1$.
+The second path capitalizes on the fact that de imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
+\begin{equation}
+\label{DST}
+\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
+\end{equation} 
+where $M = \frac{N}{2}-1$.
+
+The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
+the sites $0 \leq j \leq \frac{N}{2}$.
+This is due to the fact that each equation assumes that the real space eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
+While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
+Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
+
+The topological feature engineering strategies described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
+As equations \eqref{DCT} and \eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
+
+We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
+The accuracy scores obtained in each experiment are listed in table \ref{accuracy_scores}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
+
+The lattice compression strategies tested in this work were: i) learning topological phases from only a subset of the real space lattice sites; ii) learning topological phases from the DCT or DST engineered features of equations; iii) learning topologcal phases from a fraction of the DCT or DST topological features and iv) learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
+
+In strategy \emph{i)} the lattice sites used in the SSH1 and SSH2 systems were
+\begin{equation}
+\label{lattice_subsets}
+\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
+\end{equation}
+Note that for the nearest-neighbor SSH system $\mathcal{S}_1$ correspond to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
+Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
+In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as $X_{\mathcal{S}_1}$ and $X_{\mathcal{S}_2}$, according to the SSH system they relate to.
+
+In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
+These features are denoted in table \ref{accuracy_scores} by $\hat{X}^c_1$, $\hat{X}^s_1$, $\hat{X}^c_2$, $\hat{X}^s_2$ according to which set of topological features and SSH systems they refer to.
+
+Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH1 and SSH2 systems,
+\begin{equation}
+\label{DCT_subsets}
+\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
+\end{equation}
+and the DST topological features,
+\begin{equation}
+\label{DST_subsets}
+\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
+\end{equation}
+The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by $\hat{X}^c_{\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{O}_2}$ according to the topological features and wavevector sites used with each SSH system.
+
+The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
+It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
+Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
+Mathematically, we can expess the topological features used in strategy \emph{iv)} as follows:
+\begin{equation}
+\label{DCT_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \mathbbm{1}_{\mathcal{S}}[0]x[0] + (-1)^n\mathbbm{1}_{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
+\end{equation}
+\begin{equation}
+\label{DST_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}.
+\end{equation}
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, i.e.
+$\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
+The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH system, type of topological features used as well as which features in real and wavevector space were used to engineer them.
+
+The results shown in table \ref{accuracy_scores} carry some important surprises.
+For example, the topological phase transition boundaries of SSH-1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores in the .
+The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ produce accuracy scores at near the same level as using the whole lattice.
+
+Even more striking is the performance achieved by the DCT topological features $\hat{X}^c_{\mathcal{S},\mathcal{E}}$ defined in equation \eqref{DCT_very_compressed}.
+For SSH-1 systems, they perform on par with using the full set of real space features $X_1$, while for SSH-2 systems a small loss in accuracy is incurred.
+
+Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features versus DST topological features.
+The latter seems to have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features $\hat{X}^s_{\mathcal{S},\mathcal{O}}$ in both SSH-1 and SSH-2 systems.
+This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
+
+The accuracy scores obtained with the real space features $X_{\mathcal{S}_\alpha}$ and the DCT topological features $\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
+\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+
+%\newcommand\SSHSys{\thead{SSH systems}}
+%\newcommand\Feat{\thead{Features}}
+%\newcommand\ValEig{\thead{Val. eigenvectors}}
+%\newcommand\TestEig{\thead{Test eigenvectors}}
+%\newcommand\ValHam{\thead{Val. Hamiltonians}}
+%\newcommand\TestHam{\thead{Test Hamiltonians}}
+
 \textcolor{blue}{
@@
 \textcolor{blue}{The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}\citequote{superior_comparable}
-
-\textcolor{blue}{This paper should also be contrasted with \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
-In \cite{ml_interpretability}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
+This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}%\citequote{superior_comparable}
+
+\textcolor{blue}{This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
+In \cite{zhang2020interpreting}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
 We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
 In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}\citequote{superior_comparable}
+While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}%\citequote{superior_comparable}
 
@@
 The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.}\citequote{pipeline_not_work}  We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.} We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
 
@@
 This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}\citequote{unsupervised_learning}
+Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}
 
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
+\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances.png}}\quad
+\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances.png}}\quad
 \caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
@@
 
-\citequote{motif_real_space}
-
 %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{56}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Hasan}\ and\ \citenamefont
-  {Kane}(2010)}]{RevModPhys.82.3045}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
-  {Hasan}}\ and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
-  {Kane}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {3045}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Continentino}(2017)}]{CONTINENTINO2017A1}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physica B: Condensed Matter}\ }\textbf {\bibinfo {volume} {505}},\ \bibinfo
-  {pages} {A1 } (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Puel}\ \emph {et~al.}(2017)\citenamefont {Puel},
-  \citenamefont {Sacramento},\ and\ \citenamefont
-  {Continentino}}]{PhysRevB.95.094509}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~O.}\ \bibnamefont
-  {Puel}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
-  {Sacramento}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {094509}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Griffith}\ and\ \citenamefont
-  {Continentino}(2018)}]{PhysRevE.97.012107}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Griffith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {012107}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ryu}\ \emph {et~al.}(2010)\citenamefont {Ryu},
-  \citenamefont {Schnyder}, \citenamefont {Furusaki},\ and\ \citenamefont
-  {Ludwig}}]{ryu2010topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Ryu}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont {Schnyder}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Furusaki}}, \ and\
-  \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont {Ludwig}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {New Journal of
-  Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {065010}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Atala}\ \emph {et~al.}(2013)\citenamefont {Atala},
-  \citenamefont {Aidelsburger}, \citenamefont {Barreiro}, \citenamefont
-  {Abanin}, \citenamefont {Kitagawa}, \citenamefont {Demler},\ and\
-  \citenamefont {Bloch}}]{atala2013direct}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Atala}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Aidelsburger}},
-  \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont {Barreiro}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Abanin}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Kitagawa}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Bloch}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {9}},\ \bibinfo {pages} {795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stuhl}\ \emph {et~al.}(2015)\citenamefont {Stuhl},
-  \citenamefont {Lu}, \citenamefont {Aycock}, \citenamefont {Genkina},\ and\
-  \citenamefont {Spielman}}]{Stuhl1514}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~K.}\ \bibnamefont
-  {Stuhl}}, \bibinfo {author} {\bibfnamefont {H.-I.}\ \bibnamefont {Lu}},
-  \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont {Aycock}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Genkina}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {I.~B.}\ \bibnamefont {Spielman}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {349}},\ \bibinfo {pages} {1514} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Leder}\ \emph {et~al.}(2016)\citenamefont {Leder},
-  \citenamefont {Grossert}, \citenamefont {Sitta}, \citenamefont {Genske},
-  \citenamefont {Rosch},\ and\ \citenamefont {Weitz}}]{leder2016real}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Leder}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Grossert}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sitta}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Genske}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Rosch}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {13112} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goldman}\ \emph {et~al.}(2016)\citenamefont
-  {Goldman}, \citenamefont {Budich},\ and\ \citenamefont
-  {Zoller}}]{goldman2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Goldman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Budich}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
-  }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {639} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Meier}\ \emph {et~al.}(2016)\citenamefont {Meier},
-  \citenamefont {An},\ and\ \citenamefont {Gadway}}]{meier2016observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
-  {Meier}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {An}}, \
-  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  communications}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {13986}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hafezi}\ \emph {et~al.}(2013)\citenamefont {Hafezi},
-  \citenamefont {Mittal}, \citenamefont {Fan}, \citenamefont {Migdall},\ and\
-  \citenamefont {Taylor}}]{hafezi2013imaging}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hafezi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mittal}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Fan}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Migdall}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Taylor}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Photonics}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {1001} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Lu}\ \emph {et~al.}(2016)\citenamefont {Lu},
-  \citenamefont {Joannopoulos},\ and\ \citenamefont
-  {Solja{\v{c}}i{\'c}}}]{lu2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Lu}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
-  {Joannopoulos}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Solja{\v{c}}i{\'c}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-  {pages} {626} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Peano}\ \emph {et~al.}(2015)\citenamefont {Peano},
-  \citenamefont {Brendel}, \citenamefont {Schmidt},\ and\ \citenamefont
-  {Marquardt}}]{PhysRevX.5.031011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Peano}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Brendel}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Schmidt}}, \ and\
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marquardt}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {5}},\ \bibinfo {pages} {031011} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2012)\citenamefont
-  {Kitagawa}, \citenamefont {Broome}, \citenamefont {Fedrizzi}, \citenamefont
-  {Rudner}, \citenamefont {Berg}, \citenamefont {Kassal}, \citenamefont
-  {Aspuru-Guzik}, \citenamefont {Demler},\ and\ \citenamefont
-  {White}}]{kitagawa2012observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Broome}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Fedrizzi}},
-  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Kassal}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~G.}\
-  \bibnamefont {White}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature communications}\ }\textbf {\bibinfo {volume} {3}},\
-  \bibinfo {pages} {882} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cardano}\ \emph {et~al.}(2016)\citenamefont
-  {Cardano}, \citenamefont {Maffei}, \citenamefont {Massa}, \citenamefont
-  {Piccirillo}, \citenamefont {De~Lisio}, \citenamefont {De~Filippis},
-  \citenamefont {Cataudella}, \citenamefont {Santamato},\ and\ \citenamefont
-  {Marrucci}}]{cardano2016statistical}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Cardano}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maffei}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Massa}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Piccirillo}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {De~Lisio}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {De~Filippis}}, \bibinfo {author}
-  {\bibfnamefont {V.}~\bibnamefont {Cataudella}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Santamato}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {Marrucci}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {11439} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Flurin}\ \emph {et~al.}(2017)\citenamefont {Flurin},
-  \citenamefont {Ramasesh}, \citenamefont {Hacohen-Gourgy}, \citenamefont
-  {Martin}, \citenamefont {Yao},\ and\ \citenamefont
-  {Siddiqi}}]{PhysRevX.7.031023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Flurin}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
-  {Ramasesh}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Hacohen-Gourgy}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
-  {Martin}}, \bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont {Yao}}, \
-  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Siddiqi}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {031023} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Soluyanov}\ \emph {et~al.}(2015)\citenamefont
-  {Soluyanov}, \citenamefont {Gresch}, \citenamefont {Wang}, \citenamefont
-  {Wu}, \citenamefont {Troyer}, \citenamefont {Dai},\ and\ \citenamefont
-  {Bernevig}}]{soluyanov2015type}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-  {Soluyanov}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gresch}},
-  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {Q.}~\bibnamefont {Wu}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Troyer}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \ and\ \bibinfo {author} {\bibfnamefont {B.~A.}\
-  \bibnamefont {Bernevig}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {527}},\ \bibinfo {pages}
-  {495} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lv}\ \emph {et~al.}(2015)\citenamefont {Lv},
-  \citenamefont {Weng}, \citenamefont {Fu}, \citenamefont {Wang}, \citenamefont
-  {Miao}, \citenamefont {Ma}, \citenamefont {Richard}, \citenamefont {Huang},
-  \citenamefont {Zhao}, \citenamefont {Chen}, \citenamefont {Fang},
-  \citenamefont {Dai}, \citenamefont {Qian},\ and\ \citenamefont
-  {Ding}}]{PhysRevX.5.031013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~Q.}\ \bibnamefont
-  {Lv}}, \bibinfo {author} {\bibfnamefont {H.~M.}\ \bibnamefont {Weng}},
-  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Fu}}, \bibinfo
-  {author} {\bibfnamefont {X.~P.}\ \bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Miao}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ma}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Richard}}, \bibinfo {author} {\bibfnamefont {X.~C.}\ \bibnamefont {Huang}},
-  \bibinfo {author} {\bibfnamefont {L.~X.}\ \bibnamefont {Zhao}}, \bibinfo
-  {author} {\bibfnamefont {G.~F.}\ \bibnamefont {Chen}}, \bibinfo {author}
-  {\bibfnamefont {Z.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Qian}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {031013} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Su}\ \emph {et~al.}(1979)\citenamefont {Su},
-  \citenamefont {Schrieffer},\ and\ \citenamefont
-  {Heeger}}]{PhysRevLett.42.1698}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~P.}\ \bibnamefont
-  {Su}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Schrieffer}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Heeger}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1698} (\bibinfo {year}
-  {1979})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},
-  \citenamefont {Dauphin}, \citenamefont {Cardano}, \citenamefont
-  {Lewenstein},\ and\ \citenamefont {Massignan}}]{maffei2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Maffei}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Cardano}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Massignan}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
-  {\bibinfo {volume} {20}},\ \bibinfo {pages} {013023} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heeger}(2001)}]{RevModPhys.73.681}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Heeger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {681}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kane}\ and\ \citenamefont
-  {Lubensky}(2014)}]{kane2014topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Kane}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lubensky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {39}
-  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
-  \citenamefont {Upadhyaya},\ and\ \citenamefont {Vitelli}}]{Chen13004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.-g.}\
-  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Upadhyaya}}, \ and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Vitelli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
-  {volume} {111}},\ \bibinfo {pages} {13004} (\bibinfo {year}
-  {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carrasquilla}\ and\ \citenamefont
-  {Melko}(2017)}]{carrasquilla2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}\ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {431}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ch'ng}\ \emph {et~al.}(2017)\citenamefont {Ch'ng},
-  \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\ \citenamefont
-  {Khatami}}]{PhysRevX.7.031038}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ch'ng}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Carrasquilla}},
-  \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \ and\
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Khatami}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {7}},\ \bibinfo {pages} {031038} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wang}(2016)}]{PhysRevB.94.195105}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wang}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {195105}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Broecker}\ \emph {et~al.}(2017)\citenamefont
-  {Broecker}, \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\
-  \citenamefont {Trebst}}]{broecker2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Broecker}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}}, \ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Trebst}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Scientific reports}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
-  {8823} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Van~Nieuwenburg}\ \emph {et~al.}(2017)\citenamefont
-  {Van~Nieuwenburg}, \citenamefont {Liu},\ and\ \citenamefont
-  {Huber}}]{van2017learning}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
-  {Van~Nieuwenburg}}, \bibinfo {author} {\bibfnamefont {Y.-H.}\ \bibnamefont
-  {Liu}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
-  {Huber}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {435}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2018)\citenamefont {Zhang},
-  \citenamefont {Shen},\ and\ \citenamefont {Zhai}}]{PhysRevLett.120.066401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {120}},\ \bibinfo {pages} {066401} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
-  \citenamefont {Yi}, \citenamefont {Zhang}, \citenamefont {Shen},\ and\
-  \citenamefont {Zhai}}]{PhysRevB.98.085402}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Yi}}, \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Zhang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {98}},\ \bibinfo {pages} {085402} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Suchsland}\ and\ \citenamefont
-  {Wessel}(2018)}]{PhysRevB.97.174435}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Suchsland}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Wessel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {174435}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont
-  {Kim}(2017)}]{PhysRevLett.118.216401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont
-  {Kim}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. Lett.}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {216401}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Venderley}\ \emph {et~al.}(2018)\citenamefont
-  {Venderley}, \citenamefont {Khemani},\ and\ \citenamefont
-  {Kim}}]{PhysRevLett.120.257204}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Venderley}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Khemani}},
-  \ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {120}},\ \bibinfo {pages} {257204} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ohtsuki}\ and\ \citenamefont
-  {Ohtsuki}(2017)}]{ohtsuki2017deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo {volume}
-  {86}},\ \bibinfo {pages} {044708} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Yoshioka}\ \emph {et~al.}(2018)\citenamefont
-  {Yoshioka}, \citenamefont {Akagi},\ and\ \citenamefont
-  {Katsura}}]{PhysRevB.97.205110}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Yoshioka}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Akagi}}, \
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Katsura}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {205110} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2017)\citenamefont {Deng},
-  \citenamefont {Li},\ and\ \citenamefont {Das~Sarma}}]{PhysRevB.96.195145}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.-L.}\ \bibnamefont
-  {Deng}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}}, \ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf
-  {\bibinfo {volume} {96}},\ \bibinfo {pages} {195145} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huembeli}\ \emph {et~al.}(2018)\citenamefont
-  {Huembeli}, \citenamefont {Dauphin},\ and\ \citenamefont
-  {Wittek}}]{PhysRevB.97.134109}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Huembeli}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wittek}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {134109} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carvalho}\ \emph {et~al.}(2018)\citenamefont
-  {Carvalho}, \citenamefont {Garc\'{\i}a-Mart\'{\i}nez}, \citenamefont {Lado},\
-  and\ \citenamefont {Fern\'andez-Rossier}}]{PhysRevB.97.115453}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Carvalho}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
-  {Garc\'{\i}a-Mart\'{\i}nez}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
-  \bibnamefont {Lado}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Fern\'andez-Rossier}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {97}},\ \bibinfo {pages} {115453} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2017)\citenamefont {Zhang},
-  \citenamefont {Melko},\ and\ \citenamefont {Kim}}]{PhysRevB.96.245119}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \
-  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {245119} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rodriguez-Nieva}\ and\ \citenamefont
-  {Scheurer}(2018)}]{rodriguez2018identifying}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
-  {Rodriguez-Nieva}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\
-  \bibnamefont {Scheurer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {arXiv preprint arXiv:1805.05961}\ } (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
-  {Breiman}, \citenamefont {Friedman}, \citenamefont {Stone},\ and\
-  \citenamefont {Olshen}}]{breiman2017classification}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},
-  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Stone}}, \ and\
-  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Olshen}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Classification and regression
-  trees}}}\ (\bibinfo  {publisher} {Chapman and Hall/CRC, London, UK},\
-  \bibinfo {year} {1984})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}(2001)}]{Breiman2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Machine Learning}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {5}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
-  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
-  {Tibshirani}}]{friedman2001elements}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
-  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
-  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
-  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
-  {year} {2001})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
-  {Resta}(2011)}]{PhysRevB.84.241106}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Bianco}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Resta}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {241106} (\bibinfo
-  {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Caio}\ \emph {et~al.}(2019)\citenamefont {Caio},
-  \citenamefont {M{\"o}ller}, \citenamefont {Cooper},\ and\ \citenamefont
-  {Bhaseen}}]{caio2019topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
-  {Caio}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {M{\"o}ller}},
-  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Cooper}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bhaseen}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ ,\ \bibinfo
-  {pages} {1}} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carlsson}(2009)}]{carlsson2009topology}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Carlsson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Bulletin of the American Mathematical Society}\ }\textbf {\bibinfo {volume}
-  {46}},\ \bibinfo {pages} {255} (\bibinfo {year} {2009})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wasserman}(2018)}]{wasserman2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wasserman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Annual Review of Statistics and Its Application}\ }\textbf {\bibinfo
-  {volume} {5}},\ \bibinfo {pages} {501} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2005)\citenamefont {Wang},
-  \citenamefont {Zhang},\ and\ \citenamefont {Zha}}]{wang2005adaptive}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\ }in\ \href@noop
-  {} {\emph {\bibinfo {booktitle} {Advances in neural information processing
-  systems}}}\ (\bibinfo {year} {2005})\ pp.\ \bibinfo {pages}
-  {1473--1480}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lin}\ and\ \citenamefont
-  {Zha}(2008)}]{lin2008riemannian}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lin}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Transactions
-  on Pattern Analysis and Machine Intelligence}\ }\textbf {\bibinfo {volume}
-  {30}},\ \bibinfo {pages} {796} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Belkin}(2003)}]{belkin2003problems}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Belkin}},\ }\href@noop {} {\emph {\bibinfo {title} {Problems of learning on
-  manifolds}}}\ (\bibinfo  {publisher} {The University of Chicago, Chicago, IL,
-  USA},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
-  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
-  {P{\'a}lyi}}]{asboth2016short}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
-  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}} (\bibinfo
-  {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
-  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
-  {Courville}}]{goodfellow2016deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
-  {publisher} {MIT press, Cambridge, MA, USA},\ \bibinfo {year}
-  {2016})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
-  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
-  machine learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\
-  \bibinfo {year} {2006})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
-  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
-  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
-  {Mitter}(2010)}]{narayanan2010sample}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
-  Neural Information Processing Systems}}}\ (\bibinfo {year} {2010})\ pp.\
-  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
-  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
-  and\ \citenamefont {Muller}}]{rifai2011manifold}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
-  {\bibinfo {booktitle} {Advances in Neural Information Processing Systems}}}\
-  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
-  {NoStop}%
-\end{thebibliography}%
+
+\bibliography{bibl}{}
 

### 2020-07-22 07_paper/article.tex
First alpha. Will now edit figures of information entropy signatures

@@
 %\end{document}
-
+\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
 %%%%%% Numerical experiments parameters
@@
 %\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
-\newcommand\SSHSys{SSH systems}         
+\newcommand\SSHSys{SSH system}         
 \newcommand\Feat{Features}              
@@
 %%%%%%%%%%%%%%% ssh1 experiments
+%%% data statistics
 \newcommand\sshOneTrainNHam{556}
+\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
 \newcommand\sshOneValNHam{5000}
+\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
 \newcommand\sshOneTestNHam{1005}
-\newcommand\sshOneTrainValWindZeroNHam{2822} %number of winding = 0 in train+val set
-\newcommand\sshOneTrainValWindOneNHam{2734}  %number of winding = 1 in train+val set
+\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
+\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
+\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
 \newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
 \newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
+\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
+\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
 %%% real space accuracies
-\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
-\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
-\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
-\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
-\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
-\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
+%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
+%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
+%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
+%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
+%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
+%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
+%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
+
+%%% ssh1 baseline accuracy
+\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
 %%% x1 features table entries 
@@
 \newcommand\sshTwoTrainNHam{2761}
+\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
 \newcommand\sshTwoValNHam{2760}
+\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
 \newcommand\sshTwoTestNHam{1040}
+\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}
 
-\newcommand\sshTwoTrainValWindMinusOneNHam{988} %number of winding = -1 in train+val set
-\newcommand\sshTwoTrainValWindZeroNHam{1795} %number of winding = 0 in train+val set
-\newcommand\sshTwoTrainValWindOneNHam{1781}  %number of winding = 1 in train+val set
-\newcommand\sshTwoTrainValWindTwoNHam{957}   %number of winding = 2 in train+val set
+\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
+\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
+\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
+\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
+\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
 
@@
 \newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
+\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
 
@@
 
+%%% ssh2 baseline accuracy
+\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
 %%% x2 features table entries 
@@
 \newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
+
 %%% x_S2 features table entries  
@@
 \newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
-%%% x^cO_2 features table entries  
-\newcommand\xcOTwo{$\hat{X}^c_{\mathcal{O}_2}$}
-\newcommand\xcOTwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
-\newcommand\xcOTwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
-\newcommand\xcOTwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
-\newcommand\xcOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcOTwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
-\newcommand\xcOTwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
+%%% x^cE_2 features table entries  
+\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
+\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
+\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
+\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
+\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
+\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
 
-%%% x^cSO_2 features table entries  
-\newcommand\xcSOTwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{O}_2}$}
-\newcommand\xcSOTwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
-\newcommand\xcSOTwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
-\newcommand\xcSOTwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
-\newcommand\xcSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcSOTwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
-\newcommand\xcSOTwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
+%%% x^cSE_2 features table entries  
+\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
+\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
+\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
+\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
+\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
+\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
 %%% x^s_2 features table entries  
@@
 \newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
+
+%%% more feature commands
+%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
+%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}
+
+\newcommand\xalpha{$X_\alpha$}
+\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
+
+\newcommand\xcalpha{$\hat{X}^c_\alpha$}
+\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
+\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
+
+\newcommand\xsalpha{$\hat{X}^s_\alpha$}
+\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
+\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
 
@@
 
-\textcolor{blue}{The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
 disordered systems in condensed matter) do not have.
@@
 The data-driven approach described in this article addresses these issues.
-In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems} %\citequote{motif_real_space}
-
-%We develop here an alternative data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
-%\citequote{motif_real_space}
+In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
 
@@
 The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
+We describe the algorithm in detail in section \ref{the_eigenvector_ensembling_algorithm} and demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
+This is performed in section \ref{numerical_experiments}.
 
@@
 To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
+These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}
 
-\textcolor{blue}{The topological signals recovered from the analysis of real space eigenvector data are then further theoretically explored as information entropy mass functions along the lattices in real space.
-By computing their Fourier transform, we retrieve similar information entropy mass functions in wavevector space.
-These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
-This allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of Shannon information entropy in topological phase transitions.}  %\citequote{eigenvector_physics}, \citequote{physical_insights}
+In possession of the information entropy signatures, we demonstrate how the symmetries in real and wavevector space eigenvectors can be manipulated with signal processing tools commonly employed in audio and image processing to execute two standard unsupervised learning tasks, namely dimensionality reduction and feature engineering.
+The topological features resulting from this analysis, here denominated DCT and DST topological features, are discussed in section \ref{topological_feature_engineering}.
 
-The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The information entropy signatures are finally explored as theoretical constructs in terms of information entropy mass functions along the lattices.
+By taking their continuum limit and admitting that they are quantum in nature, we show how the information entropy signatures can be naturally understood in terms of emergent information entropy wave functions along the lattices.
+The theoretical formulation of the results obtained with machine learning in terms of emergent quantum mechanical wave functions allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of information entropy in topological phase transitions.
+The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}
 
-\textcolor{blue}{As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
+The  description of information entropy signatures (which were obtained here with machine learning) as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+
+As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
 This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were already known.
-By proposing new concepts from the analysis of data from physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
-}%\citequote{pipeline_not_work}
+By proposing new concepts from the data analysis of physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
 \begin{figure}
@@
 
-\section{The eigenvector ensembling algorithm}%\citequote{eigenvector_ensembling_alg}
+\section{The eigenvector ensembling algorithm}
 \label{the_eigenvector_ensembling_algorithm}
-\textcolor{blue}{
 The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
@@
 The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}}
+\end{enumerate}
 
 \vspace{.3cm}
-\textcolor{blue}{Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
+Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
 The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
-The intuition that eigenvectors can be used in replacement to raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$, }
+The intuition that eigenvectors can be used in replacement to raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
 \begin{equation}
@@
 \end{equation}
-where $\lambda^{(i)}$ \textcolor{blue}{is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
+where $\lambda^{(i)}$ is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
 It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
@@
 the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
-Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.}
-
-%\textcolor{blue}{In step 3) we used the implementations of decision trees and random forests from Python's scikit-learn module}\citequote{eigenvector_ensembling_alg}
+Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.
 
@@
 
-\textcolor{blue}{As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
+As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
 These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}%\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
+Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.
 
@@
 The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
-\textcolor{blue}{Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ experiments.
-The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps}.
+Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ experiments.
+The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps.
 As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
 
-\textcolor{blue}{The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module.} %\cite{scikit}
+The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module.
 
@@
 Our test set in this experiment contained \sshOneTestNHam\ Hamiltonians (approx.
-\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}\% of all data).
-Of the remaining \fpeval{\sshOneTrainNHam+\sshOneValNHam} Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
-\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}\%) and \sshOneValNHam\ (approx.
-\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}\%) were used to compute validation scores at each iteration.
+\sshOneTestFracHam\% of all data).
+Of the remaining \sshOneTrainPlusValNHam\ Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
+\sshOneTrainFracHam\%) and \sshOneValNHam\ (approx.
+\sshOneValFracHam\%) were used to compute validation scores at each iteration.
 These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was \fpeval{round(\sshOneTrainValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}\% of Hamiltonians with winding number $W$ = 0 and \fpeval{round(\sshOneTrainValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}\% with winding number $W$ = 1.
-The composition of the test set was \fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% of Hamiltonians with winding number $W$ = 0 and \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.%\citequote{eigenvector_ensembling_alg}
+The composition of the train + validation set for this experiment was \sshOneTrainPlusValWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTrainPlusValWindOneFracHam\% with winding number $W$ = 1.
+The composition of the test set was \sshOneTestWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTestWindOneFracHam\% with winding number $W=1$.
+Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
 
 The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (\fpeval{round(\sshOneEigenTrainAcc,\accPrec)}), validation eigenvectors (\fpeval{round(\sshOneEigenValAcc,\accPrec)}) and test eigenvectors (\fpeval{round(\sshOneEigenTestAcc,\accPrec)}).
+In particular, we report mean accuracies on training eigenvectors (\xOneEigTrain), validation eigenvectors (\xOneEigVal) and test eigenvectors (\xOneEigTest).
 Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were \fpeval{round(\sshOneHamTrainAcc,\accPrec)} for training Hamiltonians, \fpeval{round(\sshOneHamValAcc,\accPrec)} for validation Hamiltonians and \fpeval{round(\sshOneHamTestAcc,\accPrec)}  for test Hamiltonians.
-\textcolor{blue}{When compared with the baseline test accuracy of \fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)} of a system that predicts the whole test set as having winding number $W=1$, the accuracy of \fpeval{round(\sshOneHamTestAcc,\accPrec)} on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} %\citequote{sufficient_accuracy}
+These were \xOneHamTrain\ for training Hamiltonians, \xOneHamVal\ for validation Hamiltonians and \xOneHamTest\ for test Hamiltonians.
+When compared with the baseline test accuracy of \sshOneHamTestBaseline\ of a system that predicts the whole test set as having winding number $W=1$, the accuracy achieved on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.
 
@@
 For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with \nEst\ decision trees.
-Our data set consisted of \sshTwoTestNHam\ (\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}\%) test Hamiltonians.
-The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}\%) training Hamiltonians and \sshTwoValNHam\ (\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\fpeval{round(\sshTwoTrainValWindMinusOneNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%), $W$ = 0 (\fpeval{round(\sshTwoTrainValWindZeroNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%), $W$ = 1 (\fpeval{round(\sshTwoTrainValWindOneNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%) and $W$ = 2 (\fpeval{round(\sshTwoTrainValWindTwoNHam/(\sshTwoTrainNHam+\sshTwoValNHam)*100,\nPrec)}\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%), $W$ = 0 (\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%), $W$ = 1 (\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%) and $W$ = 2 (\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}\%).
+Our data set consisted of \sshTwoTestNHam\ (\sshTwoTestFracHam\%) test Hamiltonians.
+The remaining \sshTwoTrainPlusValNHam\ Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\sshTwoTrainFracHam\%) training Hamiltonians and \sshTwoValNHam\ (\sshTwoValFracHam\%) validation Hamiltonians.
+The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\sshTwoTrainPlusValWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTrainPlusValWindZeroFracHam\%), $W$ = 1 (\sshTwoTrainPlusValWindOneFracHam\%) and $W$ = 2 (\sshTwoTrainPlusValWindTwoFracHam\%).
+The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\sshTwoTestWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTestWindZeroFracHam\%), $W$ = 1 (\sshTwoTestWindOneFracHam\%) and $W$ = 2 (\sshTwoTestWindTwoFracHam\%).
 
-Mean accuracies across \nExp\ repetitions of experiment 2 were \fpeval{round(\sshTwoEigenTrainAcc,\accPrec)} for training eigenvectors, \fpeval{round(\sshTwoEigenValAcc,\accPrec)} for validation eigenvectors and \fpeval{round(\sshTwoEigenTestAcc,\accPrec)} for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were \fpeval{round(\sshTwoHamTrainAcc,\accPrec)} for training Hamiltonians, \fpeval{round(\sshTwoHamValAcc,\accPrec)} for validation Hamiltonians and \fpeval{round(\sshTwoHamTestAcc,\accPrec)} for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from \fpeval{round(\sshTwoEigenTestAcc,\accPrec)} eigenvector accuracy to \fpeval{round(\sshTwoHamTestAcc,\accPrec)} Hamiltonian accuracy) attests to its power.
-The effectiveness of eigenvector ensembling is also evident from the much worse performance (\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
+Mean accuracies across \nExp\ repetitions of experiment 2 were \xTwoEigTrain\ for training eigenvectors, \xTwoEigVal\ for validation eigenvectors and \xTwoEigTest\ for test eigenvectors.
+Mean accuracies resulting from eigenvector ensembling were \xTwoHamTrain\ for training Hamiltonians, \xTwoHamVal\ for validation Hamiltonians and \xTwoHamTest\ for test Hamiltonians.
+The large accuracy gain achieved by eigenvector ensembling in the test set (going from \xTwoEigTest\ eigenvector accuracy to \xTwoHamTest\ Hamiltonian accuracy) attests to its power.
+The effectiveness of eigenvector ensembling is also evident from the much worse performance (\sshTwoHamTestBaseline) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
 
@@
 
-The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g.
-Shannon information entropy or Gini impurity \cite{friedman2001elements}).
+The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of samples).
 By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
 These signals are the information entropy signatures of each topological phase transition.
+
+We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy.
+This would similarly lead us to Gini impurity signatures of topological phase transitions.
+Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures produced very similar results, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
+Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely open \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
 
@@
 For experiment 1 (section \ref{experiment_1}), only six lattice sites (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites(0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
 As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
 
-\textcolor{blue}{We should remark on the subtleties of the information entropy signatures presented here.
+The information entropy signatures presented here have some interesting subtleties.
 Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
 In the next section, where we develop a quantum formalism for the information entropy signatures discovered in this section, these seemingly antagonistic conceptions shall be harmonized.
-What is important to emphasize at this point is that the information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.}
+What is important to emphasize at this point is that the information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
 
-\textcolor{blue}{To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
+To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
 This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
 The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.}
+In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
 
-%Another important point to be emphasized is that these signals were recovered from the analysis of data from several thousand SSH systems in %each experiment and therefore they are not a property of a single SSH lattice.
-They are rather a pattern that emerges from correlating %topological winding numbers with lattice eigenvector data for several SSH systems.
-
-\textcolor{blue}{Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
+Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
 In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
 They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-%The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further %theoretical investigation.
-This is pursued in the next section.
-We present the information entropy signatures for longer lattices in the %section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-%To see if learning the topological phases can be achieved efficiently by employing simpler models we reran each experiment using only a small %subset of most relevant lattice sites.
-In our rerun of experiment 1 (section \ref{experiment_1}) using only lattice sites $S'_1$ = (0, 50, %51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy), mean accuracies were 97.0\% for training %eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector ensembling were %99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-%Mean accuracies for our rerun of experiment 2 (section \ref{experiment_2}) using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, %99) (which contributed approximately 20 \% of total reduction in Shannon information entropy) were 99.9\% for training eigenvectors, 87.7\% %for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector ensembling yields mean accuracies of 100\% for training %Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
+The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
@@
 2                     &\xcTwo            &\xcTwoEigVal       &\xcTwoEigTest      &\xcTwoHamVal         &\xcTwoHamTest      \tableRowEnd
-2                     &\xcOTwo           &\xcOTwoEigVal      &\xcOTwoEigTest     &\xcOTwoHamVal        &\xcOTwoHamTest     \tableRowEnd
-2                     &\xcSOTwo          &\xcSOTwoEigVal     &\xcSOTwoEigTest    &\xcSOTwoHamVal       &\xcSOTwoHamTest    \tableRowEnd
+2                     &\xcETwo           &\xcETwoEigVal      &\xcETwoEigTest     &\xcETwoHamVal        &\xcETwoHamTest     \tableRowEnd
+2                     &\xcSETwo          &\xcSETwoEigVal     &\xcSETwoEigTest    &\xcSETwoHamVal       &\xcSETwoHamTest    \tableRowEnd
 2                     &\xsTwo            &\xsTwoEigVal       &\xsTwoEigTest      &\xsTwoHamVal         &\xsTwoHamTest      \tableRowEnd
@@
 \caption{\label{accuracy_scores}Accuracy scores of numerical experiments.
-The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH-$\alpha$ systems were as follows.
-Real space features: all real space lattice sites ($X_\alpha$) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ ($X_{\mathcal{S}_{\alpha}}$) (equation \eqref{lattice_subsets}).
-DCT topological features: all DCT topological features $\hat{X}^c_\alpha$ (equation \eqref{DCT}); DCT topological features from subset $\hat{X}^c_{\mathcal{E}_\alpha}$ (equation \eqref{DCT_subsets}; DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ ($\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$) (equation \eqref{DCT_very_compressed}).
-DST topological features: all DST topological features $\hat{X}^s_\alpha$ (equation \eqref{DST}); DST topological features from subset $\hat{X}^s_{\mathcal{O}_\alpha}$ (equation \eqref{DST_subsets}; DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ ($\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$) (equation \eqref{DST_very_compressed}).
+The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH systems were as follows.
+Real space features: all real space lattice sites (\xalpha) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ (\xSalpha) (equation \eqref{lattice_subsets}).
+DCT topological features: all DCT topological features (\xcalpha) (equation \eqref{DCT}); DCT topological features from subset $\mathcal{E}_\alpha$ (\xcEalpha) (equation \eqref{DCT_subsets}); DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xcSEalpha) (equation \eqref{DCT_very_compressed}).
+DST topological features: all DST topological features (\xsalpha) (equation \eqref{DST}); DST topological features from subset $\mathcal{O}_\alpha$ (\xsOalpha) (equation \eqref{DST_subsets}); DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xsSOalpha) (equation \eqref{DST_very_compressed}).
 }
@@
 
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from an information-theoretic perspective, in particular as related to data compression.
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from asignal processing perspective and show how the same machinery used previously is able to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
+
 As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
@@
 Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as $X_{\mathcal{S}_1}$ and $X_{\mathcal{S}_2}$, according to the SSH system they relate to.
+In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xOne and \xTwo, according to the SSH system they relate to.
 
 In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
-These features are denoted in table \ref{accuracy_scores} by $\hat{X}^c_1$, $\hat{X}^s_1$, $\hat{X}^c_2$, $\hat{X}^s_2$ according to which set of topological features and SSH systems they refer to.
+These features are denoted in table \ref{accuracy_scores} by \xcOne, \xsOne, \xcTwo, \xsTwo, according to which set of topological features and SSH systems they refer to.
 
@@
 \end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by $\hat{X}^c_{\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{O}_2}$ according to the topological features and wavevector sites used with each SSH system.
+The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector sites used with each SSH system.
 
@@
 \label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \mathbbm{1}_{\mathcal{S}}[0]x[0] + (-1)^n\mathbbm{1}_{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
+\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
 \end{equation}
@@
 \end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, i.e.
-$\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
-The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH system, type of topological features used as well as which features in real and wavevector space were used to engineer them.
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, 
+\begin{equation}
+\label{indicator_function}
+\indicator{\mathcal{S}}[j] = \begin{cases}
+      1 & \text{if } j \in \mathcal{S} \\
+      0 & \text{otherwise}.
+    \end{cases}
+\end{equation}
+The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used as well as which features in real and wavevector space engineered them and the appropriate SSH system.
 
 The results shown in table \ref{accuracy_scores} carry some important surprises.
-For example, the topological phase transition boundaries of SSH-1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores in the .
-The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ produce accuracy scores at near the same level as using the whole lattice.
+For example, the topological phase transition boundaries of SSH 1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores for the features \xSOne.
+The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
 
-Even more striking is the performance achieved by the DCT topological features $\hat{X}^c_{\mathcal{S},\mathcal{E}}$ defined in equation \eqref{DCT_very_compressed}.
-For SSH-1 systems, they perform on par with using the full set of real space features $X_1$, while for SSH-2 systems a small loss in accuracy is incurred.
+Even more striking is the performance achieved by the DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
+For SSH 1 systems, they perform on par with using the full set of real space features \xOne, while for SSH 2 systems a small loss in accuracy is incurred relative to the full set of real space features \xTwo.
 
-Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features versus DST topological features.
-The latter seems to have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features $\hat{X}^s_{\mathcal{S},\mathcal{O}}$ in both SSH-1 and SSH-2 systems.
+Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features \xcSEalpha\ versus DST topological features \xsSOalpha.
+The latter have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
 This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
 
-The accuracy scores obtained with the real space features $X_{\mathcal{S}_\alpha}$ and the DCT topological features $\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
+The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha\, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
 \textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
 
-%\newcommand\SSHSys{\thead{SSH systems}}
-%\newcommand\Feat{\thead{Features}}
-%\newcommand\ValEig{\thead{Val. eigenvectors}}
-%\newcommand\TestEig{\thead{Test eigenvectors}}
-%\newcommand\ValHam{\thead{Val. Hamiltonians}}
-%\newcommand\TestHam{\thead{Test Hamiltonians}}
-
-\textcolor{blue}{
 \section{Emergent information entropy wave functions}
 \label{emergent_information_entropy_wave_functions}
-}
-\textcolor{blue}{
-The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
+
+The information entropy signatures that we have been investigating pose an immediate theoretical question: how can a signal that is locally defined arise from a global property of the whole SSH lattice?
 In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
-Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
-The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
+Our goal is to arrive at a theoretical framework that will allow us to interpret the information entropy signatures in terms of quantum mechanics.
+%The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
-\textcolor{blue}{
 We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
-macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
-By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by}
+macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices, which themselves become 1D manifolds.
+By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuous limit will be given by
 
@@
 \label{entropy_density}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
+F_S(x) = \int_{\ell}^{(x)}\rho_S(x')dx'
 \end{equation}
-where $x \in [0,1]$ is a spatial coordinate along the continuous lattice (which we shall call from now on string, to emphasize its continuity as opposed to a discrete lattice) and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
+where $\rho_S(x)$ is the local information entropy density function in the continuum limit and $x$ is defined by the coordinate system specified on the 1D manifold $\ell$.
+The index $S$ is meant to emphasize that the we have used in this paper Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
+Gini impurity.
 
-\textcolor{blue}{
-Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
-}
+Our use of periodic boundary conditions implies that the coordinate $x$ should be defined on the circle $ S^1 = [0, 1]/R$, where $R$ is the equivalence relation in $[0,1]$ defining the circle $S^1$ , 
+\begin{equation}
+x \text{ } R \text{ } y \iff x=y \text{ or } (x,y)\in \{(0,1), (1,0)\}.
+\end{equation}
+For open boundary conditions, the spatial coordinate $x$ is defined on the closed interval $[0,1]$ or, in the case of infinite systems, $\mathbb{R}$.
+However, for the sake of generality, we shall continue to use the caligraphic $\ell$ to denote an arbitrary 1D manifold in this section.
+
+Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial information entropy wave function,
+
 \begin{equation}
@@
 \end{equation}
-the amount of topological information available from a single point in the string then being expressed in bra-ket notation by Born's rule,
+the amount of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
 
@@
 
-\textcolor{blue}{
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform 
 \begin{equation}
 \label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
+\hat{\psi}_S(k) = \int_{\ell}\psi_S(x)e^{-2\pi ikx}dx
 \end{equation}
-\textcolor{blue}{
-from which the Shannon information entropy density function in wavevector space can be computed,}
+from which the information entropy density function in wavevector space can be computed,
 \begin{equation}
@@
 
-\textcolor{blue}{
-The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
+The interpretation of information entropy signatures in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
 Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
-}
 
-\textcolor{blue}{
-Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have }
+Let us denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H{\rho_S}$ respectively. Explicitly, we have 
 \begin{subequations}
@@
 \label{mean}
-\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
+\bar{\rho}_S = \int_{\ell}x\rho_S(x)dx,
 \end{equation}
@@
 \label{variance}
-\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
+\Delta\rho_S^2 = \int_{\ell}(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
 \end{equation}
@@
 \label{entropy}
-H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx,
+H{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
 \end{equation}
 \end{subequations}
-\textcolor{blue}{
-with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H[\hat{\rho_S}]$ in terms of $k$ and $\hat{\rho}$.}
+with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
 
-\textcolor{blue}{
-In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}: }
+In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}:
 
@@
 \label{hirschman}
-H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
+H{\rho_S} + H{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). \quad
 \end{equation}
@@
 
-\textcolor{blue}{
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
+The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signature} from sheer data analysis of finite SSH systems in real space.
 In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
-}
 
-\textcolor{blue}{
-Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D continuous string is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the whole SSH system.
+Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
 Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
 Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
-}
-
-\textcolor{blue}{
-Given that our analysis has now come full circle back to theoretical physics, the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-}
 
@@
 
-\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
-}
+By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
 
-\textcolor{blue}{
 The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
@@
 Thus, the discovery and engineering of topological features from real space data as demonstrated in this work carries great promise to the theoretical investigation of these systems.
-}
 
-\textcolor{blue}{
 Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
@@
 We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
-}
 
@@
 
-\textcolor{blue}{The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}%\citequote{superior_comparable}
+The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
+This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.
 
-\textcolor{blue}{This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
+This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
 In \cite{zhang2020interpreting}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
@@
 In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}%\citequote{superior_comparable}
+While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.
 
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of Shannon information entropy given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of information entropy given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
 Whether there is any relationship between the local topological markers detailed in \cite{PhysRevB.84.241106,caio2019topological} and the information entropy of the ensemble of eigenvectors discussed here is left for speculation.
@@
 
-\textcolor{blue}{As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
+As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
 This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
@@
 The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.} We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.
+We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
 
-\textcolor{blue}{Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
+Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
 In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
 This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}
+Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.
 
@@
 \end{figure}
-
-%\begin{figure}
-%\centering
-%\subfigure[]{\label{fourier_feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
-%\subfigure[]{\label{fourier_feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
-%\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section %%\ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for %approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located %along lattice sites $S_2$.}
-%\label{fourier_feature_importances}
-%\end{figure}
-
-%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
 
@@
 
-Correspondence and requests for materials should be addressed to N.
-L.
-Holanda.
-The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
+Correspondence and requests for materials should be addressed to N. L. Holanda. 
+%The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
 

### 2020-07-22 02_results/simulation_results.py
Fixed entropy signature figures in main paper

@@ -36,7 +36,7 @@ SSH2_PERIODIC_180_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"perio
 SSH2_PERIODIC_220_6561_SIMULATION_DIR = os.path.join(SSH2_SIMULATIONS_DIR,"periodic_220_6561")
 
 ### Paper directory
-FIGURES_DIR = "/home/rio/ml_topological_phases_in_real_space/5_paper"
+FIGURES_DIR = "/home/rio/ml_topological_phases_in_real_space/07_paper/supp"
 # ssh1 figures
 SSH1_FIGURES_DIR = os.path.join(FIGURES_DIR,"ssh1")
 SSH1_PERIODIC_100_6561_FIGURES_DIR = os.path.join(SSH1_FIGURES_DIR,"periodic_100_6561")

### 2020-07-22 06_results_with_engineered_features/results_template_parameters.py

@@ -144,8 +144,8 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "hist_precision": 1000,
     "fig_params": {"figsize": [12,12]}, 
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "reduction in information entropy (%)", "fontsize": 24},
-    "title_params": {"label": "Information entropy signature (real space) - SSH 1", "fontsize": 24},
+    "ylabel_params": {"ylabel": "reduction in information entropy", "fontsize": 24},
+    "title_params": {"label": "Information entropy signature - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
     "xticks_params": {"ticks": [int(i) for i in np.linspace(0,int(chain_length)-1,10).astype(int)], "fontsize": 24},
@@ -163,8 +163,8 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "plot_params": {"color":"indianred", "width": 0.7},
     "fig_params": {"figsize": [12,12]},
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "cumulative reduction in information entropy (%)", "fontsize": 24},
-    "title_params": {"label": "Cumulative information entropy signature (real space) - SSH 1", "fontsize": 24},
+    "ylabel_params": {"ylabel": "cumulative reduction in information entropy", "fontsize": 24},
+    "title_params": {"label": "Cumulative information entropy signature - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
     "xticks_params": {"ticks": [int(i) for i in np.linspace(0,int(chain_length)-1,10).astype(int)], "fontsize": 24},
@@ -183,7 +183,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "hist_precision": 1000,
     "fig_params": {"figsize": [12,12]}, 
     "xlabel_params": {"xlabel": "reciprocal lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "reduction in information entropy (%)", "fontsize": 24},
+    "ylabel_params": {"ylabel": "reduction in information entropy", "fontsize": 24},
[…]

### 2020-07-22 06_results_with_engineered_features/results_template_parameters.py
Generated feature importances figures again

@@ -144,7 +144,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "hist_precision": 1000,
     "fig_params": {"figsize": [12,12]}, 
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "reduction in information entropy", "fontsize": 24},
+    "ylabel_params": {"ylabel": "reduction in information entropy (%)", "fontsize": 24},
     "title_params": {"label": "Information entropy signature - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
@@ -163,7 +163,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "plot_params": {"color":"indianred", "width": 0.7},
     "fig_params": {"figsize": [12,12]},
     "xlabel_params": {"xlabel": "lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "cumulative reduction in information entropy", "fontsize": 24},
+    "ylabel_params": {"ylabel": "cumulative reduction in information entropy (%)" , "fontsize": 24},
     "title_params": {"label": "Cumulative information entropy signature - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
@@ -183,7 +183,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "hist_precision": 1000,
     "fig_params": {"figsize": [12,12]}, 
     "xlabel_params": {"xlabel": "reciprocal lattice site", "fontsize": 24},
-    "ylabel_params": {"ylabel": "reduction in information entropy", "fontsize": 24},
+    "ylabel_params": {"ylabel": "reduction in information entropy (%)", "fontsize": 24},
     "title_params": {"label": "Information entropy signature (wavevector space) - SSH 1", "fontsize": 24},
     "xlim_params": {},
     "ylim_params": {},
@@ -202,7 +202,7 @@ def get_parameters_ssh1(ssh_type, chain_length, n_hamiltonians, experiment_name=
     "plot_params": {"color":"palevioletred", "width": 0.7},
     "fig_params": {"figsize": [12,12]},
     "xlabel_params": {"xlabel": "reciprocal lattice site", "fontsize": 24},
[…]

### 2020-07-22 07_paper/supplementary.tex
First alpha version. Revieweing for typos.

--- 2020-06-21 8_prb_submission/1_reply_referee/supplementary/supplementary.tex
@@
 
+\newcommand\xSOne{$X_{\mathcal{S}_1}$}
+\newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
+\newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
+\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
+\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
+\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
+
 \begin{document}
@@
 \label{SSH}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
+\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
 \end{equation}
@@
 An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
-This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a very challenging task.
+This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a challenging task.
 
@@
 \end{equation}
-where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\hat{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
+where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\mathbf{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
 Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure 1 in the article.
@@
 \centering
-\subfigure[]{\label{less_feat:a}\includegraphics[width=.49\textwidth]{./ssh1/periodic_less_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\subfigure[]{\label{less_feat:b}\includegraphics[width=.49\textwidth]{./ssh2/periodic_less_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Phase diagrams learned from most relevant lattice sites.
-(a) Phase diagram learned by a combination of decision trees with eigenvector ensembling in experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99).
-The accuracy achieved for Hamiltonians in the test set using only the four lattice sites in $S'_1$ was approximately 95\%.
-(b) Phase diagram learned by a combination of random forests with eigenvector ensembling in experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99).
-The accuracy achieved for Hamiltonians in the test set using only the nine lattice sites in $S'_2$ was approximately 74\%.}
-\label{less_feat}
+\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/real_space_best_04_sites/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dct_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dst_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
+\caption{Phase diagrams learned from compressed representations of the SSH 1 system.
+(a) Phase diagram learned using the real space features \xSOne.
+(b) Phase diagram learned from the DCT topological features \xcSEOne.
+(b) Phase diagram learned from the DST topological features \xsSOOne.}
+\label{eng_feat_ssh1}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/real_space_best_12_sites/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dct_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dst_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
+\caption{Phase diagrams learned from compressed representations of the SSH 2 system.
+(a) Phase diagram learned using the real space features \xSTwo.
+(b) Phase diagram learned from the DCT topological features \xcSETwo.
+(b) Phase diagram learned from the DST topological features \xsSOTwo.}
 \end{figure}
@@
 
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
+%The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
+%\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+%disordered systems in condensed matter) do not have.
+Moreover, since real space and wavevector space eigenvectors are related by Fourier %transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
+We argue here that a data-driven %approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
 
-Our reasoning goes as follows.
+The insights behind our intuition that topological phases can be learned from local features are as follows.
 First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
@@
 
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as the curse of dimensionality \cite{bishop2006pattern}.
+The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as \emph{the curse of dimensionality} \cite{bishop2006pattern}.
 It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
@@
 Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
-As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data (see figure \ref{less_feat}).
-In this sense, key topological information can be said to be localized on few lattice sites.
+As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data, which reveals that there is a lot of redundancy in the information content of real space eigenvectors.
+This fact can be exploited to generate compressed representations of SSH systems that still carry most of the relevant topological information, as can be seen in figures \ref{eng_feat_ssh1} and \ref{eng_feat_ssh2}.
 
-\subsection*{The eigenvector ensembling algorithm}
-
-We describe here in detail each step of the eigenvector ensembling algorithm.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our parameter $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will generate $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
-\vspace{.3cm}
-In this work we implemented the eigenvector ensembling algorithm with Python's Scikit tools.
-
-\subsection*{Information entropy signatures in the macroscopic limit}
+\subsection*{Numerical explorations on longer lattices}
 
@@
 
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b)) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
-
-Figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} suggest that the information entropy signatures presented here can be viewed as entropy mass functions along the lattices.
-In the limit of an infinite chain, the cumulative entropy distribution $F_S(x)$ associated with a Shannon information entropy signal will be given by the integral of an entropy density function $\rho_S$($x$),
-
-\begin{equation}
-\label{entropy_dens}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
-\end{equation}
-where $x$ $\in$ [0,1] is a spatial coordinate along the lattice (being strict, our use of periodic boundary conditions implies that the coordinate $x$ should be defined in the quotient space $[0,1]/R$, where $R$ is the equivalence relation in [0,1] defining the unit circle $S^1$, i.e.
-$x$ $R$ $x'$ if and only if $x$ = $x'$ or ($x$,$x'$) $\in$ \{(0,1), (1,0)\}.
-For open boundary conditions, the spatial coordinate $x$ is defined in the closed interval [0,1]).
-In this continuum limit, an information entropy signature will be given by the entropy density function $\rho_S(x)$.
-Figures \ref{cdf1} and \ref{cdf2} show the cumulative entropy distributions corresponding to the information entropy signatures in figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}.
-
-The results presented in this article suggest that the macroscopic limit $\rho_S(x)$ of the information entropy signatures may have strong theoretical interest and pave new roads to the investigation of topological materials.
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
+This naturally leads us to speculation about the continuum limit of information entropy signatures, a matter formally explored in the article.
 
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_feature_importances.png}}
 \caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_feature_importances.png}}
-\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_feature_importances.png}}
 \caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
@@
 \centering
-\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
 \caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
@@
 \centering
-\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
-\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
 \caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.

### 2020-07-23 07_paper/article.tex
Beta of paper finished. Waiting Griffith's reply.

@@
 \label{SSH_ham}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
+\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
 \end{equation}
@@
 To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}
+These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}.
 
 In possession of the information entropy signatures, we demonstrate how the symmetries in real and wavevector space eigenvectors can be manipulated with signal processing tools commonly employed in audio and image processing to execute two standard unsupervised learning tasks, namely dimensionality reduction and feature engineering.
-The topological features resulting from this analysis, here denominated DCT and DST topological features, are discussed in section \ref{topological_feature_engineering}.
+The topological features resulting from this analysis, here denominated Discrete Cosine Transform and Discrete Sine Transform topological features, are discussed in section \ref{topological_feature_engineering}.
 
@@
 The theoretical formulation of the results obtained with machine learning in terms of emergent quantum mechanical wave functions allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of information entropy in topological phase transitions.
-The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}
+The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}.
 
-The  description of information entropy signatures (which were obtained here with machine learning) as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The  description of information entropy signatures as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
 
 As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
-This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were already known.
+This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were known in advance.
 By proposing new concepts from the data analysis of physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
@@
 The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
-The intuition that eigenvectors can be used in replacement to raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
+The intuition that eigenvectors can be used in replacement of raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
 \begin{equation}
@@
 This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = \epsilonValue$ around the correct winding number values.
+For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a minimum range of $\epsilon = \epsilonValue$ from the correct winding number values.
 Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
@@
 The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
-Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ experiments.
+Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across $n_{exp}$ experiments.
 The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps.
@@
 
-The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module.
+The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit-learn,sklearn_api}.
 
@@
 We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
+Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test the eigenvector ensembling algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
 
-The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of samples).
+The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of ensembles of eigenvectors).
 By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
@@
 Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures produced very similar results, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
-Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely open \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
+Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely undecided \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
 
@@
 Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
-In the next section, where we develop a quantum formalism for the information entropy signatures discovered in this section, these seemingly antagonistic conceptions shall be harmonized.
-What is important to emphasize at this point is that the information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
+In section \ref{emergent_information_entropy_wave_functions}, where we develop a quantum formalism for the information entropy signatures obtained in this section, these seemingly antagonistic conceptions shall be harmonized.
+What is important to emphasize at this point is that an information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
 
@@
 
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from asignal processing perspective and show how the same machinery used previously is able to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective and show how the same machinery used previously is able to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
 
-As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
+As we have argued in section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
 Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
-Here we show how the symmetries in the real space information entropy signatures in figure \ref{feature_importances} can be exploited to engineer new global topological features, leading to an effective compression of topological information.
+Here we show how the symmetries in real space eigenvectors and information entropy signatures can be exploited to engineer new global topological features, leading to an effective compression of topological information.
 
@@
 where $M = \frac{N}{2}+1$.
-The second path capitalizes on the fact that de imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
+The second path capitalizes on the fact that the imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
 \begin{equation}
@@
 The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
-the sites $0 \leq j \leq \frac{N}{2}$.
-This is due to the fact that each equation assumes that the real space eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
+the sites $0 \leq l \leq \frac{N}{2}$.
+This is due to the fact that each equation assumes that the eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
 While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
@@
 
-The topological feature engineering strategies described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
-As equations \eqref{DCT} and \eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
+The topological feature engineering techniques described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
+As equations \eqref{hermitian_symmetry}-\eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from the existence of certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
 
@@
 
-The lattice compression strategies tested in this work were: i) learning topological phases from only a subset of the real space lattice sites; ii) learning topological phases from the DCT or DST engineered features of equations; iii) learning topologcal phases from a fraction of the DCT or DST topological features and iv) learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
+The lattice compression strategies tested in this work were: \emph{i)} learning topological phases from only a subset of real space lattice sites; \emph{ii)} learning topological phases from the DCT or DST engineered features of equations \eqref{DCT} and \eqref{DST}; \emph{iii)} learning topological phases from a fraction of the DCT or DST topological features and \emph{iv)} learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
 
-In strategy \emph{i)} the lattice sites used in the SSH1 and SSH2 systems were
+In strategy \emph{i)} the lattice sites used in the SSH 1 and SSH 2 systems were
 \begin{equation}
@@
 \end{equation}
-Note that for the nearest-neighbor SSH system $\mathcal{S}_1$ correspond to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xOne and \xTwo, according to the SSH system they relate to.
+Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
+Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
+In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xSOne and \xSTwo, according to the SSH systems they relate to.
 
@@
 
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH1 and SSH2 systems,
+Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH 1 and SSH 2 systems,
 \begin{equation}
@@
 \end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector sites used with each SSH system.
+The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space components used with each SSH systems.
 
@@
 Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
-Mathematically, we can expess the topological features used in strategy \emph{iv)} as follows:
+Mathematically, we can express the topological features used in strategy \emph{iv)} as follows:
 \begin{equation}
@@
 \label{DST_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}.
+\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}
 \end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, 
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$, 
 \begin{equation}
 \label{indicator_function}
-\indicator{\mathcal{S}}[j] = \begin{cases}
-      1 & \text{if } j \in \mathcal{S} \\
+\indicator{\mathcal{S}}[l] = \begin{cases}
+      1 & \text{if } l \in \mathcal{S} \\
       0 & \text{otherwise}.
@@
 \end{equation}
-The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used as well as which features in real and wavevector space engineered them and the appropriate SSH system.
+The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used, which components in real and wavevector space engineered them and the appropriate SSH systems.
 
-The results shown in table \ref{accuracy_scores} carry some important surprises.
+The results shown in table \ref{accuracy_scores} bring some startling surprises.
 For example, the topological phase transition boundaries of SSH 1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores for the features \xSOne.
-The same appears to be true to SSH-2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
+The same appears to be true to SSH 2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
 
-Even more striking is the performance achieved by the DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
+Even more striking is the performance achieved by the compressed DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
 For SSH 1 systems, they perform on par with using the full set of real space features \xOne, while for SSH 2 systems a small loss in accuracy is incurred relative to the full set of real space features \xTwo.
 
-Another interesting insight comes from comparing the accuracy scores obtained with DCT topological features \xcSEalpha\ versus DST topological features \xsSOalpha.
-The latter have poorer performance than the former, as is indicated by the sharp drop in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
+Another interesting insight comes from comparing the accuracy scores obtained with the DCT topological features versus the  DST topological features.
+The latter have poorer performance than the former, as is indicated by the sharp drops in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
 This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
 
-The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha\, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
+In this sense, key topological information can be said to be localized on few sites in the lattice.
+We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
 
@@
 where $\rho_S(x)$ is the local information entropy density function in the continuum limit and $x$ is defined by the coordinate system specified on the 1D manifold $\ell$.
-The index $S$ is meant to emphasize that the we have used in this paper Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
+The index $S$ is meant to emphasize that in this paper we have used Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
 Gini impurity.
@@
 
-Let us denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H{\rho_S}$ respectively. Explicitly, we have 
+Let us denote the mean, the variance and the entropy associated with the probability distribution $\rho_S$ by $\mu_{\rho_S}$, $\sigma_{\rho_S}^2 $ and $H_{\rho_S}$ respectively. Explicitly, we have 
 \begin{subequations}
@@
 \label{mean}
-\bar{\rho}_S = \int_{\ell}x\rho_S(x)dx,
+\mu_{\rho_S} = \int_{\ell}x\rho_S(x)dx,
 \end{equation}
@@
 \label{variance}
-\Delta\rho_S^2 = \int_{\ell}(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
+\sigma_{\rho_S}^2 = \int_{\ell}(x-\mu_{\rho_S})^2\rho_S(x)dx,\quad \text{and}
 \end{equation}
@@
 \label{entropy}
-H{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
+H_{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
 \end{equation}
 \end{subequations}
-with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
+with analogous equations for the wavevector space counterparts $\mu_{\hat{\rho}_S}$, $\sigma_{\hat{\rho}_S}^2 $ and $H_{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
 
@@
 \label{heisenberg}
-\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad \text{and }
+\sigma_{\rho_S} \cdot \sigma_{\hat{\rho}_S} \geq \frac{1}{4\pi}, \quad \text{and }
 \end{equation}
@@
 \label{hirschman}
-H{\rho_S} + H{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). \quad
+H_{\rho_S} + H_{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). 
 \end{equation}
@@
 
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signature} from sheer data analysis of finite SSH systems in real space.
+The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signatures} from sheer data analysis of finite SSH systems in real space.
 In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
 
-Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
+Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
 Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
@@
 
-By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
+By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical and theoretical possibilities offered by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
 
@@
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of information entropy given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
-Whether there is any relationship between the local topological markers detailed in \cite{PhysRevB.84.241106,caio2019topological} and the information entropy of the ensemble of eigenvectors discussed here is left for speculation.
+Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave function discussed here is left for speculation.
 
@@
 The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.
+Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in dimensionality  while still capturing all the relevant physics of a system.
 We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
@@
 (a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located along lattice sites $S_2$.}
+(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.}
 \label{feature_importances}

### 2020-07-23 07_paper/supplementary.tex
Beta of paper finished. Waiting Griffith's reply.

@@
 (b) Cumulative entropy distribution for 90 unit cells.
-(c) Cumulative entropy distribution for 110 unit cells.
-The two visible leaps in the cumulative entropy distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
+(c) Cumulative entropy distribution for 110 unit cells.}
 \label{cdf1}
@@
 (b) Cumulative entropy distributions for 90 unit cells.
-(c) Cumulative entropy distributions for 110 unit cells.
-Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable.
-The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case of 50 unit cells.}
+(c) Cumulative entropy distributions for 110 unit cells.}
 \label{cdf2}

### 2020-07-24 07_paper/00_article/article.tex
Possible version to be resubmitted to prb

--- 2020-07-23 07_paper/article.tex
@@
 
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+The main motivation for developing a data-driven approach based on real space is that the canonical method of choice for the analysis of topological systems, i.e.
+wavevector space computations of topological invariants, is often only feasible for systems with translational symmetry, which many physical systems of current interest (e.g.
 disordered systems in condensed matter) do not have.
+Furthermore, it is not always granted that the topological invariants of a physical system being investigated are known in advance, as is presently the case for many gapless insulators.
+In such cases, being able to engineer topological features that encode the topological states of a system while at the same time reducing the system's complexity may provide an alternative strategy.
 Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-The data-driven approach described in this article addresses these issues.
-In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
+Constructing theoretical methods to trace the distribution of information in topological systems may be an essential prerequisite to discovering new topological invariants and features.
+The data-driven approach designed in this article addresses these issues.
+%In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
 
@@
 
-Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
+Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
 Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
@@
 
-\bibliography{bibl}{}
+\bibliography{article_bib}{}
 

### 2020-07-24 07_paper/01_supplementary/supplementary.tex
Possible version to be resubmitted to prb

--- 2020-07-23 07_paper/supplementary.tex
@@
   \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/ssh_model.pdf}
+  \includegraphics[width=.37\textwidth]{./ssh/ssh_model.pdf}
   \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
@@
   \centering
-  \includegraphics[width=.37\textwidth]{./phase_diagrams/winding.png}
+  \includegraphics[width=.37\textwidth]{./ssh/winding.png}
   \caption{Winding number.
@@
 (b) Phase diagram learned from the DST topological features \xsSOTwo.}
+\label{eng_feat_ssh2}
 \end{figure}
@@
 
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size increases.
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size is increased.
 This naturally leads us to speculation about the continuum limit of information entropy signatures, a matter formally explored in the article.
@@
 
-\begin{thebibliography}{10}
-\bibitem{asboth2016short}
-J.~K. Asb{\'o}th, L.~Oroszl{\'a}ny, and A.~P{\'a}lyi, ``A short course on
-  topological insulators,'' {\em Lecture notes in physics}, vol.~919, 2016.
-
-\bibitem{goodfellow2016deep}
-I.~Goodfellow, Y.~Bengio, and A.~Courville, {\em Deep learning}.
-\newblock MIT press, Cambridge, MA, USA, 2016.
-
-\bibitem{bishop2006pattern}
-C.~M. Bishop, {\em Pattern recognition and machine learning}.
-\newblock Springer New York, NY, USA, 2006.
-
-\bibitem{cayton2005algorithms}
-L.~Cayton, ``Algorithms for manifold learning,'' {\em Univ. of California at
-  San Diego Tech. Rep}, vol.~12, no.~1-17, p.~1, 2005.
-
-\bibitem{narayanan2010sample}
-H.~Narayanan and S.~Mitter, ``Sample complexity of testing the manifold
-  hypothesis,'' in {\em Advances in Neural Information Processing Systems},
-  pp.~1786--1794, 2010.
-
-\bibitem{rifai2011manifold}
-S.~Rifai, Y.~N. Dauphin, P.~Vincent, Y.~Bengio, and X.~Muller, ``The manifold
-  tangent classifier,'' in {\em Advances in Neural Information Processing
-  Systems}, pp.~2294--2302, 2011.
-\end{thebibliography}
+\bibliography{supplementary_bib}{}
 

### 2020-07-24 10_prb_resubmission_01/00_article/article.tex
Possible version to be resubmitted to prb

--- 2020-06-21 8_prb_submission/1_reply_referee/article/article.tex
@@
 \usepackage[resetlabels, labeled]{multibib}
-\usepackage{xcolor}
 %\newcites{supp}{References}
@@
 Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
 

### 2020-07-24 10_prb_resubmission_01/02_letter_referee/letter_referee.tex
Possible version to be resubmitted to prb

--- 2020-07-19 10_prb_submission/02_reply_referee/00_article_with_comments/article.tex
@@
-%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
 \documentclass[10pt]{revtex4-1}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{nicefrac}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsmath} 
-\usepackage{subfigure}
-\usepackage{multirow} 
-\usepackage{tabularx} 
-\usepackage{array}
-\usepackage{units}
-\usepackage{tensor} 
-\usepackage{braket}
-\usepackage{bm}
+\usepackage{xcolor} 
 \usepackage{hyperref}
-\usepackage[resetlabels, labeled]{multibib}
-\usepackage{xcolor}
-\usepackage{bbm}
-%\newcites{supp}{References}
-
-\renewcommand{\Re}{\operatorname{{\mathrm Re}}}
-\renewcommand{\Im}{\operatorname{{\mathrm Im}}}
-\newcommand{\tr}{\operatorname{{\mathrm tr}}}
-
-\newcommand{\hc}{^{\dagger}}
-\newcommand{\ad}{\operatorname{{\mathrm ad}}}
-\newcommand{\adn}{\ad_{\hat n}}
-\newcommand{\adx}{\ad_{\hat x}}
-\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
-\newcommand{\adp}{\ad_{\hat p}}
-\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
-\newcommand{\inbk}[1]{\left[ #1 \right]}
-\newcommand{\inbr}[1]{\left\{ #1 \right\}}
-\newcommand{\inp}[1]{\left( #1 \right)}
-\newcommand{\pd}{\partial}
-\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
-\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative
-
 \newcounter{quoter}
@@
   }%
-
 \newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
 \newcommand{\citequote}[1]{\ref{#1}}
-
-\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
-
 \begin{document}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Comments referee %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Reply to the editor}
 
-\section*{Reply to the first referee }
+Dear editor,
+
+we appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900).
+We have fully addressed the issues pointed by referee 2, which have led to a much improved version of the paper, hopefully the definitive version.
+
+In what follows, we briefly summarize the modifications made to the paper.
+New results have been added to the paper in the form of two new sections: \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
+The eigenvector ensembling algorithm}.
+The section \textbf{VII.
+Discussion} has been extended to address the issues that were raised.
+The sections are now numbered for clarity.
+
+A more comprehensive account of these changes can be found in the reply to the second referee.
+
+Best regards,
+
+N.L. Holanda and M. A. S. Griffith.
+
+\section*{Reply to the first referee}
+Dear referee,
+
+we appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}.
+We are currently cleaning, pruning and documenting our code, so we expect to put the Python code used to run the numerical experiments described in the paper online as soon as possible.
+
 \section*{Reply to the second referee}
@@
 
-we appreciate the valuable insights on how to improve our article that you have provided us with.
-Below we address each of the emphasized points separately, as they were written in the reply that was sent back to us.
-We quote the issues raised in italic, and highlight in boldface the points that we thought were particularly relevant.
+we appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with.
+These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical contents.
+
+A summary of the modifications made to the paper are listed in what follows.
+New results have been added to the paper in the form of two new sections: \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
+The eigenvector ensembling algorithm}.
+The section \textbf{VII.
+Discussion} has been extended to include comments on the issues that were raised.
+The sections are now numbered for clarity.
+
+Below we address each of the issues that have been raised separately, as they were written in the reply that was sent back to us.
+We quote the issues in italic, and highlight in bold the points that we thought were particularly relevant and guided us in the improvement of the manuscript.
+The answers to each of the major points are written in blue.
 
@@
 Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
-We have added a paragraph to the section \textbf{Discussion} outlining these possibilities.
+We have added a paragraph to the section \textbf{VII.
+Discussion} outlining these possibilities.
 As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
-Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the Shannon entropy signature and the information entropy uncertainty relations for topological phase transitions presented here for the first time.
-We have added a paragraph to the \textbf{Introduction} emphasizing this point.
+Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data, the Shannon information entropy signature and finally its quantum interpretation as an emergent wave function, leading to the establishment of the uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have added a paragraph to the section \textbf{I.
+Introduction} emphasizing these new results.
 }
 
-\textcolor{blue}{\citequote{sufficient_accuracy}, \citequote{superior_comparable} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
+\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs consistently better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
 This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
-We have added a paragraph to the section \textbf{Numerical experiments} to emphasize the use of this baseline.
-As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
+We have added a paragraph to the section \textbf{III.
+Numerical experiments} to emphasize the use of this baseline.}
+
+\textcolor{blue}{\citequote{superior_comparable} As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
 Rev.
@@
 This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.}
-
-\textcolor{blue}{\citequote{superior_comparable}In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+A small paragraph was added to the section \textbf{VII.
+Discussion} to explicitly note this point.
+In another paragraph added to the section \textbf{VII.
+Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
 Rev.
@@
 When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
-While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.
-}
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-\`{a}-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
 
 \textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data-driven approach based on real space should be in the Introduction.
-We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the \textbf{Introduction}.}
+We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the section \textbf{I.
+Introduction} in the main paper.}
 
 \vspace{0.5cm}
-\emph{I am not sure which crucial problems their algorithm can solve that
-was not possible before with machine learning. Furthermore, along with
-the emerging research of unsupervised learning methods in realizing
-the topological phases, \textbf{why should the supervised learning method be
-focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript,
-where I do not see the proposal's advantages, I would prefer the
-\textbf{unsupervised approaches that could grasp information from a given
-system without knowing their phases}\genquote{unsupervised_approaches}. In my opinion, a proper intrinsic
-route for understanding physical systems without much information on
-the dynamics of the system will lead to significant future
-developments and a better understanding of physic systems.}
+\emph{I am not sure which crucial problems their algorithm can solve that was not possible before with machine learning.
+Furthermore, along with the emerging research of unsupervised learning methods in realizing the topological phases, \textbf{why should the supervised learning method be focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript, where I do not see the proposal's advantages, I would prefer the \textbf{unsupervised approaches that could grasp information from a given system without knowing their phases}\genquote{unsupervised_approaches}.
+In my opinion, a proper intrinsic route for understanding physical systems without much information on
+the dynamics of the system will lead to significant future developments and a better understanding of physic systems.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the localizability of topological information along lattices of SSH systems via model explainability tools in machine learning.
-We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of Shannon entropy as loss function provides a clear way to measure feature importance.
-This is compounded by the fact that Shannon entropy plays a very important role in information theory and physics, as is evidenced by the new section \textbf{Emergent information entropy wave functions} added to this new version of the article.}
+\textcolor{blue}{\citequote{unsupervised_learning} One of our main goals in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
+We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of information entropy as loss function provides a clear way to measure feature importance.
+This is compounded by the fact that information entropy plays a very important role in information theory and physics, as is evidenced in the new section \textbf{VI.
+Emergent information entropy wave functions} added to this new version of the article.}
 
-\textcolor{blue}{\citequote{unsupervised_approaches} Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
-This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{Discussion}.
-Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used for example as a powerful dimensionality reduction tool in data-driven physics, which by itself is an unsupervised learning task and can serve as a preprocessing step to further applications of machine learning to physics.}
+\textcolor{blue}{\citequote{unsupervised_approaches} The new section \textbf{V.
+Topological feature engineering and lattice compression} shows how unsupervised learning can be performed with eigenvector ensembling using tree based methods as learning algorithms.
+In fact, two of the main tasks under the broad umbrella of unsupervised learning are exactly those: dimensionality reduction and feature engineering.
+Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
+This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{VII.
+Discussion}.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used as a powerful dimensionality reduction tool in other, unrelated data-driven or numerical physics tasks, which by itself is another example of unsupervised learning and can serve as a preprocessing step to further applications of machine learning to physics.}
 
 \vspace{0.5cm}
-\emph{The details of \textbf{the eigenvector ensembling algorithm should be
-addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material. What is
-the specific algorithm used in the paper to train on eigenvectors? I
-think it is important even if the readers are not familiar with some
-ML techniques. Some readers in physics may find it difficult to
-understand some ML technical terms such as bootstrapping, training and
-validation, test sets, etc. In addition, \textbf{I expect proof of what
-"physics" their method captures and why the eigenvector can play an
-important role in characterizing the topological phase}\genquote{eigenvector_physics}. If this
-physical interpretability is not mentioned, it is very difficult to
-see the contribution of the method in physics.}
+\emph{The details of \textbf{the eigenvector ensembling algorithm should be addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material.
+What is the specific algorithm used in the paper to train on eigenvectors?
+I think it is important even if the readers are not familiar with some ML techniques.
+Some readers in physics may find it difficult to understand some ML technical terms such as bootstrapping, training and validation, test sets, etc.
+In addition, \textbf{I expect proof of what "physics" their method captures and why the eigenvector can play an important role in characterizing the topological phase}\genquote{eigenvector_physics}.
+If this physical interpretability is not mentioned, it is very difficult to see the contribution of the method in physics.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  We have moved the section \textbf{The eigenvector ensembling algorithm} from the Supplementary Material to the main paper.
+\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  The section \textbf{II.
+The eigenvector ensembling algorithm} has been moved from the Supplementary Material to the main paper.
 The issue of specifying the particular learning algorithms used to train on eigenvectors is addressed in the subsections for each SSH experiment (see subsections \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees} and \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}).
-In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module.}
+In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module used to run the numerical experiments in the paper.}
 
-\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
+\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{II.
+The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
 Therefore, by expressing a data set of eigenvectors on a suitable choice of basis (which in this paper is the real space basis), we are able to investigate properties of a family of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
@@
 \textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
-We have therefore moved it to the final patragraph of the section \textbf{Information entropy signatures} in the main text.}
+We have therefore moved it to the final patragraph of the section \textbf{V.
+Topological feature engineering and lattice compression} in the main text.}
 
-\textcolor{blue}{\citequote{physical_insights} We have added the new section \textbf{Emergent information entropy wave functions} in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinit lattice.
-Therefore, the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures) and finally iii) interpret these new properties in the light of theoretical physics.}
+\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we \emph{i)} propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), \emph{ii)} use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), \emph{iii)} generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
+Topological feature engineering and lattice compression},  and finally \emph{iv)} interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
+Emergent information entropy wave functions}, in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinite lattice.}
 
-\textcolor{blue}{We find it noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
-Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
+\textcolor{blue}{It is noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
+Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{VI.
+Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
 
@@
 
-\emph{The authors state in the abstract that "model explainability in
-machine learning can advance the research of exotic quantum materials
-with properties that may power future technological applications such
-as qubit engineering for quantum computing." \textbf{Could you explain a bit
-more about properties that may power future quantum computing?}\genquote{quantum_comp}}
+\emph{The authors state in the abstract that "model explainability in machine learning can advance the research of exotic quantum materials
+with properties that may power future technological applications such as qubit engineering for quantum computing." \textbf{Could you explain a bit more about properties that may power future quantum computing?}\genquote{quantum_comp}}
 
 \vspace{0.25cm}
-\citequote{quantum_comp} Insert comments about topological qubits?
+\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{VII.
+Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
 
 \vspace{0.5cm}
-\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single
-iterations of experiments 1 and 2 as seen from parameter space". \textbf{What
-are the experiments 1 and 2?}\genquote{experiments_1_2}}
+\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single iterations of experiments 1 and 2 as seen from parameter space".
+\textbf{What are the experiments 1 and 2?}\genquote{experiments_1_2}}
 
@@
 \emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
-such as "the accuracy" and "the probability heatmap," "eigenvector
-accuracy," and "Hamiltonian accuracy."}
+such as "the accuracy" and "the probability heatmap," "eigenvector accuracy," and "Hamiltonian accuracy."}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{Numerical experiments}.}
+\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{III.
+Numerical experiments}.
+Furthermore, the new section \textbf{V.
+Topological feature engineering and lattice compression} contains a summary of accuracy scores obtained in all numerical experiments performed in the paper.}
 
 \vspace{0.5cm}
-\emph{I prefer to \textbf{put the definition of information entropy signatures in
-the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
+\emph{I prefer to \textbf{put the definition of information entropy signatures in the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
 
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
+\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{VI.
+Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}
+\end{document}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Reply to the second referee}
+Dear referee,
 
-\pagebreak
+we appreciate the valuable insights on how to improve our article that you have provided us.
+These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical results.
 
-\nocite{*}
+These new results have been added to the paper in the form of two new sections: \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
+The eigenvector ensembling algorithm}.
+The section \textbf{VII.
+Discussion} has been extended to include comments on some of the issues that were raised.
+The sections are now numbered for clarity.
 
-\title{Machine learning topological phases in real space}
+Below we address each of the raised issues separately, as they were written in the reply that was sent back to us.
+We quote the raised issues in italic, and highlight in bold the points that we thought were particularly relevant and guided us in the improvement of the manuscript.
+The answers to each of the major points are written in blue.
 
-\author{N. L. Holanda}
-\email{linneuholanda@gmail.com, linneu@cbpf.br}
-\affiliation{Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
+\subsection*{Major}
 
-\author{M. A. S. Griffith}
-\email{griffithphys@gmail.com}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
+\emph{\textbf{I am not sure about the novelty and generality of their method.}\genquote{pipeline_not_work} For
+example, their pipeline cannot work for complex experimental physical systems, where the Hamiltonian could be unknown. Moreover, the authors
+state that it is sufficient to use the input data in real space to predict the topological phase with high accuracy. \textbf{It is not clear to
+me what "sufficient" and "high accuracy" mean}\genquote{sufficient_accuracy}, and the advantages of using the input data in real space instead of the Hamiltonian in wavevector space.
+\textbf{I expect the evidence to indicate that their method is superior or comparable to any other method}\genquote{superior_comparable}.
+It is worth mentioning that the author already discussed \textbf{the motivations for developing a
+data-driven approach based on real space}\genquote{motif_real_space} in the "Learning topological phases from real space data" section.
+However, these arguments should be pointed carefully in the "Introduction" section.}
 
-\date{\today }
-
-\begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems from bulk data in real lattice space.
-The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
-We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
-The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-\label{introduction}
-The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}.
-These materials feature previously unthought-of traits like bulk insulation coupled with metallic conductance at the surface and the splitting of currents according to spin orientation.
-Adding to that, these properties are protected by non-trivial topology that renders them robust to many sources of perturbation like thermal noise.
-Such characteristics make them promising candidates to being the cornerstone of 21st century technologies like spintronics and quantum computing.
-
-These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
-Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.
-
-The SSH model is the simplest tight-binding model that exhibits a topological phase transition.
-As such, it can be viewed as the \emph{Drosophila} of the field, providing a simple framework for testing new techniques.
-The model can be expressed in terms of creation and annihilation operators by the Hamiltonian
-\begin{equation}
-\label{SSH_ham}
-\hat{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-and describes e.g.
-the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material).
-The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.
-
-Many recent papers have explored the possibility of treating the general problem of determining phase transition boundaries of physical systems as machine learning tasks \cite{carrasquilla2017machine}$^-$\cite{rodriguez2018identifying}.
-In the particular case of topological phase transitions, the usual approach for supervised learning is to generate a data set $\big(H_1(k), W_1\big)$, ..., $\big(H_n(k), W_n\big)$ whose inputs are representations of Hamiltonians in wavevector space $H_i(k)$ and targets are their corresponding topological invariants $W_i$ (for the SSH model the topological invariant is the winding number).
-Our paper extends this task to the case of learning topological phase diagrams from input data in real space.
-Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-\textcolor{blue}{The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-The data-driven approach described in this article addresses these issues.
-In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems} \citequote{motif_real_space}
-
-%We develop here an alternative data-driven approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
-%\citequote{motif_real_space}
-
-To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
-The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
-
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired patterns in the data.
-This makes it much easier to trace the localization of relevant information along the features of a data set.
-Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the system as a whole emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
-To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-
-\textcolor{blue}{The topological signals recovered from the analysis of real space eigenvector data are then further theoretically explored as information entropy mass functions along the lattices in real space.
-By computing their Fourier transform, we retrieve similar information entropy mass functions in wavevector space.
-These two topological signals, the real space Shannon entropy mass function and its Fourier counterpart in  the reciprocal lattice, are knit together by entropic uncertainty relations.
-This allows us to establish the Bialynicki-Birula-Mycielski inequality as an uncertainty principle for the localizability of Shannon information entropy in topological phase transitions.}  \citequote{eigenvector_physics}, \citequote{physical_insights}
-
-The Shannon information entropy signals and the corresponding entropic uncertainty relations associated with topological phase transitions presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.\citequote{pipeline_not_work}
-
-\textcolor{blue}{As of yet model explainability\cite{https://ieeexplore.ieee.org/abstract/document/8631448?casa_token=ENOe4-VIc7kAAAAA:Tp8Aatj9Rx-9UcbOXtLbqNhG33nAt7_LEb-pG4-NC6wnQacmyRn0NqF4rrs2JGIDjgUgCNDLJaY, https://ieeexplore.ieee.org/abstract/document/8400040, https://ieeexplore.ieee.org/abstract/document/9007737} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines (this is also emphasized in \cite{https://arxiv.org/abs/1912.10057}).
-This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were already known.
-By proposing new concepts from the analysis of data from physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
-}\citequote{pipeline_not_work}
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh1.png}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh2.png}}
-\caption{Phase diagrams in parameter space.
-a) SSH model with first-neighbor hoppings $t_1$ and $t_2$.
-The (red) regions with winding number $W$ = 0 are trivial, while the (blue) regions with winding number $W$ = 1 are topologically non-trivial.
-b) SSH model with first ($t_1$ and $t_2$) and second ($T_1$ and $T_2$) nearest-neighbor hoppings.
-In this article we set $t_1$ = $t_2$ = 1 and renamed the variables $T_1$ $\rightarrow$ $t_1$, $T_2$ $\rightarrow$ $t_2$ for convenience.
-The (orange) region with winding number $W$ = 0 is trivial while the others with winding numbers $W$ = -1, $W$ = 1 and $W$ = 2 (red, green and blue respectively) are topologically non-trivial.}
-\label{fig:phasediagrams}
-\end{figure}
-
-\section{The eigenvector ensembling algorithm}\citequote{eigenvector_ensembling_alg}
-\label{the_eigenvector_ensembling_algorithm}
-\textcolor{blue}{
-The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-We describe here in detail each of these steps as they were implemented in this work.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our hopping parameters vector $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will provide $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$ to our data set.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}}
-
-\vspace{.3cm}
-\textcolor{blue}{Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
-The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
-The intuition that eigenvectors can be used in replacement to raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$, }
-\begin{equation}
-\label{eigen_decomposition}
-H = \sum_{i=1}^{N}\lambda^{(i)} \ket{\mathbf{v}^{(i)}}\bra{\mathbf{v}^{(i)}}
-\end{equation}
-where $\lambda^{(i)}$ \textcolor{blue}{is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
-It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
-By expressing the eigenvectors in a basis suitable to a particular problem (e.g.
-the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
-Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.}
-
-%\textcolor{blue}{In step 3) we used the implementations of decision trees and random forests from Python's scikit-learn module}\citequote{eigenvector_ensembling_alg}
-
-\section{Numerical experiments}
-\label{numerical_experiments}
-We performed two numerical experiments with the eigenvector ensembling algorithm.
-The first experiment deals with the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), while the second experiment uses the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
-
-In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
-The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
-
-This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the correct winding number values.
-Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
-The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
-
-\textcolor{blue}{As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
-These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.}\citequote{sufficient_accuracy} \citequote{evaluation_metrics}
-
-When generating the Hamiltonians we applied periodic boundary conditions to eliminate border effects.
-This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.
-The choice of periodic boundary conditions also implies that the information recovered from real space data comes from the bulk of the topological systems considered and therefore provides strong evidence for the existence of topological signatures in the bulk of such systems.
-
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
-The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-\textcolor{blue}{Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}-\ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1}-\ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number accross $n_{exp}$ = 100 experiments.
-The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps}.
-As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
-
-\textbf{blue}{The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit}.}
-
-\subsection{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-\label{experiment_1}
-Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
-These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
-
-The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (98.2\%), validation eigenvectors (96.4\%) and test eigenvectors (78.8\%).
-Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
-\textcolor{blue}{When compared with the baseline test accuracy of 55.2\% of a system that predicts the whole test set as having winding number $W=1$, the accuracy of 99.1\% on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.} \citequote{sufficient_accuracy}
-
-The probability heatmaps and phase diagram learned by the combination of decision trees with eigenvector ensembling used in experiment 1 are shown in figure \ref{ssh1_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
-\label{figexp1_exp}
-\end{figure}
-
-\subsection{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{experiment_2}
-
-This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 25 decision trees.
-Our data set consisted of 1040 (15.8\%) test Hamiltonians.
-The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving 2761 (42.1\%) training Hamiltonians and 2760 (42.1\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (17.9\%), $W$ = 0 (32.5\%), $W$ = 1 (32.3\%) and $W$ = 2 (17.3\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (36.3\%), $W$ = 0 (11.1\%), $W$ = 1 (12.7\%) and $W$ = 2 (39.9\%).
-
-Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.1\% for validation eigenvectors and 66.4\% for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 88.2\% for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from 66.4\% eigenvector accuracy to 88.2\% Hamiltonian accuracy) attests to its power.
-
-The probability heatmaps and phase diagram learned by the combination of random forests with eigenvector ensembling used in experiment 2 are shown in figure \ref{ssh2_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
-\label{figexp2_exp}
-\end{figure}
-
-\section{Information entropy signatures}
-\label{information_entropy_signatures}
-
-We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
-
-The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g.
-Shannon information entropy or Gini impurity \cite{friedman2001elements}).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
-These signals are the information entropy signatures of each topological phase transition.
-
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for each experiment.
-They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1 (section \ref{experiment_1}), only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-
-\textcolor{blue}{We should remark on the subtleties of the information entropy signatures presented here.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
-In the next section, where we develop a quantum formalism for the information entropy signatures discovered in this section, these seemingly antagonistic conceptions shall be harmonized.
-What is important to emphasize at this point is that the information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.}
-
-\textcolor{blue}{To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
-The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.}
-
-%Another important point to be emphasized is that these signals were recovered from the analysis of data from several thousand SSH systems in %each experiment and therefore they are not a property of a single SSH lattice.
-They are rather a pattern that emerges from correlating %topological winding numbers with lattice eigenvector data for several SSH systems.
-
-\textcolor{blue}{Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
-In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-%The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further %theoretical investigation.
-This is pursued in the next section.
-We present the information entropy signatures for longer lattices in the %section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran each experiment using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 (section \ref{experiment_1}) using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 (section \ref{experiment_2}) using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-\textcolor{blue}{In this sense, key topological information can be said to be localized on few sites in the lattice.}\citequote{key_top} We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(c) The phase diagram resulting from heatmaps (a) and (b).}
-\label{ssh1_heatmaps}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to -1.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(c) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(d) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 2.
-(e) The phase diagram resulting from heatmaps (a)-(d).}
-\label{ssh2_heatmaps}
-\end{figure}
-
-\section{Topological feature engineering and lattice compression}
-\label{topological_feature_engineering}
-
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from an information-theoretic perspective, in particular as related to data compression.
-As we have argued at the end of section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
-Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
-Here we show how the symmetries in the real space information entropy signatures in figure \ref{feature_importances} can be exploited to engineer new global topological features, leading to an effective compression of topological information.
-
-%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
-
-%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
-
-Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
-\begin{equation}
-\label{discrete_fourier_transform}
-\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
-\end{equation}
-Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
-The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
-\begin{equation}
-\label{hermitian_symmetry}
-\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
-\end{equation}
-where  we have used the notation $\overline{k} = k \mod N$.
-
-Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
-In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
-This leads us to the Discrete Cosine Transform (DCT) topological features,
-\begin{equation}
-\label{DCT}
-\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
-\end{equation}
-where $M = \frac{N}{2}+1$.
-The second path capitalizes on the fact that de imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
-\begin{equation}
-\label{DST}
-\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
-\end{equation} 
-where $M = \frac{N}{2}-1$.
-
-The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
-the sites $0 \leq j \leq \frac{N}{2}$.
-This is due to the fact that each equation assumes that the real space eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
-While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
-Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
-
-The topological feature engineering strategies described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
-As equations \eqref{DCT} and \eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
-
-We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
-The accuracy scores obtained in each experiment are listed in table \ref{numerical_results}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
-
-The lattice compression strategies tested in this work were: i) learning topological phases from only a subset of the real space lattice sites; ii) learning topological phases from the DCT or DST engineered features of equations; iii) learning topologcal phases from a fraction of the DCT or DST topological features and iv) learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
-
-In strategy \emph{i)} the lattice sites used in the SSH1 and SSH2 systems were
-\begin{equation}
-\label{lattice_subsets}
-\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
-\end{equation}
-Note that for the nearest-neighbor SSH system $\mathcal{S}_1$ correspond to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH system $\mathcal{S}_2$ correspond to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{numerical results}, the features used in strategy \emph{i)} are referred to as $X_{\mathcal{S}_1}$ and $X_{\mathcal{S}_2}$, according to the SSH system they relate to.
-
-In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
-These features are denoted in table \ref{numerical_results} by $\hat{X}^c_1$, $\hat{X}^s_1$, $\hat{X}^c_2$, $\hat{X}^s_2$ according to which set of topological features and SSH systems they refer to.
-
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH1 and SSH2 systems,
-\begin{equation}
-\label{DCT_subsets}
-\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
-\end{equation}
-and the DST topological features,
-\begin{equation}
-\label{DCT_subsets}
-\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
-\end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{O}_2}$ according to the topological features and wavevector sites used with each SSH system.
-
-The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
-It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
-Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
-Mathematically, we can expess the topological features used in strategy \emph{iv)} as follows:
-\begin{equation}
-\label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \mathbbm{1}_{\mathcal{S}}[0]x[0] + (-1)^n\mathbbm{1}_{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
-\end{equation}
-\begin{equation}
-\label{DST_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}.
-\end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[j]$ stands for the indicator function of the lattice subset $\mathcal{S}$, i.e.
-$\mathbbm{1}_{\mathcal{S}}[j] = 1$ if $j \in \mathcal{S}$ and $\mathbbm{1}_{\mathcal{S}}[j] = 0$ otherwise.
-The features engineered in strategy \emph{iv)} are denoted in table \ref{numerical_results} by $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$, $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$, $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$, $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$, again referencing the appropriate SSH systems, type of topological features used as well as which features in real and wavevector space were used to compute them.
-
-The lattice compression strategies  These numerical experiments differed both on which topological features were used (whether DCT or DST topological features), as well as which features in real space were used to compute the engineered topological features.
-The results obtained in the numerical experiments of section \ref{numerical_experiments} are also listed in table \ref{numerical_results} for the sake of reference.
-
-\begin{table}
- \begin{tabular}{||c c c c c c||} 
- \hline
-SSH     &Features                                      & Eigenvector val.    & Eigenvector test      & Hamiltonian val.    & Hamiltonian test \\ % [0.5ex] 
- \hline\hline
-        &                                              &                    &                 &                    &                      \\
-1       & $X_1$                                        & 0.964              & 0.790           & 1                  & 0.992                \\  
-\hline
-1       & $X_{\mathcal{S}_1}$                          & 0.944              & 0.776           & 0.985              & 0.990                \\
-\hline
-1       & $\hat{X}^c_1$                                & 0.952              & 0.737           & 0.998              & 0.992                \\
-\hline
-1       & $\hat{X}^c_{\mathcal{E}_1}$                  & 0.828              & 0.607           & 0.998              & 0.919                \\
-\hline
-1       & $\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$    & 0.944              & 0.818           & 0.985              & 0.993                \\
-\hline
-1       & $\hat{X}^s_1$                                & 0.953              & 0.731           & 0.991              & 0.986                \\
-\hline
-1       & $\hat{X}^s_{\mathcal{O}_1}$                  & 0.694              & 0.542           & 0.709              & 0.480                \\
-\hline
-1       & $\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$    & 0.946              & 0.782           & 0.985              & 0.940                \\
-\hline
-2       & $X_2$                                        & 0.971              & 0.663           & 0.997              & 0.880                \\  
-\hline
-2       & $X_{\mathcal{S}_2}$                          & 0.959              & 0.617           & 0.996              & 0.863                \\
-\hline
-2       & $\hat{X}^c_2$                                & 0.974              & 0.690           & 0.998              & 0.886                \\
-\hline
-2       & $\hat{X}^c_{\mathcal{E}_2}$                  & 0.899              & 0.536           & 0.995              & 0.790                \\
-\hline
-2       & $\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$    & 0.900              & 0.503           & 0.996              & 0.767                \\
-\hline
-2       & $\hat{X}^s_2$                                & 0.974              & 0.688           & 0.997              & 0.890                \\
-\hline
-2       & $\hat{X}^s_{\mathcal{O}_2}$                  & 0.904              & 0.553           & 0.992              & 0.743                \\
-\hline
-2       & $\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$    & 0.820              & 0.413           & 0.994              & 0.590                \\
-        &                                              &                    &                 &                    &                      \\
-\hline\hline
- \end{tabular}
-\caption{\label{numerical_results}Your caption.}
-\end{table}
-
-\textcolor{blue}{
-\section{Emergent information entropy wave functions}
-\label{emergent_information_entropy_wave_functions}
-}
-\textcolor{blue}{
-The information entropy signatures that we have seen in the previous section pose an immediate theoretical angst: how can a signal that is locally defined (information entropy signature) arise from a global property (topological invariant) of the whole SSH lattice?
-In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
-Our goal is to provide a theoretical framework to interpret the new concepts brought to light in the previous section.
-The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.}
-
-\textcolor{blue}{
-We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
-macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices.
-By mapping the lattice to a Riemann partition of the closed interval $[0,1]$, the cumulative distribution of topological information along a lattice will be given by}
-
-\begin{equation}
-\label{entropy_density}
-F_S(x) = \int_{0}^x\rho_S(x')dx'
-\end{equation}
-where $x \in [0,1]$ is a spatial coordinate along the continuous lattice (which we shall call from now on string, to emphasize its continuity as opposed to a discrete lattice) and $\rho_S(x)$ is the local Shannon information entropy density function in the continuum limit.
-
-\textcolor{blue}{
-Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial Shannon information entropy wave function,
-}
-\begin{equation}
-\label{shannon_wave_function}
-\rho_S(x) = |\psi_S(x)|^2,
-\end{equation}
-the amount of topological information available from a single point in the string then being expressed in bra-ket notation by Born's rule,
-
-\begin{equation}
-\label{born_rule_spatial}
-\rho_S(x) = |\braket{x|\psi_S}|^2.
-\end{equation}
-
-\textcolor{blue}{
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform }
-\begin{equation}
-\label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{0}^{1}\psi_S(x)e^{-2\pi ikx}dx
-\end{equation}
-\textcolor{blue}{
-from which the Shannon information entropy density function in wavevector space can be computed,}
-\begin{equation}
-\label{shannon_wave_function_wavevector_space}
-\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
-\end{equation}
-
-\textcolor{blue}{
-The interpretation of the information entropy signatures of the previous section in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
-Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{pipeline_not_work} We can think of several use cases for the eigenvector ensembling procedure outlined in the paper.
+Among these, we emphasize its applicability in dealing with the so-called "curse of dimensionality" that plagues many problems in condensed matter and statistical physics.
+In the paper, we have demonstrated an application in which the dimensionality of an SSH lattice can be greatly reduced in so far as its topological properties are concerned, simply by extracting the most relevant lattice sites in its information entropy signature.
+Similar feature extraction and dimensionality reduction procedures are often employed in machine learning applications and are surely to become the norm in data-driven physics.
+The eigenvector ensembling algorithm can thus be viewed as a general framework in this direction.
+Similarly, by thoughtfully attaching a probability distribution to the eigenvectors, we end up with a powerful sampling technique that may ultimately lead to great reduction in the dimensionality of a Monte Carlo simulation, while still capturing essentially all the relevant physics pertaining to the problem.
+We have added a paragraph to the section \textbf{VII.
+Discussion} outlining these possibilities.
+As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
+Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data and the Shannon information entropy signature and uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
+Topological feature engineering and lattice compression} and \textbf{VI.
+Emergent information entropy wave functions}.
+We have added a paragraph to the section \textbf{I.
+Introduction} emphasizing these new results.
 }
 
-\textcolor{blue}{
-Let us further denote the mean, the variance and the entropy of $\rho_S$ by $\bar{\rho}_S$, $\Delta \rho_S^2 $ and $H[\rho_S]$ respectively. Explicitly, we have }
-\begin{subequations}
-\label{statistics}
-\begin{equation}
-\label{mean}
-\bar{\rho}_S = \int_0^1x\rho_S(x)dx,
-\end{equation}
-\begin{equation}
-\label{variance}
-\Delta\rho_S^2 = \int_0^1(x-\bar{\rho}_S)^2\rho_S(x)dx,\quad \text{and}
-\end{equation}
-\begin{equation}
-\label{entropy}
-H[\rho_S] = \int_0^1\rho_S(x)\ln\big(\rho_S(x)\big) dx,
-\end{equation}
-\end{subequations}
-\textcolor{blue}{
-with analogous equations for the wavevector space counterparts $\bar{\hat{\rho}}_S$, $\Delta \hat{\rho}_S^2 $ and $H[\hat{\rho_S}]$ in terms of $k$ and $\hat{\rho}$.}
+\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
+This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
+We have added a paragraph to the section \textbf{III.
+Numerical experiments} to emphasize the use of this baseline.}
 
-\textcolor{blue}{
-In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}: }
+\textcolor{blue}{\citequote{superior_comparable} As to "high accuracy", we note that the accuracy scores obtained by us are comparable to the highest scores reported in Phys.
+Rev.
+Lett.
+120, 066401, where neural networks were trained on wavevector space data in a similar supervised learning task.
+This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
+In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+Rev.
+Research 2, 023283,  whose theme is model interpretability of single-layer feedforward neural networks trained to recognize phase transitions of some topological condensed matter systems.
+When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
 
-\begin{enumerate}
-\item[i)] \emph{the Heisenberg uncertainty principle}
-\begin{equation}
-\label{heisenberg}
-\Delta\rho_S \cdot \Delta\hat{\rho}_S \geq \frac{1}{4\pi}, \quad \text{and }
-\end{equation}
-\item[ii)] \emph{the Hirschman entropic uncertainty}
-\begin{equation}
-\label{hirschman}
-H[\rho_S] + H[\hat{\rho}_S] \geq \ln\Big(\frac{e}{2}\Big). \quad
-\end{equation}
-\end{enumerate}
+\textcolor{blue}{\citequote{motif_real_space} We agree that the motivations for a data-driven approach based on real space should be in the Introduction.
+We have therefore moved the first paragraph of the section \textbf{Learning topological phases from real space data} in the \textbf{Supplementary Material} that addresses this issue to the section \textbf{I.
+Introduction} in the main paper.}
 
-\textcolor{blue}{
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures discovered in the previous section from sheer data analysis of finite SSH systems in real space.
-In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
+\vspace{0.5cm}
+\emph{I am not sure which crucial problems their algorithm can solve that was not possible before with machine learning.
+Furthermore, along with the emerging research of unsupervised learning methods in realizing the topological phases, \textbf{why should the supervised learning method be focused in this context?}\genquote{unsupervised_learning} In the present stage of this manuscript, where I do not see the proposal's advantages, I would prefer the \textbf{unsupervised approaches that could grasp information from a given system without knowing their phases}\genquote{unsupervised_approaches}.
+In my opinion, a proper intrinsic route for understanding physical systems without much information on
+the dynamics of the system will lead to significant future developments and a better understanding of physic systems.}
+
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
+We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of information entropy as loss function provides a clear way to measure feature importance.
+This is compounded by the fact that information entropy plays a very important role in information theory and physics, as is evidenced in the new section \textbf{VI.
+Emergent information entropy wave functions} added to this new version of the article.}
+
+\textcolor{blue}{\citequote{unsupervised_approaches} The new section \textbf{V.
+Topological feature engineering and lattice compression} shows how unsupervised learning can be performed with eigenvector ensembling using tree based methods as learning algorithms.
+In fact, two of the main tasks under the broad umbrella of unsupervised learning are exactly those: dimensionality reduction and feature engineering.
+Furthermore, it should be noted that the eigenvector ensembling algorithm can equally be combined with unsupervised learning algorithms as well.
+This point is now explicitly mentioned in this new version of the paper, in a new paragraph added to the section \textbf{VII.
+Discussion}.
+Finally, as we mentioned in our reply to \citequote{pipeline_not_work}, our procedure can be used as a powerful dimensionality reduction tool in other, unrelated data-driven or numerical physics tasks, which by itself is another example of unsupervised learning and can serve as a preprocessing step to further applications of machine learning to physics.}
+
+\vspace{0.5cm}
+\emph{The details of \textbf{the eigenvector ensembling algorithm should be addressed in the main text}\genquote{eigenvector_ensembling_alg} instead of supplemental material.
+What is the specific algorithm used in the paper to train on eigenvectors?
+I think it is important even if the readers are not familiar with some ML techniques.
+Some readers in physics may find it difficult to understand some ML technical terms such as bootstrapping, training and validation, test sets, etc.
+In addition, \textbf{I expect proof of what "physics" their method captures and why the eigenvector can play an important role in characterizing the topological phase}\genquote{eigenvector_physics}.
+If this physical interpretability is not mentioned, it is very difficult to see the contribution of the method in physics.}
+
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{eigenvector_ensembling_alg}  The section \textbf{II.
+The eigenvector ensembling algorithm} has been moved from the Supplementary Material to the main paper.
+The issue of specifying the particular learning algorithms used to train on eigenvectors is addressed in the subsections for each SSH experiment (see subsections \textbf{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees} and \textbf{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}).
+In these subsections, we explicitly cite the papers by Breiman \emph{et al.} that were relevant to the implementation of decision trees and random forests in the Python scikit-learn module used to run the numerical experiments in the paper.}
+
+\textcolor{blue}{\citequote{eigenvector_physics} As we argue in a paragraph added to the new section \textbf{II.
+The eigenvector ensembling algorithm},  all information from a Hamiltonian can be recovered from its eigendecomposition.
+Therefore, by expressing a data set of eigenvectors on a suitable choice of basis (which in this paper is the real space basis), we are able to investigate properties of a family of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
+Thus the use of eigenvectors greatly facilitates the exploration of model explainability techniques in data-driven physics applications while at the same time not leading to a loss of information from the systems being investigated.
+As to the physics being captured by our procedure, see the answer to the issue \citequote{physical_insights}.}
+
+%While there may surely be other ways to achieve a similar result, using eigenvectors as input data is fairly straightforward and, as we have %demonstrated, as we have demonstrated tage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian %encode all the physical information of the particular system in terms of local components in real space.
+In fact, the use of eigenvectors %play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
+In the majority of %the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses %track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
+The paper paves the way for new theoretical %investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
+%In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy %signature and its corresponding entropic uncertainty relation for topological phase transitions in SSH systems.
 }
 
-\textcolor{blue}{
-Another interesting consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D continuous string is that is reconciles the apparently conflicting notions of a local topological signal arising from a global property of the whole SSH system.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of a many-particle system.
-Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
-}
+\vspace{0.5cm}
+\emph{The authors made efforts to analyze how the algorithm was able to recover the Hamiltonians' global property in the "Information Entropy
+Signatures" section. The authors state that learning topological phases from local real-space data in bulk is still possible even for
+small subsets of lattice sites, then refer us to the section "Learning topological phases from real space data" in the Supplementary
+Material.
+The authors mention on page 4 of the Supplementary Material that \textbf{"key topological information can be said to be localized on a few lattice sites," which is a particularly interesting statement to me}\genquote{key_top}.
+However, \textbf{I fail to understand the physical insights behind it}\genquote{physical_insights}.
+Without the proper explanation, it is difficult to see the effectiveness of
+their method or verify the method with a more complex model instead of the simple SSH form.}
 
-\textcolor{blue}{
-Given that our analysis has now come full circle back to theoretical physics, the task of numerically exploring equations \eqref{entropy_density}-\eqref{hirschman} will be left for the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-}
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{key_top} We agree that this sentence greatly synthesizes the results presented in the paper about the possibility of localizing topological information in SSH lattices.
+We have therefore moved it to the final patragraph of the section \textbf{V.
+Topological feature engineering and lattice compression} in the main text.}
 
-\section{Discussion}
-\label{discussion}
+\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), iii) generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
+Topological feature engineering and lattice compression},  and finally iv) interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
+Emergent information entropy wave functions}, in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinite lattice.}
 
-Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
+\textcolor{blue}{It is noteworthy that the majority of physics papers published to date on the use of machine learning in the investigation of condensed matter systems have been proofs of concept aimed at showing that the machine learning algorithms that have become ubiquitously famous during the last decade indeed are able to recognize the relevant patterns associated with previously known physical phenomena.
+Our paper goes beyond this task as we use machine learning and model explainability to discover new properties from the analysis of data from the physical systems under consideration and (with the addition of the new section \textbf{VI.
+Emergent information entropy wave functions}) map these previously unknown properties into new theoretical  constructs.}
 
-\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching in to both disciplines.
-}
+\subsection*{Minor}
 
-The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to wavevector space methods.
+\emph{The authors state in the abstract that "model explainability in machine learning can advance the research of exotic quantum materials
+with properties that may power future technological applications such as qubit engineering for quantum computing." \textbf{Could you explain a bit more about properties that may power future quantum computing?}\genquote{quantum_comp}}
 
-As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
-This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment and led us to the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
 
-\textcolor{blue}{The accuracy scores obtained in the numerical experiments of section \ref{numerical_experiments} were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.}\citequote{superior_comparable}
+\vspace{0.5cm}
+\emph{On page 4, the authors state that "Figures 2 and 3 illustrate single iterations of experiments 1 and 2 as seen from parameter space".
+\textbf{What are the experiments 1 and 2?}\genquote{experiments_1_2}}
 
-\textcolor{blue}{This paper should also be contrasted with \cite{ml_interpretability}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
-In \cite{ml_interpretability}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
-We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
-In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.}\citequote{superior_comparable}
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{experiments_1_2} We have added references to the relevant subsections whenever each numerical experiment is mentioned outside of its subsection throughout the text.
+The designation "experiment 1" is used to abbreviate the subsection \textbf{III.A Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}.
+Similarly, the designation "experiment 2" is used to abbreviate the subsection \textbf{III.B Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}.}
 
-Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the theoretical interpretation of the topological signals shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} in terms of Shannon information entropy, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
-Whether there is any relationship between the local topological markers detailed in \cite{PhysRevB.84.241106,caio2019topological} and the information entropy of the ensemble of eigenvectors discussed here is left for speculation.
+\vspace{0.5cm}
+\emph{\textbf{The authors should explain the evaluation metric in the main text}\genquote{evaluation_metrics},
+such as "the accuracy" and "the probability heatmap," "eigenvector accuracy," and "Hamiltonian accuracy."}
 
-\textcolor{blue}{By starting from eigenvector data generated from the simulation of SSH systems in real space, passing through proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the theoretical possibilities posed by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between the two disciplines can be enriching in both ways.
-}
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{evaluation_metrics} We have added more detailed explanations about the evaluation metrics and probability heatmaps to the section \textbf{III.
+Numerical experiments}.
+Furthermore, the new section \textbf{V.
+Topological feature engineering and lattice compression} contains a summary of accuracy scores obtained in all numerical experiments performed in the paper.}
 
-The eigenvector ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
-This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
+\vspace{0.5cm}
+\emph{I prefer to \textbf{put the definition of information entropy signatures in the main}\genquote{inf_entropy_sig} text to help the readers understand what the method tries to do.}
 
-\textcolor{blue}{As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
-This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
-An approach based on eigenvector ensembling can be of use in such situations both as a dimensionality reduction tool and as a sampling strategy.
-The first case was illustrated in this work, where it was shown that relevant topological information of SSH systems can be retrieved from few sites in a lattice, which can be exploited as a dimensionality reduction strategy.
-The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in the dimensionality of a problem while still capturing all the relevant physics of a system.}\citequote{pipeline_not_work}  We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
-
-\textcolor{blue}{Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
-In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
-This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.}\citequote{unsupervised_learning}
-
-One final comment should be made about the flourishing relationship between physics and machine learning.
-In this work we have demonstrated how a machine learning approach can provide new insights into complex physical phenomena of current interest.
-The other direction of this relationship (physics enhancing understanding in machine learning) is equally important.
-As the need for ever more powerful machine learning algorithms continues to grow, the development of mathematical frameworks for understanding general data spaces (i.e., a physics of data) will be of crucial relevance.
-This pursuit is seen in many theoretical works investigating the intriguing connections between geometry, topology and data \cite{carlsson2009topology}$^-$\cite{belkin2003problems}.
-The detailed study of data generated by physical models with non-trivial geometrical and topological properties such as the SSH model may provide invaluable insights into the structure and shape of real world high-dimensional data, since these models usually underscore well known mathematical frameworks behind the data generating process, a feature that is often absent from machine learning applications.
-Thus, far from being restricted to applications in physics, the study of the topological and geometrical properties of data sets generated by physical models will also be of great value to the machine learning and artificial intelligence communities.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located along lattice sites $S_2$.}
-\label{feature_importances}
-\end{figure}
-
-%\begin{figure}
-%\centering
-%\subfigure[]{\label{fourier_feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
-%\subfigure[]{\label{fourier_feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/%plot_fourier_feature_importances.png}}\quad
-%\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section %%\ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for %approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located %along lattice sites $S_2$.}
-%\label{fourier_feature_importances}
-%\end{figure}
-
-\citequote{motif_real_space}
-
-%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{56}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Hasan}\ and\ \citenamefont
-  {Kane}(2010)}]{RevModPhys.82.3045}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
-  {Hasan}}\ and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
-  {Kane}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {3045}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Continentino}(2017)}]{CONTINENTINO2017A1}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physica B: Condensed Matter}\ }\textbf {\bibinfo {volume} {505}},\ \bibinfo
-  {pages} {A1 } (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Puel}\ \emph {et~al.}(2017)\citenamefont {Puel},
-  \citenamefont {Sacramento},\ and\ \citenamefont
-  {Continentino}}]{PhysRevB.95.094509}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~O.}\ \bibnamefont
-  {Puel}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
-  {Sacramento}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {094509}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Griffith}\ and\ \citenamefont
-  {Continentino}(2018)}]{PhysRevE.97.012107}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Griffith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {012107}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ryu}\ \emph {et~al.}(2010)\citenamefont {Ryu},
-  \citenamefont {Schnyder}, \citenamefont {Furusaki},\ and\ \citenamefont
-  {Ludwig}}]{ryu2010topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Ryu}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont {Schnyder}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Furusaki}}, \ and\
-  \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont {Ludwig}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {New Journal of
-  Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {065010}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Atala}\ \emph {et~al.}(2013)\citenamefont {Atala},
-  \citenamefont {Aidelsburger}, \citenamefont {Barreiro}, \citenamefont
-  {Abanin}, \citenamefont {Kitagawa}, \citenamefont {Demler},\ and\
-  \citenamefont {Bloch}}]{atala2013direct}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Atala}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Aidelsburger}},
-  \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont {Barreiro}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Abanin}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Kitagawa}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Bloch}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {9}},\ \bibinfo {pages} {795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stuhl}\ \emph {et~al.}(2015)\citenamefont {Stuhl},
-  \citenamefont {Lu}, \citenamefont {Aycock}, \citenamefont {Genkina},\ and\
-  \citenamefont {Spielman}}]{Stuhl1514}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~K.}\ \bibnamefont
-  {Stuhl}}, \bibinfo {author} {\bibfnamefont {H.-I.}\ \bibnamefont {Lu}},
-  \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont {Aycock}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Genkina}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {I.~B.}\ \bibnamefont {Spielman}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {349}},\ \bibinfo {pages} {1514} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Leder}\ \emph {et~al.}(2016)\citenamefont {Leder},
-  \citenamefont {Grossert}, \citenamefont {Sitta}, \citenamefont {Genske},
-  \citenamefont {Rosch},\ and\ \citenamefont {Weitz}}]{leder2016real}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Leder}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Grossert}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sitta}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Genske}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Rosch}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {13112} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goldman}\ \emph {et~al.}(2016)\citenamefont
-  {Goldman}, \citenamefont {Budich},\ and\ \citenamefont
-  {Zoller}}]{goldman2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Goldman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Budich}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
-  }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {639} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Meier}\ \emph {et~al.}(2016)\citenamefont {Meier},
-  \citenamefont {An},\ and\ \citenamefont {Gadway}}]{meier2016observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
-  {Meier}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {An}}, \
-  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  communications}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {13986}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hafezi}\ \emph {et~al.}(2013)\citenamefont {Hafezi},
-  \citenamefont {Mittal}, \citenamefont {Fan}, \citenamefont {Migdall},\ and\
-  \citenamefont {Taylor}}]{hafezi2013imaging}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hafezi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mittal}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Fan}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Migdall}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Taylor}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Photonics}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {1001} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Lu}\ \emph {et~al.}(2016)\citenamefont {Lu},
-  \citenamefont {Joannopoulos},\ and\ \citenamefont
-  {Solja{\v{c}}i{\'c}}}]{lu2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Lu}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
-  {Joannopoulos}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Solja{\v{c}}i{\'c}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-  {pages} {626} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Peano}\ \emph {et~al.}(2015)\citenamefont {Peano},
-  \citenamefont {Brendel}, \citenamefont {Schmidt},\ and\ \citenamefont
-  {Marquardt}}]{PhysRevX.5.031011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Peano}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Brendel}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Schmidt}}, \ and\
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marquardt}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {5}},\ \bibinfo {pages} {031011} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2012)\citenamefont
-  {Kitagawa}, \citenamefont {Broome}, \citenamefont {Fedrizzi}, \citenamefont
-  {Rudner}, \citenamefont {Berg}, \citenamefont {Kassal}, \citenamefont
-  {Aspuru-Guzik}, \citenamefont {Demler},\ and\ \citenamefont
-  {White}}]{kitagawa2012observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Broome}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Fedrizzi}},
-  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Kassal}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~G.}\
-  \bibnamefont {White}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature communications}\ }\textbf {\bibinfo {volume} {3}},\
-  \bibinfo {pages} {882} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cardano}\ \emph {et~al.}(2016)\citenamefont
-  {Cardano}, \citenamefont {Maffei}, \citenamefont {Massa}, \citenamefont
-  {Piccirillo}, \citenamefont {De~Lisio}, \citenamefont {De~Filippis},
-  \citenamefont {Cataudella}, \citenamefont {Santamato},\ and\ \citenamefont
-  {Marrucci}}]{cardano2016statistical}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Cardano}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maffei}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Massa}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Piccirillo}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {De~Lisio}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {De~Filippis}}, \bibinfo {author}
-  {\bibfnamefont {V.}~\bibnamefont {Cataudella}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Santamato}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {Marrucci}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {11439} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Flurin}\ \emph {et~al.}(2017)\citenamefont {Flurin},
-  \citenamefont {Ramasesh}, \citenamefont {Hacohen-Gourgy}, \citenamefont
-  {Martin}, \citenamefont {Yao},\ and\ \citenamefont
-  {Siddiqi}}]{PhysRevX.7.031023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Flurin}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
-  {Ramasesh}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Hacohen-Gourgy}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
-  {Martin}}, \bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont {Yao}}, \
-  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Siddiqi}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {031023} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Soluyanov}\ \emph {et~al.}(2015)\citenamefont
-  {Soluyanov}, \citenamefont {Gresch}, \citenamefont {Wang}, \citenamefont
-  {Wu}, \citenamefont {Troyer}, \citenamefont {Dai},\ and\ \citenamefont
-  {Bernevig}}]{soluyanov2015type}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-  {Soluyanov}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gresch}},
-  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {Q.}~\bibnamefont {Wu}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Troyer}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \ and\ \bibinfo {author} {\bibfnamefont {B.~A.}\
-  \bibnamefont {Bernevig}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {527}},\ \bibinfo {pages}
-  {495} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lv}\ \emph {et~al.}(2015)\citenamefont {Lv},
-  \citenamefont {Weng}, \citenamefont {Fu}, \citenamefont {Wang}, \citenamefont
-  {Miao}, \citenamefont {Ma}, \citenamefont {Richard}, \citenamefont {Huang},
-  \citenamefont {Zhao}, \citenamefont {Chen}, \citenamefont {Fang},
-  \citenamefont {Dai}, \citenamefont {Qian},\ and\ \citenamefont
-  {Ding}}]{PhysRevX.5.031013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~Q.}\ \bibnamefont
-  {Lv}}, \bibinfo {author} {\bibfnamefont {H.~M.}\ \bibnamefont {Weng}},
-  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Fu}}, \bibinfo
-  {author} {\bibfnamefont {X.~P.}\ \bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Miao}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ma}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Richard}}, \bibinfo {author} {\bibfnamefont {X.~C.}\ \bibnamefont {Huang}},
-  \bibinfo {author} {\bibfnamefont {L.~X.}\ \bibnamefont {Zhao}}, \bibinfo
-  {author} {\bibfnamefont {G.~F.}\ \bibnamefont {Chen}}, \bibinfo {author}
-  {\bibfnamefont {Z.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Qian}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {031013} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Su}\ \emph {et~al.}(1979)\citenamefont {Su},
-  \citenamefont {Schrieffer},\ and\ \citenamefont
-  {Heeger}}]{PhysRevLett.42.1698}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~P.}\ \bibnamefont
-  {Su}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Schrieffer}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Heeger}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1698} (\bibinfo {year}
-  {1979})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},
-  \citenamefont {Dauphin}, \citenamefont {Cardano}, \citenamefont
-  {Lewenstein},\ and\ \citenamefont {Massignan}}]{maffei2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Maffei}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Cardano}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Massignan}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
-  {\bibinfo {volume} {20}},\ \bibinfo {pages} {013023} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heeger}(2001)}]{RevModPhys.73.681}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Heeger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {681}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kane}\ and\ \citenamefont
-  {Lubensky}(2014)}]{kane2014topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Kane}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lubensky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {39}
-  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
-  \citenamefont {Upadhyaya},\ and\ \citenamefont {Vitelli}}]{Chen13004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.-g.}\
-  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Upadhyaya}}, \ and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Vitelli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
-  {volume} {111}},\ \bibinfo {pages} {13004} (\bibinfo {year}
-  {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carrasquilla}\ and\ \citenamefont
-  {Melko}(2017)}]{carrasquilla2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}\ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {431}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ch'ng}\ \emph {et~al.}(2017)\citenamefont {Ch'ng},
-  \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\ \citenamefont
-  {Khatami}}]{PhysRevX.7.031038}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ch'ng}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Carrasquilla}},
-  \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \ and\
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Khatami}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {7}},\ \bibinfo {pages} {031038} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wang}(2016)}]{PhysRevB.94.195105}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wang}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {195105}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Broecker}\ \emph {et~al.}(2017)\citenamefont
-  {Broecker}, \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\
-  \citenamefont {Trebst}}]{broecker2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Broecker}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}}, \ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Trebst}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Scientific reports}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
-  {8823} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Van~Nieuwenburg}\ \emph {et~al.}(2017)\citenamefont
-  {Van~Nieuwenburg}, \citenamefont {Liu},\ and\ \citenamefont
-  {Huber}}]{van2017learning}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
-  {Van~Nieuwenburg}}, \bibinfo {author} {\bibfnamefont {Y.-H.}\ \bibnamefont
-  {Liu}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
-  {Huber}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {435}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2018)\citenamefont {Zhang},
-  \citenamefont {Shen},\ and\ \citenamefont {Zhai}}]{PhysRevLett.120.066401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {120}},\ \bibinfo {pages} {066401} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
-  \citenamefont {Yi}, \citenamefont {Zhang}, \citenamefont {Shen},\ and\
-  \citenamefont {Zhai}}]{PhysRevB.98.085402}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Yi}}, \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Zhang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {98}},\ \bibinfo {pages} {085402} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Suchsland}\ and\ \citenamefont
-  {Wessel}(2018)}]{PhysRevB.97.174435}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Suchsland}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Wessel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {174435}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont
-  {Kim}(2017)}]{PhysRevLett.118.216401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont
-  {Kim}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. Lett.}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {216401}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Venderley}\ \emph {et~al.}(2018)\citenamefont
-  {Venderley}, \citenamefont {Khemani},\ and\ \citenamefont
-  {Kim}}]{PhysRevLett.120.257204}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Venderley}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Khemani}},
-  \ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {120}},\ \bibinfo {pages} {257204} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ohtsuki}\ and\ \citenamefont
-  {Ohtsuki}(2017)}]{ohtsuki2017deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo {volume}
-  {86}},\ \bibinfo {pages} {044708} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Yoshioka}\ \emph {et~al.}(2018)\citenamefont
-  {Yoshioka}, \citenamefont {Akagi},\ and\ \citenamefont
-  {Katsura}}]{PhysRevB.97.205110}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Yoshioka}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Akagi}}, \
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Katsura}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {205110} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2017)\citenamefont {Deng},
-  \citenamefont {Li},\ and\ \citenamefont {Das~Sarma}}]{PhysRevB.96.195145}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.-L.}\ \bibnamefont
-  {Deng}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}}, \ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf
-  {\bibinfo {volume} {96}},\ \bibinfo {pages} {195145} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huembeli}\ \emph {et~al.}(2018)\citenamefont
-  {Huembeli}, \citenamefont {Dauphin},\ and\ \citenamefont
-  {Wittek}}]{PhysRevB.97.134109}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Huembeli}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wittek}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {134109} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carvalho}\ \emph {et~al.}(2018)\citenamefont
-  {Carvalho}, \citenamefont {Garc\'{\i}a-Mart\'{\i}nez}, \citenamefont {Lado},\
-  and\ \citenamefont {Fern\'andez-Rossier}}]{PhysRevB.97.115453}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Carvalho}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
-  {Garc\'{\i}a-Mart\'{\i}nez}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
-  \bibnamefont {Lado}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Fern\'andez-Rossier}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {97}},\ \bibinfo {pages} {115453} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2017)\citenamefont {Zhang},
-  \citenamefont {Melko},\ and\ \citenamefont {Kim}}]{PhysRevB.96.245119}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \
-  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {245119} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rodriguez-Nieva}\ and\ \citenamefont
-  {Scheurer}(2018)}]{rodriguez2018identifying}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
-  {Rodriguez-Nieva}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\
-  \bibnamefont {Scheurer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {arXiv preprint arXiv:1805.05961}\ } (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
-  {Breiman}, \citenamefont {Friedman}, \citenamefont {Stone},\ and\
-  \citenamefont {Olshen}}]{breiman2017classification}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},
-  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Stone}}, \ and\
-  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Olshen}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Classification and regression
-  trees}}}\ (\bibinfo  {publisher} {Chapman and Hall/CRC, London, UK},\
-  \bibinfo {year} {1984})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}(2001)}]{Breiman2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Machine Learning}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {5}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
-  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
-  {Tibshirani}}]{friedman2001elements}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
-  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
-  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
-  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
-  {year} {2001})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
-  {Resta}(2011)}]{PhysRevB.84.241106}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Bianco}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Resta}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {241106} (\bibinfo
-  {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Caio}\ \emph {et~al.}(2019)\citenamefont {Caio},
-  \citenamefont {M{\"o}ller}, \citenamefont {Cooper},\ and\ \citenamefont
-  {Bhaseen}}]{caio2019topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
-  {Caio}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {M{\"o}ller}},
-  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Cooper}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bhaseen}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ ,\ \bibinfo
-  {pages} {1}} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carlsson}(2009)}]{carlsson2009topology}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Carlsson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Bulletin of the American Mathematical Society}\ }\textbf {\bibinfo {volume}
-  {46}},\ \bibinfo {pages} {255} (\bibinfo {year} {2009})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wasserman}(2018)}]{wasserman2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wasserman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Annual Review of Statistics and Its Application}\ }\textbf {\bibinfo
-  {volume} {5}},\ \bibinfo {pages} {501} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2005)\citenamefont {Wang},
-  \citenamefont {Zhang},\ and\ \citenamefont {Zha}}]{wang2005adaptive}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\ }in\ \href@noop
-  {} {\emph {\bibinfo {booktitle} {Advances in neural information processing
-  systems}}}\ (\bibinfo {year} {2005})\ pp.\ \bibinfo {pages}
-  {1473--1480}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lin}\ and\ \citenamefont
-  {Zha}(2008)}]{lin2008riemannian}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lin}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Transactions
-  on Pattern Analysis and Machine Intelligence}\ }\textbf {\bibinfo {volume}
-  {30}},\ \bibinfo {pages} {796} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Belkin}(2003)}]{belkin2003problems}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Belkin}},\ }\href@noop {} {\emph {\bibinfo {title} {Problems of learning on
-  manifolds}}}\ (\bibinfo  {publisher} {The University of Chicago, Chicago, IL,
-  USA},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
-  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
-  {P{\'a}lyi}}]{asboth2016short}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
-  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}} (\bibinfo
-  {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
-  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
-  {Courville}}]{goodfellow2016deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
-  {publisher} {MIT press, Cambridge, MA, USA},\ \bibinfo {year}
-  {2016})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
-  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
-  machine learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\
-  \bibinfo {year} {2006})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
-  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
-  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
-  {Mitter}(2010)}]{narayanan2010sample}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
-  Neural Information Processing Systems}}}\ (\bibinfo {year} {2010})\ pp.\
-  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
-  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
-  and\ \citenamefont {Muller}}]{rifai2011manifold}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
-  {\bibinfo {booktitle} {Advances in Neural Information Processing Systems}}}\
-  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
-  {NoStop}%
-\end{thebibliography}%
-
-\section*{Acknowledgements}
-
-We thank S.
-E.
-Rowley, J.
-F.
-de Oliveira, T.
-Micklitz and M.
-A.
-Continentino for insightful discussions and S.
-E.
-Rowley for carefully reading the manuscript and suggesting improvements.
-N.
-L.
-Holanda acknowledges financial support from CENPES/Petrobr\'as/CBPF.
-M.
-A.
-R.
-Griffith acknowledges financial support from Capes.
-N.
-L.
-Holanda is grateful to the Theory of Condensed Matter and Quantum Materials groups at the Cavendish Laboratory and the Quantum Information Group at CBPF.
-
-\section*{Author contributions}
-
-Both authors of this work contributed equally to its realization at all stages.
-
-\section*{Competing financial interests}
-
-The authors declare no competing financial or non-financial interests.
-
-\section*{Additional information}
-
-Correspondence and requests for materials should be addressed to N.
-L.
-Holanda.
-The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
-
-\end{document}
+\vspace{0.25cm}
+\textcolor{blue}{\citequote{inf_entropy_sig} The definition of information entropy signatures is included in the new section \textbf{VI.
+Emergent information entropy wave functions}, where an extended theoretical interpretation of the results obtained with the eigenvector ensembling algorithm is also presented.}

### 2020-07-24 10_prb_resubmission_01/02_reply_referee/letter_referee.tex
Possible version to be resubmitted to prb

--- 2020-07-24 10_prb_resubmission_01/02_letter_referee/letter_referee.tex
@@
 
-\section*{Reply to the editor}
-
-Dear editor,
-
-we appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900).
-We have fully addressed the issues pointed by referee 2, which have led to a much improved version of the paper, hopefully the definitive version.
-
-In what follows, we briefly summarize the modifications made to the paper.
-New results have been added to the paper in the form of two new sections: \textbf{V.
-Topological feature engineering and lattice compression} and \textbf{VI.
-Emergent information entropy wave functions}.
-We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II.
-The eigenvector ensembling algorithm}.
-The section \textbf{VII.
-Discussion} has been extended to address the issues that were raised.
-The sections are now numbered for clarity.
-
-A more comprehensive account of these changes can be found in the reply to the second referee.
-
-Best regards,
-
-N.L. Holanda and M. A. S. Griffith.
-
-\section*{Reply to the first referee}
-Dear referee,
-
-we appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}.
-We are currently cleaning, pruning and documenting our code, so we expect to put the Python code used to run the numerical experiments described in the paper online as soon as possible.
-
 \section*{Reply to the second referee}
@@
 
-we appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with.
+we appreciate the valuable insights on how to improve our article that you have provided us with.
 These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical contents.
 
-A summary of the modifications made to the paper are listed in what follows.
+In what follows, we briefly summarize the modifications made to the paper.
 New results have been added to the paper in the form of two new sections: \textbf{V.
@@
 As for the novelty of the method, the article binds together contemporary concepts in physics (topological states of matter and information theory) to a leading research theme in machine learning (model explainability).
-Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data, the Shannon information entropy signature and finally its quantum interpretation as an emergent wave function, leading to the establishment of the uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
+Our work pioneers the use of model explainability in the discovery of new concepts in physics, namely, the engineering of new topological features from real space data and the Shannon information entropy signature and uncertainty relations for topological phase transitions presented here for the first time in the new sections \textbf{V.
 Topological feature engineering and lattice compression} and \textbf{VI.
@@
 
-\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs consistently better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
+\textcolor{blue}{\citequote{sufficient_accuracy} We use the term "sufficient accuracy" to denote a system that performs considerably better at predicting the phases of Hamiltonians than the baseline system that simply guesses the most frequently occurring class for all Hamiltonians.
 This gauge is needed because it ensures that the resulting entropy signatures are meaningful in the sense that they encode a summary of where useful information about the topological phase of a system can be found.
@@
 This second gauge further reinforces that the entropy signatures presented in the article indeed express a realistic summary of the availability of topological information from each lattice site.
-A small paragraph was added to the section \textbf{VII.
-Discussion} to explicitly note this point.
-In another paragraph added to the section \textbf{VII.
-Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
+A small paragraph was added to the section \textbf{Discussion} to explicitly note this point.
+In another paragraph added to the section \textbf{Discussion}, we further draw comparisons between our paper and the just recently published article Phys.
 Rev.
@@
 When contrasting our paper to the latter, we emphasize the important distinction between "model interpretability" and "model explainability".
-While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-\`{a}-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
+While both techniques rely on model introspection, the first is aimed at interpreting the model itself vis-à-vis previously known concepts and properties related to the physics underlying the data set, while in the latter the goal is to use these model introspection tools to arrive at new concepts and ideas about the physical phenomena underlying the data set, which is the main purpose of our work.}
 
@@
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{unsupervised_learning} One of our main goals in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
+\textcolor{blue}{\citequote{unsupervised_learning} Our main goal in the article is to investigate the distribution of topological information along lattices of SSH systems via model explainability tools in machine learning.
 We developed a pipeline that accomplishes this task in a very straightforward way by performing supervised learning with decision tree-based algorithms, since their use of information entropy as loss function provides a clear way to measure feature importance.
@@
 
-\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we \emph{i)} propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), \emph{ii)} use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), \emph{iii)} generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
-Topological feature engineering and lattice compression},  and finally \emph{iv)} interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
+\textcolor{blue}{\citequote{physical_insights} The upgraded version of the paper now performs a full cycle of data-driven physics, as we i) propose a method to investigate topological phase transitions using real space eigenvector data from simulations of SSH systems (the eigenvector ensembling algorithm), ii) use model explainability to extract new, previously unknown properties of the finite SSH systems (the information entropy signatures), iii) generate new topological features from real space data using the insights gained from the information entropy signatures in the added section \textbf{V.
+Topological feature engineering and lattice compression},  and finally iv) interpret these new properties in the light of theoretical physics in the added section \textbf{VI.
 Emergent information entropy wave functions}, in which we interpret the information entropy signature as a probability distribution arising from an emergent information entropy wave function in the continuum limit of an infinite lattice.}
@@
 \vspace{0.25cm}
-\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{VII.
-Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
+\textcolor{blue}{\citequote{quantum_comp} We have added a paragraph to the section \textbf{Discussion} where we comment on the importance of information-theoretic methods to the design of prospective quantum technologies like topological qubits and quantum communication.}
 

### 2020-07-25 08_arxiv/article.tex
Generated new arxiv submission

--- 2020-07-24 07_paper/00_article/article.tex
@@
 
-\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining figures directory
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article
+%%% phase diagrams (figure 1)
+\newcommand\phaseDiagramsFigs{./00_article/phase_diagrams/}
+\newcommand\SSHOnePhaseDiagram{\phaseDiagramsFigs ssh1.png}
+\newcommand\SSHTwoPhaseDiagram{\phaseDiagramsFigs ssh2.png}
+%%% ssh1 experiments (figure 2)
+\newcommand\SSHOneExperimentsFigs{./00_article/ssh1/real_space_all_sites/}
+\newcommand\SSHOneTrainValTestSplit{\SSHOneExperimentsFigs scatter_train_val_test_experiment_0.png}
+\newcommand\SSHOneWindingTrain{\SSHOneExperimentsFigs scatter_winding_train_experiment_0.png}
+\newcommand\SSHOnePredictionGrid{\SSHOneExperimentsFigs pcolormesh_prediction_grid_experiment_0.png}
+%%% ssh2 experiments (figure 3)
+\newcommand\SSHTwoExperimentsFigs{./00_article/ssh2/real_space_all_sites/}
+\newcommand\SSHTwoTrainValTestSplit{\SSHTwoExperimentsFigs scatter_train_val_test_experiment_0.png}
+\newcommand\SSHTwoWindingTrain{\SSHTwoExperimentsFigs scatter_winding_train_experiment_0.png}
+\newcommand\SSHTwoPredictionGrid{\SSHTwoExperimentsFigs pcolormesh_prediction_grid_experiment_0.png}
+%%% ssh1 probability heatmaps  (figure 4)
+\newcommand\SSHOneWindingZero{\SSHOneExperimentsFigs imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHOneWindingOne{\SSHOneExperimentsFigs imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHOneHeatmap{\SSHOneExperimentsFigs merge_imshow_winding_grids_second_sim.png}
+%%% ssh2 probability heatmaps  (figure 5)
+\newcommand\SSHTwoWindingMinusOne{\SSHTwoExperimentsFigs imshow_winding_grid_winding_-1_sim.png}
+\newcommand\SSHTwoWindingZero{\SSHTwoExperimentsFigs imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHTwoWindingOne{\SSHTwoExperimentsFigs imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHTwoWindingTwo{\SSHTwoExperimentsFigs imshow_winding_grid_winding_2_sim.png}
+\newcommand\SSHTwoHeatmap{\SSHTwoExperimentsFigs merge_imshow_winding_grids_sim.png}
+%%% information entropy signatures (figure 6)
+\newcommand\SSHOneEntropySignature{\SSHOneExperimentsFigs plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignature{\SSHTwoExperimentsFigs plot_feature_importances.png}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Supplementary material
+\newcommand\SuppFigures{./01_supplementary/}
+\newcommand\SSH{\SuppFigures ssh/}
+\newcommand\SSHOneSupp{\SuppFigures ssh1/}
+%%% lattice size 100
+\newcommand\SSHOneSuppOneZeroZero{\SSHOneSupp periodic_100_6561/}
+\newcommand\SSHOneSuppOneZeroZeroCompressedRealSpace{\SSHOneSuppOneZeroZero real_space_best_04_sites/}
+\newcommand\SSHOneSuppOneZeroZeroCompressedDCT{\SSHOneSuppOneZeroZero dct_best_04_wavevector_sites_from_best_04_real_space_sites/}
+\newcommand\SSHOneSuppOneZeroZeroCompressedDST{\SSHOneSuppOneZeroZero dst_best_04_wavevector_sites_from_best_04_real_space_sites/}
+%%% lattice size 140
+\newcommand\SSHOneSuppOneFourZero{\SSHOneSupp periodic_140_6561/}
+%\newcommand\SSHOneSuppOneFourZeroCompressedRealSpace{\SSHOneSuppOneFourZero real_space_best_04_sites/}
+%\newcommand\SSHOneSuppOneFourZeroCompressedDCT{\SSHOneSuppOneFourZero dct_best_04_wavevector_sites_from_best_04_real_space_sites/}
+%\newcommand\SSHOneSuppOneFourZeroCompressedDST{\SSHOneSuppOneFourZero dst_best_04_wavevector_sites_from_best_04_real_space_sites/}
+
+%%%% lattice size 180
+\newcommand\SSHOneSuppOneEightZero{\SSHOneSupp periodic_180_6561/}
+
+\newcommand\SSHOneSuppTwoTwoZero{\SSHOneSupp periodic_220_6561/}
+\newcommand\SSHTwoSupp{\SuppFigures ssh2/}
+\newcommand\SSHTwoSuppOneZeroZero{\SSHTwoSupp periodic_100_6561/}
+\newcommand\SSHTwoSuppOneZeroZeroCompressedRealSpace{\SSHTwoSuppOneZeroZero real_space_best_12_sites/}
+\newcommand\SSHTwoSuppOneZeroZeroCompressedDCT{\SSHTwoSuppOneZeroZero dct_best_12_wavevector_sites_from_best_12_real_space_sites/}
+\newcommand\SSHTwoSuppOneZeroZeroCompressedDST{\SSHTwoSuppOneZeroZero dst_best_12_wavevector_sites_from_best_12_real_space_sites/}
+
+\newcommand\SSHTwoSuppOneFourZero{\SSHTwoSupp periodic_140_6561/}
+\newcommand\SSHTwoSuppOneEightZero{\SSHTwoSupp periodic_180_6561/}
+\newcommand\SSHTwoSuppTwoTwoZero{\SSHTwoSupp periodic_220_6561/}
+%%% SSH model (figure 7)
+\newcommand\SSHModel{\SSH ssh_model.pdf}
+%%% Winding number (figure 8)
+\newcommand\WindingNumber{\SSH winding.png}
+%%% SSH1 compressed phase diagrams (figure 9)
+\newcommand\SSHOneCompressedRealSpacePhaseDiagram{\SSHOneSuppOneZeroZeroCompressedRealSpace merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDCTPhaseDiagram{\SSHOneSuppOneZeroZeroCompressedDCT merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDSTPhaseDiagram{\SSHOneSuppOneZeroZeroCompressedDST merge_imshow_winding_grids_second_sim.png}
+%%% SSH2 compressed phase diagrams (figure 9)
+\newcommand\SSHTwoCompressedRealSpacePhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedRealSpace merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDCTPhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedDCT merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDSTPhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedDST merge_imshow_winding_grids_sim.png}
+%%% SSH1 entropy signatures on longer lattices (figure 10)
+\newcommand\SSHOneEntropySignatureOneFourZero{\SSHOneSuppOneFourZero plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureOneEightZero{\SSHOneSuppOneEightZero plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureTwoTwoZero{\SSHOneSuppTwoTwoZero plot_feature_importances.png}
+%%% SSH2 entropy signatures on longer lattices (figure 11)
+\newcommand\SSHTwoEntropySignatureOneFourZero{\SSHTwoSuppOneFourZero plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureOneEightZero{\SSHTwoSuppOneEightZero plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureTwoTwoZero{\SSHTwoSuppTwoTwoZero plot_feature_importances.png}
+%%% SSH1 cumulative information entropy signatures (figure 12)
+\newcommand\SSHOneCumulativeEntropyOneFourZero{\SSHOneSuppOneFourZero plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyOneEightZero{\SSHOneSuppOneEightZero plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyTwoTwoZero{\SSHOneSuppTwoTwoZero plot_cumulative_feature_importances.png}
+%%% SSH2 cumulative information entropy signatures (figure 12)
+\newcommand\SSHTwoCumulativeEntropyOneFourZero{\SSHTwoSuppOneFourZero plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyOneEightZero{\SSHTwoSuppOneEightZero plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyTwoTwoZero{\SSHTwoSuppTwoTwoZero plot_cumulative_feature_importances.png}
+
+%\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
 
@@
 We further use insights obtained from these information entropy signatures to engineer global topological features from real space lattice data that still carry most of the topological information in the lattice, while greatly diminishing the size of feature space, thus effectively amounting to a topological lattice compression.
-Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which allows us to establish Heisenberg and Hirschman uncertainty relations for topological phase transitions.
+Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which lead us to Heisenberg and Hirschman uncertainty relations for topological phase transitions.
 The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
@@
 
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired patterns in the data.
+The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learning the desired patterns in the data.
 This makes it much easier to trace the localization of relevant information along the features of a data set.
@@
 \centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh1.png}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh2.png}}
+\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{\SSHOnePhaseDiagram}}\quad
+\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{\SSHTwoPhaseDiagram}}
 \caption{Phase diagrams in parameter space.
@@
 The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
-Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across $n_{exp}$ experiments.
-The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps.
+Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across 100 experiments.
+The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the corresponding probability heatmaps.
 As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
@@
 \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
+\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{\SSHOneTrainValTestSplit}}
+\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{\SSHOneWindingTrain}}
+\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{\SSHOnePredictionGrid}}
 \caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
@@
 (b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
+(c) Phase diagram learned from real space lattice data by combining a decision tree with eigenvector ensembling.}
 \label{figexp1_exp}
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
+\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{\SSHTwoTrainValTestSplit}}
+\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{\SSHTwoWindingTrain}}
+\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{\SSHTwoPredictionGrid}}
 \caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
@@
 (b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
+(c) Phase diagram learned from real space lattice data by combining a random forest with eigenvector ensembling.}
 \label{figexp2_exp}
@@
 
-We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy.
+We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy as cost function.
 This would similarly lead us to Gini impurity signatures of topological phase transitions.
-Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures produced very similar results, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
+Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures were very similar, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
 Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely undecided \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
@@
 \centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{\SSHOneWindingZero}}
+\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{\SSHOneWindingOne}}
+\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{\SSHOneHeatmap}}
 \caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
@@
 \centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{\SSHTwoWindingMinusOne}}
+\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{\SSHTwoWindingZero}}
+\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{\SSHTwoWindingOne}}
+\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{\SSHTwoWindingTwo}}
+\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{\SSHTwoHeatmap}}
 \caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
@@
 
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective and show how the same machinery used previously is able to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
-
-As we have argued in section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective.
+As we shall see, this will enable us to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
+
+As a cursory glance at figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} seems to suggest, the existence of peaks and symmetries in information entropy signatures can be exploited as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
 Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
@@
 This is due to the fact that each equation assumes that the eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
-While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
-Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
+While these assumptions are strictly true for the eigenvector representations in wavevector space, they are not generally true for the real space representations.
+Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from one half of the lattice to the other.
 
@@
 \end{equation}
-Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
+Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq l \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
+Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq l \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
 In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xSOne and \xSTwo, according to the SSH systems they relate to.
@@
 
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH 1 and SSH 2 systems,
+Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the most informative DCT topological features of both SSH 1 and SSH 2 systems that were obtained from strategy \emph{ii)},
 \begin{equation}
@@
 \end{equation}
-and the DST topological features,
+and the most informative DST topological features of both systems that were obtained from strategy \emph{ii)} as well,
 \begin{equation}
@@
 \end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space components used with each SSH systems.
+The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space subset used with each SSH system.
 
@@
 \label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
+\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}^*} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
 \end{equation}
@@
 \end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$, 
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$ and $\mathcal{S}^*$ is the complement of $\{0,M-1\}$ with respect to $\mathcal{S}$,
 \begin{equation}
@@
       1 & \text{if } l \in \mathcal{S} \\
-      0 & \text{otherwise}.
-    \end{cases}
+      0 & \text{otherwise}
+    \end{cases}, \qquad \mathcal{S}^* = \mathcal{S}{\backslash} \{0,M-1\}.
 \end{equation}
@@
 macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices, which themselves become 1D manifolds.
-By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuous limit will be given by
+By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuum limit will be given by
 
@@
 \end{equation}
-the amount of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
+the local density of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
 
@@
 
-Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
+Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
 Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
@@
 Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
-On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy of information is a necessary commodity to ensure error-correction within the system.
+On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy is a necessary commodity to ensure error-correction within the system.
 We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
@@
 The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.
+This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information is most readily available in the SSH lattices investigated.
 
@@
 We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
-In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
+In our paper we preferred the term \emph{model explainability}, as we used similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
 While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.
@@
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
-Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave function discussed here is left for speculation.
+Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} which were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave functions discussed here is left for speculation.
 
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
+\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{\SSHOneEntropySignature}}\quad
+\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{\SSHTwoEntropySignature}}\quad
+\caption{Information entropy signatures of the topological phase transitions from the numerical experiments of section \ref{numerical_experiments}.
 (a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
@@
 
-\bibliography{article_bib}{}
+%\bibliography{./article_bib/article_bib}{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{thebibliography}{63}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Hasan}\ and\ \citenamefont
+  {Kane}(2010)}]{RevModPhys.82.3045}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Hasan}}\ and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
+  {Kane}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {3045}
+  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Continentino}(2017)}]{CONTINENTINO2017A1}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physica B: Condensed Matter}\ }\textbf {\bibinfo {volume} {505}},\ \bibinfo
+  {pages} {A1 } (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Puel}\ \emph {et~al.}(2017)\citenamefont {Puel},
+  \citenamefont {Sacramento},\ and\ \citenamefont
+  {Continentino}}]{PhysRevB.95.094509}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~O.}\ \bibnamefont
+  {Puel}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
+  {Sacramento}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {094509}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Griffith}\ and\ \citenamefont
+  {Continentino}(2018)}]{PhysRevE.97.012107}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Griffith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {012107}
+  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ryu}\ \emph {et~al.}(2010)\citenamefont {Ryu},
+  \citenamefont {Schnyder}, \citenamefont {Furusaki},\ and\ \citenamefont
+  {Ludwig}}]{ryu2010topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ryu}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont {Schnyder}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Furusaki}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont {Ludwig}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {New Journal of
+  Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {065010}
+  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Atala}\ \emph {et~al.}(2013)\citenamefont {Atala},
+  \citenamefont {Aidelsburger}, \citenamefont {Barreiro}, \citenamefont
+  {Abanin}, \citenamefont {Kitagawa}, \citenamefont {Demler},\ and\
+  \citenamefont {Bloch}}]{atala2013direct}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Atala}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Aidelsburger}},
+  \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont {Barreiro}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Abanin}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Kitagawa}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Bloch}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
+  {9}},\ \bibinfo {pages} {795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stuhl}\ \emph {et~al.}(2015)\citenamefont {Stuhl},
+  \citenamefont {Lu}, \citenamefont {Aycock}, \citenamefont {Genkina},\ and\
+  \citenamefont {Spielman}}]{Stuhl1514}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~K.}\ \bibnamefont
+  {Stuhl}}, \bibinfo {author} {\bibfnamefont {H.-I.}\ \bibnamefont {Lu}},
+  \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont {Aycock}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Genkina}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {I.~B.}\ \bibnamefont {Spielman}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
+  {volume} {349}},\ \bibinfo {pages} {1514} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Leder}\ \emph {et~al.}(2016)\citenamefont {Leder},
+  \citenamefont {Grossert}, \citenamefont {Sitta}, \citenamefont {Genske},
+  \citenamefont {Rosch},\ and\ \citenamefont {Weitz}}]{leder2016real}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Leder}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Grossert}},
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sitta}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Genske}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Rosch}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {13112} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goldman}\ \emph {et~al.}(2016)\citenamefont
+  {Goldman}, \citenamefont {Budich},\ and\ \citenamefont
+  {Zoller}}]{goldman2016topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Goldman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Budich}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
+  }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {639} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Meier}\ \emph {et~al.}(2016)\citenamefont {Meier},
+  \citenamefont {An},\ and\ \citenamefont {Gadway}}]{meier2016observation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
+  {Meier}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {An}}, \
+  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  communications}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {13986}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hafezi}\ \emph {et~al.}(2013)\citenamefont {Hafezi},
+  \citenamefont {Mittal}, \citenamefont {Fan}, \citenamefont {Migdall},\ and\
+  \citenamefont {Taylor}}]{hafezi2013imaging}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Hafezi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mittal}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Fan}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Migdall}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Taylor}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Photonics}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {1001} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Lu}\ \emph {et~al.}(2016)\citenamefont {Lu},
+  \citenamefont {Joannopoulos},\ and\ \citenamefont
+  {Solja{\v{c}}i{\'c}}}]{lu2016topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Lu}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+  {Joannopoulos}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Solja{\v{c}}i{\'c}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {626} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peano}\ \emph {et~al.}(2015)\citenamefont {Peano},
+  \citenamefont {Brendel}, \citenamefont {Schmidt},\ and\ \citenamefont
+  {Marquardt}}]{PhysRevX.5.031011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Peano}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Brendel}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Schmidt}}, \ and\
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marquardt}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
+  {\bibinfo {volume} {5}},\ \bibinfo {pages} {031011} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2012)\citenamefont
+  {Kitagawa}, \citenamefont {Broome}, \citenamefont {Fedrizzi}, \citenamefont
+  {Rudner}, \citenamefont {Berg}, \citenamefont {Kassal}, \citenamefont
+  {Aspuru-Guzik}, \citenamefont {Demler},\ and\ \citenamefont
+  {White}}]{kitagawa2012observation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Broome}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Fedrizzi}},
+  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Kassal}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~G.}\
+  \bibnamefont {White}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature communications}\ }\textbf {\bibinfo {volume} {3}},\
+  \bibinfo {pages} {882} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cardano}\ \emph {et~al.}(2016)\citenamefont
+  {Cardano}, \citenamefont {Maffei}, \citenamefont {Massa}, \citenamefont
+  {Piccirillo}, \citenamefont {De~Lisio}, \citenamefont {De~Filippis},
+  \citenamefont {Cataudella}, \citenamefont {Santamato},\ and\ \citenamefont
+  {Marrucci}}]{cardano2016statistical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Cardano}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maffei}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Massa}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Piccirillo}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {De~Lisio}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {De~Filippis}}, \bibinfo {author}
+  {\bibfnamefont {V.}~\bibnamefont {Cataudella}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Santamato}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Marrucci}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {11439} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Flurin}\ \emph {et~al.}(2017)\citenamefont {Flurin},
+  \citenamefont {Ramasesh}, \citenamefont {Hacohen-Gourgy}, \citenamefont
+  {Martin}, \citenamefont {Yao},\ and\ \citenamefont
+  {Siddiqi}}]{PhysRevX.7.031023}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Flurin}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
+  {Ramasesh}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Hacohen-Gourgy}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
+  {Martin}}, \bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont {Yao}}, \
+  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Siddiqi}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
+  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {031023} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Soluyanov}\ \emph {et~al.}(2015)\citenamefont
+  {Soluyanov}, \citenamefont {Gresch}, \citenamefont {Wang}, \citenamefont
+  {Wu}, \citenamefont {Troyer}, \citenamefont {Dai},\ and\ \citenamefont
+  {Bernevig}}]{soluyanov2015type}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
+  {Soluyanov}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gresch}},
+  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {Q.}~\bibnamefont {Wu}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Troyer}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Dai}}, \ and\ \bibinfo {author} {\bibfnamefont {B.~A.}\
+  \bibnamefont {Bernevig}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {527}},\ \bibinfo {pages}
+  {495} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lv}\ \emph {et~al.}(2015)\citenamefont {Lv},
+  \citenamefont {Weng}, \citenamefont {Fu}, \citenamefont {Wang}, \citenamefont
+  {Miao}, \citenamefont {Ma}, \citenamefont {Richard}, \citenamefont {Huang},
+  \citenamefont {Zhao}, \citenamefont {Chen}, \citenamefont {Fang},
+  \citenamefont {Dai}, \citenamefont {Qian},\ and\ \citenamefont
+  {Ding}}]{PhysRevX.5.031013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~Q.}\ \bibnamefont
+  {Lv}}, \bibinfo {author} {\bibfnamefont {H.~M.}\ \bibnamefont {Weng}},
+  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Fu}}, \bibinfo
+  {author} {\bibfnamefont {X.~P.}\ \bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Miao}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ma}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Richard}}, \bibinfo {author} {\bibfnamefont {X.~C.}\ \bibnamefont {Huang}},
+  \bibinfo {author} {\bibfnamefont {L.~X.}\ \bibnamefont {Zhao}}, \bibinfo
+  {author} {\bibfnamefont {G.~F.}\ \bibnamefont {Chen}}, \bibinfo {author}
+  {\bibfnamefont {Z.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Dai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Qian}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
+  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {031013} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Su}\ \emph {et~al.}(1979)\citenamefont {Su},
+  \citenamefont {Schrieffer},\ and\ \citenamefont
+  {Heeger}}]{PhysRevLett.42.1698}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~P.}\ \bibnamefont
+  {Su}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Schrieffer}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Heeger}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1698} (\bibinfo {year}
+  {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},
+  \citenamefont {Dauphin}, \citenamefont {Cardano}, \citenamefont
+  {Lewenstein},\ and\ \citenamefont {Massignan}}]{maffei2018topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Maffei}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Cardano}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Massignan}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
+  {\bibinfo {volume} {20}},\ \bibinfo {pages} {013023} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heeger}(2001)}]{RevModPhys.73.681}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Heeger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {681}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kane}\ and\ \citenamefont
+  {Lubensky}(2014)}]{kane2014topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Kane}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Lubensky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {39}
+  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
+  \citenamefont {Upadhyaya},\ and\ \citenamefont {Vitelli}}]{Chen13004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.-g.}\
+  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Upadhyaya}}, \ and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Vitelli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
+  {volume} {111}},\ \bibinfo {pages} {13004} (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carrasquilla}\ and\ \citenamefont
+  {Melko}(2017)}]{carrasquilla2017machine}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Carrasquilla}}\ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Melko}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {431}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ch'ng}\ \emph {et~al.}(2017)\citenamefont {Ch'ng},
+  \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\ \citenamefont
+  {Khatami}}]{PhysRevX.7.031038}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Ch'ng}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Carrasquilla}},
+  \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \ and\
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Khatami}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
+  {\bibinfo {volume} {7}},\ \bibinfo {pages} {031038} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}(2016)}]{PhysRevB.94.195105}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Wang}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {195105}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Broecker}\ \emph {et~al.}(2017)\citenamefont
+  {Broecker}, \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\
+  \citenamefont {Trebst}}]{broecker2017machine}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Broecker}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Carrasquilla}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Melko}}, \ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Trebst}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Scientific reports}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
+  {8823} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Van~Nieuwenburg}\ \emph {et~al.}(2017)\citenamefont
+  {Van~Nieuwenburg}, \citenamefont {Liu},\ and\ \citenamefont
+  {Huber}}]{van2017learning}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
+  {Van~Nieuwenburg}}, \bibinfo {author} {\bibfnamefont {Y.-H.}\ \bibnamefont
+  {Liu}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Huber}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {435}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2018)\citenamefont {Zhang},
+  \citenamefont {Shen},\ and\ \citenamefont {Zhai}}]{PhysRevLett.120.066401}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {120}},\ \bibinfo {pages} {066401} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
+  \citenamefont {Yi}, \citenamefont {Zhang}, \citenamefont {Shen},\ and\
+  \citenamefont {Zhai}}]{PhysRevB.98.085402}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Yi}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Zhang}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {98}},\ \bibinfo {pages} {085402} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Suchsland}\ and\ \citenamefont
+  {Wessel}(2018)}]{PhysRevB.97.174435}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Suchsland}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Wessel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {174435}
+  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont
+  {Kim}(2017)}]{PhysRevLett.118.216401}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont
+  {Kim}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. Lett.}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {216401}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Venderley}\ \emph {et~al.}(2018)\citenamefont
+  {Venderley}, \citenamefont {Khemani},\ and\ \citenamefont
+  {Kim}}]{PhysRevLett.120.257204}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Venderley}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Khemani}},
+  \ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+  }\textbf {\bibinfo {volume} {120}},\ \bibinfo {pages} {257204} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ohtsuki}\ and\ \citenamefont
+  {Ohtsuki}(2017)}]{ohtsuki2017deep}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ohtsuki}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ohtsuki}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo {volume}
+  {86}},\ \bibinfo {pages} {044708} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Yoshioka}\ \emph {et~al.}(2018)\citenamefont
+  {Yoshioka}, \citenamefont {Akagi},\ and\ \citenamefont
+  {Katsura}}]{PhysRevB.97.205110}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Yoshioka}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Akagi}}, \
+  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Katsura}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {205110} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2017)\citenamefont {Deng},
+  \citenamefont {Li},\ and\ \citenamefont {Das~Sarma}}]{PhysRevB.96.195145}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.-L.}\ \bibnamefont
+  {Deng}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}}, \ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf
+  {\bibinfo {volume} {96}},\ \bibinfo {pages} {195145} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huembeli}\ \emph {et~al.}(2018)\citenamefont
+  {Huembeli}, \citenamefont {Dauphin},\ and\ \citenamefont
+  {Wittek}}]{PhysRevB.97.134109}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Huembeli}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wittek}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {134109} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carvalho}\ \emph {et~al.}(2018)\citenamefont
+  {Carvalho}, \citenamefont {Garc\'{\i}a-Mart\'{\i}nez}, \citenamefont {Lado},\
+  and\ \citenamefont {Fern\'andez-Rossier}}]{PhysRevB.97.115453}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Carvalho}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
+  {Garc\'{\i}a-Mart\'{\i}nez}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
+  \bibnamefont {Lado}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Fern\'andez-Rossier}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {97}},\ \bibinfo {pages} {115453} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2017)\citenamefont {Zhang},
+  \citenamefont {Melko},\ and\ \citenamefont {Kim}}]{PhysRevB.96.245119}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {245119} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rodriguez-Nieva}\ and\ \citenamefont
+  {Scheurer}(2018)}]{rodriguez2018identifying}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
+  {Rodriguez-Nieva}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\
+  \bibnamefont {Scheurer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {arXiv preprint arXiv:1805.05961}\ } (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gilpin}\ \emph {et~al.}(2018)\citenamefont {Gilpin},
+  \citenamefont {Bau}, \citenamefont {Yuan}, \citenamefont {Bajwa},
+  \citenamefont {Specter},\ and\ \citenamefont {Kagal}}]{gilpin2018explaining}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~H.}\ \bibnamefont
+  {Gilpin}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Bau}},
+  \bibinfo {author} {\bibfnamefont {B.~Z.}\ \bibnamefont {Yuan}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Bajwa}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Specter}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Kagal}},\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {2018 IEEE 5th International Conference on data science
+  and advanced analytics (DSAA)}}}\ (\bibinfo {organization} {IEEE},\ \bibinfo
+  {year} {2018})\ pp.\ \bibinfo {pages} {80--89}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Do{\v{s}}ilovi{\'c}}\ \emph
+  {et~al.}(2018)\citenamefont {Do{\v{s}}ilovi{\'c}}, \citenamefont
+  {Br{\v{c}}i{\'c}},\ and\ \citenamefont
+  {Hlupi{\'c}}}]{dovsilovic2018explainable}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~K.}\ \bibnamefont
+  {Do{\v{s}}ilovi{\'c}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Br{\v{c}}i{\'c}}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Hlupi{\'c}}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {2018 41st
+  International convention on information and communication technology,
+  electronics and microelectronics (MIPRO)}}}\ (\bibinfo {organization}
+  {IEEE},\ \bibinfo {year} {2018})\ pp.\ \bibinfo {pages}
+  {0210--0215}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Roscher}\ \emph {et~al.}(2020)\citenamefont
+  {Roscher}, \citenamefont {Bohn}, \citenamefont {Duarte},\ and\ \citenamefont
+  {Garcke}}]{roscher2020explainable}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Roscher}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bohn}},
+  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Duarte}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Garcke}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Access}\ }\textbf {\bibinfo
+  {volume} {8}},\ \bibinfo {pages} {42200} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
+  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
+  {Tibshirani}}]{friedman2001elements}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
+  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
+  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
+  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
+  {year} {2001})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pedregosa}\ \emph {et~al.}(2011)\citenamefont
+  {Pedregosa}, \citenamefont {Varoquaux}, \citenamefont {Gramfort},
+  \citenamefont {Michel}, \citenamefont {Thirion}, \citenamefont {Grisel},
+  \citenamefont {Blondel}, \citenamefont {Prettenhofer}, \citenamefont {Weiss},
+  \citenamefont {Dubourg}, \citenamefont {Vanderplas}, \citenamefont {Passos},
+  \citenamefont {Cournapeau}, \citenamefont {Brucher}, \citenamefont {Perrot},\
+  and\ \citenamefont {Duchesnay}}]{scikit-learn}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pedregosa}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Varoquaux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gramfort}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Michel}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Thirion}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Blondel}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Weiss}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Dubourg}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Vanderplas}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Passos}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Cournapeau}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Brucher}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Perrot}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Duchesnay}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Machine Learning Research}\ }\textbf
+  {\bibinfo {volume} {12}},\ \bibinfo {pages} {2825} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Buitinck}\ \emph {et~al.}(2013)\citenamefont
+  {Buitinck}, \citenamefont {Louppe}, \citenamefont {Blondel}, \citenamefont
+  {Pedregosa}, \citenamefont {Mueller}, \citenamefont {Grisel}, \citenamefont
+  {Niculae}, \citenamefont {Prettenhofer}, \citenamefont {Gramfort},
+  \citenamefont {Grobler}, \citenamefont {Layton}, \citenamefont {VanderPlas},
+  \citenamefont {Joly}, \citenamefont {Holt},\ and\ \citenamefont
+  {Varoquaux}}]{sklearn_api}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Buitinck}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Louppe}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Blondel}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Pedregosa}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Mueller}}, \bibinfo {author} {\bibfnamefont
+  {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Niculae}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Gramfort}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Grobler}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Layton}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {VanderPlas}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Joly}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Holt}}, \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Varoquaux}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {ECML PKDD
+  Workshop: Languages for Data Mining and Machine Learning}}}\ (\bibinfo {year}
+  {2013})\ pp.\ \bibinfo {pages} {108--122}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
+  {Breiman}, \citenamefont {Friedman}, \citenamefont {Stone},\ and\
+  \citenamefont {Olshen}}]{breiman2017classification}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Breiman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},
+  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Stone}}, \ and\
+  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Olshen}},\
+  }\href@noop {} {\emph {\bibinfo {title} {Classification and regression
+  trees}}}\ (\bibinfo  {publisher} {Chapman and Hall/CRC, London, UK},\
+  \bibinfo {year} {1984})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Breiman}(2001)}]{Breiman2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Breiman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Machine Learning}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {5}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Raileanu}\ and\ \citenamefont
+  {Stoffel}(2004)}]{raileanu2004theoretical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~E.}\ \bibnamefont
+  {Raileanu}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Stoffel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Annals of Mathematics and Artificial Intelligence}\ }\textbf {\bibinfo
+  {volume} {41}},\ \bibinfo {pages} {77} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2020)\citenamefont {Zhang},
+  \citenamefont {Ginsparg},\ and\ \citenamefont {Kim}}]{zhang2020interpreting}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Ginsparg}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Research}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {023283}
+  (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
+  {Resta}(2011)}]{PhysRevB.84.241106}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Bianco}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Resta}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {241106} (\bibinfo
+  {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Caio}\ \emph {et~al.}(2019)\citenamefont {Caio},
+  \citenamefont {M{\"o}ller}, \citenamefont {Cooper},\ and\ \citenamefont
+  {Bhaseen}}]{caio2019topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
+  {Caio}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {M{\"o}ller}},
+  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Cooper}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bhaseen}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ ,\ \bibinfo
+  {pages} {1}} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carlsson}(2009)}]{carlsson2009topology}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Carlsson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Bulletin of the American Mathematical Society}\ }\textbf {\bibinfo {volume}
+  {46}},\ \bibinfo {pages} {255} (\bibinfo {year} {2009})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wasserman}(2018)}]{wasserman2018topological}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Wasserman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Annual Review of Statistics and Its Application}\ }\textbf {\bibinfo
+  {volume} {5}},\ \bibinfo {pages} {501} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2005)\citenamefont {Wang},
+  \citenamefont {Zhang},\ and\ \citenamefont {Zha}}]{wang2005adaptive}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\ }in\ \href@noop
+  {} {\emph {\bibinfo {booktitle} {Advances in neural information processing
+  systems}}}\ (\bibinfo {year} {2005})\ pp.\ \bibinfo {pages}
+  {1473--1480}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lin}\ and\ \citenamefont
+  {Zha}(2008)}]{lin2008riemannian}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Lin}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Transactions
+  on Pattern Analysis and Machine Intelligence}\ }\textbf {\bibinfo {volume}
+  {30}},\ \bibinfo {pages} {796} (\bibinfo {year} {2008})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Belkin}(2003)}]{belkin2003problems}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Belkin}},\ }\href@noop {} {\emph {\bibinfo {title} {Problems of learning on
+  manifolds}}}\ (\bibinfo  {publisher} {The University of Chicago, Chicago, IL,
+  USA},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
+  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
+  {P{\'a}lyi}}]{asboth2016short}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
+  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
+  {Courville}}]{goodfellow2016deep}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
+  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
+  {publisher} {MIT press, Cambridge, MA, USA},\ \bibinfo {year}
+  {2016})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
+  machine learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\
+  \bibinfo {year} {2006})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
+  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
+  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
+  {Mitter}(2010)}]{narayanan2010sample}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
+  Neural Information Processing Systems}}}\ (\bibinfo {year} {2010})\ pp.\
+  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
+  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
+  and\ \citenamefont {Muller}}]{rifai2011manifold}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {Advances in Neural Information Processing Systems}}}\
+  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\pagebreak
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.37\textwidth]{\SSHModel}
+  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
+\label{fig:model}
+\end{figure}
+
+\begin{figure}%[h!]
+  \centering
+  \includegraphics[width=.37\textwidth]{\WindingNumber}
+  \caption{Winding number.
+The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point.
+Picture credits: Jim Belk, public domain.}
+\label{fig:winding}
+\end{figure}
+
+\section*{Supplementary Material}
+\subsection*{The SSH model}
+\label{sshapp}
+
+The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
+This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
+This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
+\begin{equation}
+\label{SSH}
+\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
+\end{equation}
+where the column vector
+\begin{equation*}
+\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
+\end{equation*}
+contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
+\begin{equation*}
+\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
+\end{equation*}
+contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
+Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.
+
+The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
+We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics.
+As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
+\begin{equation}\label{hmatrix}
+H(t_1,t_2,T_1,T_2)=\left(
+  \begin{array}{cccccc}
+    0 & t_1 & 0 & T_1 & 0 & \cdots \\
+    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
+    0 & t_2 & 0 & t_1 & 0 & \cdots\\
+    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
+    0 & T_2 & 0 & t_2 &  0& \cdots\\
+    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
+  \end{array}
+  \right)_{N \times N}.
+\end{equation}
+Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
+Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.
+
+The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
+This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
+This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system.
+In the particular case of the SSH model, the topological invariant used to classify the topological phases is the winding number.
+
+The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
+It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative).
+Figure \ref{fig:winding} shows several closed, oriented curves and their winding numbers computed with respect to a given point.
+
+An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
+This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a challenging task.
+
+For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
+\begin{equation}\label{winding_number}
+W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
+\end{equation}
+where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\mathbf{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
+Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure 1 in the article.
+%\ref{fig:phasediagrams}.
+
+\begin{figure}
+\centering
+\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{\SSHOneCompressedRealSpacePhaseDiagram}}
+\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDCTPhaseDiagram}}
+\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDSTPhaseDiagram}}
+\caption{Phase diagrams learned from compressed representations of the SSH 1 system.
+(a) Phase diagram learned using the real space features \xSOne.
+(b) Phase diagram learned from the DCT topological features \xcSEOne.
+(b) Phase diagram learned from the DST topological features \xsSOOne.}
+\label{eng_feat_ssh1}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedRealSpacePhaseDiagram}}
+\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDCTPhaseDiagram}}
+\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDSTPhaseDiagram}}
+\caption{Phase diagrams learned from compressed representations of the SSH 2 system.
+(a) Phase diagram learned using the real space features \xSTwo.
+(b) Phase diagram learned from the DCT topological features \xcSETwo.
+(b) Phase diagram learned from the DST topological features \xsSOTwo.}
+\label{eng_feat_ssh2}
+\end{figure}
+
+\subsection*{Learning topological phases from real space data}
+
+%The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
+%\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+%disordered systems in condensed matter) do not have.
+Moreover, since real space and wavevector space eigenvectors are related by Fourier %transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
+We argue here that a data-driven %approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
+
+The insights behind our intuition that topological phases can be learned from local features are as follows.
+First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
+Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space.
+Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.
+
+In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
+Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
+\begin{equation}
+\label{localconstancy}
+W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
+\end{equation}
+
+That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure 1 in the article %\ref{fig:phasediagrams}, 
+where we draw phase diagrams of SSH models with first-neighbor (figure 1(a)) and first- and second-neighbor (figure 1(b)) hoppings.
+In figure 1(a) for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
+Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.
+
+It does not immediately follow, however, that the same strategy will be successful in real space.
+Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,
+
+\begin{equation}
+\label{parameter_to_real}
+\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
+\end{equation}
+where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
+The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.
+
+This fact is well illustrated by the numerical experiments discussed in the article.
+Although it may seem from figures 2(b) and 3(b) (from the article) in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
+In such high-dimensional spaces, the data should be much sparser.
+
+The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as \emph{the curse of dimensionality} \cite{bishop2006pattern}.
+It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
+
+These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
+As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data, which reveals that there is a lot of redundancy in the information content of real space eigenvectors.
+This fact can be exploited to generate compressed representations of SSH systems that still carry most of the relevant topological information, as can be seen in figures \ref{eng_feat_ssh1} and \ref{eng_feat_ssh2}.
+
+\subsection*{Numerical explorations on longer lattices}
+
+A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
+
+The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
+Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
+
+Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
+As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
+The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector ensembling algorithm.
+
+There are still artifacts that might arise from the hyperparameters used to generate the data.
+These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space).
+Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive.
+Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the information entropy signatures is lattice size.
+
+All results presented in the article were obtained for lattices with 50 unit cells.
+Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
+Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}).
+These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
+
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size is increased.
+This naturally leads us to speculation about the continuum limit of information entropy signatures, a matter formally explored in the article.
+
+\begin{figure}
+\centering
+\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneFourZero}}
+\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneEightZero}}
+\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureTwoTwoZero}}
+\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh1_longer_lattices}
+\end{figure}
+\begin{figure}
+\centering
+\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneFourZero}}
+\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneEightZero}}
+\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureTwoTwoZero}}
+\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh2_longer_lattices}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}
+\centering
+\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneFourZero}}
+\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneEightZero}}
+\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyTwoTwoZero}}
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
+(a) Cumulative entropy distribution for 70 unit cells.
+(b) Cumulative entropy distribution for 90 unit cells.
+(c) Cumulative entropy distribution for 110 unit cells.}
+\label{cdf1}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneFourZero}}
+\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneEightZero}}
+\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyTwoTwoZero}}
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
+(a) Cumulative entropy distributions for 70 unit cells.
+(b) Cumulative entropy distributions for 90 unit cells.
+(c) Cumulative entropy distributions for 110 unit cells.}
+\label{cdf2}
+\end{figure}
+
 \end{document}

### 2020-07-25 10_prb_resubmission_01/00_article/article.tex
Generated new arxiv submission

@@
 \usepackage[resetlabels, labeled]{multibib}
+\usepackage{xcolor}
+\usepackage{bbm}
+\usepackage{xfp}
+\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
+\usepackage{booktabs}
+\renewcommand{\figurename}{Figure}
+\renewcommand{\tablename}{Table}
+\renewcommand{\thetable}{\arabic{table}}
+%\captionsetup{justification=raggedright, singlelinecheck = false}
+%\usepackage{makecell}
+%\usepackage{cellspace}
+
 %\newcites{supp}{References}
+
+%\def\basiceval#1{\the\numexpr#1\relax}
 
@@
 \newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
-\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional
-                                %derivative
+\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative
+
+%ssh1
+
+%Our test set in this experiment contained 1005 Hamiltonians (approx.
+15.3\% of all data).
+Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx.
+8.5\%) and 5000 (approx.
+76.2\%) were used to compute validation scores at each iteration.
+%These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration.
+The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
+The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$.
+\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
+
+%\documentclass{article}
+%\usepackage{xfp}
+
+%\begin{document}
+
+%\fpeval{31/45}
+
+%\fpeval{round(31/45,5)}
+
+%\end{document}
+\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
+%%%%%% Numerical experiments parameters
+\newcommand\nPrec{2}    % precision digits
+\newcommand\accPrec{4}  % precision digits for accuracy scores
+\newcommand\nHam{6561}  % total number of hamiltonians
+\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
+\newcommand\nExp{100}   % number of experiments
+%%%table commands
+%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
+\newcommand{\tableRow}[1]{\\[#1 cm]}
+\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
+\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
+\newcommand\tableRowEnd{\tableRow{0.15}}
+%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
+%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
+%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
+%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
+%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
+%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
+\newcommand\SSHSys{SSH system}         
+\newcommand\Feat{Features}              
+\newcommand\ValEig{Val. eigenvectors}   
+\newcommand\TestEig{Test eigenvectors}  
+\newcommand\ValHam{Val. Hamiltonians}   
+\newcommand\TestHam{Test Hamiltonians}
+
+%%%%%%%%%%%%%%% ssh1 experiments
+%%% data statistics
+\newcommand\sshOneTrainNHam{556}
+\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
+\newcommand\sshOneValNHam{5000}
+\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
+\newcommand\sshOneTestNHam{1005}
+\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
+\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
+\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
+\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
+\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
+\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
+\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
+\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
+%%% real space accuracies
+%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
+%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
+%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
+%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
+%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
+%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
+%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
+
+%%% ssh1 baseline accuracy
+\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
+%%% x1 features table entries 
+\newcommand\xOne{$X_1$}
+\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
+\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
+\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
+\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
+%%% x_S1 features table entries  
+\newcommand\xSOne{$X_{\mathcal{S}_1}$}
+\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
+\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
+\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
+\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
+\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
+\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
+%%% x^c_1 features table entries  
+\newcommand\xcOne{$\hat{X}^c_1$}
+\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
+\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
+\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
+\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
+\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
+\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
+%%% x^cE_1 features table entries  
+\newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
+\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
+\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
+\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
+\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
+\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
+\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
+%%% x^cSE_1 features table entries  
+\newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
+\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
+\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
+\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
+\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
+\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
+\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
+%%% x^s_1 features table entries  
+\newcommand\xsOne{$\hat{X}^s_1$}
+\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
+\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
+\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
+\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
+\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
+\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
+%%% x^SO_1 features table entries  
+\newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
+\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
+\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
+\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
+\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
+\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
+\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
+%%% x^SSO_1 features table entries  
+\newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
+\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
+\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
+\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
+\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
+\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
+\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}
+
+%ssh2
+\newcommand\sshTwoTrainNHam{2761}
+\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
+\newcommand\sshTwoValNHam{2760}
+\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
+\newcommand\sshTwoTestNHam{1040}
+\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}
+
+\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
+\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
+\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
+\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
+\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
+
+\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
+\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
+\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
+\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
+\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
+
+\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
+\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
+\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
+\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
+\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
+\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
+
+%%% ssh2 baseline accuracy
+\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
+%%% x2 features table entries 
+\newcommand\xTwo{$X_2$}
+\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
+\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
+\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
+\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
+\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
+
+%%% x_S2 features table entries  
+\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
+\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
+\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
+\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
+\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
+\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
+%%% x^c_2 features table entries  
+\newcommand\xcTwo{$\hat{X}^c_2$}
+\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
+\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
+\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
+\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
+\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
+%%% x^cE_2 features table entries  
+\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
+\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
+\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
+\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
+\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
+\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
+
+%%% x^cSE_2 features table entries  
+\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
+\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
+\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
+\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
+\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
+\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
+%%% x^s_2 features table entries  
+\newcommand\xsTwo{$\hat{X}^s_2$}
+\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
+\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
+\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
+\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
+\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
+%%% x^SO_2 features table entries  
+\newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
+\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
+\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
+\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
+\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
+\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
+%%% x^SSO_2 features table entries  
+\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
+\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
+\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
+\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
+\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
+\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
+\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
+
+%%% more feature commands
+%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
+%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}
+
+\newcommand\xalpha{$X_\alpha$}
+\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
+
+\newcommand\xcalpha{$\hat{X}^c_\alpha$}
+\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
+\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
+
+\newcommand\xsalpha{$\hat{X}^s_\alpha$}
+\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
+\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
+
+\newcommand\nEst{25}   % number of estimators in random forest
+
+\newcounter{quoter}
+\setcounter{quoter}{0}
+\renewcommand*{\thequoter}{%
+  %\textbf{%
+  %  \ifnum\value{custom}<1000 0\fi
+  %  \ifnum\value{custom}<100 0\fi
+  %  \ifnum\value{custom}<10 0\fi
+  %  \arabic{custom}%
+  \textbf{[\arabic{quoter}]}
+  }%
+
+\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
+\newcommand{\citequote}[1]{\ref{#1}}
+
+\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
 
 \begin{document}
+
 \nocite{*}
@@
 \begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases for finite condensed matter systems from bulk data in real lattice space.
+We develop a supervised machine learning algorithm that is able to learn topological phases of finite condensed matter systems from bulk data in real lattice space.
 The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
 We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
+We further use insights obtained from these information entropy signatures to engineer global topological features from real space lattice data that still carry most of the topological information in the lattice, while greatly diminishing the size of feature space, thus effectively amounting to a topological lattice compression.
+Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which lead us to Heisenberg and Hirschman uncertainty relations for topological phase transitions.
 The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
@@
 
+The main motivation for developing a data-driven approach based on real space is that the canonical method of choice for the analysis of topological systems, i.e.
+wavevector space computations of topological invariants, is often only feasible for systems with translational symmetry, which many physical systems of current interest (e.g.
+disordered systems in condensed matter) do not have.
+Furthermore, it is not always granted that the topological invariants of a physical system being investigated are known in advance, as is presently the case for many gapless insulators.
+In such cases, being able to engineer topological features that encode the topological states of a system while at the same time reducing the system's complexity may provide an alternative strategy.
+Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
+Constructing theoretical methods to trace the distribution of information in topological systems may be an essential prerequisite to discovering new topological invariants and features.
+The data-driven approach designed in this article addresses these issues.
+%In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
+
 To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
 The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
-
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired pattern in the data.
+We describe the algorithm in detail in section \ref{the_eigenvector_ensembling_algorithm} and demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
+This is performed in section \ref{numerical_experiments}.
+
+The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learning the desired patterns in the data.
 This makes it much easier to trace the localization of relevant information along the features of a data set.
 Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the whole system emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
+This is a highly non-trivial proposition since the topological phase of a system is a global property of the system as a whole emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
 To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-
-The Shannon information entropy signals presented for the first time in this work provide a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
-
+These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}.
+
+In possession of the information entropy signatures, we demonstrate how the symmetries in real and wavevector space eigenvectors can be manipulated with signal processing tools commonly employed in audio and image processing to execute two standard unsupervised learning tasks, namely dimensionality reduction and feature engineering.
+The topological features resulting from this analysis, here denominated Discrete Cosine Transform and Discrete Sine Transform topological features, are discussed in section \ref{topological_feature_engineering}.
+
+The information entropy signatures are finally explored as theoretical constructs in terms of information entropy mass functions along the lattices.
+By taking their continuum limit and admitting that they are quantum in nature, we show how the information entropy signatures can be naturally understood in terms of emergent information entropy wave functions along the lattices.
+The theoretical formulation of the results obtained with machine learning in terms of emergent quantum mechanical wave functions allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of information entropy in topological phase transitions.
+The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}.
+
+The  description of information entropy signatures as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+
+As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
+This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were known in advance.
+By proposing new concepts from the data analysis of physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
 \begin{figure}
@@
 
-\section*{Numerical experiments}
-
+\section{The eigenvector ensembling algorithm}
+\label{the_eigenvector_ensembling_algorithm}
 The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-A detailed description of the algorithm is found in the section \textbf{The eigenvector ensembling algorithm} in the Supplementary Material.
-Here we present results of the numerical experiments we performed with it.
-We start with the results from the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), then we analize the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
-
-In each experiment our grid consisted of 6561 Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
+We describe here in detail each of these steps as they were implemented in this work.
+For a comprehensive introduction to the concepts referenced in the steps below, we recommend the book \cite{friedman2001elements}.
+\vspace{.3cm}
+\begin{enumerate}%[topsep=0pt, partopsep=0pt]
+\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
+These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
+\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
+More explicitly, assume our hopping parameters vector $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
+We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
+\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will provide $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$ to our data set.
+Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
+Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
+\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
+This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
+In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
+\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
+The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
+\end{enumerate}
+
+\vspace{.3cm}
+Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
+The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
+The intuition that eigenvectors can be used in replacement of raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
+\begin{equation}
+\label{eigen_decomposition}
+H = \sum_{i=1}^{N}\lambda^{(i)} \ket{\mathbf{v}^{(i)}}\bra{\mathbf{v}^{(i)}}
+\end{equation}
+where $\lambda^{(i)}$ is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
+It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
+By expressing the eigenvectors in a basis suitable to a particular problem (e.g.
+the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
+Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.
+
+\section{Numerical experiments}
+\label{numerical_experiments}
+We performed two numerical experiments with the eigenvector ensembling algorithm.
+The first experiment deals with the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), while the second experiment uses the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
+
+In each experiment our grid consisted of \nHam\ Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
 The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
@@
 This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a range $\epsilon = 0.01$ around the allowed winding number values.
+For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a minimum range of $\epsilon = \epsilonValue$ from the correct winding number values.
 Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
 The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
+
+As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
+These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
+Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.
 
@@
 
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiments 1 and 2 as seen from parameter space.
-The accuracy statistics presented in the following subsections and probability heatmaps shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = 100 times.
-The recovered probability heatmaps faithfully portray the phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
-
-\subsection*{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-
-Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
+Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
+The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
+Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across 100 experiments.
+The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the corresponding probability heatmaps.
+As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
+
+The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit-learn,sklearn_api}.
+
+\subsection{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
+\label{experiment_1}
+Our test set in this experiment contained \sshOneTestNHam\ Hamiltonians (approx.
+\sshOneTestFracHam\% of all data).
+Of the remaining \sshOneTrainPlusValNHam\ Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
+\sshOneTrainFracHam\%) and \sshOneValNHam\ (approx.
+\sshOneValFracHam\%) were used to compute validation scores at each iteration.
 These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number $W$ = 0 and 55.2\% with winding number $W=1$.
-Our algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
+The composition of the train + validation set for this experiment was \sshOneTrainPlusValWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTrainPlusValWindOneFracHam\% with winding number $W$ = 1.
+The composition of the test set was \sshOneTestWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTestWindOneFracHam\% with winding number $W=1$.
+Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
 
 The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (98.2\%), validation eigenvectors (96.4\%) and test eigenvectors (78.8\%).
+In particular, we report mean accuracies on training eigenvectors (\xOneEigTrain), validation eigenvectors (\xOneEigVal) and test eigenvectors (\xOneEigTest).
 Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were 100\% for training Hamiltonians, 100\% for validation Hamiltonians and 99.1\% for test Hamiltonians.
+These were \xOneHamTrain\ for training Hamiltonians, \xOneHamVal\ for validation Hamiltonians and \xOneHamTest\ for test Hamiltonians.
+When compared with the baseline test accuracy of \sshOneHamTestBaseline\ of a system that predicts the whole test set as having winding number $W=1$, the accuracy achieved on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.
 
@@
 \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 1 as seen from 2D parameter space.
+\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0-1.png}}\quad
+\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0-1.png}}
+\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0-1.png}}
+\caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
 (a) Train/validation/test split.
 (b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
+(c) Phase diagram learned from real space lattice data by combining a decision tree with eigenvector ensembling.}
 \label{figexp1_exp}
@@
 
-\subsection*{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{exp2}
+\subsection{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
+\label{experiment_2}
 
 This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with 25 decision trees.
-Our data set consisted of 1040 (15.8\%) test Hamiltonians.
-The remaining Hamiltonians are randomly split in half between training and validation sets at each iteration, giving 2761 (42.1\%) training Hamiltonians and 2760 (42.1\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (17.9\%), $W$ = 0 (32.5\%), $W$ = 1 (32.3\%) and $W$ = 2 (17.3\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (36.3\%), $W$ = 0 (11.1\%), $W$ = 1 (12.7\%) and $W$ = 2 (39.9\%).
-
-Mean accuracies across 100 repetitions of experiment 2 were 99.9\% for training eigenvectors, 97.1\% for validation eigenvectors and 66.4\% for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were 100\% for training Hamiltonians, 99.7\% for validation Hamiltonians and 88.2\% for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from 66.4\% eigenvector accuracy to 88.2\% Hamiltonian accuracy) attests to its power.
+For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with \nEst\ decision trees.
+Our data set consisted of \sshTwoTestNHam\ (\sshTwoTestFracHam\%) test Hamiltonians.
+The remaining \sshTwoTrainPlusValNHam\ Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\sshTwoTrainFracHam\%) training Hamiltonians and \sshTwoValNHam\ (\sshTwoValFracHam\%) validation Hamiltonians.
+The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\sshTwoTrainPlusValWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTrainPlusValWindZeroFracHam\%), $W$ = 1 (\sshTwoTrainPlusValWindOneFracHam\%) and $W$ = 2 (\sshTwoTrainPlusValWindTwoFracHam\%).
+The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\sshTwoTestWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTestWindZeroFracHam\%), $W$ = 1 (\sshTwoTestWindOneFracHam\%) and $W$ = 2 (\sshTwoTestWindTwoFracHam\%).
+
+Mean accuracies across \nExp\ repetitions of experiment 2 were \xTwoEigTrain\ for training eigenvectors, \xTwoEigVal\ for validation eigenvectors and \xTwoEigTest\ for test eigenvectors.
+Mean accuracies resulting from eigenvector ensembling were \xTwoHamTrain\ for training Hamiltonians, \xTwoHamVal\ for validation Hamiltonians and \xTwoHamTest\ for test Hamiltonians.
+The large accuracy gain achieved by eigenvector ensembling in the test set (going from \xTwoEigTest\ eigenvector accuracy to \xTwoHamTest\ Hamiltonian accuracy) attests to its power.
+The effectiveness of eigenvector ensembling is also evident from the much worse performance (\sshTwoHamTestBaseline) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
 
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 2 as seen from 2D parameter space.
+\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0-2.png}}\quad
+\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0-2.png}}
+\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0-2.png}}
+\caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
 (a) Train/validation/test split.
 (b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
+(c) Phase diagram learned from real space lattice data by combining a random forest with eigenvector ensembling.}
 \label{figexp2_exp}
@@
 
-\section*{Information entropy signatures}
+\section{Information entropy signatures}
+\label{information_entropy_signatures}
 
 We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test our algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
-
-The (normalized) relevance of a feature is given by how much it reduces a loss function (e.g.
-Shannon information entropy or Gini impurity \cite{friedman2001elements}).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 and experiment 2 we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
+Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test the eigenvector ensembling algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
+
+The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of ensembles of eigenvectors).
+By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
 These signals are the information entropy signatures of each topological phase transition.
 
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for experiments 1 and 2.
+We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy as cost function.
+This would similarly lead us to Gini impurity signatures of topological phase transitions.
+Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures were very similar, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
+Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely undecided \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
+
+The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for each experiment.
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1, only six lattice sites $S_1$ = (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 was achieved by eighteen lattice sites $S_2$ = (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-
-Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e, number of unit cells) used to compute them.
+For experiment 1 (section \ref{experiment_1}), only six lattice sites (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
+
+The information entropy signatures presented here have some interesting subtleties.
+Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
+In section \ref{emergent_information_entropy_wave_functions}, where we develop a quantum formalism for the information entropy signatures obtained in this section, these seemingly antagonistic conceptions shall be harmonized.
+What is important to emphasize at this point is that an information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
+
+To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
+This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
+The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
+In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
+
+Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
+In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
 They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-We present the information entropy signatures for longer lattices in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
-
-To see if learning the topological phases can be achieved efficiently by employing simpler models we reran experiments 1 and 2 using only a small subset of most relevant lattice sites.
-In our rerun of experiment 1 using only lattice sites $S'_1$ = (0, 50, 51, 99) (which contributed approximately 45 \% of total reduction in Shannon information entropy in experiment 1), mean accuracies were 97.0\% for training eigenvectors, 91.5\% for validation eigenvectors and 72.8\% for test eigenvectors.
-Mean accuracies obtained from eigenvector ensembling were 99.1\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 94.5\% for test Hamiltonians.
-
-Mean accuracies for our rerun of experiment 2 using only lattice sites $S'_2$ = (0, 1, 3, 48, 50, 51, 96, 98, 99) (which contributed approximately 20 \% of total reduction in Shannon information entropy in experiment 2) were 99.9\% for training eigenvectors, 87.7\% for validation eigenvectors and 47.3\% for test eigenvectors.
-Eigenvector ensembling yields mean accuracies of 100\% for training Hamiltonians, 99.5\% for validation Hamiltonians and 74.5\% for test Hamiltonians.
-
-These results demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
@@
 \centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/periodic_100_6561/merge_imshow_winding_grids_second_sim.png}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1.
+\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim-1.png}}
+\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim-1.png}}
+\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim-1.png}}
+\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
 Heatmaps were averaged across all 100 iterations of the experiment.
@@
 \centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/periodic_100_6561/merge_imshow_winding_grids_sim.png}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2.
+\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim-2.png}}
+\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim-2.png}}
+\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim-2.png}}
+\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim-2.png}}
+\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim-2.png}}
+\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
 Heatmaps were averaged across all 100 iterations of the experiment.
@@
 
-\section*{Discussion}
+\begin{table}
+\begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
+%\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.} \label{numerical_results}
+%\begin{table}[th]
+%\caption{An Example of a Table}
+%\centering\label{table_example}
+%\begin{tabular}{|Sc*{9}{c|}}
+\toprule
+\SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd 
+\midrule
+%                     &                  &                   &                   &                     &                   \tableRow{0.3}
+1                     &\xOne             &\xOneEigVal        &\xOneEigTest       &\xOneHamVal          &\xOneHamTest       \tableRowEnd
+1                     &\xSOne            &\xSOneEigVal       &\xSOneEigTest      &\xSOneHamVal         &\xSOneHamVal       \tableRowEnd
+1                     &\xcOne            &\xcOneEigVal       &\xcOneEigTest      &\xcOneHamVal         &\xcOneHamTest      \tableRowEnd
+1                     &\xcEOne           &\xcEOneEigVal      &\xcEOneEigTest     &\xcEOneHamVal        &\xcEOneHamTest     \tableRowEnd
+1                     &\xcSEOne          &\xcSEOneEigVal     &\xcSEOneEigTest    &\xcSEOneHamVal       &\xcSEOneHamTest    \tableRowEnd
+1                     &\xsOne            &\xsOneEigVal       &\xsOneEigTest      &\xsOneHamVal         &\xsOneHamTest      \tableRowEnd
+1                     &\xsOOne           &\xsOOneEigVal      &\xsOOneEigTest     &\xsOOneHamVal        &\xsOOneHamTest     \tableRowEnd
+1                     &\xsSOOne          &\xsSOOneEigVal     &\xsSOOneEigTest    &\xsSOOneHamVal       &\xsSOOneHamTest    \tableRowEnd
+2                     &\xTwo             &\xTwoEigVal        &\xTwoEigTest       &\xTwoHamVal          &\xTwoHamTest       \tableRowEnd
+2                     &\xSTwo            &\xSTwoEigVal       &\xSTwoEigTest      &\xSTwoHamVal         &\xSTwoHamVal       \tableRowEnd
+2                     &\xcTwo            &\xcTwoEigVal       &\xcTwoEigTest      &\xcTwoHamVal         &\xcTwoHamTest      \tableRowEnd
+2                     &\xcETwo           &\xcETwoEigVal      &\xcETwoEigTest     &\xcETwoHamVal        &\xcETwoHamTest     \tableRowEnd
+2                     &\xcSETwo          &\xcSETwoEigVal     &\xcSETwoEigTest    &\xcSETwoHamVal       &\xcSETwoHamTest    \tableRowEnd
+2                     &\xsTwo            &\xsTwoEigVal       &\xsTwoEigTest      &\xsTwoHamVal         &\xsTwoHamTest      \tableRowEnd
+2                     &\xsOTwo           &\xsOTwoEigVal      &\xsOTwoEigTest     &\xsOTwoHamVal        &\xsOTwoHamTest     \tableRowEnd
+2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
+\bottomrule
+\end{tabular}
+\caption{\label{accuracy_scores}Accuracy scores of numerical experiments.
+The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH systems were as follows.
+Real space features: all real space lattice sites (\xalpha) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ (\xSalpha) (equation \eqref{lattice_subsets}).
+DCT topological features: all DCT topological features (\xcalpha) (equation \eqref{DCT}); DCT topological features from subset $\mathcal{E}_\alpha$ (\xcEalpha) (equation \eqref{DCT_subsets}); DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xcSEalpha) (equation \eqref{DCT_very_compressed}).
+DST topological features: all DST topological features (\xsalpha) (equation \eqref{DST}); DST topological features from subset $\mathcal{O}_\alpha$ (\xsOalpha) (equation \eqref{DST_subsets}); DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xsSOalpha) (equation \eqref{DST_very_compressed}).
+}
+\end{table}
+
+\section{Topological feature engineering and lattice compression}
+\label{topological_feature_engineering}
+
+In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective.
+As we shall see, this will enable us to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
+
+As a cursory glance at figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} seems to suggest, the existence of peaks and symmetries in information entropy signatures can be exploited as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
+Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
+Here we show how the symmetries in real space eigenvectors and information entropy signatures can be exploited to engineer new global topological features, leading to an effective compression of topological information.
+
+%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
+Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
+
+%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
+
+Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
+\begin{equation}
+\label{discrete_fourier_transform}
+\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
+\end{equation}
+Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
+The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
+\begin{equation}
+\label{hermitian_symmetry}
+\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
+\end{equation}
+where  we have used the notation $\overline{k} = k \mod N$.
+
+Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
+In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
+This leads us to the Discrete Cosine Transform (DCT) topological features,
+\begin{equation}
+\label{DCT}
+\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
+\end{equation}
+where $M = \frac{N}{2}+1$.
+The second path capitalizes on the fact that the imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
+\begin{equation}
+\label{DST}
+\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
+\end{equation} 
+where $M = \frac{N}{2}-1$.
+
+The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
+the sites $0 \leq l \leq \frac{N}{2}$.
+This is due to the fact that each equation assumes that the eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
+While these assumptions are strictly true for the eigenvector representations in wavevector space, they are not generally true for the real space representations.
+Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from one half of the lattice to the other.
+
+The topological feature engineering techniques described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
+As equations \eqref{hermitian_symmetry}-\eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from the existence of certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
+
+We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
+The accuracy scores obtained in each experiment are listed in table \ref{accuracy_scores}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
+
+The lattice compression strategies tested in this work were: \emph{i)} learning topological phases from only a subset of real space lattice sites; \emph{ii)} learning topological phases from the DCT or DST engineered features of equations \eqref{DCT} and \eqref{DST}; \emph{iii)} learning topological phases from a fraction of the DCT or DST topological features and \emph{iv)} learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
+
+In strategy \emph{i)} the lattice sites used in the SSH 1 and SSH 2 systems were
+\begin{equation}
+\label{lattice_subsets}
+\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
+\end{equation}
+Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq l \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
+Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq l \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
+In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xSOne and \xSTwo, according to the SSH systems they relate to.
+
+In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
+These features are denoted in table \ref{accuracy_scores} by \xcOne, \xsOne, \xcTwo, \xsTwo, according to which set of topological features and SSH systems they refer to.
+
+Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the most informative DCT topological features of both SSH 1 and SSH 2 systems that were obtained from strategy \emph{ii)},
+\begin{equation}
+\label{DCT_subsets}
+\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
+\end{equation}
+and the most informative DST topological features of both systems that were obtained from strategy \emph{ii)} as well,
+\begin{equation}
+\label{DST_subsets}
+\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
+\end{equation}
+The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space subset used with each SSH system.
+
+The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
+It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
+Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
+Mathematically, we can express the topological features used in strategy \emph{iv)} as follows:
+\begin{equation}
+\label{DCT_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}^*} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
+\end{equation}
+\begin{equation}
+\label{DST_very_compressed}
+\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}
+\end{equation}
+where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$ and $\mathcal{S}^*$ is the complement of $\{0,M-1\}$ with respect to $\mathcal{S}$,
+\begin{equation}
+\label{indicator_function}
+\indicator{\mathcal{S}}[l] = \begin{cases}
+      1 & \text{if } l \in \mathcal{S} \\
+      0 & \text{otherwise}
+    \end{cases}, \qquad \mathcal{S}^* = \mathcal{S}{\backslash} \{0,M-1\}.
+\end{equation}
+The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used, which components in real and wavevector space engineered them and the appropriate SSH systems.
+
+The results shown in table \ref{accuracy_scores} bring some startling surprises.
+For example, the topological phase transition boundaries of SSH 1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores for the features \xSOne.
+The same appears to be true to SSH 2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
+
+Even more striking is the performance achieved by the compressed DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
+For SSH 1 systems, they perform on par with using the full set of real space features \xOne, while for SSH 2 systems a small loss in accuracy is incurred relative to the full set of real space features \xTwo.
+
+Another interesting insight comes from comparing the accuracy scores obtained with the DCT topological features versus the  DST topological features.
+The latter have poorer performance than the former, as is indicated by the sharp drops in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
+This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
+
+The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
+In this sense, key topological information can be said to be localized on few sites in the lattice.
+We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+
+\section{Emergent information entropy wave functions}
+\label{emergent_information_entropy_wave_functions}
+
+The information entropy signatures that we have been investigating pose an immediate theoretical question: how can a signal that is locally defined arise from a global property of the whole SSH lattice?
+In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
+Our goal is to arrive at a theoretical framework that will allow us to interpret the information entropy signatures in terms of quantum mechanics.
+%The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
+
+We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
+macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices, which themselves become 1D manifolds.
+By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuum limit will be given by
+
+\begin{equation}
+\label{entropy_density}
+F_S(x) = \int_{\ell}^{(x)}\rho_S(x')dx'
+\end{equation}
+where $\rho_S(x)$ is the local information entropy density function in the continuum limit and $x$ is defined by the coordinate system specified on the 1D manifold $\ell$.
+The index $S$ is meant to emphasize that in this paper we have used Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
+Gini impurity.
+
+Our use of periodic boundary conditions implies that the coordinate $x$ should be defined on the circle $ S^1 = [0, 1]/R$, where $R$ is the equivalence relation in $[0,1]$ defining the circle $S^1$ , 
+\begin{equation}
+x \text{ } R \text{ } y \iff x=y \text{ or } (x,y)\in \{(0,1), (1,0)\}.
+\end{equation}
+For open boundary conditions, the spatial coordinate $x$ is defined on the closed interval $[0,1]$ or, in the case of infinite systems, $\mathbb{R}$.
+However, for the sake of generality, we shall continue to use the caligraphic $\ell$ to denote an arbitrary 1D manifold in this section.
+
+Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial information entropy wave function,
+
+\begin{equation}
+\label{shannon_wave_function}
+\rho_S(x) = |\psi_S(x)|^2,
+\end{equation}
+the local density of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
+
+\begin{equation}
+\label{born_rule_spatial}
+\rho_S(x) = |\braket{x|\psi_S}|^2.
+\end{equation}
+
+The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform 
+\begin{equation}
+\label{fourier_shannon_wave_function}
+\hat{\psi}_S(k) = \int_{\ell}\psi_S(x)e^{-2\pi ikx}dx
+\end{equation}
+from which the information entropy density function in wavevector space can be computed,
+\begin{equation}
+\label{shannon_wave_function_wavevector_space}
+\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
+\end{equation}
+
+The interpretation of information entropy signatures in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
+Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+
+Let us denote the mean, the variance and the entropy associated with the probability distribution $\rho_S$ by $\mu_{\rho_S}$, $\sigma_{\rho_S}^2 $ and $H_{\rho_S}$ respectively. Explicitly, we have 
+\begin{subequations}
+\label{statistics}
+\begin{equation}
+\label{mean}
+\mu_{\rho_S} = \int_{\ell}x\rho_S(x)dx,
+\end{equation}
+\begin{equation}
+\label{variance}
+\sigma_{\rho_S}^2 = \int_{\ell}(x-\mu_{\rho_S})^2\rho_S(x)dx,\quad \text{and}
+\end{equation}
+\begin{equation}
+\label{entropy}
+H_{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
+\end{equation}
+\end{subequations}
+with analogous equations for the wavevector space counterparts $\mu_{\hat{\rho}_S}$, $\sigma_{\hat{\rho}_S}^2 $ and $H_{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
+
+In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}:
+
+\begin{enumerate}
+\item[i)] \emph{the Heisenberg uncertainty principle}
+\begin{equation}
+\label{heisenberg}
+\sigma_{\rho_S} \cdot \sigma_{\hat{\rho}_S} \geq \frac{1}{4\pi}, \quad \text{and }
+\end{equation}
+\item[ii)] \emph{the Hirschman entropic uncertainty}
+\begin{equation}
+\label{hirschman}
+H_{\rho_S} + H_{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). 
+\end{equation}
+\end{enumerate}
+
+The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signatures} from sheer data analysis of finite SSH systems in real space.
+In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
+
+Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
+Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
+
+\section{Discussion}
+\label{discussion}
 
 Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have implemented a data-driven approach to the search for new topological materials bypassing the use of wavevector space data.
+Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
+
+By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical and theoretical possibilities offered by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
 
 The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to wavevector space methods.
-
-An advantage of using data from real space is that it enables us to investigate how topological information is distributed in the system.
-This was demonstrated by the information entropy signatures recovered from the Shannon entropy of ensembles of eigenvectors in each experiment.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning can be an important tool in the investigation and discovery of new quantum materials.
-
-We should remark on the subtleties of the information entropy signatures presented here.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, these importances actually express a global property of the whole lattice.
-Therefore, a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
-To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites in the subset.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
-Furthermore, it should be emphasized that these signals were recovered from the analysis of data from several thousand SSH systems in each experiment and therefore they are not a property of a single SSH lattice.
-They are rather a pattern that emerges from correlating topological phase with lattice eigenvector data for several SSH systems.
-
-We performed several tests on the information entropy signatures.
-By rerunning each experiment with longer lattices (i.e.
-increasing the number of unit cells) we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-The macroscopic limit of these information entropy signals may be an important signature of topological systems and thus merits further theoretical investigation.
-A detailed discussion of this point is presented in the section \textbf{Information entropy signatures in the macroscopic limit} in the Supplementary Material.
+Such systems usually break translational symmetry and therefore are not amenable to canonical wavevector space methods.
+Thus, the discovery and engineering of topological features from real space data as demonstrated in this work carries great promise to the theoretical investigation of these systems.
+
+Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
+On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy is a necessary commodity to ensure error-correction within the system.
+We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
+
+As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
+This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment executed in section \ref{numerical_experiments} and led us to the new topological features of section \ref{topological_feature_engineering} and the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
+The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
+
+The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
+This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information is most readily available in the SSH lattices investigated.
+
+This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
+In \cite{zhang2020interpreting}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
+We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
+In our paper we preferred the term \emph{model explainability}, as we used similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
+While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.
 
 Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given that topological signals such as the ones shown in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} are measured in terms of quantities that have actual physical meaning such as Shannon information entropy or Gini impurity, the results presented here suggest a new road for theoretical investigation.
-Whether there is any relationship between local topological markers and the information entropy of the ensemble of eigenvectors is left for speculation.
+Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} which were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
+Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave functions discussed here is left for speculation.
 
@@
 This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
-It is therefore expected that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+
+As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
+This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
+An approach based on eigenvector ensembling can be of use in such situations both as a dimensionality reduction tool and as a sampling strategy.
+The first case was illustrated in this work, where it was shown that relevant topological information of SSH systems can be retrieved from few sites in a lattice, which can be exploited as a dimensionality reduction strategy.
+The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
+Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in dimensionality  while still capturing all the relevant physics of a system.
+We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
+
+Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
+In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
+This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
+Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.
 
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/periodic_100_6561/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/periodic_100_6561/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions from experiments 1 and 2.
-(a) In experiment 1, the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-These two peaks correspond to the lattice sites $S_1$.
-(b) In experiment 2, the three visible peaks account for approximately 30\% of reduction in information entropy.
-These three peaks are located along lattice sites $S_2$.}
+\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances-1.png}}\quad
+\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances-2.png}}\quad
+\caption{Information entropy signatures of the topological phase transitions from the numerical experiments of section \ref{numerical_experiments}.
+(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
+(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.}
 \label{feature_importances}
@@
 
-%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{56}%
+%%%%%%%%%% Bibliography %%%%%%%%%%%%%
+
+\begin{thebibliography}{63}%
 \makeatletter
@@
   {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gilpin}\ \emph {et~al.}(2018)\citenamefont {Gilpin},
+  \citenamefont {Bau}, \citenamefont {Yuan}, \citenamefont {Bajwa},
+  \citenamefont {Specter},\ and\ \citenamefont {Kagal}}]{gilpin2018explaining}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~H.}\ \bibnamefont
+  {Gilpin}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Bau}},
+  \bibinfo {author} {\bibfnamefont {B.~Z.}\ \bibnamefont {Yuan}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Bajwa}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Specter}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Kagal}},\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {2018 IEEE 5th International Conference on data science
+  and advanced analytics (DSAA)}}}\ (\bibinfo {organization} {IEEE},\ \bibinfo
+  {year} {2018})\ pp.\ \bibinfo {pages} {80--89}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Do{\v{s}}ilovi{\'c}}\ \emph
+  {et~al.}(2018)\citenamefont {Do{\v{s}}ilovi{\'c}}, \citenamefont
+  {Br{\v{c}}i{\'c}},\ and\ \citenamefont
+  {Hlupi{\'c}}}]{dovsilovic2018explainable}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~K.}\ \bibnamefont
+  {Do{\v{s}}ilovi{\'c}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Br{\v{c}}i{\'c}}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Hlupi{\'c}}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {2018 41st
+  International convention on information and communication technology,
+  electronics and microelectronics (MIPRO)}}}\ (\bibinfo {organization}
+  {IEEE},\ \bibinfo {year} {2018})\ pp.\ \bibinfo {pages}
+  {0210--0215}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Roscher}\ \emph {et~al.}(2020)\citenamefont
+  {Roscher}, \citenamefont {Bohn}, \citenamefont {Duarte},\ and\ \citenamefont
+  {Garcke}}]{roscher2020explainable}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Roscher}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bohn}},
+  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Duarte}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Garcke}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Access}\ }\textbf {\bibinfo
+  {volume} {8}},\ \bibinfo {pages} {42200} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
+  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
+  {Tibshirani}}]{friedman2001elements}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
+  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
+  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
+  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
+  {year} {2001})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pedregosa}\ \emph {et~al.}(2011)\citenamefont
+  {Pedregosa}, \citenamefont {Varoquaux}, \citenamefont {Gramfort},
+  \citenamefont {Michel}, \citenamefont {Thirion}, \citenamefont {Grisel},
+  \citenamefont {Blondel}, \citenamefont {Prettenhofer}, \citenamefont {Weiss},
+  \citenamefont {Dubourg}, \citenamefont {Vanderplas}, \citenamefont {Passos},
+  \citenamefont {Cournapeau}, \citenamefont {Brucher}, \citenamefont {Perrot},\
+  and\ \citenamefont {Duchesnay}}]{scikit-learn}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pedregosa}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Varoquaux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gramfort}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Michel}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Thirion}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Blondel}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Weiss}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Dubourg}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Vanderplas}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Passos}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Cournapeau}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Brucher}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Perrot}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Duchesnay}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Machine Learning Research}\ }\textbf
+  {\bibinfo {volume} {12}},\ \bibinfo {pages} {2825} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Buitinck}\ \emph {et~al.}(2013)\citenamefont
+  {Buitinck}, \citenamefont {Louppe}, \citenamefont {Blondel}, \citenamefont
+  {Pedregosa}, \citenamefont {Mueller}, \citenamefont {Grisel}, \citenamefont
+  {Niculae}, \citenamefont {Prettenhofer}, \citenamefont {Gramfort},
+  \citenamefont {Grobler}, \citenamefont {Layton}, \citenamefont {VanderPlas},
+  \citenamefont {Joly}, \citenamefont {Holt},\ and\ \citenamefont
+  {Varoquaux}}]{sklearn_api}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Buitinck}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Louppe}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Blondel}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Pedregosa}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Mueller}}, \bibinfo {author} {\bibfnamefont
+  {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Niculae}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Gramfort}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Grobler}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Layton}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {VanderPlas}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Joly}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Holt}}, \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Varoquaux}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {ECML PKDD
+  Workshop: Languages for Data Mining and Machine Learning}}}\ (\bibinfo {year}
+  {2013})\ pp.\ \bibinfo {pages} {108--122}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
@@
   (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
-  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
-  {Tibshirani}}]{friedman2001elements}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
-  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
-  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
-  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
-  {year} {2001})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Raileanu}\ and\ \citenamefont
+  {Stoffel}(2004)}]{raileanu2004theoretical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~E.}\ \bibnamefont
+  {Raileanu}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Stoffel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Annals of Mathematics and Artificial Intelligence}\ }\textbf {\bibinfo
+  {volume} {41}},\ \bibinfo {pages} {77} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2020)\citenamefont {Zhang},
+  \citenamefont {Ginsparg},\ and\ \citenamefont {Kim}}]{zhang2020interpreting}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Ginsparg}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Research}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {023283}
+  (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
@@
 \end{thebibliography}%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-07-25 10_prb_resubmission_01/01_supplementary/supplementary.tex
Generated new arxiv submission

--- 2020-07-23 07_paper/article.tex
@@
 \documentclass[10pt]{revtex4-1}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
 \usepackage{graphicx}
@@
 \usepackage[resetlabels, labeled]{multibib}
-\usepackage{xcolor}
-\usepackage{bbm}
-\usepackage{xfp}
-\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
-\usepackage{booktabs}
-\renewcommand{\figurename}{Figure}
-\renewcommand{\tablename}{Table}
-\renewcommand{\thetable}{\arabic{table}}
-%\captionsetup{justification=raggedright, singlelinecheck = false}
-%\usepackage{makecell}
-%\usepackage{cellspace}
-
 %\newcites{supp}{References}
-
-%\def\basiceval#1{\the\numexpr#1\relax}
 
@@
 \newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
-\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative
+\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional
+                                %derivative
 
-%ssh1
-
-%Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
-%These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
-
-%\documentclass{article}
-%\usepackage{xfp}
-
-%\begin{document}
-
-%\fpeval{31/45}
-
-%\fpeval{round(31/45,5)}
-
-%\end{document}
-\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
-%%%%%% Numerical experiments parameters
-\newcommand\nPrec{2}    % precision digits
-\newcommand\accPrec{4}  % precision digits for accuracy scores
-\newcommand\nHam{6561}  % total number of hamiltonians
-\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
-\newcommand\nExp{100}   % number of experiments
-%%%table commands
-%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
-\newcommand{\tableRow}[1]{\\[#1 cm]}
-\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
-\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
-\newcommand\tableRowEnd{\tableRow{0.15}}
-%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
-%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
-%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
-%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
-%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
-%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
-\newcommand\SSHSys{SSH system}         
-\newcommand\Feat{Features}              
-\newcommand\ValEig{Val. eigenvectors}   
-\newcommand\TestEig{Test eigenvectors}  
-\newcommand\ValHam{Val. Hamiltonians}   
-\newcommand\TestHam{Test Hamiltonians}
-
-%%%%%%%%%%%%%%% ssh1 experiments
-%%% data statistics
-\newcommand\sshOneTrainNHam{556}
-\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneValNHam{5000}
-\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
-\newcommand\sshOneTestNHam{1005}
-\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
-\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
-\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
-\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
-\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-%%% real space accuracies
-%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
-%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
-%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
-%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
-%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
-%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
-%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
-
-%%% ssh1 baseline accuracy
-\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
-%%% x1 features table entries 
-\newcommand\xOne{$X_1$}
-\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
-\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
-\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
-\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
-%%% x_S1 features table entries  
 \newcommand\xSOne{$X_{\mathcal{S}_1}$}
-\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
-\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
-\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
-\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
-\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
-\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
-%%% x^c_1 features table entries  
-\newcommand\xcOne{$\hat{X}^c_1$}
-\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
-\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
-\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
-\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
-\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
-\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
-%%% x^cE_1 features table entries  
-\newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
-\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
-\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
-\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
-\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
-\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
-\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
-%%% x^cSE_1 features table entries  
 \newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
-\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
-\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
-\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
-\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
-\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
-\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
-%%% x^s_1 features table entries  
-\newcommand\xsOne{$\hat{X}^s_1$}
-\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
-\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
-\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
-\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
-\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
-\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
-%%% x^SO_1 features table entries  
-\newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
-\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
-\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
-\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
-\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
-\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
-\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
-%%% x^SSO_1 features table entries  
 \newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
-\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
-\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
-\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
-\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
-\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
-\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}
-
-%ssh2
-\newcommand\sshTwoTrainNHam{2761}
-\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoValNHam{2760}
-\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
-\newcommand\sshTwoTestNHam{1040}
-\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}
-
-\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
-\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
-\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
-\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
-\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-
-\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
-\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
-\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
-\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
-\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-
-\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
-\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
-\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
-\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
-\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
-\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
-
-%%% ssh2 baseline accuracy
-\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
-%%% x2 features table entries 
-\newcommand\xTwo{$X_2$}
-\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
-\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
-\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
-\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
-\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
-
-%%% x_S2 features table entries  
 \newcommand\xSTwo{$X_{\mathcal{S}_2}$}
-\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
-\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
-\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
-\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
-\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
-%%% x^c_2 features table entries  
-\newcommand\xcTwo{$\hat{X}^c_2$}
-\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
-\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
-\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
-\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
-\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
-%%% x^cE_2 features table entries  
-\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
-\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
-\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
-\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
-\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
-\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
-
-%%% x^cSE_2 features table entries  
 \newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
-\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
-\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
-\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
-\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
-\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
-%%% x^s_2 features table entries  
-\newcommand\xsTwo{$\hat{X}^s_2$}
-\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
-\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
-\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
-\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
-\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
-%%% x^SO_2 features table entries  
-\newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
-\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
-\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
-\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
-\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
-\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
-%%% x^SSO_2 features table entries  
 \newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
-\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
-\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
-\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
-\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
-\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
-
-%%% more feature commands
-%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
-%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}
-
-\newcommand\xalpha{$X_\alpha$}
-\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
-
-\newcommand\xcalpha{$\hat{X}^c_\alpha$}
-\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
-\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
-
-\newcommand\xsalpha{$\hat{X}^s_\alpha$}
-\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
-\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
-
-\newcommand\nEst{25}   % number of estimators in random forest
-
-\newcounter{quoter}
-\setcounter{quoter}{0}
-\renewcommand*{\thequoter}{%
-  %\textbf{%
-  %  \ifnum\value{custom}<1000 0\fi
-  %  \ifnum\value{custom}<100 0\fi
-  %  \ifnum\value{custom}<10 0\fi
-  %  \arabic{custom}%
-  \textbf{[\arabic{quoter}]}
-  }%
-
-\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
-\newcommand{\citequote}[1]{\ref{#1}}
-
-\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
 
 \begin{document}
-
 \nocite{*}
-
-\title{Machine learning topological phases in real space}
-
-\author{N. L. Holanda}
-\email{linneuholanda@gmail.com, linneu@cbpf.br}
-\affiliation{Integrated Quantum Materials, Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-
-\author{M. A. S. Griffith}
-\email{griffithphys@gmail.com}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
-
-\date{\today }
-
-\begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases of finite condensed matter systems from bulk data in real lattice space.
-The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
-We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
-We further use insights obtained from these information entropy signatures to engineer global topological features from real space lattice data that still carry most of the topological information in the lattice, while greatly diminishing the size of feature space, thus effectively amounting to a topological lattice compression.
-Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which allows us to establish Heisenberg and Hirschman uncertainty relations for topological phase transitions.
-The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-\label{introduction}
-The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}.
-These materials feature previously unthought-of traits like bulk insulation coupled with metallic conductance at the surface and the splitting of currents according to spin orientation.
-Adding to that, these properties are protected by non-trivial topology that renders them robust to many sources of perturbation like thermal noise.
-Such characteristics make them promising candidates to being the cornerstone of 21st century technologies like spintronics and quantum computing.
-
-These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
-Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.
-
-The SSH model is the simplest tight-binding model that exhibits a topological phase transition.
-As such, it can be viewed as the \emph{Drosophila} of the field, providing a simple framework for testing new techniques.
-The model can be expressed in terms of creation and annihilation operators by the Hamiltonian
-\begin{equation}
-\label{SSH_ham}
-\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-and describes e.g.
-the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material).
-The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.
-
-Many recent papers have explored the possibility of treating the general problem of determining phase transition boundaries of physical systems as machine learning tasks \cite{carrasquilla2017machine}$^-$\cite{rodriguez2018identifying}.
-In the particular case of topological phase transitions, the usual approach for supervised learning is to generate a data set $\big(H_1(k), W_1\big)$, ..., $\big(H_n(k), W_n\big)$ whose inputs are representations of Hamiltonians in wavevector space $H_i(k)$ and targets are their corresponding topological invariants $W_i$ (for the SSH model the topological invariant is the winding number).
-Our paper extends this task to the case of learning topological phase diagrams from input data in real space.
-Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-The main motivations for developing a data-driven approach based on real space are that wavevector space computations of topological invariants are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-The data-driven approach described in this article addresses these issues.
-In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
-
-To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
-The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We describe the algorithm in detail in section \ref{the_eigenvector_ensembling_algorithm} and demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
-This is performed in section \ref{numerical_experiments}.
-
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learn the desired patterns in the data.
-This makes it much easier to trace the localization of relevant information along the features of a data set.
-Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the system as a whole emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
-To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}.
-
-In possession of the information entropy signatures, we demonstrate how the symmetries in real and wavevector space eigenvectors can be manipulated with signal processing tools commonly employed in audio and image processing to execute two standard unsupervised learning tasks, namely dimensionality reduction and feature engineering.
-The topological features resulting from this analysis, here denominated Discrete Cosine Transform and Discrete Sine Transform topological features, are discussed in section \ref{topological_feature_engineering}.
-
-The information entropy signatures are finally explored as theoretical constructs in terms of information entropy mass functions along the lattices.
-By taking their continuum limit and admitting that they are quantum in nature, we show how the information entropy signatures can be naturally understood in terms of emergent information entropy wave functions along the lattices.
-The theoretical formulation of the results obtained with machine learning in terms of emergent quantum mechanical wave functions allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of information entropy in topological phase transitions.
-The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}.
-
-The  description of information entropy signatures as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
-
-As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
-This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were known in advance.
-By proposing new concepts from the data analysis of physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh1.png}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{./phase_diagrams/ssh2.png}}
-\caption{Phase diagrams in parameter space.
-a) SSH model with first-neighbor hoppings $t_1$ and $t_2$.
-The (red) regions with winding number $W$ = 0 are trivial, while the (blue) regions with winding number $W$ = 1 are topologically non-trivial.
-b) SSH model with first ($t_1$ and $t_2$) and second ($T_1$ and $T_2$) nearest-neighbor hoppings.
-In this article we set $t_1$ = $t_2$ = 1 and renamed the variables $T_1$ $\rightarrow$ $t_1$, $T_2$ $\rightarrow$ $t_2$ for convenience.
-The (orange) region with winding number $W$ = 0 is trivial while the others with winding numbers $W$ = -1, $W$ = 1 and $W$ = 2 (red, green and blue respectively) are topologically non-trivial.}
-\label{fig:phasediagrams}
-\end{figure}
-
-\section{The eigenvector ensembling algorithm}
-\label{the_eigenvector_ensembling_algorithm}
-The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-We describe here in detail each of these steps as they were implemented in this work.
-For a comprehensive introduction to the concepts referenced in the steps below, we recommend the book \cite{friedman2001elements}.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our hopping parameters vector $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will provide $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$ to our data set.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
-
-\vspace{.3cm}
-Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
-The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
-The intuition that eigenvectors can be used in replacement of raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
-\begin{equation}
-\label{eigen_decomposition}
-H = \sum_{i=1}^{N}\lambda^{(i)} \ket{\mathbf{v}^{(i)}}\bra{\mathbf{v}^{(i)}}
-\end{equation}
-where $\lambda^{(i)}$ is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
-It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
-By expressing the eigenvectors in a basis suitable to a particular problem (e.g.
-the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
-Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.
-
-\section{Numerical experiments}
-\label{numerical_experiments}
-We performed two numerical experiments with the eigenvector ensembling algorithm.
-The first experiment deals with the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), while the second experiment uses the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
-
-In each experiment our grid consisted of \nHam\ Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
-The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
-
-This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a minimum range of $\epsilon = \epsilonValue$ from the correct winding number values.
-Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
-The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
-
-As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
-These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.
-
-When generating the Hamiltonians we applied periodic boundary conditions to eliminate border effects.
-This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.
-The choice of periodic boundary conditions also implies that the information recovered from real space data comes from the bulk of the topological systems considered and therefore provides strong evidence for the existence of topological signatures in the bulk of such systems.
-
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
-The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
-Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across $n_{exp}$ experiments.
-The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the correponding probability heatmaps.
-As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
-
-The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit-learn,sklearn_api}.
-
-\subsection{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-\label{experiment_1}
-Our test set in this experiment contained \sshOneTestNHam\ Hamiltonians (approx.
-\sshOneTestFracHam\% of all data).
-Of the remaining \sshOneTrainPlusValNHam\ Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
-\sshOneTrainFracHam\%) and \sshOneValNHam\ (approx.
-\sshOneValFracHam\%) were used to compute validation scores at each iteration.
-These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was \sshOneTrainPlusValWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTrainPlusValWindOneFracHam\% with winding number $W$ = 1.
-The composition of the test set was \sshOneTestWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTestWindOneFracHam\% with winding number $W=1$.
-Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
-
-The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (\xOneEigTrain), validation eigenvectors (\xOneEigVal) and test eigenvectors (\xOneEigTest).
-Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were \xOneHamTrain\ for training Hamiltonians, \xOneHamVal\ for validation Hamiltonians and \xOneHamTest\ for test Hamiltonians.
-When compared with the baseline test accuracy of \sshOneHamTestBaseline\ of a system that predicts the whole test set as having winding number $W=1$, the accuracy achieved on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.
-
-The probability heatmaps and phase diagram learned by the combination of decision trees with eigenvector ensembling used in experiment 1 are shown in figure \ref{ssh1_heatmaps}.
 
@@
   \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of decision tree and eigenvector ensembling.}
-\label{figexp1_exp}
+  \includegraphics[width=.37\textwidth]{./ssh/ssh_model.pdf}
+  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
+\label{fig:model}
 \end{figure}
 
-\subsection{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{experiment_2}
+\begin{figure}%[h!]
+  \centering
+  \includegraphics[width=.37\textwidth]{./ssh/winding.png}
+  \caption{Winding number.
+The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point.
+Picture credits: Jim Belk, public domain.}
+\label{fig:winding}
+\end{figure}
 
-This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with \nEst\ decision trees.
-Our data set consisted of \sshTwoTestNHam\ (\sshTwoTestFracHam\%) test Hamiltonians.
-The remaining \sshTwoTrainPlusValNHam\ Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\sshTwoTrainFracHam\%) training Hamiltonians and \sshTwoValNHam\ (\sshTwoValFracHam\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\sshTwoTrainPlusValWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTrainPlusValWindZeroFracHam\%), $W$ = 1 (\sshTwoTrainPlusValWindOneFracHam\%) and $W$ = 2 (\sshTwoTrainPlusValWindTwoFracHam\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\sshTwoTestWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTestWindZeroFracHam\%), $W$ = 1 (\sshTwoTestWindOneFracHam\%) and $W$ = 2 (\sshTwoTestWindTwoFracHam\%).
+\section*{Supplementary Material}
+\subsection*{The SSH model}
+\label{sshapp}
 
-Mean accuracies across \nExp\ repetitions of experiment 2 were \xTwoEigTrain\ for training eigenvectors, \xTwoEigVal\ for validation eigenvectors and \xTwoEigTest\ for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were \xTwoHamTrain\ for training Hamiltonians, \xTwoHamVal\ for validation Hamiltonians and \xTwoHamTest\ for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from \xTwoEigTest\ eigenvector accuracy to \xTwoHamTest\ Hamiltonian accuracy) attests to its power.
-The effectiveness of eigenvector ensembling is also evident from the much worse performance (\sshTwoHamTestBaseline) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
+The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
+This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
+This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
+\begin{equation}
+\label{SSH}
+\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
+\end{equation}
+where the column vector
+\begin{equation*}
+\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
+\end{equation*}
+contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
+\begin{equation*}
+\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
+\end{equation*}
+contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
+Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.
 
-The probability heatmaps and phase diagram learned by the combination of random forests with eigenvector ensembling used in experiment 2 are shown in figure \ref{ssh2_heatmaps}.
+The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
+We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics.
+As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
+\begin{equation}\label{hmatrix}
+H(t_1,t_2,T_1,T_2)=\left(
+  \begin{array}{cccccc}
+    0 & t_1 & 0 & T_1 & 0 & \cdots \\
+    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
+    0 & t_2 & 0 & t_1 & 0 & \cdots\\
+    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
+    0 & T_2 & 0 & t_2 &  0& \cdots\\
+    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
+  \end{array}
+  \right)_{N \times N}.
+\end{equation}
+Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
+Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.
+
+The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
+This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
+This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system.
+In the particular case of the SSH model, the topological invariant used to classify the topological phases is the winding number.
+
+The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
+It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative).
+Figure \ref{fig:winding} shows several closed, oriented curves and their winding numbers computed with respect to a given point.
+
+An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
+This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a challenging task.
+
+For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
+\begin{equation}\label{winding_number}
+W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
+\end{equation}
+where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\mathbf{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
+Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure 1 in the article.
+%\ref{fig:phasediagrams}.
 
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
-\caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by a combination of random forest and eigenvector ensembling.}
-\label{figexp2_exp}
-\end{figure}
-
-\section{Information entropy signatures}
-\label{information_entropy_signatures}
-
-We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test the eigenvector ensembling algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
-
-The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of ensembles of eigenvectors).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
-These signals are the information entropy signatures of each topological phase transition.
-
-We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy.
-This would similarly lead us to Gini impurity signatures of topological phase transitions.
-Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures produced very similar results, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
-Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely undecided \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
-
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for each experiment.
-They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1 (section \ref{experiment_1}), only six lattice sites (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
-
-The information entropy signatures presented here have some interesting subtleties.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
-In section \ref{emergent_information_entropy_wave_functions}, where we develop a quantum formalism for the information entropy signatures obtained in this section, these seemingly antagonistic conceptions shall be harmonized.
-What is important to emphasize at this point is that an information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
-
-To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
-The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
-
-Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
-In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim.png}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(c) The phase diagram resulting from heatmaps (a) and (b).}
-\label{ssh1_heatmaps}
+\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/real_space_best_04_sites/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dct_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
+\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dst_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
+\caption{Phase diagrams learned from compressed representations of the SSH 1 system.
+(a) Phase diagram learned using the real space features \xSOne.
+(b) Phase diagram learned from the DCT topological features \xcSEOne.
+(b) Phase diagram learned from the DST topological features \xsSOOne.}
+\label{eng_feat_ssh1}
 \end{figure}
@@
 \centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim.png}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to -1.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(c) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(d) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 2.
-(e) The phase diagram resulting from heatmaps (a)-(d).}
-\label{ssh2_heatmaps}
+\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/real_space_best_12_sites/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dct_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
+\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dst_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
+\caption{Phase diagrams learned from compressed representations of the SSH 2 system.
+(a) Phase diagram learned using the real space features \xSTwo.
+(b) Phase diagram learned from the DCT topological features \xcSETwo.
+(b) Phase diagram learned from the DST topological features \xsSOTwo.}
+\label{eng_feat_ssh2}
 \end{figure}
 
-\begin{table}
-\begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
-%\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.} \label{numerical_results}
-%\begin{table}[th]
-%\caption{An Example of a Table}
-%\centering\label{table_example}
-%\begin{tabular}{|Sc*{9}{c|}}
-\toprule
-\SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd 
-\midrule
-%                     &                  &                   &                   &                     &                   \tableRow{0.3}
-1                     &\xOne             &\xOneEigVal        &\xOneEigTest       &\xOneHamVal          &\xOneHamTest       \tableRowEnd
-1                     &\xSOne            &\xSOneEigVal       &\xSOneEigTest      &\xSOneHamVal         &\xSOneHamVal       \tableRowEnd
-1                     &\xcOne            &\xcOneEigVal       &\xcOneEigTest      &\xcOneHamVal         &\xcOneHamTest      \tableRowEnd
-1                     &\xcEOne           &\xcEOneEigVal      &\xcEOneEigTest     &\xcEOneHamVal        &\xcEOneHamTest     \tableRowEnd
-1                     &\xcSEOne          &\xcSEOneEigVal     &\xcSEOneEigTest    &\xcSEOneHamVal       &\xcSEOneHamTest    \tableRowEnd
-1                     &\xsOne            &\xsOneEigVal       &\xsOneEigTest      &\xsOneHamVal         &\xsOneHamTest      \tableRowEnd
-1                     &\xsOOne           &\xsOOneEigVal      &\xsOOneEigTest     &\xsOOneHamVal        &\xsOOneHamTest     \tableRowEnd
-1                     &\xsSOOne          &\xsSOOneEigVal     &\xsSOOneEigTest    &\xsSOOneHamVal       &\xsSOOneHamTest    \tableRowEnd
-2                     &\xTwo             &\xTwoEigVal        &\xTwoEigTest       &\xTwoHamVal          &\xTwoHamTest       \tableRowEnd
-2                     &\xSTwo            &\xSTwoEigVal       &\xSTwoEigTest      &\xSTwoHamVal         &\xSTwoHamVal       \tableRowEnd
-2                     &\xcTwo            &\xcTwoEigVal       &\xcTwoEigTest      &\xcTwoHamVal         &\xcTwoHamTest      \tableRowEnd
-2                     &\xcETwo           &\xcETwoEigVal      &\xcETwoEigTest     &\xcETwoHamVal        &\xcETwoHamTest     \tableRowEnd
-2                     &\xcSETwo          &\xcSETwoEigVal     &\xcSETwoEigTest    &\xcSETwoHamVal       &\xcSETwoHamTest    \tableRowEnd
-2                     &\xsTwo            &\xsTwoEigVal       &\xsTwoEigTest      &\xsTwoHamVal         &\xsTwoHamTest      \tableRowEnd
-2                     &\xsOTwo           &\xsOTwoEigVal      &\xsOTwoEigTest     &\xsOTwoHamVal        &\xsOTwoHamTest     \tableRowEnd
-2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
-\bottomrule
-\end{tabular}
-\caption{\label{accuracy_scores}Accuracy scores of numerical experiments.
-The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH systems were as follows.
-Real space features: all real space lattice sites (\xalpha) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ (\xSalpha) (equation \eqref{lattice_subsets}).
-DCT topological features: all DCT topological features (\xcalpha) (equation \eqref{DCT}); DCT topological features from subset $\mathcal{E}_\alpha$ (\xcEalpha) (equation \eqref{DCT_subsets}); DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xcSEalpha) (equation \eqref{DCT_very_compressed}).
-DST topological features: all DST topological features (\xsalpha) (equation \eqref{DST}); DST topological features from subset $\mathcal{O}_\alpha$ (\xsOalpha) (equation \eqref{DST_subsets}); DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xsSOalpha) (equation \eqref{DST_very_compressed}).
-}
-\end{table}
+\subsection*{Learning topological phases from real space data}
 
-\section{Topological feature engineering and lattice compression}
-\label{topological_feature_engineering}
+%The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
+%\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
+%disordered systems in condensed matter) do not have.
+Moreover, since real space and wavevector space eigenvectors are related by Fourier %transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
+We argue here that a data-driven %approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
 
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective and show how the same machinery used previously is able to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
+The insights behind our intuition that topological phases can be learned from local features are as follows.
+First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
+Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space.
+Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.
 
-As we have argued in section \ref{information_entropy_signatures}, the information entropy signatures can be used as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
-Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
-Here we show how the symmetries in real space eigenvectors and information entropy signatures can be exploited to engineer new global topological features, leading to an effective compression of topological information.
+In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
+Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
+\begin{equation}
+\label{localconstancy}
+W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
+\end{equation}
 
-%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
+That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure 1 in the article %\ref{fig:phasediagrams}, 
+where we draw phase diagrams of SSH models with first-neighbor (figure 1(a)) and first- and second-neighbor (figure 1(b)) hoppings.
+In figure 1(a) for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
+Were we able to collect data on the topological phases of several Hamiltonians in parameter space, the problem of learning phase boundaries in a supervised setting would reduce to a standard problem of curve estimation which could be tackled with conventional machine learning algorithms.
 
-%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
-
-Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
-\begin{equation}
-\label{discrete_fourier_transform}
-\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
-\end{equation}
-Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
-The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
-\begin{equation}
-\label{hermitian_symmetry}
-\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
-\end{equation}
-where  we have used the notation $\overline{k} = k \mod N$.
-
-Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
-In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
-This leads us to the Discrete Cosine Transform (DCT) topological features,
-\begin{equation}
-\label{DCT}
-\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
-\end{equation}
-where $M = \frac{N}{2}+1$.
-The second path capitalizes on the fact that the imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
-\begin{equation}
-\label{DST}
-\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
-\end{equation} 
-where $M = \frac{N}{2}-1$.
-
-The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
-the sites $0 \leq l \leq \frac{N}{2}$.
-This is due to the fact that each equation assumes that the eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
-While these assumptions are strictly true for the eigenvector representations in wavevector space, this is not generally true for the real space representations.
-Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from half of the lattice in real space.
-
-The topological feature engineering techniques described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
-As equations \eqref{hermitian_symmetry}-\eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from the existence of certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
-
-We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
-The accuracy scores obtained in each experiment are listed in table \ref{accuracy_scores}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
-
-The lattice compression strategies tested in this work were: \emph{i)} learning topological phases from only a subset of real space lattice sites; \emph{ii)} learning topological phases from the DCT or DST engineered features of equations \eqref{DCT} and \eqref{DST}; \emph{iii)} learning topological phases from a fraction of the DCT or DST topological features and \emph{iv)} learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
-
-In strategy \emph{i)} the lattice sites used in the SSH 1 and SSH 2 systems were
-\begin{equation}
-\label{lattice_subsets}
-\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
-\end{equation}
-Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq j \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq j \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xSOne and \xSTwo, according to the SSH systems they relate to.
-
-In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
-These features are denoted in table \ref{accuracy_scores} by \xcOne, \xsOne, \xcTwo, \xsTwo, according to which set of topological features and SSH systems they refer to.
-
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the DCT topological features used in the SSH 1 and SSH 2 systems,
-\begin{equation}
-\label{DCT_subsets}
-\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
-\end{equation}
-and the DST topological features,
-\begin{equation}
-\label{DST_subsets}
-\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
-\end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space components used with each SSH systems.
-
-The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
-It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
-Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
-Mathematically, we can express the topological features used in strategy \emph{iv)} as follows:
-\begin{equation}
-\label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
-\end{equation}
-\begin{equation}
-\label{DST_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}
-\end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$, 
-\begin{equation}
-\label{indicator_function}
-\indicator{\mathcal{S}}[l] = \begin{cases}
-      1 & \text{if } l \in \mathcal{S} \\
-      0 & \text{otherwise}.
-    \end{cases}
-\end{equation}
-The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used, which components in real and wavevector space engineered them and the appropriate SSH systems.
-
-The results shown in table \ref{accuracy_scores} bring some startling surprises.
-For example, the topological phase transition boundaries of SSH 1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores for the features \xSOne.
-The same appears to be true to SSH 2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
-
-Even more striking is the performance achieved by the compressed DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
-For SSH 1 systems, they perform on par with using the full set of real space features \xOne, while for SSH 2 systems a small loss in accuracy is incurred relative to the full set of real space features \xTwo.
-
-Another interesting insight comes from comparing the accuracy scores obtained with the DCT topological features versus the  DST topological features.
-The latter have poorer performance than the former, as is indicated by the sharp drops in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
-This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
-
-The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-In this sense, key topological information can be said to be localized on few sites in the lattice.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
-
-\section{Emergent information entropy wave functions}
-\label{emergent_information_entropy_wave_functions}
-
-The information entropy signatures that we have been investigating pose an immediate theoretical question: how can a signal that is locally defined arise from a global property of the whole SSH lattice?
-In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
-Our goal is to arrive at a theoretical framework that will allow us to interpret the information entropy signatures in terms of quantum mechanics.
-%The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-
-We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
-macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices, which themselves become 1D manifolds.
-By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuous limit will be given by
+It does not immediately follow, however, that the same strategy will be successful in real space.
+Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,
 
 \begin{equation}
-\label{entropy_density}
-F_S(x) = \int_{\ell}^{(x)}\rho_S(x')dx'
+\label{parameter_to_real}
+\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
 \end{equation}
-where $\rho_S(x)$ is the local information entropy density function in the continuum limit and $x$ is defined by the coordinate system specified on the 1D manifold $\ell$.
-The index $S$ is meant to emphasize that in this paper we have used Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
-Gini impurity.
+where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
+The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.
 
-Our use of periodic boundary conditions implies that the coordinate $x$ should be defined on the circle $ S^1 = [0, 1]/R$, where $R$ is the equivalence relation in $[0,1]$ defining the circle $S^1$ , 
-\begin{equation}
-x \text{ } R \text{ } y \iff x=y \text{ or } (x,y)\in \{(0,1), (1,0)\}.
-\end{equation}
-For open boundary conditions, the spatial coordinate $x$ is defined on the closed interval $[0,1]$ or, in the case of infinite systems, $\mathbb{R}$.
-However, for the sake of generality, we shall continue to use the caligraphic $\ell$ to denote an arbitrary 1D manifold in this section.
+This fact is well illustrated by the numerical experiments discussed in the article.
+Although it may seem from figures 2(b) and 3(b) (from the article) in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
+In such high-dimensional spaces, the data should be much sparser.
 
-Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial information entropy wave function,
+The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as \emph{the curse of dimensionality} \cite{bishop2006pattern}.
+It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
 
-\begin{equation}
-\label{shannon_wave_function}
-\rho_S(x) = |\psi_S(x)|^2,
-\end{equation}
-the amount of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
+These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
+As we have demonstrated in the article, only a small fraction of the 2D surfaces (i.e., eigenvector lattice coordinates $v^{(j,l)}(t_1,t_2)$) were needed to retrieve the 2D parameter space phase diagrams from the 100D real space data, which reveals that there is a lot of redundancy in the information content of real space eigenvectors.
+This fact can be exploited to generate compressed representations of SSH systems that still carry most of the relevant topological information, as can be seen in figures \ref{eng_feat_ssh1} and \ref{eng_feat_ssh2}.
 
-\begin{equation}
-\label{born_rule_spatial}
-\rho_S(x) = |\braket{x|\psi_S}|^2.
-\end{equation}
+\subsection*{Numerical explorations on longer lattices}
 
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform 
-\begin{equation}
-\label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{\ell}\psi_S(x)e^{-2\pi ikx}dx
-\end{equation}
-from which the information entropy density function in wavevector space can be computed,
-\begin{equation}
-\label{shannon_wave_function_wavevector_space}
-\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
-\end{equation}
+A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
 
-The interpretation of information entropy signatures in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
-Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
+The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
+Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
 
-Let us denote the mean, the variance and the entropy associated with the probability distribution $\rho_S$ by $\mu_{\rho_S}$, $\sigma_{\rho_S}^2 $ and $H_{\rho_S}$ respectively. Explicitly, we have 
-\begin{subequations}
-\label{statistics}
-\begin{equation}
-\label{mean}
-\mu_{\rho_S} = \int_{\ell}x\rho_S(x)dx,
-\end{equation}
-\begin{equation}
-\label{variance}
-\sigma_{\rho_S}^2 = \int_{\ell}(x-\mu_{\rho_S})^2\rho_S(x)dx,\quad \text{and}
-\end{equation}
-\begin{equation}
-\label{entropy}
-H_{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
-\end{equation}
-\end{subequations}
-with analogous equations for the wavevector space counterparts $\mu_{\hat{\rho}_S}$, $\sigma_{\hat{\rho}_S}^2 $ and $H_{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
+Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
+As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
+The bootstrapping (step 5) is designed to remove artifacts originating from randomization in the eigenvector ensembling algorithm.
 
-In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}:
+There are still artifacts that might arise from the hyperparameters used to generate the data.
+These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space).
+Such artifacts can only be controlled for by bootstrapping over different hyperparameter settings, which may be computationally prohibitive.
+Intuitively, the hyperparameter we identify as likely having the most noticeable effect in the information entropy signatures is lattice size.
 
-\begin{enumerate}
-\item[i)] \emph{the Heisenberg uncertainty principle}
-\begin{equation}
-\label{heisenberg}
-\sigma_{\rho_S} \cdot \sigma_{\hat{\rho}_S} \geq \frac{1}{4\pi}, \quad \text{and }
-\end{equation}
-\item[ii)] \emph{the Hirschman entropic uncertainty}
-\begin{equation}
-\label{hirschman}
-H_{\rho_S} + H_{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). 
-\end{equation}
-\end{enumerate}
+All results presented in the article were obtained for lattices with 50 unit cells.
+Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
+Here we present the information entropy signatures obtained for lattices with 70, 90 and 110 unit cells for both experiments (figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices}).
+These signals were generated in exactly the same way as the information entropy signatures obtained for 50 unit cells (i.e., after bootstrapping $n_{exp}$ = 100 times and averaging lattice site relevances across all iterations).
 
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signatures} from sheer data analysis of finite SSH systems in real space.
-In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
-
-Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
-Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
-
-\section{Discussion}
-\label{discussion}
-
-Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
-
-By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical and theoretical possibilities offered by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
-
-The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to canonical wavevector space methods.
-Thus, the discovery and engineering of topological features from real space data as demonstrated in this work carries great promise to the theoretical investigation of these systems.
-
-Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
-On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy of information is a necessary commodity to ensure error-correction within the system.
-We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
-
-As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
-This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment executed in section \ref{numerical_experiments} and led us to the new topological features of section \ref{topological_feature_engineering} and the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
-
-The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented in section \ref{information_entropy_signatures} indeed express where topological information is most readily available in the SSH lattices investigated.
-
-This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
-In \cite{zhang2020interpreting}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
-We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
-In our paper we prefer the term \emph{model explainability}, as we are using similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.
-
-Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} that were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
-Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave function discussed here is left for speculation.
-
-The eigenvector ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
-This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
-
-As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
-This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
-An approach based on eigenvector ensembling can be of use in such situations both as a dimensionality reduction tool and as a sampling strategy.
-The first case was illustrated in this work, where it was shown that relevant topological information of SSH systems can be retrieved from few sites in a lattice, which can be exploited as a dimensionality reduction strategy.
-The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in dimensionality  while still capturing all the relevant physics of a system.
-We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
-
-Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
-In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
-This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.
-
-One final comment should be made about the flourishing relationship between physics and machine learning.
-In this work we have demonstrated how a machine learning approach can provide new insights into complex physical phenomena of current interest.
-The other direction of this relationship (physics enhancing understanding in machine learning) is equally important.
-As the need for ever more powerful machine learning algorithms continues to grow, the development of mathematical frameworks for understanding general data spaces (i.e., a physics of data) will be of crucial relevance.
-This pursuit is seen in many theoretical works investigating the intriguing connections between geometry, topology and data \cite{carlsson2009topology}$^-$\cite{belkin2003problems}.
-The detailed study of data generated by physical models with non-trivial geometrical and topological properties such as the SSH model may provide invaluable insights into the structure and shape of real world high-dimensional data, since these models usually underscore well known mathematical frameworks behind the data generating process, a feature that is often absent from machine learning applications.
-Thus, far from being restricted to applications in physics, the study of the topological and geometrical properties of data sets generated by physical models will also be of great value to the machine learning and artificial intelligence communities.
+It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size is increased.
+This naturally leads us to speculation about the continuum limit of information entropy signatures, a matter formally explored in the article.
 
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances.png}}\quad
-\caption{Information entropy signatures of the topological phase transitions obtained from the numerical experiments described in section \ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.}
-\label{feature_importances}
+\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_feature_importances.png}}
+\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh1_longer_lattices}
+\end{figure}
+\begin{figure}
+\centering
+\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_feature_importances.png}}
+\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_feature_importances.png}}
+\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
+(a) Information entropy signature for 70 unit cells.
+(b) Information entropy signature for 90 unit cells.
+(c) Information entropy signature for 110 unit cells.}
+\label{feature_importances_ssh2_longer_lattices}
 \end{figure}
 
-\bibliography{bibl}{}
+\begin{figure}
+\centering
+\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
+(a) Cumulative entropy distribution for 70 unit cells.
+(b) Cumulative entropy distribution for 90 unit cells.
+(c) Cumulative entropy distribution for 110 unit cells.}
+\label{cdf1}
+\end{figure}
 
-\section*{Acknowledgements}
+\begin{figure}
+\centering
+\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
+\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
+\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
+(a) Cumulative entropy distributions for 70 unit cells.
+(b) Cumulative entropy distributions for 90 unit cells.
+(c) Cumulative entropy distributions for 110 unit cells.}
+\label{cdf2}
+\end{figure}
 
-We thank S.
-E.
-Rowley, J.
-F.
-de Oliveira, T.
-Micklitz and M.
-A.
-Continentino for insightful discussions and S.
-E.
-Rowley for carefully reading the manuscript and suggesting improvements.
-N.
-L.
-Holanda acknowledges financial support from CENPES/Petrobr\'as/CBPF.
-M.
-A.
-R.
-Griffith acknowledges financial support from Capes.
-N.
-L.
-Holanda is grateful to the Theory of Condensed Matter and Quantum Materials groups at the Cavendish Laboratory and the Quantum Information Group at CBPF.
+%\newpage
+%\bibliographystylesupp{ieeetr}
+%\bibliographysupp{supp}
 
-\section*{Author contributions}
+%%%%%%%%%%%%%%%%% bibliography %%%%%%%%%%%%%%%%%%%%
+\begin{thebibliography}{6}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
+  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
+  {P{\'a}lyi}}]{asboth2016short}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}},\ \bibinfo
+  {pages} {997} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
+  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
+  {Courville}}]{goodfellow2016deep}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
+  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
+  {publisher} {MIT press},\ \bibinfo {year} {2016})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
+  machine learning}}}\ (\bibinfo  {publisher} {springer},\ \bibinfo {year}
+  {2006})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
+  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
+  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
+  {Mitter}(2010)}]{narayanan2010sample}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
+  neural information processing systems}}}\ (\bibinfo {year} {2010})\ pp.\
+  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
+  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
+  and\ \citenamefont {Muller}}]{rifai2011manifold}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {Advances in neural information processing systems}}}\
+  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
 
-Both authors of this work contributed equally to its realization at all stages.
-
-\section*{Competing financial interests}
-
-The authors declare no competing financial or non-financial interests.
-
-\section*{Additional information}
-
-Correspondence and requests for materials should be addressed to N. L. Holanda. 
-%The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-07-27 07_paper/article.tex
Generated version of paper without buggy macros

@@
 
-\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining figures directory
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article
+%%% phase diagrams (figure 1)
+%\newcommand\phaseDiagramsFigs{./00_article/phase_diagrams/}
+\newcommand\SSHOnePhaseDiagram{./ssh1_phase_diagram.png}
+\newcommand\SSHTwoPhaseDiagram{./ssh2_phase_diagram.png}
+%%% ssh1 experiments (figure 2)
+%\newcommand\SSHOneExperimentsFigs{./00_article/ssh1/real_space_all_sites/}
+\newcommand\SSHOneTrainValTestSplit{./ssh1_scatter_train_val_test_experiment_0.png}
+\newcommand\SSHOneWindingTrain{./ssh1_scatter_winding_train_experiment_0.png}
+\newcommand\SSHOnePredictionGrid{./ssh1_pcolormesh_prediction_grid_experiment_0.png}
+%%% ssh2 experiments (figure 3)
+%\newcommand\SSHTwoExperimentsFigs{./00_article/ssh2/real_space_all_sites/}
+\newcommand\SSHTwoTrainValTestSplit{./ssh2_scatter_train_val_test_experiment_0.png}
+\newcommand\SSHTwoWindingTrain{./ssh2_scatter_winding_train_experiment_0.png}
+\newcommand\SSHTwoPredictionGrid{./ssh2_pcolormesh_prediction_grid_experiment_0.png}
+%%% ssh1 probability heatmaps  (figure 4)
+\newcommand\SSHOneWindingZero{./ssh1_imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHOneWindingOne{./ssh1_imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHOneHeatmap{./ssh1_merge_imshow_winding_grids_second_sim.png}
+%%% ssh2 probability heatmaps  (figure 5)
+\newcommand\SSHTwoWindingMinusOne{./ssh2_imshow_winding_grid_winding_-1_sim.png}
+\newcommand\SSHTwoWindingZero{./ssh2_imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHTwoWindingOne{./ssh2_imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHTwoWindingTwo{./ssh2_imshow_winding_grid_winding_2_sim.png}
+\newcommand\SSHTwoHeatmap{./ssh2_merge_imshow_winding_grids_sim.png}
+%%% information entropy signatures (figure 6)
+\newcommand\SSHOneEntropySignature{./ssh1_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignature{./ssh2_plot_feature_importances.png}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Supplementary material
+%%% SSH model (figure 7)
+\newcommand\SSHModel{./supp_ssh_model.pdf}
+%%% Winding number (figure 8)
+\newcommand\WindingNumber{./supp_winding.png}
+%%% SSH1 compressed phase diagrams (figure 9)
+\newcommand\SSHOneCompressedRealSpacePhaseDiagram{./supp_ssh1_real_merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDCTPhaseDiagram{./supp_ssh1_dct_merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDSTPhaseDiagram{./supp_ssh1_dst_merge_imshow_winding_grids_second_sim.png}
+%%% SSH2 compressed phase diagrams (figure 9)
+\newcommand\SSHTwoCompressedRealSpacePhaseDiagram{./supp_ssh2_real_merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDCTPhaseDiagram{./supp_ssh2_dct_merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDSTPhaseDiagram{./supp_ssh2_dst_merge_imshow_winding_grids_sim.png}
+%%% SSH1 entropy signatures on longer lattices (figure 10)
+\newcommand\SSHOneEntropySignatureOneFourZero{./supp_ssh1_140_plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureOneEightZero{./supp_ssh1_180_plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureTwoTwoZero{./supp_ssh1_220_plot_feature_importances.png}
+%%% SSH2 entropy signatures on longer lattices (figure 11)
+\newcommand\SSHTwoEntropySignatureOneFourZero{./supp_ssh2_140_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureOneEightZero{./supp_ssh2_180_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureTwoTwoZero{./supp_ssh2_220_plot_feature_importances.png}
+%%% SSH1 cumulative information entropy signatures (figure 12)
+\newcommand\SSHOneCumulativeEntropyOneFourZero{./supp_ssh1_140_plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyOneEightZero{./supp_ssh1_180_plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyTwoTwoZero{./supp_ssh1_220_plot_cumulative_feature_importances.png}
+%%% SSH2 cumulative information entropy signatures (figure 12)
+\newcommand\SSHTwoCumulativeEntropyOneFourZero{./supp_ssh2_140_plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyOneEightZero{./supp_ssh2_180_plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyTwoTwoZero{./supp_ssh2_220_plot_cumulative_feature_importances.png}
+
+%\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
 
@@
 
-The  description of information entropy signatures as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The  discovery of information entropy signatures of topological phase transitions and their description as a measurable phenomenon emerging from information entropy wave functions provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
 
@@
 
-Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution arising from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH system.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
-Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
+Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of an ensemble of SSH Hamiltonians.
+Therefore, the information entropy wave function $\psi_S(x)$ and its corresponding information entropy density function $\rho_S(x)$ can be pictured as emergent properties of an ensemble of quantum many-body systems.
 
@@
 
-\bibliography{bibl}{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% bibtext %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{./article_bib/article_bib}{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Full bibliography (if bibtex is not used) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-07-27 deprecated/07_paper_DEPRECATED/00_article/article.tex
Generated version of paper without buggy macros

--- 2020-07-25 10_prb_resubmission_01/00_article/article.tex
@@
 \centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0-1.png}}\quad
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0-1.png}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0-1.png}}
+\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
@@
 \centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0-2.png}}\quad
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0-2.png}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0-2.png}}
+\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_train_val_test_experiment_0.png}}\quad
+\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/scatter_winding_train_experiment_0.png}}
+\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/pcolormesh_prediction_grid_experiment_0.png}}
 \caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
@@
 \centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim-1.png}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim-1.png}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim-1.png}}
+\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{./ssh1/real_space_all_sites/merge_imshow_winding_grids_second_sim.png}}
 \caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
@@
 \centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim-2.png}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim-2.png}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim-2.png}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim-2.png}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim-2.png}}
+\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_-1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_0_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_1_sim.png}}
+\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/imshow_winding_grid_winding_2_sim.png}}
+\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{./ssh2/real_space_all_sites/merge_imshow_winding_grids_sim.png}}
 \caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
@@
 \centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances-1.png}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances-2.png}}\quad
+\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{./ssh1/real_space_all_sites/plot_feature_importances.png}}\quad
+\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{./ssh2/real_space_all_sites/plot_feature_importances.png}}\quad
 \caption{Information entropy signatures of the topological phase transitions from the numerical experiments of section \ref{numerical_experiments}.
@@
 
-%%%%%%%%%% Bibliography %%%%%%%%%%%%%
-
-\begin{thebibliography}{63}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Hasan}\ and\ \citenamefont
-  {Kane}(2010)}]{RevModPhys.82.3045}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
-  {Hasan}}\ and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
-  {Kane}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {3045}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Continentino}(2017)}]{CONTINENTINO2017A1}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physica B: Condensed Matter}\ }\textbf {\bibinfo {volume} {505}},\ \bibinfo
-  {pages} {A1 } (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Puel}\ \emph {et~al.}(2017)\citenamefont {Puel},
-  \citenamefont {Sacramento},\ and\ \citenamefont
-  {Continentino}}]{PhysRevB.95.094509}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~O.}\ \bibnamefont
-  {Puel}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
-  {Sacramento}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {094509}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Griffith}\ and\ \citenamefont
-  {Continentino}(2018)}]{PhysRevE.97.012107}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Griffith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Continentino}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {012107}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ryu}\ \emph {et~al.}(2010)\citenamefont {Ryu},
-  \citenamefont {Schnyder}, \citenamefont {Furusaki},\ and\ \citenamefont
-  {Ludwig}}]{ryu2010topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Ryu}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont {Schnyder}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Furusaki}}, \ and\
-  \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont {Ludwig}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {New Journal of
-  Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {065010}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Atala}\ \emph {et~al.}(2013)\citenamefont {Atala},
-  \citenamefont {Aidelsburger}, \citenamefont {Barreiro}, \citenamefont
-  {Abanin}, \citenamefont {Kitagawa}, \citenamefont {Demler},\ and\
-  \citenamefont {Bloch}}]{atala2013direct}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Atala}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Aidelsburger}},
-  \bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont {Barreiro}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Abanin}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Kitagawa}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Bloch}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {9}},\ \bibinfo {pages} {795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stuhl}\ \emph {et~al.}(2015)\citenamefont {Stuhl},
-  \citenamefont {Lu}, \citenamefont {Aycock}, \citenamefont {Genkina},\ and\
-  \citenamefont {Spielman}}]{Stuhl1514}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~K.}\ \bibnamefont
-  {Stuhl}}, \bibinfo {author} {\bibfnamefont {H.-I.}\ \bibnamefont {Lu}},
-  \bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont {Aycock}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Genkina}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {I.~B.}\ \bibnamefont {Spielman}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {349}},\ \bibinfo {pages} {1514} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Leder}\ \emph {et~al.}(2016)\citenamefont {Leder},
-  \citenamefont {Grossert}, \citenamefont {Sitta}, \citenamefont {Genske},
-  \citenamefont {Rosch},\ and\ \citenamefont {Weitz}}]{leder2016real}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Leder}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Grossert}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sitta}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Genske}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Rosch}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {13112} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goldman}\ \emph {et~al.}(2016)\citenamefont
-  {Goldman}, \citenamefont {Budich},\ and\ \citenamefont
-  {Zoller}}]{goldman2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Goldman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Budich}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\
-  }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {639} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Meier}\ \emph {et~al.}(2016)\citenamefont {Meier},
-  \citenamefont {An},\ and\ \citenamefont {Gadway}}]{meier2016observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
-  {Meier}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {An}}, \
-  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Gadway}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  communications}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {13986}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hafezi}\ \emph {et~al.}(2013)\citenamefont {Hafezi},
-  \citenamefont {Mittal}, \citenamefont {Fan}, \citenamefont {Migdall},\ and\
-  \citenamefont {Taylor}}]{hafezi2013imaging}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hafezi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mittal}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Fan}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Migdall}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Taylor}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Photonics}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {1001} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Lu}\ \emph {et~al.}(2016)\citenamefont {Lu},
-  \citenamefont {Joannopoulos},\ and\ \citenamefont
-  {Solja{\v{c}}i{\'c}}}]{lu2016topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Lu}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
-  {Joannopoulos}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Solja{\v{c}}i{\'c}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-  {pages} {626} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Peano}\ \emph {et~al.}(2015)\citenamefont {Peano},
-  \citenamefont {Brendel}, \citenamefont {Schmidt},\ and\ \citenamefont
-  {Marquardt}}]{PhysRevX.5.031011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Peano}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Brendel}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Schmidt}}, \ and\
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marquardt}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {5}},\ \bibinfo {pages} {031011} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2012)\citenamefont
-  {Kitagawa}, \citenamefont {Broome}, \citenamefont {Fedrizzi}, \citenamefont
-  {Rudner}, \citenamefont {Berg}, \citenamefont {Kassal}, \citenamefont
-  {Aspuru-Guzik}, \citenamefont {Demler},\ and\ \citenamefont
-  {White}}]{kitagawa2012observation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Broome}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Fedrizzi}},
-  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Kassal}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Aspuru-Guzik}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Demler}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~G.}\
-  \bibnamefont {White}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature communications}\ }\textbf {\bibinfo {volume} {3}},\
-  \bibinfo {pages} {882} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cardano}\ \emph {et~al.}(2016)\citenamefont
-  {Cardano}, \citenamefont {Maffei}, \citenamefont {Massa}, \citenamefont
-  {Piccirillo}, \citenamefont {De~Lisio}, \citenamefont {De~Filippis},
-  \citenamefont {Cataudella}, \citenamefont {Santamato},\ and\ \citenamefont
-  {Marrucci}}]{cardano2016statistical}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Cardano}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maffei}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Massa}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Piccirillo}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {De~Lisio}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {De~Filippis}}, \bibinfo {author}
-  {\bibfnamefont {V.}~\bibnamefont {Cataudella}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Santamato}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {Marrucci}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {11439} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Flurin}\ \emph {et~al.}(2017)\citenamefont {Flurin},
-  \citenamefont {Ramasesh}, \citenamefont {Hacohen-Gourgy}, \citenamefont
-  {Martin}, \citenamefont {Yao},\ and\ \citenamefont
-  {Siddiqi}}]{PhysRevX.7.031023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Flurin}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
-  {Ramasesh}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Hacohen-Gourgy}}, \bibinfo {author} {\bibfnamefont {L.~S.}\ \bibnamefont
-  {Martin}}, \bibinfo {author} {\bibfnamefont {N.~Y.}\ \bibnamefont {Yao}}, \
-  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Siddiqi}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {031023} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Soluyanov}\ \emph {et~al.}(2015)\citenamefont
-  {Soluyanov}, \citenamefont {Gresch}, \citenamefont {Wang}, \citenamefont
-  {Wu}, \citenamefont {Troyer}, \citenamefont {Dai},\ and\ \citenamefont
-  {Bernevig}}]{soluyanov2015type}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-  {Soluyanov}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gresch}},
-  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {Q.}~\bibnamefont {Wu}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Troyer}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \ and\ \bibinfo {author} {\bibfnamefont {B.~A.}\
-  \bibnamefont {Bernevig}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {527}},\ \bibinfo {pages}
-  {495} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lv}\ \emph {et~al.}(2015)\citenamefont {Lv},
-  \citenamefont {Weng}, \citenamefont {Fu}, \citenamefont {Wang}, \citenamefont
-  {Miao}, \citenamefont {Ma}, \citenamefont {Richard}, \citenamefont {Huang},
-  \citenamefont {Zhao}, \citenamefont {Chen}, \citenamefont {Fang},
-  \citenamefont {Dai}, \citenamefont {Qian},\ and\ \citenamefont
-  {Ding}}]{PhysRevX.5.031013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~Q.}\ \bibnamefont
-  {Lv}}, \bibinfo {author} {\bibfnamefont {H.~M.}\ \bibnamefont {Weng}},
-  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Fu}}, \bibinfo
-  {author} {\bibfnamefont {X.~P.}\ \bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Miao}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ma}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Richard}}, \bibinfo {author} {\bibfnamefont {X.~C.}\ \bibnamefont {Huang}},
-  \bibinfo {author} {\bibfnamefont {L.~X.}\ \bibnamefont {Zhao}}, \bibinfo
-  {author} {\bibfnamefont {G.~F.}\ \bibnamefont {Chen}}, \bibinfo {author}
-  {\bibfnamefont {Z.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Dai}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Qian}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {031013} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Su}\ \emph {et~al.}(1979)\citenamefont {Su},
-  \citenamefont {Schrieffer},\ and\ \citenamefont
-  {Heeger}}]{PhysRevLett.42.1698}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~P.}\ \bibnamefont
-  {Su}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Schrieffer}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Heeger}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1698} (\bibinfo {year}
-  {1979})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},
-  \citenamefont {Dauphin}, \citenamefont {Cardano}, \citenamefont
-  {Lewenstein},\ and\ \citenamefont {Massignan}}]{maffei2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Maffei}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Cardano}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Lewenstein}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Massignan}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
-  {\bibinfo {volume} {20}},\ \bibinfo {pages} {013023} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heeger}(2001)}]{RevModPhys.73.681}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Heeger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {681}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kane}\ and\ \citenamefont
-  {Lubensky}(2014)}]{kane2014topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Kane}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lubensky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {39}
-  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
-  \citenamefont {Upadhyaya},\ and\ \citenamefont {Vitelli}}]{Chen13004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.-g.}\
-  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Upadhyaya}}, \ and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Vitelli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
-  {volume} {111}},\ \bibinfo {pages} {13004} (\bibinfo {year}
-  {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carrasquilla}\ and\ \citenamefont
-  {Melko}(2017)}]{carrasquilla2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}\ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {431}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ch'ng}\ \emph {et~al.}(2017)\citenamefont {Ch'ng},
-  \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\ \citenamefont
-  {Khatami}}]{PhysRevX.7.031038}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ch'ng}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Carrasquilla}},
-  \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \ and\
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Khatami}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf
-  {\bibinfo {volume} {7}},\ \bibinfo {pages} {031038} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wang}(2016)}]{PhysRevB.94.195105}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wang}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {195105}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Broecker}\ \emph {et~al.}(2017)\citenamefont
-  {Broecker}, \citenamefont {Carrasquilla}, \citenamefont {Melko},\ and\
-  \citenamefont {Trebst}}]{broecker2017machine}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Broecker}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Carrasquilla}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Melko}}, \ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Trebst}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Scientific reports}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
-  {8823} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Van~Nieuwenburg}\ \emph {et~al.}(2017)\citenamefont
-  {Van~Nieuwenburg}, \citenamefont {Liu},\ and\ \citenamefont
-  {Huber}}]{van2017learning}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~P.}\ \bibnamefont
-  {Van~Nieuwenburg}}, \bibinfo {author} {\bibfnamefont {Y.-H.}\ \bibnamefont
-  {Liu}}, \ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
-  {Huber}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {435}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2018)\citenamefont {Zhang},
-  \citenamefont {Shen},\ and\ \citenamefont {Zhai}}]{PhysRevLett.120.066401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {120}},\ \bibinfo {pages} {066401} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
-  \citenamefont {Yi}, \citenamefont {Zhang}, \citenamefont {Shen},\ and\
-  \citenamefont {Zhai}}]{PhysRevB.98.085402}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Yi}}, \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Zhang}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Shen}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Zhai}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {98}},\ \bibinfo {pages} {085402} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Suchsland}\ and\ \citenamefont
-  {Wessel}(2018)}]{PhysRevB.97.174435}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Suchsland}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Wessel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {174435}
-  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont
-  {Kim}(2017)}]{PhysRevLett.118.216401}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont
-  {Kim}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. Lett.}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {216401}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Venderley}\ \emph {et~al.}(2018)\citenamefont
-  {Venderley}, \citenamefont {Khemani},\ and\ \citenamefont
-  {Kim}}]{PhysRevLett.120.257204}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Venderley}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Khemani}},
-  \ and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
-  }\textbf {\bibinfo {volume} {120}},\ \bibinfo {pages} {257204} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ohtsuki}\ and\ \citenamefont
-  {Ohtsuki}(2017)}]{ohtsuki2017deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ohtsuki}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo {volume}
-  {86}},\ \bibinfo {pages} {044708} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Yoshioka}\ \emph {et~al.}(2018)\citenamefont
-  {Yoshioka}, \citenamefont {Akagi},\ and\ \citenamefont
-  {Katsura}}]{PhysRevB.97.205110}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Yoshioka}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Akagi}}, \
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Katsura}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {205110} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2017)\citenamefont {Deng},
-  \citenamefont {Li},\ and\ \citenamefont {Das~Sarma}}]{PhysRevB.96.195145}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.-L.}\ \bibnamefont
-  {Deng}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}}, \ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf
-  {\bibinfo {volume} {96}},\ \bibinfo {pages} {195145} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huembeli}\ \emph {et~al.}(2018)\citenamefont
-  {Huembeli}, \citenamefont {Dauphin},\ and\ \citenamefont
-  {Wittek}}]{PhysRevB.97.134109}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Huembeli}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Dauphin}}, \
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wittek}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {134109} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carvalho}\ \emph {et~al.}(2018)\citenamefont
-  {Carvalho}, \citenamefont {Garc\'{\i}a-Mart\'{\i}nez}, \citenamefont {Lado},\
-  and\ \citenamefont {Fern\'andez-Rossier}}]{PhysRevB.97.115453}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Carvalho}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
-  {Garc\'{\i}a-Mart\'{\i}nez}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
-  \bibnamefont {Lado}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Fern\'andez-Rossier}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {97}},\ \bibinfo {pages} {115453} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2017)\citenamefont {Zhang},
-  \citenamefont {Melko},\ and\ \citenamefont {Kim}}]{PhysRevB.96.245119}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont {Melko}}, \
-  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {245119} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rodriguez-Nieva}\ and\ \citenamefont
-  {Scheurer}(2018)}]{rodriguez2018identifying}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont
-  {Rodriguez-Nieva}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\
-  \bibnamefont {Scheurer}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {arXiv preprint arXiv:1805.05961}\ } (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gilpin}\ \emph {et~al.}(2018)\citenamefont {Gilpin},
-  \citenamefont {Bau}, \citenamefont {Yuan}, \citenamefont {Bajwa},
-  \citenamefont {Specter},\ and\ \citenamefont {Kagal}}]{gilpin2018explaining}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~H.}\ \bibnamefont
-  {Gilpin}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Bau}},
-  \bibinfo {author} {\bibfnamefont {B.~Z.}\ \bibnamefont {Yuan}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Bajwa}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Specter}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {Kagal}},\ }in\ \href@noop {} {\emph
-  {\bibinfo {booktitle} {2018 IEEE 5th International Conference on data science
-  and advanced analytics (DSAA)}}}\ (\bibinfo {organization} {IEEE},\ \bibinfo
-  {year} {2018})\ pp.\ \bibinfo {pages} {80--89}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Do{\v{s}}ilovi{\'c}}\ \emph
-  {et~al.}(2018)\citenamefont {Do{\v{s}}ilovi{\'c}}, \citenamefont
-  {Br{\v{c}}i{\'c}},\ and\ \citenamefont
-  {Hlupi{\'c}}}]{dovsilovic2018explainable}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~K.}\ \bibnamefont
-  {Do{\v{s}}ilovi{\'c}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Br{\v{c}}i{\'c}}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Hlupi{\'c}}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {2018 41st
-  International convention on information and communication technology,
-  electronics and microelectronics (MIPRO)}}}\ (\bibinfo {organization}
-  {IEEE},\ \bibinfo {year} {2018})\ pp.\ \bibinfo {pages}
-  {0210--0215}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Roscher}\ \emph {et~al.}(2020)\citenamefont
-  {Roscher}, \citenamefont {Bohn}, \citenamefont {Duarte},\ and\ \citenamefont
-  {Garcke}}]{roscher2020explainable}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Roscher}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bohn}},
-  \bibinfo {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Duarte}}, \ and\
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Garcke}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Access}\ }\textbf {\bibinfo
-  {volume} {8}},\ \bibinfo {pages} {42200} (\bibinfo {year}
-  {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2001)\citenamefont
-  {Friedman}, \citenamefont {Hastie},\ and\ \citenamefont
-  {Tibshirani}}]{friedman2001elements}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Friedman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hastie}}, \
-  and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},\
-  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
-  learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\ \bibinfo
-  {year} {2001})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pedregosa}\ \emph {et~al.}(2011)\citenamefont
-  {Pedregosa}, \citenamefont {Varoquaux}, \citenamefont {Gramfort},
-  \citenamefont {Michel}, \citenamefont {Thirion}, \citenamefont {Grisel},
-  \citenamefont {Blondel}, \citenamefont {Prettenhofer}, \citenamefont {Weiss},
-  \citenamefont {Dubourg}, \citenamefont {Vanderplas}, \citenamefont {Passos},
-  \citenamefont {Cournapeau}, \citenamefont {Brucher}, \citenamefont {Perrot},\
-  and\ \citenamefont {Duchesnay}}]{scikit-learn}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pedregosa}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Varoquaux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gramfort}},
-  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Michel}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Thirion}}, \bibinfo {author}
-  {\bibfnamefont {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Blondel}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Weiss}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Dubourg}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Vanderplas}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Passos}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Cournapeau}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Brucher}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Perrot}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Duchesnay}},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Machine Learning Research}\ }\textbf
-  {\bibinfo {volume} {12}},\ \bibinfo {pages} {2825} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Buitinck}\ \emph {et~al.}(2013)\citenamefont
-  {Buitinck}, \citenamefont {Louppe}, \citenamefont {Blondel}, \citenamefont
-  {Pedregosa}, \citenamefont {Mueller}, \citenamefont {Grisel}, \citenamefont
-  {Niculae}, \citenamefont {Prettenhofer}, \citenamefont {Gramfort},
-  \citenamefont {Grobler}, \citenamefont {Layton}, \citenamefont {VanderPlas},
-  \citenamefont {Joly}, \citenamefont {Holt},\ and\ \citenamefont
-  {Varoquaux}}]{sklearn_api}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Buitinck}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Louppe}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Blondel}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Pedregosa}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Mueller}}, \bibinfo {author} {\bibfnamefont
-  {O.}~\bibnamefont {Grisel}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Niculae}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Prettenhofer}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Gramfort}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Grobler}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Layton}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {VanderPlas}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Joly}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Holt}}, \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Varoquaux}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {ECML PKDD
-  Workshop: Languages for Data Mining and Machine Learning}}}\ (\bibinfo {year}
-  {2013})\ pp.\ \bibinfo {pages} {108--122}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}\ \emph {et~al.}(1984)\citenamefont
-  {Breiman}, \citenamefont {Friedman}, \citenamefont {Stone},\ and\
-  \citenamefont {Olshen}}]{breiman2017classification}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},
-  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Stone}}, \ and\
-  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Olshen}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Classification and regression
-  trees}}}\ (\bibinfo  {publisher} {Chapman and Hall/CRC, London, UK},\
-  \bibinfo {year} {1984})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Breiman}(2001)}]{Breiman2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Breiman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Machine Learning}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {5}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Raileanu}\ and\ \citenamefont
-  {Stoffel}(2004)}]{raileanu2004theoretical}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~E.}\ \bibnamefont
-  {Raileanu}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Stoffel}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Annals of Mathematics and Artificial Intelligence}\ }\textbf {\bibinfo
-  {volume} {41}},\ \bibinfo {pages} {77} (\bibinfo {year} {2004})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2020)\citenamefont {Zhang},
-  \citenamefont {Ginsparg},\ and\ \citenamefont {Kim}}]{zhang2020interpreting}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Ginsparg}}, \
-  and\ \bibinfo {author} {\bibfnamefont {E.-A.}\ \bibnamefont {Kim}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  Research}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {023283}
-  (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bianco}\ and\ \citenamefont
-  {Resta}(2011)}]{PhysRevB.84.241106}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Bianco}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Resta}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {241106} (\bibinfo
-  {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Caio}\ \emph {et~al.}(2019)\citenamefont {Caio},
-  \citenamefont {M{\"o}ller}, \citenamefont {Cooper},\ and\ \citenamefont
-  {Bhaseen}}]{caio2019topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
-  {Caio}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {M{\"o}ller}},
-  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Cooper}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bhaseen}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ ,\ \bibinfo
-  {pages} {1}} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carlsson}(2009)}]{carlsson2009topology}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Carlsson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Bulletin of the American Mathematical Society}\ }\textbf {\bibinfo {volume}
-  {46}},\ \bibinfo {pages} {255} (\bibinfo {year} {2009})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wasserman}(2018)}]{wasserman2018topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Wasserman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Annual Review of Statistics and Its Application}\ }\textbf {\bibinfo
-  {volume} {5}},\ \bibinfo {pages} {501} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2005)\citenamefont {Wang},
-  \citenamefont {Zhang},\ and\ \citenamefont {Zha}}]{wang2005adaptive}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\ }in\ \href@noop
-  {} {\emph {\bibinfo {booktitle} {Advances in neural information processing
-  systems}}}\ (\bibinfo {year} {2005})\ pp.\ \bibinfo {pages}
-  {1473--1480}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lin}\ and\ \citenamefont
-  {Zha}(2008)}]{lin2008riemannian}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Lin}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zha}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Transactions
-  on Pattern Analysis and Machine Intelligence}\ }\textbf {\bibinfo {volume}
-  {30}},\ \bibinfo {pages} {796} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Belkin}(2003)}]{belkin2003problems}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Belkin}},\ }\href@noop {} {\emph {\bibinfo {title} {Problems of learning on
-  manifolds}}}\ (\bibinfo  {publisher} {The University of Chicago, Chicago, IL,
-  USA},\ \bibinfo {year} {2003})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Asb{\'o}th}\ \emph {et~al.}(2016)\citenamefont
-  {Asb{\'o}th}, \citenamefont {Oroszl{\'a}ny},\ and\ \citenamefont
-  {P{\'a}lyi}}]{asboth2016short}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
-  {Asb{\'o}th}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Oroszl{\'a}ny}}, \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {P{\'a}lyi}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Lecture notes in physics}\ }\textbf {\bibinfo {volume} {919}} (\bibinfo
-  {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goodfellow}\ \emph {et~al.}(2016)\citenamefont
-  {Goodfellow}, \citenamefont {Bengio},\ and\ \citenamefont
-  {Courville}}]{goodfellow2016deep}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Goodfellow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Courville}},\
-  }\href@noop {} {\emph {\bibinfo {title} {Deep learning}}}\ (\bibinfo
-  {publisher} {MIT press, Cambridge, MA, USA},\ \bibinfo {year}
-  {2016})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bishop}(2006)}]{bishop2006pattern}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
-  {Bishop}},\ }\href@noop {} {\emph {\bibinfo {title} {Pattern recognition and
-  machine learning}}}\ (\bibinfo  {publisher} {Springer New York, NY, USA},\
-  \bibinfo {year} {2006})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cayton}(2005)}]{cayton2005algorithms}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Cayton}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Univ.
-  of California at San Diego Tech. Rep}\ }\textbf {\bibinfo {volume} {12}},\
-  \bibinfo {pages} {1} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Narayanan}\ and\ \citenamefont
-  {Mitter}(2010)}]{narayanan2010sample}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Narayanan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Mitter}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Advances in
-  Neural Information Processing Systems}}}\ (\bibinfo {year} {2010})\ pp.\
-  \bibinfo {pages} {1786--1794}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rifai}\ \emph {et~al.}(2011)\citenamefont {Rifai},
-  \citenamefont {Dauphin}, \citenamefont {Vincent}, \citenamefont {Bengio},\
-  and\ \citenamefont {Muller}}]{rifai2011manifold}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Rifai}}, \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont {Dauphin}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Vincent}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Bengio}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Muller}},\ }in\ \href@noop {} {\emph
-  {\bibinfo {booktitle} {Advances in Neural Information Processing Systems}}}\
-  (\bibinfo {year} {2011})\ pp.\ \bibinfo {pages} {2294--2302}\BibitemShut
-  {NoStop}%
-\end{thebibliography}%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{article_bib}{}
 

### 2020-07-27 07_paper/article.tex
Generated version of paper without buggy macros

@@
 \usepackage{bbm}
-\usepackage{xfp}
-\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
-\usepackage{booktabs}
-\renewcommand{\figurename}{Figure}
-\renewcommand{\tablename}{Table}
-\renewcommand{\thetable}{\arabic{table}}
-%\captionsetup{justification=raggedright, singlelinecheck = false}
-%\usepackage{makecell}
-%\usepackage{cellspace}
-
-%\newcites{supp}{References}
-
-%\def\basiceval#1{\the\numexpr#1\relax}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Some macros for mathematicall notation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative 
-
-%ssh1
-
-%Our test set in this experiment contained 1005 Hamiltonians (approx.
-15.3\% of all data).
-Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx.
-8.5\%) and 5000 (approx.
-76.2\%) were used to compute validation scores at each iteration.
-%These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration.
-The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1.
-The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$.
-\textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}
-
-%\documentclass{article}
-%\usepackage{xfp}
-
-%\begin{document}
-
-%\fpeval{31/45}
-
-%\fpeval{round(31/45,5)}
-
-%\end{document}
-\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
-%%%%%% Numerical experiments parameters
-\newcommand\nPrec{2}    % precision digits
-\newcommand\accPrec{4}  % precision digits for accuracy scores
+\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}} % Indicator function
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section III. Numerical Experiments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand\nHam{6561}  % total number of hamiltonians
@@
 \newcommand\nExp{100}   % number of experiments
-%%%table commands
-%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
+%%%% experiment 1
+\newcommand\sshOneTestNHam{1005}
+\newcommand\sshOneTestFracHam{15.32}
+\newcommand\sshOneTrainPlusValNHam{5556}
+\newcommand\sshOneTrainNHam{556}
+\newcommand\sshOneTrainFracHam{8.47}
+\newcommand\sshOneValNHam{5000}
+\newcommand\sshOneValFracHam{76.21}
+\newcommand\sshOneTrainPlusValWindZeroFracHam{50.79}
+\newcommand\sshOneTrainPlusValWindOneFracHam{49.21}
+\newcommand\sshOneTestWindZeroFracHam{44.79}
+\newcommand\sshOneTestWindOneFracHam{55.21}
+\newcommand\sshOneHamTestBaseline{0.5521}
+%%%% experiment 2
+\newcommand\nEst{25}   % number of estimators in random forest
+\newcommand\sshTwoTestNHam{1040}
+\newcommand\sshTwoTestFracHam{15.85}
+\newcommand\sshTwoTrainPlusValNHam{5521}
+\newcommand\sshTwoTrainNHam{2761}
+\newcommand\sshTwoTrainFracHam{42.08}
+\newcommand\sshTwoValNHam{2760}
+\newcommand\sshTwoValFracHam{42.07}
+\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{17.90}
+\newcommand\sshTwoTrainPlusValWindZeroFracHam{32.51}
+\newcommand\sshTwoTrainPlusValWindOneFracHam{32.26}
+\newcommand\sshTwoTrainPlusValWindTwoFracHam{17.33}
+\newcommand\sshTwoTestWindMinusOneFracHam{36.32}
+\newcommand\sshTwoTestWindZeroFracHam{11.06}
+\newcommand\sshTwoTestWindOneFracHam{12.69}
+\newcommand\sshTwoTestWindTwoFracHam{39.93}
+\newcommand\sshTwoHamTestBaseline{0.3993}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section IV. Information Entropy Signatures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand\sitesExpOne{(0, 1, 3, 50, 51, 53)}
+\newcommand\sitesExpTwo{(0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section V. Topological Feature Engineering And Lattice Compression  %%%%%%%%%%%%%%%%%%%%%%%%
+%%% ssh1 lattice sites
+\newcommand\sitesSOne{(0, 1, 3, 50)}
+\newcommand\sitesEOne{(1, 2, 36, 49)}
+\newcommand\sitesOOne{(0, 18, 28, 30)}
+%%% ssh2 lattice sites
+\newcommand\sitesSTwo{(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50)}
+\newcommand\sitesETwo{(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50)}
+\newcommand\sitesOTwo{(0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48)}
+%%% feature names
+\newcommand\xalpha{$X_\alpha$}
+\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
+\newcommand\xcalpha{$\hat{X}^c_\alpha$}
+\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
+\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
+\newcommand\xsalpha{$\hat{X}^s_\alpha$}
+\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
+\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\tableRow}[1]{\\[#1 cm]}
-\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
+\newcommand{\tableRowHeader}[1]{\\[#1 cm]}
 \newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
 \newcommand\tableRowEnd{\tableRow{0.15}}
-%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
-%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
-%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
-%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
-%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
-%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
+%%% table columns
 \newcommand\SSHSys{SSH system}         
@@
 \newcommand\TestHam{Test Hamiltonians}  
-
-%%%%%%%%%%%%%%% ssh1 experiments
-%%% data statistics
-\newcommand\sshOneTrainNHam{556}
-\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneValNHam{5000}
-\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
-\newcommand\sshOneTestNHam{1005}
-\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
-\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
-\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
-\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
-\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-%%% real space accuracies
-%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
-%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
-%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
-%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
-%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
-%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
-%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
-
-%%% ssh1 baseline accuracy
-\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
 %%% x1 features table entries 
 \newcommand\xOne{$X_1$}
-\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
-\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
-\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
-\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
+\newcommand\xOneEigTrain{0.9814}
+\newcommand\xOneEigVal{0.9639}
+\newcommand\xOneEigTest{0.7897}
+\newcommand\xOneHamTrain{1.000}
+\newcommand\xOneHamVal{1.000}
+\newcommand\xOneHamTest{0.9919}
 %%% x_S1 features table entries  
 \newcommand\xSOne{$X_{\mathcal{S}_1}$}
-\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
-\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
-\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
-\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
-\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
-\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
+\newcommand\xSOneEigTrain{0.9700}
+\newcommand\xSOneEigVal{0.9444}
+\newcommand\xSOneEigTest{0.7763}
+\newcommand\xSOneHamTrain{0.9880}
+\newcommand\xSOneHamVal{0.9853}
+\newcommand\xSOneHamTest{0.9905}
 %%% x^c_1 features table entries  
 \newcommand\xcOne{$\hat{X}^c_1$}
-\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
-\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
-\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
-\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
-\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
-\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
+\newcommand\xcOneEigTrain{0.9753}
+\newcommand\xcOneEigVal{0.9521}
+\newcommand\xcOneEigTest{0.7374}
+\newcommand\xcOneHamTrain{0.9983}
+\newcommand\xcOneHamVal{0.9976}
+\newcommand\xcOneHamTest{0.9916}
 %%% x^cE_1 features table entries  
 \newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
-\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
-\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
-\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
-\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
-\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
-\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
+\newcommand\xcEOneEigTrain{0.9755}
+\newcommand\xcEOneEigVal{0.8280}
+\newcommand\xcEOneEigTest{0.6067}
+\newcommand\xcEOneHamTrain{0.9985}
+\newcommand\xcEOneHamVal{0.9979}
+\newcommand\xcEOneHamTest{0.9191}
 %%% x^cSE_1 features table entries  
 \newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
-\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
-\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
-\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
-\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
-\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
-\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
+\newcommand\xcSEOneEigTrain{0.9701}
+\newcommand\xcSEOneEigVal{0.9444}
+\newcommand\xcSEOneEigTest{0.8176}
+\newcommand\xcSEOneHamTrain{0.9882}
+\newcommand\xcSEOneHamVal{0.9853}
+\newcommand\xcSEOneHamTest{0.9934}
 %%% x^s_1 features table entries  
 \newcommand\xsOne{$\hat{X}^s_1$}
-\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
-\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
-\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
-\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
-\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
-\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
+\newcommand\xsOneEigTrain{0.9752}
+\newcommand\xsOneEigVal{0.9533}
+\newcommand\xsOneEigTest{0.7314}
+\newcommand\xsOneHamTrain{0.9931}
+\newcommand\xsOneHamVal{0.9906}
+\newcommand\xsOneHamTest{0.9856}
 %%% x^SO_1 features table entries  
 \newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
-\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
-\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
-\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
-\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
-\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
-\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
+\newcommand\xsOOneEigTrain{0.8079}
+\newcommand\xsOOneEigVal{0.6942}
+\newcommand\xsOOneEigTest{0.5420}
+\newcommand\xsOOneHamTrain{0.9919}
+\newcommand\xsOOneHamVal{0.7088}
+\newcommand\xsOOneHamTest{0.4798}
 %%% x^SSO_1 features table entries  
 \newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
-\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
-\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
-\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
-\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
-\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
-\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}
-
-%ssh2
-\newcommand\sshTwoTrainNHam{2761}
-\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoValNHam{2760}
-\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
-\newcommand\sshTwoTestNHam{1040}
-\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}
-
-\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
-\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
-\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
-\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
-\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-
-\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
-\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
-\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
-\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
-\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-
-\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
-\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
-\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
-\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
-\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
-\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
-
-%%% ssh2 baseline accuracy
-\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
+\newcommand\xsSOOneEigTrain{0.9695}
+\newcommand\xsSOOneEigVal{0.9456}
+\newcommand\xsSOOneEigTest{0.7818}
+\newcommand\xsSOOneHamTrain{0.9876}
+\newcommand\xsSOOneHamVal{0.9854}
+\newcommand\xsSOOneHamTest{0.9399}
 %%% x2 features table entries 
 \newcommand\xTwo{$X_2$}
-\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
-\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
-\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
-\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
-\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
-
+\newcommand\xTwoEigTrain{0.9997}
+\newcommand\xTwoEigVal{0.9709}
+\newcommand\xTwoEigTest{0.6634}
+\newcommand\xTwoHamTrain{1.000}
+\newcommand\xTwoHamVal{0.9972}
+\newcommand\xTwoHamTest{0.8797}
 %%% x_S2 features table entries  
 \newcommand\xSTwo{$X_{\mathcal{S}_2}$}
-\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
-\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
-\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
-\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
-\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
+\newcommand\xSTwoEigTrain{0.9996}
+\newcommand\xSTwoEigVal{0.9590}
+\newcommand\xSTwoEigTest{0.6168}
+\newcommand\xSTwoHamTrain{1.000}
+\newcommand\xSTwoHamVal{0.9961}
+\newcommand\xSTwoHamTest{0.8626}
 %%% x^c_2 features table entries  
 \newcommand\xcTwo{$\hat{X}^c_2$}
-\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
-\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
-\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
-\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
-\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
+\newcommand\xcTwoEigTrain{0.9996}
+\newcommand\xcTwoEigVal{0.9740}
+\newcommand\xcTwoEigTest{0.6895}
+\newcommand\xcTwoHamTrain{1.000}
+\newcommand\xcTwoHamVal{0.9976}
+\newcommand\xcTwoHamTest{0.8862}
 %%% x^cE_2 features table entries  
 \newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
-\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
-\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
-\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
-\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
-\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
-
+\newcommand\xcETwoEigTrain{0.9994}
+\newcommand\xcETwoEigVal{0.8990}
+\newcommand\xcETwoEigTest{0.5357}
+\newcommand\xcETwoHamTrain{1.000}
+\newcommand\xcETwoHamVal{0.9955}
+\newcommand\xcETwoHamTest{0.7897}
 %%% x^cSE_2 features table entries  
 \newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
-\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
-\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
-\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
-\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
-\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
+\newcommand\xcSETwoEigTrain{0.9994}
+\newcommand\xcSETwoEigVal{0.8999}
+\newcommand\xcSETwoEigTest{0.5030}
+\newcommand\xcSETwoHamTrain{1.000}
+\newcommand\xcSETwoHamVal{0.9956}
+\newcommand\xcSETwoHamTest{0.7671}
 %%% x^s_2 features table entries  
 \newcommand\xsTwo{$\hat{X}^s_2$}
-\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
-\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
-\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
-\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
-\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
+\newcommand\xsTwoEigTrain{0.9997}
+\newcommand\xsTwoEigVal{0.9735}
+\newcommand\xsTwoEigTest{0.6878}
+\newcommand\xsTwoHamTrain{1.000}
+\newcommand\xsTwoHamVal{0.9971}
+\newcommand\xsTwoHamTest{0.8899}
 %%% x^SO_2 features table entries  
 \newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
-\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
-\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
-\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
-\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
-\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
+\newcommand\xsOTwoEigTrain{0.9994}
+\newcommand\xsOTwoEigVal{0.9042}
+\newcommand\xsOTwoEigTest{0.5527}
+\newcommand\xsOTwoHamTrain{1.000}
+\newcommand\xsOTwoHamVal{0.9918}
+\newcommand\xsOTwoHamTest{0.7427}
 %%% x^SSO_2 features table entries  
 \newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
-\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
-\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
-\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
-\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
-\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
-
-%%% more feature commands
-%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
-%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}
-
-\newcommand\xalpha{$X_\alpha$}
-\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
-
-\newcommand\xcalpha{$\hat{X}^c_\alpha$}
-\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
-\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
-
-\newcommand\xsalpha{$\hat{X}^s_\alpha$}
-\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
-\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
-
-\newcommand\nEst{25}   % number of estimators in random forest
-
-\newcounter{quoter}
-\setcounter{quoter}{0}
-\renewcommand*{\thequoter}{%
-  %\textbf{%
-  %  \ifnum\value{custom}<1000 0\fi
-  %  \ifnum\value{custom}<100 0\fi
-  %  \ifnum\value{custom}<10 0\fi
-  %  \arabic{custom}%
-  \textbf{[\arabic{quoter}]}
-  }%
-
-\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
-\newcommand{\citequote}[1]{\ref{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining figures directory
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article
+\newcommand\xsSOTwoEigTrain{0.9992}
+\newcommand\xsSOTwoEigVal{0.8204}
+\newcommand\xsSOTwoEigTest{0.4127}
+\newcommand\xsSOTwoHamTrain{1.000}
+\newcommand\xsSOTwoHamVal{0.9942}
+\newcommand\xsSOTwoHamTest{0.5903}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% phase diagrams (figure 1)
@@
 
-%\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
-
 \begin{document}
@@
 
-The  discovery of information entropy signatures of topological phase transitions and their description as a measurable phenomenon emerging from information entropy wave functions provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The  discovery of information entropy signatures of topological phase transitions and their description as a measurable emergent phenomenon originating from the information entropy of ensembles of topological systems proximal to phase transition boundaries provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
 
@@
 They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1 (section \ref{experiment_1}), only six lattice sites (0, 1, 3, 50, 51, 53) corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites (0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99) distributed along the three peaks in figure \ref{feature_importances_ssh2}.
+For experiment 1 (section \ref{experiment_1}), only six lattice sites \sitesExpOne\ corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
+Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites \sitesExpTwo\ distributed along the three peaks in figure \ref{feature_importances_ssh2}.
 As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
@@
 %\begin{tabular}{|Sc*{9}{c|}}
-\toprule
+%\toprule
+\hline
 \SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd 
-\midrule
+%\midrule
 %                     &                  &                   &                   &                     &                   \tableRow{0.3}
@@
 2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
-\bottomrule
+%\bottomrule
+\hline
 \end{tabular}
@@
 \label{lattice_subsets}
-\mathcal{S}_1 = (0, 1, 3, 50 ) \quad \text{and} \quad  \mathcal{S}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50).   
+\mathcal{S}_1 = \sitesSOne \quad \text{and} \quad  \mathcal{S}_2 =\sitesSTwo.   
 \end{equation}
@@
 \label{DCT_subsets}
-\mathcal{E}_1 = (1, 2, 36, 49) \quad \text{and} \quad  \mathcal{E}_2 =(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50) \qquad \text{(DCT)}  
+\mathcal{E}_1 = \sitesEOne \quad \text{and} \quad  \mathcal{E}_2 =\sitesETwo \qquad \text{(DCT)}  
 \end{equation}
@@
 \label{DST_subsets}
-\mathcal{O}_1 =  (0, 18, 28, 30) \quad \text{and} \quad  \mathcal{O}_2 = (0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48) \qquad \text{(DST)}.  
+\mathcal{O}_1 =  \sitesOOne \quad \text{and} \quad  \mathcal{O}_2 = \sitesOTwo \qquad \text{(DST)}.  
 \end{equation}
@@
 Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information of an ensemble of SSH Hamiltonians.
-Therefore, the information entropy wave function $\psi_S(x)$ and its corresponding information entropy density function $\rho_S(x)$ can be pictured as emergent properties of an ensemble of quantum many-body systems.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the spatial distribution of topological information of an ensemble of SSH Hamiltonians close to phase transition boundaries in parameter space.
+Therefore, the information entropy wave function $\psi_S(x)$ and its corresponding information entropy density function $\rho_S(x)$ can be pictured as emergent properties of an ensemble of quantum many-body systems near phase transitions.
 

### 2020-07-27 08_arxiv/article.tex
Generated version of paper without buggy macros

@@
 \newcommand\TestHam{Test Hamiltonians}  
-
-%%%%%%%%%%%%%%% ssh1 experiments
-%%% data statistics
-\newcommand\sshOneTrainNHam{556}
-\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneValNHam{5000}
-\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
-\newcommand\sshOneTestNHam{1005}
-\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
-\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
-\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
-\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
-\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
-%%% real space accuracies
-%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
-%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
-%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
-%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
-%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
-%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
-%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
-
-%%% ssh1 baseline accuracy
-\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
 %%% x1 features table entries 
 \newcommand\xOne{$X_1$}
-\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
-\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
-\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
-\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
+\newcommand\xOneEigTrain{0.9814}
+\newcommand\xOneEigVal{0.9639}
+\newcommand\xOneEigTest{0.7897}
+\newcommand\xOneHamTrain{1.000}
+\newcommand\xOneHamVal{1.000}
+\newcommand\xOneHamTest{0.9919}
 %%% x_S1 features table entries  
 \newcommand\xSOne{$X_{\mathcal{S}_1}$}
-\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
-\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
-\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
-\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
-\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
-\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
+\newcommand\xSOneEigTrain{0.9700}
+\newcommand\xSOneEigVal{0.9444}
+\newcommand\xSOneEigTest{0.7763}
+\newcommand\xSOneHamTrain{0.9880}
+\newcommand\xSOneHamVal{0.9853}
+\newcommand\xSOneHamTest{0.9905}
 %%% x^c_1 features table entries  
 \newcommand\xcOne{$\hat{X}^c_1$}
-\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
-\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
-\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
-\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
-\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
-\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
+\newcommand\xcOneEigTrain{0.9753}
+\newcommand\xcOneEigVal{0.9521}
+\newcommand\xcOneEigTest{0.7374}
+\newcommand\xcOneHamTrain{0.9983}
+\newcommand\xcOneHamVal{0.9976}
+\newcommand\xcOneHamTest{0.9916}
 %%% x^cE_1 features table entries  
 \newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
-\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
-\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
-\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
-\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
-\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
-\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
+\newcommand\xcEOneEigTrain{0.9755}
+\newcommand\xcEOneEigVal{0.8280}
+\newcommand\xcEOneEigTest{0.6067}
+\newcommand\xcEOneHamTrain{0.9985}
+\newcommand\xcEOneHamVal{0.9979}
+\newcommand\xcEOneHamTest{0.9191}
 %%% x^cSE_1 features table entries  
 \newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
-\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
-\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
-\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
-\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
-\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
-\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
+\newcommand\xcSEOneEigTrain{0.9701}
+\newcommand\xcSEOneEigVal{0.9444}
+\newcommand\xcSEOneEigTest{0.8176}
+\newcommand\xcSEOneHamTrain{0.9882}
+\newcommand\xcSEOneHamVal{0.9853}
+\newcommand\xcSEOneHamTest{0.9934}
 %%% x^s_1 features table entries  
 \newcommand\xsOne{$\hat{X}^s_1$}
-\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
-\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
-\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
-\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
-\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
-\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
+\newcommand\xsOneEigTrain{0.9752}
+\newcommand\xsOneEigVal{0.9533}
+\newcommand\xsOneEigTest{0.7314}
+\newcommand\xsOneHamTrain{0.9931}
+\newcommand\xsOneHamVal{0.9906}
+\newcommand\xsOneHamTest{0.9856}
 %%% x^SO_1 features table entries  
 \newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
-\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
-\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
-\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
-\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
-\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
-\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
+\newcommand\xsOOneEigTrain{0.8079}
+\newcommand\xsOOneEigVal{0.6942}
+\newcommand\xsOOneEigTest{0.5420}
+\newcommand\xsOOneHamTrain{0.9919}
+\newcommand\xsOOneHamVal{0.7088}
+\newcommand\xsOOneHamTest{0.4798}
 %%% x^SSO_1 features table entries  
 \newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
-\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
-\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
-\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
-\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
-\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
-\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}
-
-%ssh2
-\newcommand\sshTwoTrainNHam{2761}
-\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoValNHam{2760}
-\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
-\newcommand\sshTwoTestNHam{1040}
-\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}
-
-\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
-\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
-\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
-\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
-\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
-
-\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
-\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
-\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
-\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
-\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
-
-\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
-\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
-\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
-\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
-\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
-\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy
-
-%%% ssh2 baseline accuracy
-\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
+\newcommand\xsSOOneEigTrain{0.9695}
+\newcommand\xsSOOneEigVal{0.9456}
+\newcommand\xsSOOneEigTest{0.7818}
+\newcommand\xsSOOneHamTrain{0.9876}
+\newcommand\xsSOOneHamVal{0.9854}
+\newcommand\xsSOOneHamTest{0.9399}
 %%% x2 features table entries 
 \newcommand\xTwo{$X_2$}
-\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
-\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
-\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
-\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
-\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}
-
+\newcommand\xTwoEigTrain{0.9997}
+\newcommand\xTwoEigVal{0.9709}
+\newcommand\xTwoEigTest{0.6634}
+\newcommand\xTwoHamTrain{1.000}
+\newcommand\xTwoHamVal{0.9972}
+\newcommand\xTwoHamTest{0.8797}
 %%% x_S2 features table entries  
 \newcommand\xSTwo{$X_{\mathcal{S}_2}$}
-\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
-\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
-\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
-\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
-\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
+\newcommand\xSTwoEigTrain{0.9996}
+\newcommand\xSTwoEigVal{0.9590}
+\newcommand\xSTwoEigTest{0.6168}
+\newcommand\xSTwoHamTrain{1.000}
+\newcommand\xSTwoHamVal{0.9961}
+\newcommand\xSTwoHamTest{0.8626}
 %%% x^c_2 features table entries  
 \newcommand\xcTwo{$\hat{X}^c_2$}
-\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
-\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
-\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
-\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
-\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
+\newcommand\xcTwoEigTrain{0.9996}
+\newcommand\xcTwoEigVal{0.9740}
+\newcommand\xcTwoEigTest{0.6895}
+\newcommand\xcTwoHamTrain{1.000}
+\newcommand\xcTwoHamVal{0.9976}
+\newcommand\xcTwoHamTest{0.8862}
 %%% x^cE_2 features table entries  
 \newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
-\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
-\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
-\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
-\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
-\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}
-
+\newcommand\xcETwoEigTrain{0.9994}
+\newcommand\xcETwoEigVal{0.8990}
+\newcommand\xcETwoEigTest{0.5357}
+\newcommand\xcETwoHamTrain{1.000}
+\newcommand\xcETwoHamVal{0.9955}
+\newcommand\xcETwoHamTest{0.7897}
 %%% x^cSE_2 features table entries  
 \newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
-\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
-\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
-\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
-\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
-\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
+\newcommand\xcSETwoEigTrain{0.9994}
+\newcommand\xcSETwoEigVal{0.8999}
+\newcommand\xcSETwoEigTest{0.5030}
+\newcommand\xcSETwoHamTrain{1.000}
+\newcommand\xcSETwoHamVal{0.9956}
+\newcommand\xcSETwoHamTest{0.7671}
 %%% x^s_2 features table entries  
 \newcommand\xsTwo{$\hat{X}^s_2$}
-\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
-\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
-\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
-\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
-\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
+\newcommand\xsTwoEigTrain{0.9997}
+\newcommand\xsTwoEigVal{0.9735}
+\newcommand\xsTwoEigTest{0.6878}
+\newcommand\xsTwoHamTrain{1.000}
+\newcommand\xsTwoHamVal{0.9971}
+\newcommand\xsTwoHamTest{0.8899}
 %%% x^SO_2 features table entries  
 \newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
-\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
-\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
-\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
-\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
-\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
+\newcommand\xsOTwoEigTrain{0.9994}
+\newcommand\xsOTwoEigVal{0.9042}
+\newcommand\xsOTwoEigTest{0.5527}
+\newcommand\xsOTwoHamTrain{1.000}
+\newcommand\xsOTwoHamVal{0.9918}
+\newcommand\xsOTwoHamTest{0.7427}
 %%% x^SSO_2 features table entries  
 \newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
-\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
-\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
-\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
-\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
-\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
-\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}
-
-%%% more feature commands
-%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
-%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}
-
-\newcommand\xalpha{$X_\alpha$}
-\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
-
-\newcommand\xcalpha{$\hat{X}^c_\alpha$}
-\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
-\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
-
-\newcommand\xsalpha{$\hat{X}^s_\alpha$}
-\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
-\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}
-
-\newcommand\nEst{25}   % number of estimators in random forest
-
-\newcounter{quoter}
-\setcounter{quoter}{0}
-\renewcommand*{\thequoter}{%
-  %\textbf{%
-  %  \ifnum\value{custom}<1000 0\fi
-  %  \ifnum\value{custom}<100 0\fi
-  %  \ifnum\value{custom}<10 0\fi
-  %  \arabic{custom}%
-  \textbf{[\arabic{quoter}]}
-  }%
-
-\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
-\newcommand{\citequote}[1]{\ref{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Defining figures directory
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article
+\newcommand\xsSOTwoEigTrain{0.9992}
+\newcommand\xsSOTwoEigVal{0.8204}
+\newcommand\xsSOTwoEigTest{0.4127}
+\newcommand\xsSOTwoHamTrain{1.000}
+\newcommand\xsSOTwoHamVal{0.9942}
+\newcommand\xsSOTwoHamTest{0.5903}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% phase diagrams (figure 1)
-\newcommand\phaseDiagramsFigs{./00_article/phase_diagrams/}
-\newcommand\SSHOnePhaseDiagram{\phaseDiagramsFigs ssh1.png}
-\newcommand\SSHTwoPhaseDiagram{\phaseDiagramsFigs ssh2.png}
+%\newcommand\phaseDiagramsFigs{./00_article/phase_diagrams/}
+\newcommand\SSHOnePhaseDiagram{./ssh1_phase_diagram.png}
+\newcommand\SSHTwoPhaseDiagram{./ssh2_phase_diagram.png}
 %%% ssh1 experiments (figure 2)
-\newcommand\SSHOneExperimentsFigs{./00_article/ssh1/real_space_all_sites/}
-\newcommand\SSHOneTrainValTestSplit{\SSHOneExperimentsFigs scatter_train_val_test_experiment_0.png}
-\newcommand\SSHOneWindingTrain{\SSHOneExperimentsFigs scatter_winding_train_experiment_0.png}
-\newcommand\SSHOnePredictionGrid{\SSHOneExperimentsFigs pcolormesh_prediction_grid_experiment_0.png}
+%\newcommand\SSHOneExperimentsFigs{./00_article/ssh1/real_space_all_sites/}
+\newcommand\SSHOneTrainValTestSplit{./ssh1_scatter_train_val_test_experiment_0.png}
+\newcommand\SSHOneWindingTrain{./ssh1_scatter_winding_train_experiment_0.png}
+\newcommand\SSHOnePredictionGrid{./ssh1_pcolormesh_prediction_grid_experiment_0.png}
 %%% ssh2 experiments (figure 3)
-\newcommand\SSHTwoExperimentsFigs{./00_article/ssh2/real_space_all_sites/}
-\newcommand\SSHTwoTrainValTestSplit{\SSHTwoExperimentsFigs scatter_train_val_test_experiment_0.png}
-\newcommand\SSHTwoWindingTrain{\SSHTwoExperimentsFigs scatter_winding_train_experiment_0.png}
-\newcommand\SSHTwoPredictionGrid{\SSHTwoExperimentsFigs pcolormesh_prediction_grid_experiment_0.png}
+%\newcommand\SSHTwoExperimentsFigs{./00_article/ssh2/real_space_all_sites/}
+\newcommand\SSHTwoTrainValTestSplit{./ssh2_scatter_train_val_test_experiment_0.png}
+\newcommand\SSHTwoWindingTrain{./ssh2_scatter_winding_train_experiment_0.png}
+\newcommand\SSHTwoPredictionGrid{./ssh2_pcolormesh_prediction_grid_experiment_0.png}
 %%% ssh1 probability heatmaps  (figure 4)
-\newcommand\SSHOneWindingZero{\SSHOneExperimentsFigs imshow_winding_grid_winding_0_sim.png}
-\newcommand\SSHOneWindingOne{\SSHOneExperimentsFigs imshow_winding_grid_winding_1_sim.png}
-\newcommand\SSHOneHeatmap{\SSHOneExperimentsFigs merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneWindingZero{./ssh1_imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHOneWindingOne{./ssh1_imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHOneHeatmap{./ssh1_merge_imshow_winding_grids_second_sim.png}
 %%% ssh2 probability heatmaps  (figure 5)
-\newcommand\SSHTwoWindingMinusOne{\SSHTwoExperimentsFigs imshow_winding_grid_winding_-1_sim.png}
-\newcommand\SSHTwoWindingZero{\SSHTwoExperimentsFigs imshow_winding_grid_winding_0_sim.png}
-\newcommand\SSHTwoWindingOne{\SSHTwoExperimentsFigs imshow_winding_grid_winding_1_sim.png}
-\newcommand\SSHTwoWindingTwo{\SSHTwoExperimentsFigs imshow_winding_grid_winding_2_sim.png}
-\newcommand\SSHTwoHeatmap{\SSHTwoExperimentsFigs merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoWindingMinusOne{./ssh2_imshow_winding_grid_winding_-1_sim.png}
+\newcommand\SSHTwoWindingZero{./ssh2_imshow_winding_grid_winding_0_sim.png}
+\newcommand\SSHTwoWindingOne{./ssh2_imshow_winding_grid_winding_1_sim.png}
+\newcommand\SSHTwoWindingTwo{./ssh2_imshow_winding_grid_winding_2_sim.png}
+\newcommand\SSHTwoHeatmap{./ssh2_merge_imshow_winding_grids_sim.png}
 %%% information entropy signatures (figure 6)
-\newcommand\SSHOneEntropySignature{\SSHOneExperimentsFigs plot_feature_importances.png}
-\newcommand\SSHTwoEntropySignature{\SSHTwoExperimentsFigs plot_feature_importances.png}
+\newcommand\SSHOneEntropySignature{./ssh1_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignature{./ssh2_plot_feature_importances.png}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Supplementary material
-\newcommand\SuppFigures{./01_supplementary/}
-\newcommand\SSH{\SuppFigures ssh/}
-\newcommand\SSHOneSupp{\SuppFigures ssh1/}
-%%% lattice size 100
-\newcommand\SSHOneSuppOneZeroZero{\SSHOneSupp periodic_100_6561/}
-\newcommand\SSHOneSuppOneZeroZeroCompressedRealSpace{\SSHOneSuppOneZeroZero real_space_best_04_sites/}
-\newcommand\SSHOneSuppOneZeroZeroCompressedDCT{\SSHOneSuppOneZeroZero dct_best_04_wavevector_sites_from_best_04_real_space_sites/}
-\newcommand\SSHOneSuppOneZeroZeroCompressedDST{\SSHOneSuppOneZeroZero dst_best_04_wavevector_sites_from_best_04_real_space_sites/}
-%%% lattice size 140
-\newcommand\SSHOneSuppOneFourZero{\SSHOneSupp periodic_140_6561/}
-%\newcommand\SSHOneSuppOneFourZeroCompressedRealSpace{\SSHOneSuppOneFourZero real_space_best_04_sites/}
-%\newcommand\SSHOneSuppOneFourZeroCompressedDCT{\SSHOneSuppOneFourZero dct_best_04_wavevector_sites_from_best_04_real_space_sites/}
-%\newcommand\SSHOneSuppOneFourZeroCompressedDST{\SSHOneSuppOneFourZero dst_best_04_wavevector_sites_from_best_04_real_space_sites/}
-
-%%%% lattice size 180
-\newcommand\SSHOneSuppOneEightZero{\SSHOneSupp periodic_180_6561/}
-
-\newcommand\SSHOneSuppTwoTwoZero{\SSHOneSupp periodic_220_6561/}
-\newcommand\SSHTwoSupp{\SuppFigures ssh2/}
-\newcommand\SSHTwoSuppOneZeroZero{\SSHTwoSupp periodic_100_6561/}
-\newcommand\SSHTwoSuppOneZeroZeroCompressedRealSpace{\SSHTwoSuppOneZeroZero real_space_best_12_sites/}
-\newcommand\SSHTwoSuppOneZeroZeroCompressedDCT{\SSHTwoSuppOneZeroZero dct_best_12_wavevector_sites_from_best_12_real_space_sites/}
-\newcommand\SSHTwoSuppOneZeroZeroCompressedDST{\SSHTwoSuppOneZeroZero dst_best_12_wavevector_sites_from_best_12_real_space_sites/}
-
-\newcommand\SSHTwoSuppOneFourZero{\SSHTwoSupp periodic_140_6561/}
-\newcommand\SSHTwoSuppOneEightZero{\SSHTwoSupp periodic_180_6561/}
-\newcommand\SSHTwoSuppTwoTwoZero{\SSHTwoSupp periodic_220_6561/}
 %%% SSH model (figure 7)
-\newcommand\SSHModel{\SSH ssh_model.pdf}
+\newcommand\SSHModel{./supp_ssh_model.pdf}
 %%% Winding number (figure 8)
-\newcommand\WindingNumber{\SSH winding.png}
+\newcommand\WindingNumber{./supp_winding.png}
 %%% SSH1 compressed phase diagrams (figure 9)
-\newcommand\SSHOneCompressedRealSpacePhaseDiagram{\SSHOneSuppOneZeroZeroCompressedRealSpace merge_imshow_winding_grids_second_sim.png}
-\newcommand\SSHOneCompressedDCTPhaseDiagram{\SSHOneSuppOneZeroZeroCompressedDCT merge_imshow_winding_grids_second_sim.png}
-\newcommand\SSHOneCompressedDSTPhaseDiagram{\SSHOneSuppOneZeroZeroCompressedDST merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedRealSpacePhaseDiagram{./supp_ssh1_real_merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDCTPhaseDiagram{./supp_ssh1_dct_merge_imshow_winding_grids_second_sim.png}
+\newcommand\SSHOneCompressedDSTPhaseDiagram{./supp_ssh1_dst_merge_imshow_winding_grids_second_sim.png}
 %%% SSH2 compressed phase diagrams (figure 9)
-\newcommand\SSHTwoCompressedRealSpacePhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedRealSpace merge_imshow_winding_grids_sim.png}
-\newcommand\SSHTwoCompressedDCTPhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedDCT merge_imshow_winding_grids_sim.png}
-\newcommand\SSHTwoCompressedDSTPhaseDiagram{\SSHTwoSuppOneZeroZeroCompressedDST merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedRealSpacePhaseDiagram{./supp_ssh2_real_merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDCTPhaseDiagram{./supp_ssh2_dct_merge_imshow_winding_grids_sim.png}
+\newcommand\SSHTwoCompressedDSTPhaseDiagram{./supp_ssh2_dst_merge_imshow_winding_grids_sim.png}
 %%% SSH1 entropy signatures on longer lattices (figure 10)
-\newcommand\SSHOneEntropySignatureOneFourZero{\SSHOneSuppOneFourZero plot_feature_importances.png}
-\newcommand\SSHOneEntropySignatureOneEightZero{\SSHOneSuppOneEightZero plot_feature_importances.png}
-\newcommand\SSHOneEntropySignatureTwoTwoZero{\SSHOneSuppTwoTwoZero plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureOneFourZero{./supp_ssh1_140_plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureOneEightZero{./supp_ssh1_180_plot_feature_importances.png}
+\newcommand\SSHOneEntropySignatureTwoTwoZero{./supp_ssh1_220_plot_feature_importances.png}
 %%% SSH2 entropy signatures on longer lattices (figure 11)
-\newcommand\SSHTwoEntropySignatureOneFourZero{\SSHTwoSuppOneFourZero plot_feature_importances.png}
-\newcommand\SSHTwoEntropySignatureOneEightZero{\SSHTwoSuppOneEightZero plot_feature_importances.png}
-\newcommand\SSHTwoEntropySignatureTwoTwoZero{\SSHTwoSuppTwoTwoZero plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureOneFourZero{./supp_ssh2_140_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureOneEightZero{./supp_ssh2_180_plot_feature_importances.png}
+\newcommand\SSHTwoEntropySignatureTwoTwoZero{./supp_ssh2_220_plot_feature_importances.png}
 %%% SSH1 cumulative information entropy signatures (figure 12)
-\newcommand\SSHOneCumulativeEntropyOneFourZero{\SSHOneSuppOneFourZero plot_cumulative_feature_importances.png}
-\newcommand\SSHOneCumulativeEntropyOneEightZero{\SSHOneSuppOneEightZero plot_cumulative_feature_importances.png}
-\newcommand\SSHOneCumulativeEntropyTwoTwoZero{\SSHOneSuppTwoTwoZero plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyOneFourZero{./supp_ssh1_140_plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyOneEightZero{./supp_ssh1_180_plot_cumulative_feature_importances.png}
+\newcommand\SSHOneCumulativeEntropyTwoTwoZero{./supp_ssh1_220_plot_cumulative_feature_importances.png}
 %%% SSH2 cumulative information entropy signatures (figure 12)
-\newcommand\SSHTwoCumulativeEntropyOneFourZero{\SSHTwoSuppOneFourZero plot_cumulative_feature_importances.png}
-\newcommand\SSHTwoCumulativeEntropyOneEightZero{\SSHTwoSuppOneEightZero plot_cumulative_feature_importances.png}
-\newcommand\SSHTwoCumulativeEntropyTwoTwoZero{\SSHTwoSuppTwoTwoZero plot_cumulative_feature_importances.png}
-
-%\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
+\newcommand\SSHTwoCumulativeEntropyOneFourZero{./supp_ssh2_140_plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyOneEightZero{./supp_ssh2_180_plot_cumulative_feature_importances.png}
+\newcommand\SSHTwoCumulativeEntropyTwoTwoZero{./supp_ssh2_220_plot_cumulative_feature_importances.png}
 
@@
 
-The  description of information entropy signatures as a measurable phenomenon emerging from information entropy wave functions provides a clear illustration of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The  discovery of information entropy signatures of topological phase transitions and their description as a measurable emergent phenomenon originating from the information entropy of ensembles of topological systems proximal to phase transition boundaries provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
 
@@
 Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the distribution of topological information in a many-particle system.
-Therefore, the information entropy wave function $\psi_S(x)$ can be seen as an emergent property of a quantum many-body system.
+Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the spatial distribution of topological information of an ensemble of SSH Hamiltonians close to phase transition boundaries in parameter space.
+Therefore, the information entropy wave function $\psi_S(x)$ and its corresponding information entropy density function $\rho_S(x)$ can be pictured as emergent properties of an ensemble of quantum many-body systems near phase transitions.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% bibtext %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\bibliography{./article_bib/article_bib}{}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Full bibliography (if bibtex is not used) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-07-28 10_prb_resubmission_01/article.tex
Submitted to Arxiv and PRB

--- 2020-07-27 08_arxiv/article.tex
@@
 The data-driven approach designed in this article addresses these issues.
-%In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
 
@@
 
-The  discovery of information entropy signatures of topological phase transitions and their description as a measurable emergent phenomenon originating from the information entropy of ensembles of topological systems proximal to phase transition boundaries provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
+The  discovery of information entropy signatures of topological phase transitions and their description as a measurable emergent phenomenon originating from the information entropy of ensembles of topological systems proximal to phase transition boundaries provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.
 
@@
 \vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
+\begin{enumerate}
 \item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
@@
 \begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
-%\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.} \label{numerical_results}
-%\begin{table}[th]
-%\caption{An Example of a Table}
-%\centering\label{table_example}
-%\begin{tabular}{|Sc*{9}{c|}}
-%\toprule
 \hline
 \SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd
-%\midrule
-%                     &                  &                   &                   &                     &                   \tableRow{0.3}
+
 1                     &\xOne             &\xOneEigVal        &\xOneEigTest       &\xOneHamVal          &\xOneHamTest       \tableRowEnd
@@
 2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
-%\bottomrule
+
 \hline
@@
 
-%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
-
-%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
-
 Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
@@
 Our goal is to arrive at a theoretical framework that will allow us to interpret the information entropy signatures in terms of quantum mechanics.
-%The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
 
@@
 Correspondence and requests for materials should be addressed to N. L. Holanda.
-%The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\pagebreak
-
-\begin{figure}
-  \centering
-  \includegraphics[width=.37\textwidth]{\SSHModel}
-  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
-\label{fig:model}
-\end{figure}
-
-\begin{figure}%[h!]
-  \centering
-  \includegraphics[width=.37\textwidth]{\WindingNumber}
-  \caption{Winding number.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%\pagebreak
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=.37\textwidth]{\SSHModel}
+%  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
+%\label{fig:model}
+%\end{figure}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=.37\textwidth]{\WindingNumber}
+%  \caption{Winding number.
 The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point.
 Picture credits: Jim Belk, public domain.}
-\label{fig:winding}
-\end{figure}
-
-\section*{Supplementary Material}
-\subsection*{The SSH model}
-\label{sshapp}
-
-The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
+%\label{fig:winding}
+%\end{figure}
+
+%\section*{Supplementary Material}
+%\subsection*{The SSH model}
+%\label{sshapp}
+
+%The SSH model \cite{asboth2016short} describes the movement of free electrons along a dimerized chain whose basic units consist of two distinct atoms.
 This movement, usually called ``hopping'' in the literature, can be made either between atoms in a unit cell or between unit cells, and the allowed hopping rules for a given system completely determine its Hamiltonian.
 This is because the kinetic energies of the electrons are parameterized by a vector of real numbers $\mathbf{t}$ that also encodes hopping terms, thus allowing for a compact mathematical description of a Hamiltonian in terms of creation/annihilation operators as
-\begin{equation}
-\label{SSH}
-\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-where the column vector
-\begin{equation*}
-\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
-\end{equation*}
-contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
-\begin{equation*}
-\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
-\end{equation*}
-contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
+%\begin{equation}
+%\label{SSH}
+%\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
+%\end{equation}
+%where the column vector
+%\begin{equation*}
+%\mathbf{c} =\Big(c^{A}_1,c^{B}_1,\cdots,c^{A}_\frac{N}{2},c^{B}_\frac{N}{2}\Big)^T
+%\end{equation*}
+%contains annihilation operators $c^{A(B)}_p$ that erase electrons at atom A (B) and lattice site $p$ and similarly the row vector
+%\begin{equation*}
+%\mathbf{c}^\dagger =\Big(c^{A\dagger}_1,c^{B\dagger}_1,\cdots,c^{A\dagger}_\frac{N}{2},c^{B\dagger}_\frac{N}{2}\Big)
+%\end{equation*}
+%contains creation operators $c^{A(B)\dagger}_p$ that produce electrons at atom A (B) and lattice site $p$.
 Please note that $N$ is twice the number of unit cells in the chain and therefore an even integer.
 
-The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
+%The convenience of equation \eqref{SSH} is that all information about a system such as its eigenstates and eigenenergies can be recovered from the $N\times N$ matrix $H(\mathbf{t})$.
 We can thus think of the vectors $\mathbf{t}$ in parameter space as very compact representations of SSH models: each point in $\mathbf{t}$-space can be mapped to a $N\times N$ matrix $H(\mathbf{t})$ whose eigenvectors and eigenvalues can then be computed, as is usually done in quantum mechanics.
 As an example, a general matrix $H(\mathbf{t})$ describing a SSH system with hoppings between nearest and second nearest neighbors is given by
-\begin{equation}\label{hmatrix}
-H(t_1,t_2,T_1,T_2)=\left(
-  \begin{array}{cccccc}
-    0 & t_1 & 0 & T_1 & 0 & \cdots \\
-    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
-    0 & t_2 & 0 & t_1 & 0 & \cdots\\
-    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
-    0 & T_2 & 0 & t_2 &  0& \cdots\\
-    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
-  \end{array}
-  \right)_{N \times N}.
-\end{equation}
-Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
+%\begin{equation}\label{hmatrix}
+%H(t_1,t_2,T_1,T_2)=\left(
+%  \begin{array}{cccccc}
+%    0 & t_1 & 0 & T_1 & 0 & \cdots \\
+%    t_1 & 0 & t_2& 0 & T_2 & \cdots\\
+%    0 & t_2 & 0 & t_1 & 0 & \cdots\\
+%    T_1 & 0 & t_1 & 0 & t_2 & \cdots\\
+%    0 & T_2 & 0 & t_2 &  0& \cdots\\
+%    \vdots & \vdots    & \vdots & \vdots &  \vdots & \ddots\\
+%  \end{array}
+%  \right)_{N \times N}.
+%\end{equation}
+%Knowing the vector $\mathbf{t}=(t_1,t_2,T_1,T_2)$ corresponding to a particular system described by the Hamiltonian in equation \eqref{hmatrix} should suffice to compute any of its physical properties, including its topological phase.
 Figure \ref{fig:model} depicts a SSH system described by equation \eqref{hmatrix}.
 
-The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
-This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
+%The reason why topological materials garnered so much interest in recent years is that their physical properties are topologically robust.
+%This means that these properties are stable under continuous (i.e., adiabatic) mathematical operations performed on the system's underlying wave functions.
 This topological robustness is expressed theoretically in terms of a topological invariant that characterizes different phases of a system.
@@
 
-The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
+%The winding number is a topological property of any closed, oriented curve that measures how many times the curve winds around a point that does not belong to itself.
 It can be any integer and is usually chosen to be positive when the curve winds in counterclockwise motion with respect to the reference point (equivalently, when a closed, oriented curve winds in clockwise motion around a reference point its winding number is negative).
@@
 
-An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
+%An interesting property of topological invariants like the winding number is that they are a global feature of geometric objects: for each of the curves in figure \ref{fig:winding} for example the winding number is a property of the whole curve that cannot be defined locally for each of its points.
 This fundamental characteristic of topological invariants makes the study of topological phases of matter from local lattice data a challenging task.
 
-For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
-\begin{equation}\label{winding_number}
-W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
-\end{equation}
-where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\mathbf{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
+%For SSH systems with translational symmetry like the finite systems with periodic boundary conditions investigated in the article, the winding number is usually computed in wavevector space via
+%\begin{equation}\label{winding_number}
+%W=\frac{1}{4\pi i}\int_0^{2\pi} dk Tr( \sigma_3 H(k)^{-1} \partial_k H(k)),
+%\end{equation}
+%where $H(k)$ is the kernel in wavevector space of a Hamiltonian $\mathbf{H}$$($$\mathbf{t}$$)$ and $\sigma_3$ is the chiral operator.
 Equation \eqref{winding_number} can be evaluated for several Hamiltonians by varying the parameter $\mathbf{t}$, resulting in phase diagrams in parameter space like the ones shown in figure 1 in the article.
-%\ref{fig:phasediagrams}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{\SSHOneCompressedRealSpacePhaseDiagram}}
-\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDCTPhaseDiagram}}
-\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDSTPhaseDiagram}}
-\caption{Phase diagrams learned from compressed representations of the SSH 1 system.
+
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{\SSHOneCompressedRealSpacePhaseDiagram}}
+%\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDCTPhaseDiagram}}
+%\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{\SSHOneCompressedDSTPhaseDiagram}}
+%\caption{Phase diagrams learned from compressed representations of the SSH 1 system.
 (a) Phase diagram learned using the real space features \xSOne.
@@
 (b) Phase diagram learned from the DST topological features \xsSOOne.}
-\label{eng_feat_ssh1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedRealSpacePhaseDiagram}}
-\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDCTPhaseDiagram}}
-\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDSTPhaseDiagram}}
-\caption{Phase diagrams learned from compressed representations of the SSH 2 system.
+%\label{eng_feat_ssh1}
+%\end{figure}
+
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedRealSpacePhaseDiagram}}
+%\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDCTPhaseDiagram}}
+%\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{\SSHTwoCompressedDSTPhaseDiagram}}
+%\caption{Phase diagrams learned from compressed representations of the SSH 2 system.
 (a) Phase diagram learned using the real space features \xSTwo.
@@
 (b) Phase diagram learned from the DST topological features \xsSOTwo.}
-\label{eng_feat_ssh2}
-\end{figure}
-
-\subsection*{Learning topological phases from real space data}
-
-%The main motivations for developing a data-driven approach based on real space are that wavevector space computations such as eq.
-%\eqref{winding_number} are only possible for systems with translational symmetry, which many physical systems of current interest (e.g.
-%disordered systems in condensed matter) do not have.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier %transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-We argue here that a data-driven %approach based on real space offers a viable alternative to wavevector space computations that addresses these shortcomings.
-
-The insights behind our intuition that topological phases can be learned from local features are as follows.
+%\label{eng_feat_ssh2}
+%\end{figure}
+
+%\subsection*{Learning topological phases from real space data}
+
+%We now discuss the principles that lead us to the intuition that learning topological phases from local real space data should be possible.
 First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
@@
 
-In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
+%In a data-driven approach, locality is often exploited by means of a local constancy hypothesis \cite{goodfellow2016deep}.
 Mathematically, this policy prescribes the value of a function $W(\mathbf{t}')$ at points where it is unknown in a vicinity of a data point $\mathbf{t}$ as approximately equal to its known value $W(\mathbf{t})$,
-\begin{equation}
-\label{localconstancy}
-W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
-\end{equation}
-
-That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure 1 in the article %\ref{fig:phasediagrams}, 
-where we draw phase diagrams of SSH models with first-neighbor (figure 1(a)) and first- and second-neighbor (figure 1(b)) hoppings.
+%\begin{equation}
+%\label{localconstancy}
+%W(\mathbf{t} + \boldsymbol{\delta}) \approx W(\mathbf{t}).
+%\end{equation}
+
+%That such a policy will be successful in classifying topological phases in parameter space can be visualized in figure 1 in the article %\ref{fig:phasediagrams}, 
+%where we draw phase diagrams of SSH models with first-neighbor (figure 1(a)) and first- and second-neighbor (figure 1(b)) hoppings.
 In figure 1(a) for example, it is clear that knowing a particular Hamiltonian $H(t_1,t_2)$ with winding number $W = 0$ (that is, in one of the red regions) means that there is a small neighborhood around $(t_1,t_2)$ in which all Hamiltonians  belong to the same topological phase.
@@
 
-It does not immediately follow, however, that the same strategy will be successful in real space.
+%It does not immediately follow, however, that the same strategy will be successful in real space.
 Indeed, at first sight it may appear that a local constancy policy should be able to easily exploit locality in real space through the diagonalization maps $v^{(j,l)}: \mathbb{R}^h \rightarrow \mathbb{R}^{N}$,
 
-\begin{equation}
-\label{parameter_to_real}
-\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
-\end{equation}
-where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
+%\begin{equation}
+%\label{parameter_to_real}
+%\mathbf{t} = (t_1,..,t_h) \rightarrow \Big(v^{(j,1)}(t_1,...,t_h),...,v^{(j,N)}(t_1,...,t_h)\Big) = \mathbf{v}^{(j)}(\mathbf{t}) 
+%\end{equation}
+%where $j$ $=$ $1$, ..., $N$ and $\mathbf{v}^{(j)}$$($$\mathbf{t}$$)$ is an eigenvector of the Hamiltonian $H$$($$\mathbf{t}$$)$.
 The trouble with this reasoning is that it disregards the high dimensionality of real space, i.e., the fact that $h$ $\ll$ $N$.
 
-This fact is well illustrated by the numerical experiments discussed in the article.
+%This fact is well illustrated by the numerical experiments discussed in the article.
 Although it may seem from figures 2(b) and 3(b) (from the article) in 2D parameter space that we have used a large number of data points for this learning task, it is important to note that in the numerical experiments the decision trees have taken as inputs 100D eigenvectors in real lattice space.
@@
 
-The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as \emph{the curse of dimensionality} \cite{bishop2006pattern}.
+%The difficulty arising from machine learning problems in high-dimensional spaces is commonly referred to as \emph{the curse of dimensionality} \cite{bishop2006pattern}.
 It essentially expresses the fact that the amount of data needed to ensure a machine learning algorithm will generalize well out of its training set grows exponentially with the dimensionality of feature space.
 
-These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
+%These apparently conflicting facets of our learning problem are harmonized by the manifold hypothesis \cite{cayton2005algorithms,narayanan2010sample}: even though the eigenvectors exist in a high-dimensional space (100D in the numerical experiments), they are actually much lower-dimensional surfaces (2D in the numerical experiments) embedded in this space.
 Furthermore, the different classes in our problem correspond to different submanifolds as can easily be seen in parameter space (this is often referred to as the manifold hypothesis for classification \cite{rifai2011manifold}).
@@
 
-\subsection*{Numerical explorations on longer lattices}
-
-A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
-
-The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
+%\subsection*{Numerical explorations on longer lattices}
+
+%A natural question that comes to mind regarding the information entropy signatures presented here is whether these signals are artifacts of the numerical procedure used to generate them.
+
+%The eigenvector ensembling algorithm used in this work contains steps for generating data (step 1), sampling training data (step 2) and training a supervised learning algorithm on the sampled training data (step 3).
 Each of these steps can generate misleading artifacts that do not represent real properties of the physical systems we are investigating.
 
-Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
+%Artifacts resulting from randomization in the eigenvector ensembling algorithm can be traced to sampling (step 2) or any random components in the supervised learning algorithm used (step 3).
 As an example, random forests allocate subsets of features stochastically to each of its decision trees, thus generating a randomization effect.
@@
 
-There are still artifacts that might arise from the hyperparameters used to generate the data.
+%There are still artifacts that might arise from the hyperparameters used to generate the data.
 These hyperparameters include lattice size and grid specifications (i.e., choices regarding the discretization of parameter space).
@@
 
-All results presented in the article were obtained for lattices with 50 unit cells.
+%All results presented in the article were obtained for lattices with 50 unit cells.
 Each cell contains two different atoms, thus leading to 100$\times$100 Hamiltonian matrices and their corresponding eigenvectors in $\mathbb{R}^{100}$.
@@
 
-It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size is increased.
+%It is clear from figures \ref{feature_importances_ssh1_longer_lattices} and \ref{feature_importances_ssh2_longer_lattices} that the patterns seen with 50 unit cells (figures 6(a) and 6(b) in the article) are stable across higher lattice sizes, with finer details emerging in the signals as the lattice size is increased.
 This naturally leads us to speculation about the continuum limit of information entropy signatures, a matter formally explored in the article.
 
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneFourZero}}
-\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneEightZero}}
-\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureTwoTwoZero}}
-\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneFourZero}}
+%\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureOneEightZero}}
+%\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneEntropySignatureTwoTwoZero}}
+%\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes.
 (a) Information entropy signature for 70 unit cells.
@@
 (c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh1_longer_lattices}
-\end{figure}
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneFourZero}}
-\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneEightZero}}
-\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureTwoTwoZero}}
-\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
+%\label{feature_importances_ssh1_longer_lattices}
+%\end{figure}
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneFourZero}}
+%\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureOneEightZero}}
+%\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoEntropySignatureTwoTwoZero}}
+%\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes.
 (a) Information entropy signature for 70 unit cells.
@@
 (c) Information entropy signature for 110 unit cells.}
-\label{feature_importances_ssh2_longer_lattices}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneFourZero}}
-\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneEightZero}}
-\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyTwoTwoZero}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
+%\label{feature_importances_ssh2_longer_lattices}
+%\end{figure}
+
+%\pagebreak
+
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneFourZero}}
+%\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyOneEightZero}}
+%\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{\SSHOneCumulativeEntropyTwoTwoZero}}
+%\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1.
 (a) Cumulative entropy distribution for 70 unit cells.
@@
 (c) Cumulative entropy distribution for 110 unit cells.}
-\label{cdf1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneFourZero}}
-\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneEightZero}}
-\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyTwoTwoZero}}
-\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
+%\label{cdf1}
+%\end{figure}
+
+%\begin{figure}
+%\centering
+%\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneFourZero}}
+%\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyOneEightZero}}
+%\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{\SSHTwoCumulativeEntropyTwoTwoZero}}
+%\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2.
 (a) Cumulative entropy distributions for 70 unit cells.
@@
 (c) Cumulative entropy distributions for 110 unit cells.}
-\label{cdf2}
-\end{figure}
+%\label{cdf2}
+%\end{figure}
 

### 2020-07-28 10_prb_resubmission_01/letter_referee/letter_referee.tex
Submitted to Arxiv and PRB

--- 2020-07-24 10_prb_resubmission_01/02_letter_referee/letter_referee.tex
@@
 
-we appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900).
+We appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900).
 We have fully addressed the issues pointed by referee 2, which have led to a much improved version of the paper, hopefully the definitive version.
@@
 The eigenvector ensembling algorithm}.
-The section \textbf{VII.
-Discussion} has been extended to address the issues that were raised.
+The sections \textbf{I.
+Introduction}, \textbf{VII.
+Discussion} as well as the \textbf{Abstract} have been extended to conform with these additions.
 The sections are now numbered for clarity.
@@
 
-we appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}.
+We appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}.
 We are currently cleaning, pruning and documenting our code, so we expect to put the Python code used to run the numerical experiments described in the paper online as soon as possible.
@@
 
-we appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with.
+We appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with.
 These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical contents.
@@
 The eigenvector ensembling algorithm}.
-The section \textbf{VII.
-Discussion} has been extended to include comments on the issues that were raised.
+The sections \textbf{I.
+Introduction}, \textbf{VII.
+Discussion} as well as the \textbf{Abstract} have been extended to conform with these additions.
 The sections are now numbered for clarity.
@@
 As to the physics being captured by our procedure, see the answer to the issue \citequote{physical_insights}.}
-
-%While there may surely be other ways to achieve a similar result, using eigenvectors as input data is fairly straightforward and, as we have %demonstrated, as we have demonstrated tage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian %encode all the physical information of the particular system in terms of local components in real space.
-In fact, the use of eigenvectors %play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
-In the majority of %the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses %track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
-The paper paves the way for new theoretical %investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
-%In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy %signature and its corresponding entropic uncertainty relation for topological phase transitions in SSH systems.
-}
 
@@
 
-%While there may surely be other ways to achieve a similar result, using eigenvectors as input data is fairly straightforward and, as we have %demonstrated, as we have demonstrated tage of using eigenvectors in real space is that the set of eigenvectors of a particular Hamiltonian %encode all the physical information of the particular system in terms of local components in real space.
-In fact, the use of eigenvectors %play an essential role in this paper and is one of the main features that distinguishes it from the existing literature.
-In the majority of %the published papers investigating phase transitions in condensed matter physics, neural networks are employed on a data structure that loses %track of local information ADD THIS TO  EIGENVECTOR ENSEMBLING ALG SECTION  IN PAPER!!!
-The paper paves the way for new theoretical %investigation on the relations between the shannon entropy of eigenvectors and topological phase transitions.
-%In our paper, we use model explainability tools from decision trees and random forests to arrive at a previously unknown spatial entropy %signature and its corresponding entropic uncertainty relation for topological phase transitions in SSH systems.
-}
-
 \vspace{0.5cm}

### 2020-08-12 11_prb_resubmission_02/article.tex
The end?

--- 2020-07-28 10_prb_resubmission_01/article.tex
@@
 and describes e.g.
-the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material).
+the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material \cite{supplementary}).
 The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.
@@
 They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
+The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material \cite{supplementary}.
 
@@
 In this sense, key topological information can be said to be localized on few sites in the lattice.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
+We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material \cite{supplementary} for a discussion of how this is possible.
 
@@
   {1979})}\BibitemShut {NoStop}%
+%%%%% Reference to supplementary material %%%%%%%
+\bibitem{supplementary} See Supplementary Material at url inserted by publisher for further discussions on the SSH model as well as the mathematical feasibility of learning topological phases from real space data\BibitemShut {NoStop}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibitem [{\citenamefont {Maffei}\ \emph {et~al.}(2018)\citenamefont {Maffei},

### 2020-08-21 11_prb_resubmission_02/supplementary/supplemental.tex
Reviewing proofs

--- 2020-07-27 07_paper/article.tex
@@
 \usepackage{bbm}
+\usepackage{multibib}
 
@@
 
-\begin{document}
-
-\nocite{*}
-
-\title{Machine learning topological phases in real space}
-
-\author{N. L. Holanda}
-\email{linneuholanda@gmail.com, linneu@cbpf.br}
-\affiliation{Integrated Quantum Materials, Cavendish Laboratory, University of Cambridge, J. J. Thomson Avenue, Cambridge, CB3 0HE, United Kingdom}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-
-\author{M. A. S. Griffith}
-\email{griffithphys@gmail.com}
-\affiliation{Centro Brasileiro de Pesquisas F\'isicas, \\Rua Dr. Xavier Sigaud, 150 - Urca, 22290-180,  Rio de Janeiro, RJ, Brazil}
-\affiliation{Departamento de Ciências Naturais, Universidade Federal de S\~ao Jo\~ao Del Rei, Praça Dom Helv\'ecio 74, 36301-160, S\~ao Jo\~ao Del Rei, MG, Brazil}
-
-\date{\today }
-
-\begin{abstract}
-We develop a supervised machine learning algorithm that is able to learn topological phases of finite condensed matter systems from bulk data in real lattice space.
-The algorithm employs diagonalization in real space together with any supervised learning algorithm to learn topological phases through an eigenvector ensembling procedure.
-We combine our algorithm with decision trees and random forests to successfully recover topological phase diagrams of Su-Schrieffer-Heeger (SSH) models from bulk lattice data in real space and show how the Shannon information entropy of ensembles of lattice eigenvectors can be used to retrieve a signal detailing how topological information is distributed in the bulk.
-We further use insights obtained from these information entropy signatures to engineer global topological features from real space lattice data that still carry most of the topological information in the lattice, while greatly diminishing the size of feature space, thus effectively amounting to a topological lattice compression.
-Finally, we explore the theoretical possibility of interpreting the information entropy topological signatures in terms of emergent information entropy wave functions, which lead us to Heisenberg and Hirschman uncertainty relations for topological phase transitions.
-The discovery of Shannon information entropy signals associated with topological phase transitions from the analysis of data from several thousand SSH systems illustrates how model explainability in machine learning can advance the research of exotic quantum materials with properties that may power future technological applications such as qubit engineering for quantum computing.
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-\label{introduction}
-The quest for innovative materials that harness exotic quantum properties has lured physicists into the realm of topological insulators and topological states of matter \cite{RevModPhys.82.3045}.
-These materials feature previously unthought-of traits like bulk insulation coupled with metallic conductance at the surface and the splitting of currents according to spin orientation.
-Adding to that, these properties are protected by non-trivial topology that renders them robust to many sources of perturbation like thermal noise.
-Such characteristics make them promising candidates to being the cornerstone of 21st century technologies like spintronics and quantum computing.
-
-These new topological states of matter have been studied in several contexts in condensed matter physics including superconductors \cite {CONTINENTINO2017A1}$^-$\cite{ryu2010topological}, ultracold atoms \cite{atala2013direct}$^-$\cite{meier2016observation}, photonic crystals \cite{hafezi2013imaging}$^-$\cite{PhysRevX.5.031011}, photonic quantum walks \cite{kitagawa2012observation}$^-$\cite{PhysRevX.7.031023} and Weyl semimetals \cite{soluyanov2015type,PhysRevX.5.031013}.
-Among these, the Su-Schrieffer-Heeger (SSH) model \cite{PhysRevLett.42.1698} has attracted particular theoretical interest due to its simplicity and generality.
-
-The SSH model is the simplest tight-binding model that exhibits a topological phase transition.
-As such, it can be viewed as the \emph{Drosophila} of the field, providing a simple framework for testing new techniques.
-The model can be expressed in terms of creation and annihilation operators by the Hamiltonian
-\begin{equation}
-\label{SSH_ham}
-\mathbf{H}(\mathbf{t})=\mathbf{c}^{\dagger}H(\mathbf{t})\mathbf{c}
-\end{equation}
-and describes e.g.
-the hopping of electrons along a one-dimensional chain comprising two atoms per unit cell (a brief discussion of the SSH model and its topological properties can be found in the section \textbf{The SSH model} in the Supplementary Material).
-The SSH model has found several interesting applications in the modelling of diverse systems with non-trivial topology like optical lattices \cite{maffei2018topological}, polymeric materials \cite{RevModPhys.73.681} and topological mechanisms \cite{kane2014topological,Chen13004}.
-
-Many recent papers have explored the possibility of treating the general problem of determining phase transition boundaries of physical systems as machine learning tasks \cite{carrasquilla2017machine}$^-$\cite{rodriguez2018identifying}.
-In the particular case of topological phase transitions, the usual approach for supervised learning is to generate a data set $\big(H_1(k), W_1\big)$, ..., $\big(H_n(k), W_n\big)$ whose inputs are representations of Hamiltonians in wavevector space $H_i(k)$ and targets are their corresponding topological invariants $W_i$ (for the SSH model the topological invariant is the winding number).
-Our paper extends this task to the case of learning topological phase diagrams from input data in real space.
-Strikingly, we find that information localized on a few lattice sites in the bulk is sufficient to predict with high accuracy which topological phase a particular Hamiltonian belongs to.
-
-The main motivation for developing a data-driven approach based on real space is that the canonical method of choice for the analysis of topological systems, i.e.
-wavevector space computations of topological invariants, is often only feasible for systems with translational symmetry, which many physical systems of current interest (e.g.
-disordered systems in condensed matter) do not have.
-Furthermore, it is not always granted that the topological invariants of a physical system being investigated are known in advance, as is presently the case for many gapless insulators.
-In such cases, being able to engineer topological features that encode the topological states of a system while at the same time reducing the system's complexity may provide an alternative strategy.
-Moreover, since real space and wavevector space eigenvectors are related by Fourier transforms, the latter are essentially delocalized and therefore so is any information recovered from them.
-Constructing theoretical methods to trace the distribution of information in topological systems may be an essential prerequisite to discovering new topological invariants and features.
-The data-driven approach designed in this article addresses these issues.
-%In particular, we employ it to scrutinize the issue of localizability of information in topological condensed matter systems.
-
-To investigate topological phases of matter in real space we have designed a novel supervised learning algorithm (here called eigenvector ensembling algorithm) tailored for the task of learning phase transition boundaries from local features.
-The algorithm is based on eigenvector decomposition and eigenvector ensembling and therefore will require minimal changes to be applicable to a broader class of data-driven physics problems.
-We describe the algorithm in detail in section \ref{the_eigenvector_ensembling_algorithm} and demonstrate its effectiveness by combining it with decision trees and random forests to recover the topological phase diagrams of SSH systems from local coordinates of eigenstates in real space.
-This is performed in section \ref{numerical_experiments}.
-
-The advantage of using decision tree-based algorithms to learn topological phases from local eigenvector data is that their use of entropy-based cost functions (such as Shannon information entropy or Gini impurity) furnishes them with an intrinsinc model explanaibility tool that summarizes how important each feature was to learning the desired patterns in the data.
-This makes it much easier to trace the localization of relevant information along the features of a data set.
-Here we use the Shannon information entropy of ensembles of real space eigenvectors to recover a signal quantifying the amount of topological information available from each lattice site.
-This is a highly non-trivial proposition since the topological phase of a system is a global property of the system as a whole emerging from complex interactions between its components, and therefore even defining a local topological signal is a daunting theoretical task.
-To our knowledge this is the first time that a signal describing the localization of topological information in the bulk of topological condensed matter systems is presented in the literature.
-These topological signals, here called information entropy signatures, are the subject of section \ref{information_entropy_signatures}.
-
-In possession of the information entropy signatures, we demonstrate how the symmetries in real and wavevector space eigenvectors can be manipulated with signal processing tools commonly employed in audio and image processing to execute two standard unsupervised learning tasks, namely dimensionality reduction and feature engineering.
-The topological features resulting from this analysis, here denominated Discrete Cosine Transform and Discrete Sine Transform topological features, are discussed in section \ref{topological_feature_engineering}.
-
-The information entropy signatures are finally explored as theoretical constructs in terms of information entropy mass functions along the lattices.
-By taking their continuum limit and admitting that they are quantum in nature, we show how the information entropy signatures can be naturally understood in terms of emergent information entropy wave functions along the lattices.
-The theoretical formulation of the results obtained with machine learning in terms of emergent quantum mechanical wave functions allows us to establish Heisenberg and Hirschman uncertainty principles for the localizability of information entropy in topological phase transitions.
-The emergent information entropy wave functions are the theme of section \ref{emergent_information_entropy_wave_functions}.
-
-The  discovery of information entropy signatures of topological phase transitions and their description as a measurable emergent phenomenon originating from the information entropy of ensembles of topological systems proximal to phase transition boundaries provide clear illustrations of how model explainability in machine learning can guide new discoveries in condensed matter and quantum materials physics, since the existence of these signals was established by analyzing data from several thousand SSH systems which, taken individually, could not have provided any concrete hint of their existence.%\citequote{pipeline_not_work}
-
-As of yet model explainability \cite{gilpin2018explaining}-\cite{roscher2020explainable} is one of the topics at the edge of machine learning research that has been little explored by the physics community working at the interface between the two disciplines.
-This raises important questions as to whether machine learning can in fact help to advance theoretical investigation in physics, since the majority of physics papers published on the subject are proofs of concept aimed at showing that modern machine learning techniques are capable of recognizing the relevant patterns in data from physical systems whose properties were known in advance.
-By proposing new concepts from the data analysis of physical systems of contemporary interest and knitting together ideas from topological phase transitions and information theory by dint of model explainability, we expect to draw the physics community's attention to this essential machine learning tool.
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1}\includegraphics[width=.45\textwidth]{\SSHOnePhaseDiagram}}\quad
-\subfigure[]{\label{ssh2}\includegraphics[width=.45\textwidth]{\SSHTwoPhaseDiagram}}
-\caption{Phase diagrams in parameter space.
-a) SSH model with first-neighbor hoppings $t_1$ and $t_2$.
-The (red) regions with winding number $W$ = 0 are trivial, while the (blue) regions with winding number $W$ = 1 are topologically non-trivial.
-b) SSH model with first ($t_1$ and $t_2$) and second ($T_1$ and $T_2$) nearest-neighbor hoppings.
-In this article we set $t_1$ = $t_2$ = 1 and renamed the variables $T_1$ $\rightarrow$ $t_1$, $T_2$ $\rightarrow$ $t_2$ for convenience.
-The (orange) region with winding number $W$ = 0 is trivial while the others with winding numbers $W$ = -1, $W$ = 1 and $W$ = 2 (red, green and blue respectively) are topologically non-trivial.}
-\label{fig:phasediagrams}
-\end{figure}
-
-\section{The eigenvector ensembling algorithm}
-\label{the_eigenvector_ensembling_algorithm}
-The eigenvector ensembling algorithm consists of five steps: 1) Generating Hamiltonians in real space and their corresponding winding numbers; 2) Creating training, validation and test sets; 3) Training on real space eigenvectors of Hamiltonians in the training set; 4) Eigenvector ensembling and 5) Bootstrapping.
-We describe here in detail each of these steps as they were implemented in this work.
-For a comprehensive introduction to the concepts referenced in the steps below, we recommend the book \cite{friedman2001elements}.
-\vspace{.3cm}
-\begin{enumerate}%[topsep=0pt, partopsep=0pt]
-\item[1)] \textbf{Generating Hamiltonians and winding numbers:} we start generating a number of paremeterized Hamiltonians $H(\mathbf{t})$ in real space and their corresponding winding numbers $W(\mathbf{t})$, where $\mathbf{t} = (t_1, t_2,...,t_h)$ is a vector of $h$ hopping parameters (in the simplest case of the SSH model $h$ = 2).
-These Hamiltonians are $N\times N$ matrices, where $N$ is twice the number of unit cells in the chain.
-\item[2)] \textbf{Creating training, validation and test sets:} we split our set of parameterized Hamiltonians and winding numbers into training, validation and test sets, as is usualy done in machine learning.
-More explicitly, assume our hopping parameters vector $\mathbf{t}$ takes on the values $\mathbf{t}_1, \mathbf{t}_2, ..., \mathbf{t}_n$ corresponding to the Hamiltonian-winding number pairs ($H_1$, $W_1$), ..., ($H_n$, $W_n$).
-We partition the set \{($H_i$, $W_i$)$\mid$ $i=1,...,n$\} in three disjoint subsets: the training set, the validation set and the test set.
-\item[3)] \textbf{Training on eigenvectors in real space:} since each Hamiltonian $H_i$ is represented by an $N\times N$ matrix, each one will provide $N$ eigenvectors $\mathbf{v}_i^{(1)}, \mathbf{v}_i^{(2)},...,\mathbf{v}_i^{(N)}$ to our data set.
-Our supervised learning algorithm of choice will take as inputs the real space eigenvectors $\mathbf{v}^{(j)}_i$ of each Hamiltonian $H_i$ in the training set and be trained to learn the winding number $W_i$ of their parent Hamiltonian $H_i$.
-Therefore, our dataset will consist of eigenvector-winding number pairs $(\mathbf{v}_i^{(j)}, W_i)$.
-\item[4)]\textbf{Eigenvector ensembling:} in order to predict the phase of a system described by a particular Hamiltonian we need to take into account how each of its eigenvectors were classified.
-This amounts to performing ensemble learning on the eigenvectors of each Hamiltonian.
-In this work we estimate the phase probabilities for each Hamiltonian as the fraction of its eigenvectors that were classified in each phase.
-\item[5)] \textbf{Bootstrapping:} We refine the phase probabilities for each Hamiltonian using a bootstrapping procedure, i.e., we repeat steps (1)-(4) $n_\text{exp}$ times, at each round sampling randomly a new training set from our grid in \textbf{t}-space.
-The final estimated probabilities are then arrived at by averaging the probabilities obtained in each experiment.
-\end{enumerate}
-
-\vspace{.3cm}
-Before continuing to the analyses of the SSH systems with the eigenvector ensembling algorithm, it will be timely to digress a moment and peek into the algorithm itself.
-The focus on eigenvectors (and hence the algorithm's name) as the input data to a machine learning algorithm of choice is a hallmark of the procedure as it differentiates it from related applications of machine learning to the study of phase transitions.
-The intuition that eigenvectors can be used in replacement of raw Hamiltonians can be grasped when we consider the spectral decomposition of a Hamiltonian $H$,
-\begin{equation}
-\label{eigen_decomposition}
-H = \sum_{i=1}^{N}\lambda^{(i)} \ket{\mathbf{v}^{(i)}}\bra{\mathbf{v}^{(i)}}
-\end{equation}
-where $\lambda^{(i)}$ is the eigenenergy corresponding to the eigenstate $\ket{\mathbf{v}^{(i)}}$.
-It is therefore clear that all information available from a Hamiltonian can be recovered from its spectral decomposition.
-By expressing the eigenvectors in a basis suitable to a particular problem (e.g.
-the real space basis chosen in this article), it becomes possible to investigate the properties of a set of Hamiltonians using the coordinates of eigenvectors in the chosen basis as features.
-Thus the eigenvector ensembling procedure described above provides a broad framework for the implementation of model explainability in applications to data-driven physics.
-
-\section{Numerical experiments}
-\label{numerical_experiments}
-We performed two numerical experiments with the eigenvector ensembling algorithm.
-The first experiment deals with the simplest case, the SSH model with nearest-neighbor hopping (here called SSH 1, figure \ref{ssh1}), while the second experiment uses the SSH model with first and second nearest-neighbor hoppings (here called SSH 2, figure \ref{ssh2}).
-
-In each experiment our grid consisted of \nHam\ Hamiltonians uniformly distributed in the closed square $[-2,2]\times[-2,2]$ in the $t_1$-$t_2$ plane in parameter space.
-The goal in each experiment is to recover the corresponding phase diagram in 2D (two-dimensional) parameter space, figures \ref{ssh1} and \ref{ssh2}, from local lattice data in the much higher-dimensional real space (100D - in both experiments lattices have 50 unit cells, yielding 100$\times$100 Hamiltonian matrices).
-
-This task is particularly hard near phase transition boundaries, where numerical computation of winding numbers become less stable.
-For this reason, when sampling the training set we only consider those Hamiltonians in the grid whose numerically computed winding numbers lie in a minimum range of $\epsilon = \epsilonValue$ from the correct winding number values.
-Therefore, a good performance metric is the accuracy measured at those Hamiltonians near phase transitions that are never used for training, and thus we assign them to the test set.
-The remaining Hamiltonians in the grid are split into training and validation sets as detailed in the subsections below.
-
-As performance metrics, we report here both accuracy of predicted classes for eigenvectors as well as accuracy of predicted classes for Hamiltonians obtained from eigenvector ensembling.
-These accuracy scores are to be gauged against the baseline of a system that simply guesses the most frequent class for all Hamiltonians.
-Checking against this baseline is important because it indicates whether the decision trees are in fact learning the underlying patterns that relate real space coordinates to winding numbers, and therefore whether the associated information entropy signature is meaningful or not.
-
-When generating the Hamiltonians we applied periodic boundary conditions to eliminate border effects.
-This should make recovering a topological signal from local eigenvector coordinates even harder, since in this case the translational symmetry of the systems should allow for no obvious way to distinguish between unit cells.
-The choice of periodic boundary conditions also implies that the information recovered from real space data comes from the bulk of the topological systems considered and therefore provides strong evidence for the existence of topological signatures in the bulk of such systems.
-
-Figures \ref{figexp1_exp} and \ref{figexp2_exp} respectively illustrate single iterations of experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) as seen from parameter space.
-The accuracy statistics presented in the following subsections, as well as the probability heatmaps and recovered phase diagrams shown in figures \ref{ssh1_heatmaps} and \ref{ssh2_heatmaps} were obtained after bootstrapping each experiment $n_{exp}$ = \nExp\ times.
-Thus, each probability heatmap shown in figures \ref{ssh1_heatmap_0}, \ref{ssh1_heatmap_1} and \ref{ssh2_heatmap_-1} to \ref{ssh2_heatmap_2} represents the averaged fraction of eigenvectors of each Hamiltonian in the grid that were classified with a given winding number across 100 experiments.
-The recovered phase diagrams \ref{ssh1_heatmap} and \ref{ssh2_heatmap} are constructed by superposing the corresponding probability heatmaps.
-As these figure make clear, the recovered phase diagrams faithfully portray the true phase diagrams in figure \ref{fig:phasediagrams}, with clear phase transition lines appearing in the regions of highest uncertainty.
-
-The numerical experiments with the eigenvector ensembling algorithm described in the next subsections were implemented in Python using the scikit-learn module \cite{scikit-learn,sklearn_api}.
-
-\subsection{Experiment 1: Learning a first-neighbor hopping SSH model with decision trees}
-\label{experiment_1}
-Our test set in this experiment contained \sshOneTestNHam\ Hamiltonians (approx.
-\sshOneTestFracHam\% of all data).
-Of the remaining \sshOneTrainPlusValNHam\ Hamiltonians, \sshOneTrainNHam\ were randomly assigned to the training set (approx.
-\sshOneTrainFracHam\%) and \sshOneValNHam\ (approx.
-\sshOneValFracHam\%) were used to compute validation scores at each iteration.
-These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were used for training at each iteration.
-The composition of the train + validation set for this experiment was \sshOneTrainPlusValWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTrainPlusValWindOneFracHam\% with winding number $W$ = 1.
-The composition of the test set was \sshOneTestWindZeroFracHam\% of Hamiltonians with winding number $W$ = 0 and \sshOneTestWindOneFracHam\% with winding number $W=1$.
-Our learning algorithm of choice for this experiment was a simple decision tree model \cite{breiman2017classification}.
-
-The bootstrap allows us to collect several statistics to evaluate performance.
-In particular, we report mean accuracies on training eigenvectors (\xOneEigTrain), validation eigenvectors (\xOneEigVal) and test eigenvectors (\xOneEigTest).
-Eigenvector ensembling substantially improved mean accuracies for Hamiltonians.
-These were \xOneHamTrain\ for training Hamiltonians, \xOneHamVal\ for validation Hamiltonians and \xOneHamTest\ for test Hamiltonians.
-When compared with the baseline test accuracy of \sshOneHamTestBaseline\ of a system that predicts the whole test set as having winding number $W=1$, the accuracy achieved on test Hamiltonians indicates that the decision trees indeed learned the patterns that relate real space coordinates to winding numbers.
-
-The probability heatmaps and phase diagram learned by the combination of decision trees with eigenvector ensembling used in experiment 1 are shown in figure \ref{ssh1_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp1_exp:a}\includegraphics[width=.32\textwidth]{\SSHOneTrainValTestSplit}}
-\subfigure[]{\label{figexp1_exp:b}\includegraphics[width=.32\textwidth]{\SSHOneWindingTrain}}
-\subfigure[]{\label{figexp1_exp:c}\includegraphics[width=.32\textwidth]{\SSHOnePredictionGrid}}
-\caption{Visualization of a single iteration of experiment 1 (section \ref{experiment_1}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by combining a decision tree with eigenvector ensembling.}
-\label{figexp1_exp}
-\end{figure}
-
-\subsection{Experiment 2: Learning a first- and second-neighbor hoppings SSH model with random forests}
-\label{experiment_2}
-
-This task is considerably more difficult than the previous one due to the higher number of classes and the fact that some of the labels encompass disconnected regions.
-For this reason, instead of using a single decision tree, we upgraded our model to a random forest \cite{Breiman2001} with \nEst\ decision trees.
-Our data set consisted of \sshTwoTestNHam\ (\sshTwoTestFracHam\%) test Hamiltonians.
-The remaining \sshTwoTrainPlusValNHam\ Hamiltonians are randomly split in half between training and validation sets at each iteration, giving \sshTwoTrainNHam\ (\sshTwoTrainFracHam\%) training Hamiltonians and \sshTwoValNHam\ (\sshTwoValFracHam\%) validation Hamiltonians.
-The distribution of winding numbers for the Hamiltonians in the train + validation set for this experiment was $W$ = -1 (\sshTwoTrainPlusValWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTrainPlusValWindZeroFracHam\%), $W$ = 1 (\sshTwoTrainPlusValWindOneFracHam\%) and $W$ = 2 (\sshTwoTrainPlusValWindTwoFracHam\%).
-The distribution of winding numbers for the Hamiltonians in the test set was $W$ = -1 (\sshTwoTestWindMinusOneFracHam\%), $W$ = 0 (\sshTwoTestWindZeroFracHam\%), $W$ = 1 (\sshTwoTestWindOneFracHam\%) and $W$ = 2 (\sshTwoTestWindTwoFracHam\%).
-
-Mean accuracies across \nExp\ repetitions of experiment 2 were \xTwoEigTrain\ for training eigenvectors, \xTwoEigVal\ for validation eigenvectors and \xTwoEigTest\ for test eigenvectors.
-Mean accuracies resulting from eigenvector ensembling were \xTwoHamTrain\ for training Hamiltonians, \xTwoHamVal\ for validation Hamiltonians and \xTwoHamTest\ for test Hamiltonians.
-The large accuracy gain achieved by eigenvector ensembling in the test set (going from \xTwoEigTest\ eigenvector accuracy to \xTwoHamTest\ Hamiltonian accuracy) attests to its power.
-The effectiveness of eigenvector ensembling is also evident from the much worse performance (\sshTwoHamTestBaseline) achieved by a baseline system that simply guesses $W=2$ for all test Hamiltonians in this experiment.
-
-The probability heatmaps and phase diagram learned by the combination of random forests with eigenvector ensembling used in experiment 2 are shown in figure \ref{ssh2_heatmaps}.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{figexp2_exp:a}\includegraphics[width=.32\textwidth]{\SSHTwoTrainValTestSplit}}
-\subfigure[]{\label{figexp2_exp:b}\includegraphics[width=.32\textwidth]{\SSHTwoWindingTrain}}
-\subfigure[]{\label{figexp2_exp:c}\includegraphics[width=.32\textwidth]{\SSHTwoPredictionGrid}}
-\caption{Visualization of a single iteration of experiment 2 (section \ref{experiment_2}) as seen from 2D parameter space.
-(a) Train/validation/test split.
-(b) Distribution of winding numbers in the training set.
-(c) Phase diagram learned from real space lattice data by combining a random forest with eigenvector ensembling.}
-\label{figexp2_exp}
-\end{figure}
-
-\section{Information entropy signatures}
-\label{information_entropy_signatures}
-
-We now analyze how the algorithm was able to recover a global property of the Hamiltonians (their topological phase) from bulk local features (real space eigenvector coordinates on each lattice site).
-Alongside the fact that decision trees and random forests are very easy to train and visualize, the other reason that led us to test the eigenvector ensembling algorithm with them was that they allow us to check which features (and thus which lattice sites) were most informative in training.
-
-The (normalized) relevance of a feature is given by how much it reduces a loss function (in this paper, the Shannon information entropy of ensembles of eigenvectors).
-By averaging normalized relevances as measured by reduction in the information entropy of ensembles of real space eigenvectors across $n_{exp}$ = 100 iterations of both experiment 1 (section \ref{experiment_1}) and experiment 2 (section \ref{experiment_2}) we recovered Shannon entropy signals that reveal which lattice sites were consistently more relevant in learning topological phases from data in real space for each experiment.
-These signals are the information entropy signatures of each topological phase transition.
-
-We should briefly comment on the possibility of using the Gini impurity of ensembles of eigenvectors \cite{friedman2001elements} instead of their Shannon entropy as cost function.
-This would similarly lead us to Gini impurity signatures of topological phase transitions.
-Given that in the examples analysed in this paper the Gini impurity signatures and the Shannon entropy signatures were very similar, the larger familiarity of a general physics audience with the latter influenced us to choose it over the former.
-Nevertheless, the question of which split criterion  should be used when training decision trees is as of yet largely undecided \cite{raileanu2004theoretical} and may be of relevance in the analysis of other physical systems than the ones studied here.
-
-The bar plots in figure \ref{feature_importances} show how informative each lattice site was in learning topological phases for each experiment.
-They represent the information entropy signatures along the lattices in each SSH system.
-For experiment 1 (section \ref{experiment_1}), only six lattice sites \sitesExpOne\ corresponding to the two sharp peaks seen in figure \ref{feature_importances_ssh1} contributed approximately 70\% of total reduction in Shannon entropy.
-Similarly, approximately 30\% of total reduction in the Shannon information entropy of eigenvector data from experiment 2 (section \ref{experiment_2}) was achieved by eighteen lattice sites \sitesExpTwo\ distributed along the three peaks in figure \ref{feature_importances_ssh2}.
-As we shall see in section \ref{topological_feature_engineering}, the information entropy signatures can be used to compress the topological information in SSH lattices.
-
-The information entropy signatures presented here have some interesting subtleties.
-Although they give us a visualization of how important each lattice site was in determining the topological phases of Hamiltonians, they actually express a global property of the whole lattice.
-In section \ref{emergent_information_entropy_wave_functions}, where we develop a quantum formalism for the information entropy signatures obtained in this section, these seemingly antagonistic conceptions shall be harmonized.
-What is important to emphasize at this point is that an information entropy signature should not be naively taken at face value: a lattice site that appears unimportant in an information entropy signature plot may not be unimportant or void of topological information by itself.
-
-To give a concrete example, reduction in Shannon entropy tends to be distributed among highly correlated variables.
-This implies that if only a single lattice site in a highly correlated subset is used by a learning algorithm, it will likely inherit most of the reduction in Shannon entropy from the other correlated lattice sites that were not taken into account by the algorithm.
-The corollary of this fact is that lattice sites that carry redundant information that is also available from other lattice sites tend to have decreased importance in the information entropy signature.
-In this regard the information entropy signatures presented here express a summary of relations between lattice sites and are therefore intrinsically global.
-
-Each of the information entropy signatures shown in figure \ref{feature_importances} captures a general pattern that persists regardless of the length of the lattice (i.e., the number of unit cells) used to compute them.
-In fact, by rerunning each experiment with longer lattices we have verified that the signals in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} appear to converge to well defined continuous density functions in the macroscopic limit.
-They are not, therefore, artifacts of particular choices of hyperparameters used to run the eigenvector ensembling algorithm.
-The information entropy signatures for longer lattices are presented in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh1_heatmap_0}\includegraphics[width=.32\textwidth]{\SSHOneWindingZero}}
-\subfigure[]{\label{ssh1_heatmap_1}\includegraphics[width=.32\textwidth]{\SSHOneWindingOne}}
-\subfigure[]{\label{ssh1_heatmap}\includegraphics[width=.32\textwidth]{\SSHOneHeatmap}}
-\caption{Probability heatmaps learned by a combination of decision trees with eigenvector ensembling from bulk real space eigenvector data in experiment 1 (section \ref{experiment_1}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(c) The phase diagram resulting from heatmaps (a) and (b).}
-\label{ssh1_heatmaps}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\label{ssh2_heatmap_-1}\includegraphics[width=.32\textwidth]{\SSHTwoWindingMinusOne}}
-\subfigure[]{\label{ssh2_heatmap_0}\includegraphics[width=.32\textwidth]{\SSHTwoWindingZero}}
-\subfigure[]{\label{ssh2_heatmap_1}\includegraphics[width=.32\textwidth]{\SSHTwoWindingOne}}
-\subfigure[]{\label{ssh2_heatmap_2}\includegraphics[width=.32\textwidth]{\SSHTwoWindingTwo}}
-\subfigure[]{\label{ssh2_heatmap}\includegraphics[width=.32\textwidth]{\SSHTwoHeatmap}}
-\caption{Probability heatmaps learned by a combination of random forests with eigenvector ensembling from bulk real space eigenvector data in experiment 2 (section \ref{experiment_2}).
-Heatmaps were averaged across all 100 iterations of the experiment.
-(a) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to -1.
-(b) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 0.
-(c) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 1.
-(d) Probability heatmap showing the probability that a Hamiltonian in the grid has winding number equal to 2.
-(e) The phase diagram resulting from heatmaps (a)-(d).}
-\label{ssh2_heatmaps}
-\end{figure}
-
-\begin{table}
-\begin{tabular}{||c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c@{\hskip 0.3in} c||} 
-%\caption{ACCURACY SCORES OF NUMERICAL EXPERIMENTS.} \label{numerical_results}
-%\begin{table}[th]
-%\caption{An Example of a Table}
-%\centering\label{table_example}
-%\begin{tabular}{|Sc*{9}{c|}}
-%\toprule
-\hline
-\SSHSys               &\Feat             &\ValEig            &\TestEig           &\ValHam              &\TestHam         \tableRowHeaderEnd 
-%\midrule
-%                     &                  &                   &                   &                     &                   \tableRow{0.3}
-1                     &\xOne             &\xOneEigVal        &\xOneEigTest       &\xOneHamVal          &\xOneHamTest       \tableRowEnd
-1                     &\xSOne            &\xSOneEigVal       &\xSOneEigTest      &\xSOneHamVal         &\xSOneHamVal       \tableRowEnd
-1                     &\xcOne            &\xcOneEigVal       &\xcOneEigTest      &\xcOneHamVal         &\xcOneHamTest      \tableRowEnd
-1                     &\xcEOne           &\xcEOneEigVal      &\xcEOneEigTest     &\xcEOneHamVal        &\xcEOneHamTest     \tableRowEnd
-1                     &\xcSEOne          &\xcSEOneEigVal     &\xcSEOneEigTest    &\xcSEOneHamVal       &\xcSEOneHamTest    \tableRowEnd
-1                     &\xsOne            &\xsOneEigVal       &\xsOneEigTest      &\xsOneHamVal         &\xsOneHamTest      \tableRowEnd
-1                     &\xsOOne           &\xsOOneEigVal      &\xsOOneEigTest     &\xsOOneHamVal        &\xsOOneHamTest     \tableRowEnd
-1                     &\xsSOOne          &\xsSOOneEigVal     &\xsSOOneEigTest    &\xsSOOneHamVal       &\xsSOOneHamTest    \tableRowEnd
-2                     &\xTwo             &\xTwoEigVal        &\xTwoEigTest       &\xTwoHamVal          &\xTwoHamTest       \tableRowEnd
-2                     &\xSTwo            &\xSTwoEigVal       &\xSTwoEigTest      &\xSTwoHamVal         &\xSTwoHamVal       \tableRowEnd
-2                     &\xcTwo            &\xcTwoEigVal       &\xcTwoEigTest      &\xcTwoHamVal         &\xcTwoHamTest      \tableRowEnd
-2                     &\xcETwo           &\xcETwoEigVal      &\xcETwoEigTest     &\xcETwoHamVal        &\xcETwoHamTest     \tableRowEnd
-2                     &\xcSETwo          &\xcSETwoEigVal     &\xcSETwoEigTest    &\xcSETwoHamVal       &\xcSETwoHamTest    \tableRowEnd
-2                     &\xsTwo            &\xsTwoEigVal       &\xsTwoEigTest      &\xsTwoHamVal         &\xsTwoHamTest      \tableRowEnd
-2                     &\xsOTwo           &\xsOTwoEigVal      &\xsOTwoEigTest     &\xsOTwoHamVal        &\xsOTwoHamTest     \tableRowEnd
-2                     &\xsSOTwo          &\xsSOTwoEigVal     &\xsSOTwoEigTest    &\xsSOTwoHamVal       &\xsSOTwoHamTest    \tableRowEnd
-%\bottomrule
-\hline
-\end{tabular}
-\caption{\label{accuracy_scores}Accuracy scores of numerical experiments.
-The features used to train the decision trees (SSH 1) or random forests (SSH 2) in the numerical experiments with SSH systems were as follows.
-Real space features: all real space lattice sites (\xalpha) (sections \ref{experiment_1} and \ref{experiment_2}); real space lattice sites from subset $\mathcal{S}_{\alpha}$ (\xSalpha) (equation \eqref{lattice_subsets}).
-DCT topological features: all DCT topological features (\xcalpha) (equation \eqref{DCT}); DCT topological features from subset $\mathcal{E}_\alpha$ (\xcEalpha) (equation \eqref{DCT_subsets}); DCT topological features from subset $\mathcal{E}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xcSEalpha) (equation \eqref{DCT_very_compressed}).
-DST topological features: all DST topological features (\xsalpha) (equation \eqref{DST}); DST topological features from subset $\mathcal{O}_\alpha$ (\xsOalpha) (equation \eqref{DST_subsets}); DST topological features from subset $\mathcal{O}_\alpha$ computed using only real space lattice sites $\mathcal{S}_{\alpha}$ (\xsSOalpha) (equation \eqref{DST_very_compressed}).
-}
-\end{table}
-
-\section{Topological feature engineering and lattice compression}
-\label{topological_feature_engineering}
-
-In this section, we explore the information entropy signatures obtained in section \ref{information_entropy_signatures} from a signal processing perspective.
-As we shall see, this will enable us to perform two important unsupervised learning tasks on topological systems: dimensionality reduction and data compression.
-
-As a cursory glance at figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} seems to suggest, the existence of peaks and symmetries in information entropy signatures can be exploited as a powerful dimensionality reduction tool: by keeping only the most relevant lattice sites in an information entropy signature, the amount of data needed to characterize the topological phase of a SSH system can be largely decreased with little loss of information.
-Nevertheless, given that the topological phase of a SSH system is a global property of the whole lattice, it is natural to expect that it should be possible to engineer global features from real space coordinates.
-Here we show how the symmetries in real space eigenvectors and information entropy signatures can be exploited to engineer new global topological features, leading to an effective compression of topological information.
-
-%simply extracting local coordinates of real space eigenvectors may not be the most effective way to condense a lattice's topological %information.
-Here we explore the engineering of new global topological features in real space, and how these global features lead to an %effective compression of topological information.
-
-%The information entropy signatures in wavevector space can be easily computed from their counterparts in real space (figures %\ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}) using equation \eqref{fourier_shannon_wave_function} and assuming that the %real space information entropy wave functions are real.
-
-Given a real space eigenvector $x[m]$, we can compute its coordinates in wavevector space using the Discrete Fourier Transform (DFT),  
-\begin{equation}
-\label{discrete_fourier_transform}
-\hat{x}[n] = \frac{1}{\sqrt{N}}\sum_{m=0}^{N-1}x[m]e^{-i\frac{2\pi}{N}nm}, \quad n=0,\dots,N-1.
-\end{equation}
-Since the choice of phase of the real space eigenvectors was such that they were all in $\mathbb{R}^{N}$, the eigenvectors in wavevector space computed from equation \eqref{discrete_fourier_transform} will be Hermitian vectors in $\mathbb{C}^N$.
-The Hermitian symmetry of the wavevector space eigenvectors manifests itself mathematically in closed lattices with periodic boundary conditions as
-\begin{equation}
-\label{hermitian_symmetry}
-\hat{x}[\overline{k}] = \hat{x}^*[\overline{N-k}], \quad k = 0,\dots, N-1,
-\end{equation}
-where  we have used the notation $\overline{k} = k \mod N$.
-
-Equation \eqref{hermitian_symmetry} forks into two natural paths to topological feature engineering.
-In the first path, we exploit the fact that the real part of $\hat{x}[m]$ is even-symmetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$.
-This leads us to the Discrete Cosine Transform (DCT) topological features,
-\begin{equation}
-\label{DCT}
-\hat{x}^{c}[n] = x[0] + (-1)^n x[M-1] + \sum_{m=1}^{M-2} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n=0,\dots,M-1, 
-\end{equation}
-where $M = \frac{N}{2}+1$.
-The second path capitalizes on the fact that the imaginary part of $\hat{x}[m]$ is odd-symetric around the reciprocal lattice sites $0$ and $\frac{N}{2}$, thus yielding the Discrete Sine Transform (DST) topological features,
-\begin{equation}
-\label{DST}
-\hat{x}^{s}[n] = \sum_{m=0}^{M-1} 2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n=0,\dots,M-1,
-\end{equation} 
-where $M = \frac{N}{2}-1$.
-
-The topological features in both equations \eqref{DCT} and \eqref{DST} are generated from only half of the real space lattice, i.e.
-the sites $0 \leq l \leq \frac{N}{2}$.
-This is due to the fact that each equation assumes that the eigenvectors are even-symmetric (DCT topological features) or odd-symmetric (DST topological features) around the lattice sites $0$ and $\frac{N}{2}$ in real space as well.
-While these assumptions are strictly true for the eigenvector representations in wavevector space, they are not generally true for the real space representations.
-Therefore, equations \eqref{DCT} and \eqref{DST} achieve lattice compression by keeping only half of the real space eigenvector coordinates and imposing the corresponding boundary conditions (even symmetry or odd symmetry) on the lattice sites $0$ and $\frac{N}{2}$ to extrapolate the information from one half of the lattice to the other.
-
-The topological feature engineering techniques described above are commonly employed in several applications of Digital Signal Processing like audio and image processing and, most importantly here, data compression.
-As equations \eqref{hermitian_symmetry}-\eqref{DST} show, signal transforms such as the DCT and DST profit from the redundance of information arising from the existence of certain symmetries in signals, allowing us to write a signal of length $N$ in terms of at most $M = \frac{N}{2}+1$ features.
-
-We ran several numerical experiments to evaluate if the DCT and DST topological features defined in equations \eqref{DCT} and \eqref{DST}  are able to efficiently encode the topological information existing in SSH lattices.
-The accuracy scores obtained in each experiment are listed in table \ref{accuracy_scores}, where we also report the accuracy scores of the numerical experiments of section \ref{numerical_experiments}.
-
-The lattice compression strategies tested in this work were: \emph{i)} learning topological phases from only a subset of real space lattice sites; \emph{ii)} learning topological phases from the DCT or DST engineered features of equations \eqref{DCT} and \eqref{DST}; \emph{iii)} learning topological phases from a fraction of the DCT or DST topological features and \emph{iv)} learning topological phases from a fraction of the DCT or DST features, computed from only a fraction of real space lattice sites.
-
-In strategy \emph{i)} the lattice sites used in the SSH 1 and SSH 2 systems were
-\begin{equation}
-\label{lattice_subsets}
-\mathcal{S}_1 = \sitesSOne \quad \text{and} \quad  \mathcal{S}_2 =\sitesSTwo.   
-\end{equation}
-Note that for the nearest-neighbor SSH systems $\mathcal{S}_1$ corresponds to the four most informative sites such that $0\leq l \leq 50$ as indicated by the information entropy signature in figure \ref{feature_importances_ssh1}.
-Similarly, for the first- and second- nearest neighbors SSH systems $\mathcal{S}_2$ corresponds to the twelve most informative sites such that $0\leq l \leq 50$ in the corresponding information entropy signature in figure \ref{feature_importances_ssh2}.
-In table \ref{accuracy_scores}, the features used in strategy \emph{i)} are referred to as \xSOne and \xSTwo, according to the SSH systems they relate to.
-
-In strategy \emph{ii)}, the full set of DCT or DST topological features written in equations \eqref{DCT} and \eqref{DST} were used.
-These features are denoted in table \ref{accuracy_scores} by \xcOne, \xsOne, \xcTwo, \xsTwo, according to which set of topological features and SSH systems they refer to.
-
-Similarly to strategy \emph{i)}, in strategy \emph{iii)} we selected the most informative DCT topological features of both SSH 1 and SSH 2 systems that were obtained from strategy \emph{ii)},
-\begin{equation}
-\label{DCT_subsets}
-\mathcal{E}_1 = \sitesEOne \quad \text{and} \quad  \mathcal{E}_2 =\sitesETwo \qquad \text{(DCT)}  
-\end{equation}
-and the most informative DST topological features of both systems that were obtained from strategy \emph{ii)} as well,
-\begin{equation}
-\label{DST_subsets}
-\mathcal{O}_1 =  \sitesOOne \quad \text{and} \quad  \mathcal{O}_2 = \sitesOTwo \qquad \text{(DST)}.  
-\end{equation}
-The features in strategy \emph{iii)} are denoted in table \ref{accuracy_scores} by \xcEOne, \xsOOne, \xcETwo, \xsOTwo,   according to the topological features and wavevector space subset used with each SSH system.
-
-The most aggressive lattice compression strategy tested in this work was strategy \emph{iv)}.
-It consists of using the DCT (DST) topological features of equation \eqref{DCT_subsets} (equation \eqref{DST_subsets}), but having computed these topological features using only the real space lattice sites given in equation \eqref{lattice_subsets}.
-Thus in strategy \emph{iv)} a lossy compression is performed both on real space features and the engineered DCT (DST) topological features.
-Mathematically, we can express the topological features used in strategy \emph{iv)} as follows:
-\begin{equation}
-\label{DCT_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{E}}^c[n] = \indicator{\mathcal{S}}[0]x[0] + (-1)^n\indicator{\mathcal{S}}[M-1] x[M-1] + \sum_{m \in \mathcal{S}^*} 2x[m]\cos\bigg(\frac{\pi}{M-1}nm\bigg), \quad n \in \mathcal{E} \qquad \text{(DCT)}
-\end{equation}
-\begin{equation}
-\label{DST_very_compressed}
-\hat{x}_{\mathcal{S}, \mathcal{O}}^s[n] = \sum_{m \in \mathcal{S}}2x[m+1]\sin\bigg(\frac{\pi}{M+1}(n+1)(m+1)\bigg), \quad n \in \mathcal{O} \qquad \text{(DST)}
-\end{equation}
-where in equation \eqref{DCT_very_compressed} the notation $\mathbbm{1}_{\mathcal{S}}[l]$ stands for the indicator function of the lattice subset $\mathcal{S}$ and $\mathcal{S}^*$ is the complement of $\{0,M-1\}$ with respect to $\mathcal{S}$,
-\begin{equation}
-\label{indicator_function}
-\indicator{\mathcal{S}}[l] = \begin{cases}
-      1 & \text{if } l \in \mathcal{S} \\
-      0 & \text{otherwise}
-    \end{cases}, \qquad \mathcal{S}^* = \mathcal{S}{\backslash} \{0,M-1\}.
-\end{equation}
-The features engineered in strategy \emph{iv)} are denoted in table \ref{accuracy_scores} by \xcSEOne, \xsSOOne, \xcSETwo, \xsSOTwo, again referencing the type of topological features used, which components in real and wavevector space engineered them and the appropriate SSH systems.
-
-The results shown in table \ref{accuracy_scores} bring some startling surprises.
-For example, the topological phase transition boundaries of SSH 1 systems can be learned using only the four real space lattice sites $\mathcal{S}_1$ with virtually no loss in accuracy, as seen from eigenvector and Hamiltonian accuracy scores for the features \xSOne.
-The same appears to be true to SSH 2 systems, where the twelve real space lattice sites $\mathcal{S}_2$ corresponding to the features \xSTwo\ in the table produce accuracy scores at near the same level as using the whole lattice.
-
-Even more striking is the performance achieved by the compressed DCT topological features \xcSEalpha\ defined in equation \eqref{DCT_very_compressed}.
-For SSH 1 systems, they perform on par with using the full set of real space features \xOne, while for SSH 2 systems a small loss in accuracy is incurred relative to the full set of real space features \xTwo.
-
-Another interesting insight comes from comparing the accuracy scores obtained with the DCT topological features versus the  DST topological features.
-The latter have poorer performance than the former, as is indicated by the sharp drops in accuracy scores obtained with the DST topological features in both SSH 1 and SSH 2 systems.
-This may be related to the fact that the odd-symmetric boundary conditions imposed on DST topological features imply discarding the lattice sites 0 and $50$, which correspond to sharp peaks in the information entropy signatures of figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2}.
-
-The accuracy scores obtained with the real space features \xSalpha\ and the DCT topological features \xcSEalpha, both of which use information from a small fraction of real space lattice sites, demonstrate that learning topological phases from local real space data in the bulk is still possible even for small subsets of lattice sites.
-In this sense, key topological information can be said to be localized on few sites in the lattice.
-We refer the reader to the section \textbf{Learning topological phases from real space data} in the Supplementary Material for a discussion of how this is possible.
-
-\section{Emergent information entropy wave functions}
-\label{emergent_information_entropy_wave_functions}
-
-The information entropy signatures that we have been investigating pose an immediate theoretical question: how can a signal that is locally defined arise from a global property of the whole SSH lattice?
-In this section we venture into a theoretical exploration of the information entropy signatures in the hope of elucidating this issue.
-Our goal is to arrive at a theoretical framework that will allow us to interpret the information entropy signatures in terms of quantum mechanics.
-%The discussion presented here will be complemented by the numerical experiments in the section \textbf{Numerical explorations on longer lattices} in the Supplementary Material.
-
-We can think of the Shannon information entropy signatures in figures \ref{feature_importances_ssh1} and \ref{feature_importances_ssh2} as discrete information entropy mass functions that, in the continuum (i.e.
-macroscopic) limit of an infinite chain, lead to local entropy density functions along the lattices, which themselves become 1D manifolds.
-By mapping the lattice to a  partition of the 1D manifold, the cumulative distribution of topological information in the continuum limit will be given by
-
-\begin{equation}
-\label{entropy_density}
-F_S(x) = \int_{\ell}^{(x)}\rho_S(x')dx'
-\end{equation}
-where $\rho_S(x)$ is the local information entropy density function in the continuum limit and $x$ is defined by the coordinate system specified on the 1D manifold $\ell$.
-The index $S$ is meant to emphasize that in this paper we have used Shannon's definition of entropy to arrive at the information entropy signatures as opposed to e.g.
-Gini impurity.
-
-Our use of periodic boundary conditions implies that the coordinate $x$ should be defined on the circle $ S^1 = [0, 1]/R$, where $R$ is the equivalence relation in $[0,1]$ defining the circle $S^1$ , 
-\begin{equation}
-x \text{ } R \text{ } y \iff x=y \text{ or } (x,y)\in \{(0,1), (1,0)\}.
-\end{equation}
-For open boundary conditions, the spatial coordinate $x$ is defined on the closed interval $[0,1]$ or, in the case of infinite systems, $\mathbb{R}$.
-However, for the sake of generality, we shall continue to use the caligraphic $\ell$ to denote an arbitrary 1D manifold in this section.
-
-Given the quantum nature of the phase transitions being discussed, the information entropy density function $\rho_S(x)$ can be naturally interpreted as the squared magnitude of a spatial information entropy wave function,
-
-\begin{equation}
-\label{shannon_wave_function}
-\rho_S(x) = |\psi_S(x)|^2,
-\end{equation}
-the local density of topological information available from a single point in the 1D manifold then being expressed in bra-ket notation by Born's rule,
-
-\begin{equation}
-\label{born_rule_spatial}
-\rho_S(x) = |\braket{x|\psi_S}|^2.
-\end{equation}
-
-The counterpart of the spatial information entropy wave function $\psi_S(x)$ in wavevector space is its Fourier transform 
-\begin{equation}
-\label{fourier_shannon_wave_function}
-\hat{\psi}_S(k) = \int_{\ell}\psi_S(x)e^{-2\pi ikx}dx
-\end{equation}
-from which the information entropy density function in wavevector space can be computed,
-\begin{equation}
-\label{shannon_wave_function_wavevector_space}
-\hat{\rho}_S(k) = |\hat{\psi}_S(k)|^2.
-\end{equation}
-
-The interpretation of information entropy signatures in terms of information entropy wave functions opens several avenues of investigation of possible connections between exotic states of matter and quantum information theory.
-Here we explore its most forthright corollary, which is the establishment of uncertainty relations for topological phase transitions.
-
-Let us denote the mean, the variance and the entropy associated with the probability distribution $\rho_S$ by $\mu_{\rho_S}$, $\sigma_{\rho_S}^2 $ and $H_{\rho_S}$ respectively. Explicitly, we have 
-\begin{subequations}
-\label{statistics}
-\begin{equation}
-\label{mean}
-\mu_{\rho_S} = \int_{\ell}x\rho_S(x)dx,
-\end{equation}
-\begin{equation}
-\label{variance}
-\sigma_{\rho_S}^2 = \int_{\ell}(x-\mu_{\rho_S})^2\rho_S(x)dx,\quad \text{and}
-\end{equation}
-\begin{equation}
-\label{entropy}
-H_{\rho_S} = \int_{\ell}\rho_S(x)\ln\big(\rho_S(x)\big) dx,
-\end{equation}
-\end{subequations}
-with analogous equations for the wavevector space counterparts $\mu_{\hat{\rho}_S}$, $\sigma_{\hat{\rho}_S}^2 $ and $H_{\hat{\rho}_S}$ in terms of $\hat{\rho}(k)$.
-
-In possession of this quantum formalism, we may write topological versions of two canonical uncertainty relations that bind together the real space and wavevector space information entropy density functions \eqref{shannon_wave_function} and \eqref{shannon_wave_function_wavevector_space}:
-
-\begin{enumerate}
-\item[i)] \emph{the Heisenberg uncertainty principle}
-\begin{equation}
-\label{heisenberg}
-\sigma_{\rho_S} \cdot \sigma_{\hat{\rho}_S} \geq \frac{1}{4\pi}, \quad \text{and }
-\end{equation}
-\item[ii)] \emph{the Hirschman entropic uncertainty}
-\begin{equation}
-\label{hirschman}
-H_{\rho_S} + H_{\hat{\rho}_S} \geq \ln\Big(\frac{e}{2}\Big). 
-\end{equation}
-\end{enumerate}
-
-The information entropy density function $\rho_S$ devised in this section furnishes a physics-grounded interpretation of the information entropy signatures obtained in section \ref{information_entropy_signatures} from sheer data analysis of finite SSH systems in real space.
-In particular, the uncertainty relations \eqref{heisenberg} and \eqref{hirschman} express concisely the trade-off between the localizability of information in topological phase transitions in real space and wavevector space.
-
-Perhaps the fundamental consequence of interpreting the information entropy density function $\rho_S(x)$ as the probability distribution resulting from an information entropy wave function $\psi_S(x)$ defined on a 1D manifold is that it reconciles the apparently conflicting notions of a local topological signal arising from a global property of the SSH systems.
-Indeed, while $\psi_S(x)$ is defined locally at every point of the 1D manifold, it is a single, global wave function encoding the spatial distribution of topological information of an ensemble of SSH Hamiltonians close to phase transition boundaries in parameter space.
-Therefore, the information entropy wave function $\psi_S(x)$ and its corresponding information entropy density function $\rho_S(x)$ can be pictured as emergent properties of an ensemble of quantum many-body systems near phase transitions.
-
-\section{Discussion}
-\label{discussion}
-
-Given the increasing complexity of systems studied in condensed matter physics and the rising demand for materials with exotic and robust properties to power future technological progress, it is only expected that data-driven approaches to physics will grow in demand.
-Our work represents a step in this direction, as we have devised (section \ref{the_eigenvector_ensembling_algorithm}) and implemented (section \ref{numerical_experiments}) a data-driven approach to the discovery of previously unknown properties of topological materials from real space data.
-
-By starting from eigenvector data generated from the simulation of SSH systems in real space, proposing an approach based on eigenvector ensembling and decision trees and using model explainability to uncover the information entropy signatures presented in this article, and then exploring the numerical and theoretical possibilities offered by the information entropy signatures, our work exemplifies a full cycle of data-driven physics and illustrates how the interactions between machine learning and physics can be enriching to both disciplines.
-
-The development of data-driven methods based on real space lattice data will be particularly relevant to the study of disordered systems in condensed matter.
-Such systems usually break translational symmetry and therefore are not amenable to canonical wavevector space methods.
-Thus, the discovery and engineering of topological features from real space data as demonstrated in this work carries great promise to the theoretical investigation of these systems.
-
-Furthermore, as is generally the case in engineering, the evolution of quantum technologies such as quantum computing and quantum communication  will likely depend on a delicate balance between simplicity and robustness of components such as topological qubits.
-On the simplicity side, engineers try to build their systems with as little redundancy as possible to reduce design complexity, whilst for robustness redundancy is a necessary commodity to ensure error-correction within the system.
-We expect that information theoretic approaches to quantum materials such as the one advanced by this paper shall eventually become a staple of quantum engineering.
-
-As we have seen, the use of real space data enabled us to investigate how topological information is spatially distributed in SSH systems.
-This was demonstrated by the information entropy signatures of section \ref{information_entropy_signatures}, which were recovered from the Shannon entropy of ensembles of eigenvectors in each numerical experiment executed in section \ref{numerical_experiments} and led us to the new topological features of section \ref{topological_feature_engineering} and the emergent information entropy wave functions of section \ref{emergent_information_entropy_wave_functions}.
-The existence of such signals that can be recovered from data from many distinct physical systems but are hard to conceptualize from sheer theoretical reasoning provides a clear example of how machine learning and model explainability can be important tools in the investigation of quantum materials.
-
-The accuracy scores obtained in the numerical experiments performed in this paper were comparable to those reported in \cite{PhysRevLett.120.066401}, where dense and convolutional neural networks were trained on wavevector space data to predict the winding numbers of SSH Hamiltonians via supervised learning.
-This high accuracy level serves as a strong evidence that the entropy signatures presented here indeed express where topological information is most readily available in the SSH lattices investigated.
-
-This paper should also be contrasted with \cite{zhang2020interpreting}, where the subject of investigation is the interpretability of neural network models trained to recognize topological phase transitions in some condensed matter systems.
-In \cite{zhang2020interpreting}, interesting visualizations are shown demonstrating that the patterns captured by a single-layer feedforward neural network indeed map directly to known physical quantities that are relevant to the problems at hand.
-We agree that such tasks should be called \emph{model interpretability}, as in that case the authors introspect into their models to make sure that they are learning patterns of physical pertinence to the systems being investigated.
-In our paper we preferred the term \emph{model explainability}, as we used similar model introspection tools to propose previously unknown concepts and properties of the physical systems being investigated.
-While the nuances in the semantics of these two terms are the subject of often heated philosophical debates in the artificial intelligence community, this choice of nomenclature suits the practical application of these model introspection techniques to physics well.
-
-Recent works have demonstrated the existence of local topological markers in real space that carry important information on the topological state of a system \cite{PhysRevB.84.241106,caio2019topological}.
-Given the new DCT and DST topological features introduced in section \ref{topological_feature_engineering} which were shown to carry relevant topological information and the theoretical interpretation of the topological signals in terms of information entropy wave functions given in section \ref{emergent_information_entropy_wave_functions}, the results presented here suggest a new road for the theoretical exploration of local topological markers in terms of information theory as well.
-Whether there is any relationship between the local topological markers of \cite{PhysRevB.84.241106,caio2019topological} and the information entropy wave functions discussed here is left for speculation.
-
-The eigenvector ensembling algorithm employed in this work is likely to have further applications in data-driven physics.
-This is because most of physics is based on eigenvector decomposition, and statistical physics itself can be seen as an application of similar ensembling principles.
-
-As a concrete example, the study of several many-body systems of current interest in condensed matter physics is hindered by their large dimensionality.
-This problem, known as \emph{the curse of dimensionality} in the scientific computing community, arises from the necessity of collecting or processing exponentially larger amounts of data as the feature space dimensionality of a problem grows.
-An approach based on eigenvector ensembling can be of use in such situations both as a dimensionality reduction tool and as a sampling strategy.
-The first case was illustrated in this work, where it was shown that relevant topological information of SSH systems can be retrieved from few sites in a lattice, which can be exploited as a dimensionality reduction strategy.
-The latter case, which was not explored here, also poses interesting possibilities, such as sampling eigenstates according to a desired distribution in Monte Carlo simulations of condensed matter systems.
-Indeed, sampling eigenvectors from a carefully designed probability distribution can ultimately lead to a great reduction in dimensionality  while still capturing all the relevant physics of a system.
-We therefore expect that a much broader class of data-driven physics problems could benefit from the techniques described in this paper.
-
-Another interesting prospect is the combination of eigenvector ensembling with unsupervised learning algorithms.
-In the paper, our preference for decision trees and random forests was based on their powerful and accessible model explainability aptitudes.
-This choice was made in conformity with our main purpose, which was to exploit model explainability tools to investigate how topological information is distributed along a spatial lattice in SSH systems.
-Nevertheless, the eigenvector ensembling procedure we described here is flexible and can easily be repurposed for other supervised or unsupervised learning tasks.
-
-One final comment should be made about the flourishing relationship between physics and machine learning.
-In this work we have demonstrated how a machine learning approach can provide new insights into complex physical phenomena of current interest.
-The other direction of this relationship (physics enhancing understanding in machine learning) is equally important.
-As the need for ever more powerful machine learning algorithms continues to grow, the development of mathematical frameworks for understanding general data spaces (i.e., a physics of data) will be of crucial relevance.
-This pursuit is seen in many theoretical works investigating the intriguing connections between geometry, topology and data \cite{carlsson2009topology}$^-$\cite{belkin2003problems}.
-The detailed study of data generated by physical models with non-trivial geometrical and topological properties such as the SSH model may provide invaluable insights into the structure and shape of real world high-dimensional data, since these models usually underscore well known mathematical frameworks behind the data generating process, a feature that is often absent from machine learning applications.
-Thus, far from being restricted to applications in physics, the study of the topological and geometrical properties of data sets generated by physical models will also be of great value to the machine learning and artificial intelligence communities.
-
-\begin{figure}
-\centering
-\subfigure[]{\label{feature_importances_ssh1}\includegraphics[width=0.49\textwidth]{\SSHOneEntropySignature}}\quad
-\subfigure[]{\label{feature_importances_ssh2}\includegraphics[width=0.49\textwidth]{\SSHTwoEntropySignature}}\quad
-\caption{Information entropy signatures of the topological phase transitions from the numerical experiments of section \ref{numerical_experiments}.
-(a) In experiment 1 (section \ref{experiment_1}), the two sharp peaks in the Shannon entropy signal account for approximately 70\% of reduction in information entropy.
-(b) In experiment 2 (section \ref{experiment_2}), the three visible peaks account for approximately 30\% of reduction in information entropy.}
-\label{feature_importances}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% bibtext %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{./article_bib/article_bib}{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Full bibliography (if bibtex is not used) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-We thank S.
-E.
-Rowley, J.
-F.
-de Oliveira, T.
-Micklitz and M.
-A.
-Continentino for insightful discussions and S.
-E.
-Rowley for carefully reading the manuscript and suggesting improvements.
-N.
-L.
-Holanda acknowledges financial support from CENPES/Petrobr\'as/CBPF.
-M.
-A.
-R.
-Griffith acknowledges financial support from Capes.
-N.
-L.
-Holanda is grateful to the Theory of Condensed Matter and Quantum Materials groups at the Cavendish Laboratory and the Quantum Information Group at CBPF.
-
-\section*{Author contributions}
-
-Both authors of this work contributed equally to its realization at all stages.
-
-\section*{Competing financial interests}
-
-The authors declare no competing financial or non-financial interests.
-
-\section*{Additional information}
-
-Correspondence and requests for materials should be addressed to N. L. Holanda. 
-%The source code used to run simulations is available on \href{https://github.com/linneuholanda/ml_topological_phases_in_real_space}{Github}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplementary %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\pagebreak
-
+\begin{document}
 \begin{figure}
@@
 
-\section*{Supplementary Material}
+\section*{Supplemental Material}
 \subsection*{The SSH model}
@@
 
-The insights behind our intuition that topological phases can be learned from local features are as follows.
+We now discuss the principles that lead us to the intuition that learning topological phases from local real space data should be possible.
+
 First, while the topological invariants that characterize distinct topological phases are usually computed in wavevector space, the topological properties of a Hamiltonian are the same regardless of the basis in Hilbert space used to represent it.
 Thus, information on the topological phase of a Hamiltonian should still be available when it is represented in real lattice space.
+
 Second, even though the topological properties of a Hamiltonian are global, meaning that in general they cannot be said to be localized at a particular lattice site, in parameter space topology is indeed a local property: knowing the vector $\mathbf{t}$ associated with a Hamiltonian completely determines its topological phase.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% bibtext %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{./supp_bib}{}
+
 \end{document}

### 2020-08-21 12_proofs/corrections/proofs_review.tex
Reviewing proofs

\documentclass[10pt]{revtex4-1}
\usepackage{xcolor} 
\usepackage{hyperref}
\newcounter{quoter}
\setcounter{quoter}{0}
\renewcommand*{\thequoter}{%
  %\textbf{%
  %  \ifnum\value{custom}<1000 0\fi
  %  \ifnum\value{custom}<100 0\fi
  %  \ifnum\value{custom}<10 0\fi
  %  \arabic{custom}%
  \textbf{[\arabic{quoter}]}
  }%
\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
\newcommand{\citequote}[1]{\ref{#1}}
\begin{document}

\section*{Specific Questions and Comments to Address for This Paper}

Dear editor,

below are the revisions for each topic raised, as well as a few typos that we found in the text.

\begin{enumerate} %[\begingroup\color{blue} 1)\endgroup]
%\textcolor{blue}{
    \item OK.
    \item OK.
    \item OK.
    \item Line 838 should be replaced with "connections between geometry, topology, and data [54-64].", to explicitly cite those references. 
    \item OK. 
    \item The full reference details of reference [53] are provided below.
    \begin{itemize}
    \item title: Topological marker currents in Chern insulators
    \item author: Caio, Marcello Davide and M{\"o}ller, Gunnar and Cooper, Nigel R and Bhaseen, MJ
    \item journal: Nature Physics
    \item volume: 15
    \item number: 3
    \item pages: 257--261
    \item year: 2019
    \item publisher: Nature Publishing Group.
    \end{itemize}
    \item The full reference details of reference [59] are provided below. 
    \begin{itemize}
    \item title: A short course on topological insulators
    \item author: Asb{\'o}th, J{\'a}nos K and Oroszl{\'a}ny, L{\'a}szl{\'o} and P{\'a}lyi, Andr{\'a}s
    \item journal: Lecture notes in physics
    \item volume: 919
    \item pages: 997--1000
    \item year: 2016
    \item publisher: Springer
    \end{itemize}
    \item[FQ.] Replace Capes with CAPES (BR).
    \item[Q.] The full details of reference [46] are provided below.
    \begin{itemize}
    \item title: Scikit-learn: Machine learning in Python
    \item author: Pedregosa, Fabian and Varoquaux, Ga{\"e}l and Gramfort, Alexandre and Michel, Vincent and Thirion, Bertrand and Grisel, Olivier and Blondel, Mathieu and Prettenhofer, Peter and Weiss, Ron and Dubourg, Vincent and others
    \item journal: the Journal of machine Learning research
    \item volume: 12
    \item pages: 2825--2830
    \item year: 2011
    \item publisher: JMLR. org
    \end{itemize}
    \item[Q.] The full details of reference [62] are provided below.
    \begin{itemize}
    \item title: Algorithms for manifold learning
    \item author: Cayton, Lawrence
    \item journal: Univ. of California at San Diego Tech. Rep
    \item volume: 12
    \item number: 1-17
    \item pages: 1
    \item year: 2005
    \end{itemize}
    \item In line 6, apparently a comma is missing: "and Centro Brasileiro de Pesquisas F\'isicas Rua Dr. Xavier Sigaud..." should become "and Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud..." 
    \item Equation (19c) is missing a minus sign before the integration symbol.  
    \item The numbering of references in the Supplemental Material was incorrect. Also, the header of the Supplemental Material originally read "Supplementary Material" instead of "Supplemental Material", as used throughout the main paper. We are sending a new pdf of the Supplemental Material that fixes theses issues. 
    \item The ORCID links for both authors are: N. L. Holanda (\url{https://orcid.org/0000-0002-8484-4635}), M. A. R. Griffith (\url{https://orcid.org/0000-0003-4090-1156})

\end{enumerate}

Best regards,
N. L. Holanda.

\end{document}
